### 2018-06-29 ms.tex
Switch primary ms to tex so that switching into plos template is easy.

Which journal? Comp bio was original plan? go for that.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Use Madagascar + Indonesia as case studies.
\item
  do cross validation on both pr and polygon. no good way to combine so
  just have to report both in every case
\item
  can't see good way to compare stacked generalisation with linear
  polygon so have to do all linear.
\item
  if this paper falls out easily can expand to ml and polygon as
  covariates. or project for ra?
\item
  probably want random cv and spatial cv?
\item
  might need more countries but do first draft like this.
\item
  spatial only. but need to choose year/year range. year is difficult as
  pr and polygons don't match.
\item
  compare Pearson and spearman. maybe Mae as well.
\item
  how to handle spatial priors? try 3 values and pick best CV in each
  case.
\item
  gives country X model X CV X metric X prevalence vs incidence.
\end{enumerate}

figure 1. data and cross validation. columns county. rows: data values,
CV group 1, CV group 2.

figure 2. predicted prevalence and incidence maps. but how with CV? all
data X model?

figure 3. accuracy summary. Dodge by model. facet by prevelance
incidence and county. symbol metric. colour by cv type. points for
individual CV, line for mean? but how to distinguish CV type line?

figure 4 predicted Vs observed. facet by country and prev inc. colour by
cv?

\subsection{intro}\label{intro}

malaria is bad but decreasing moving to strategy of elimination country
by country elimination requires maps of low prevalence areas but maps in
low prevalence areas are difficult sometimes little data traditional
prevalence mapping won't work we need new sources of data.

however surveillance data is sometimes high quality in these areas pixel
level maps from aggregates data is difficult (sturrock, inla, Leon,
others) not much information for covariates sturrock used two.
undeveloped area of statistics but see Leon.

Ideal situation is to combine data benefits of both but data are on
different scales Ewan says there's a relationship.

here we compared 3 models, point only, polygon only and joint models we
use Madagascar and Indonesia as case studies as they have good
surveillance data and good pr data. we find that\ldots{}

\subsection{methods}\label{methods}

malaria data prevalence data prevalence standardisation incidence data
geography counts to incidence rate

covariate data

full model full hierarchical equations linear predictor link to
prevalence prevalence to incidence multilevel

\subsubsection{Malaria data}\label{malaria-data}

We used two data sources that reflect malaria burden; point prevalence
surveys and polygon-level, aggregated incidence data. We selected
Madagascar and Indonesia as case examples as they have both good
surveillance data and good country wide surveys from approximately the
same time. Given the available data we chose to focus our analysis on
2012-2015 for Indonesia and 2013-2014 for Madagascar.

\subsubsection{Prevalence survey data}\label{prevalence-survey-data}

The prevalence survey data were extracted from the MAP prevalence survey
database {[}@{]}. As the prevalence surveys cover different are ranges
they were standardisePars using the model from {[}@{]}.

\subsubsection{Polygon incidence data}\label{polygon-incidence-data}

\subsubsection{Population data}\label{population-data}

\subsubsection{Covariate data}\label{covariate-data}

\subsubsection{The model}\label{the-model}

We compared three models 1) a full model with prevalence surveys and
aggregated incidence data 2) the submodel with only prevalence data and
3) the submodel with only aggregated incidence data.

The full, joint likelihood model is described as follows. Values at the
aggregate, polygon level are given the subscript \(a\) while pixel or
point level below are indexed with \(b\). The polygon case count data,
\(y_j\) is given a Poisson likelihood

\[y_a \sim \operatorname{Pois}(i_a\mathrm{pop_a})\]

where \(i_a\) is the estimated polygon incidence rate and
\(\mathrm{pop_a}\) is the observed polygon population-at-risk.

The point-level prevalence data, \(z_b\), is given a binomial likelihood

\[z_b \sim \operatorname{Binom}(p_b, n_b) \]

where \(p_b\) is the estimated prevalence and \(n_b\) is the observed
survey sample size.

The two quantities are linked to each other and to the predictor
variables by the following system of equations.

\[i_a = \frac{ \sum(i_b \mathrm{pop}_b)}{\sum  \mathrm{pop}_b} \]

\[i_b = \mathrm{p2i}(p_b)\]

where \(\mathrm{p2i}\) is a from a model that was published previously.
{[}@cameron2015defining{]} After fitting, this model defines a function
\[\mathrm{p2i}: f\left(P\right) = 2.616P - 3.596P^2 + 1.594P^3\].

The linear predictor of the model, \(\eta_b\), is related to prevalence
by a typical logit link function.

\[p_b = \operatorname{logit}^{-1}(\eta_b)\]

The linear predictor is composed of an intercept, covariates and a
spatial, Gaussian random field.

\[\eta_b = \beta_0 + \beta X  + u(s, \tau, \kappa)\]

The spatial effect \(u(s, \tau, \kappa)\) has a Mat'ern covariance
function and two hyper parameters. blah.

Finally, we complete the model by setting priors on the parameters
\(\beta_0, \beta, \tau\) and \(\kappa\).

We set

\[\log(\tau)\sim \operatorname{ Norm}(2, 6)\]

which corresponds to a mean nominal range \(r = \frac{\tau}{\sqrt{2}}\)
of one fifth of the range of the study area.

We set \[\log(\kappa)\sim \operatorname{ Norm}(2, 6)\]

for some reason. Finally, we set regularising priors on the regression
coefficients

\[\beta_i \sim \operatorname{ Norm}(0, \sigma)\]

where we try the values for \(\sigma\), 0.2, 1 and 2.

Given this setup, we get predictions of prevalence and incidence
simultaneously whether we used both data types or just one.

\subsubsection{experiments}\label{experiments}

To compare the three models we used two cross validation schemes. In the
first, the combined data set of prevalence and incidence data was split
into five cross-validation folds stratified by data type. This reflects
real world data where we sometimes have incidence data but no prevalence
data and visa versa. In the second validation scheme the incidence data
was split into five spatial cross-validation folds (see
Figure\textasciitilde{}\ref{fig:data}b). Then, any prevalence data
within the hold out incidence polygons was also withheld. This scheme is
testing the models' ability to predict into new areas with no
information from the spatial random field.

In both cases we examined performance metrics for both the withheld
prevalence data and the withheld incidence data. As there is no good way
of combining predictive error from both types of data into one
performance metric, we considered performance separately throughout. Our
main performance metric was Pearson's correlation. However, we also
considered Spearman's correlation. If the prevalence-incidence
relationship is poorly estimated, this will strongly affect the
Pearson's correlation while the Spearman's correlation will be
relatively robust to this source of poor model performance.

\subsection{results}\label{results}

\subsection{discussion}\label{discussion}

what did and didn't work application to global maps further ml work
potential way to refine prevalence incidence relationship.

### 2018-06-29 ms.tex
Copy in plos styling.

@@
-Which journal? Comp bio was original plan? go for that.
+% Template for PLoS
+% Version 3.5 March 2018
+%
+% % % % % % % % % % % % % % % % % % % % % %
+%
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended 
+% to minimize problems and delays during our production 
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Once your paper is accepted for publication, 
+% PLEASE REMOVE ALL TRACKED CHANGES in this file 
+% and leave only the final text of your manuscript. 
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that 
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file. 
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
+%
+% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column. 
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Use Madagascar + Indonesia as case studies.
-\item
-  do cross validation on both pr and polygon. no good way to combine so
-  just have to report both in every case
-\item
-  can't see good way to compare stacked generalisation with linear
-  polygon so have to do all linear.
-\item
-  if this paper falls out easily can expand to ml and polygon as
-  covariates. or project for ra?
-\item
-  probably want random cv and spatial cv?
-\item
-  might need more countries but do first draft like this.
-\item
-  spatial only. but need to choose year/year range. year is difficult as
-  pr and polygons don't match.
-\item
-  compare Pearson and spearman. maybe Mae as well.
-\item
-  how to handle spatial priors? try 3 values and pick best CV in each
-  case.
-\item
-  gives country X model X CV X metric X prevalence vs incidence.
-\end{enumerate}
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
 
-figure 1. data and cross validation. columns county. rows: data values,
-CV group 1, CV group 2.
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
 
-figure 2. predicted prevalence and incidence maps. but how with CV? all
-data X model?
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
 
-figure 3. accuracy summary. Dodge by model. facet by prevelance
-incidence and county. symbol metric. colour by cv type. points for
-individual CV, line for mean? but how to distinguish CV type line?
+% Use Unicode characters when possible
+\usepackage[utf8x]{inputenc}
 
-figure 4 predicted Vs observed. facet by country and prev inc. colour by
-cv?
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
 
-\subsection{intro}\label{intro}
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
 
-malaria is bad but decreasing moving to strategy of elimination country
-by country elimination requires maps of low prevalence areas but maps in
-low prevalence areas are difficult sometimes little data traditional
-prevalence mapping won't work we need new sources of data.
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
 
-however surveillance data is sometimes high quality in these areas pixel
-level maps from aggregates data is difficult (sturrock, inla, Leon,
-others) not much information for covariates sturrock used two.
-undeveloped area of statistics but see Leon.
+% line numbers
+\usepackage[right]{lineno}
 
-Ideal situation is to combine data benefits of both but data are on
-different scales Ewan says there's a relationship.
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
 
-here we compared 3 models, point only, polygon only and joint models we
-use Madagascar and Indonesia as case studies as they have good
-surveillance data and good pr data. we find that\ldots{}
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
 
-\subsection{methods}\label{methods}
+% array package and thick rules for tables
+\usepackage{array}
 
-malaria data prevalence data prevalence standardisation incidence data
-geography counts to incidence rate
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
 
-covariate data
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
 
-full model full hierarchical equations linear predictor link to
-prevalence prevalence to incidence multilevel
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
 
-\subsubsection{Malaria data}\label{malaria-data}
+% Remove comment for double spacing
+%\usepackage{setspace} 
+%\doublespacing
 
-We used two data sources that reflect malaria burden; point prevalence
-surveys and polygon-level, aggregated incidence data. We selected
-Madagascar and Indonesia as case examples as they have both good
-surveillance data and good country wide surveys from approximately the
-same time. Given the available data we chose to focus our analysis on
-2012-2015 for Indonesia and 2013-2014 for Madagascar.
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
 
-\subsubsection{Prevalence survey data}\label{prevalence-survey-data}
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
 
-The prevalence survey data were extracted from the MAP prevalence survey
-database {[}@{]}. As the prevalence surveys cover different are ranges
-they were standardisePars using the model from {[}@{]}.
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
 
-\subsubsection{Polygon incidence data}\label{polygon-incidence-data}
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
 
-\subsubsection{Population data}\label{population-data}
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+%\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+%\setlength{\headheight}{27.023pt}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\today}
 
-\subsubsection{Covariate data}\label{covariate-data}
+%% Include all macros below
 
-\subsubsection{The model}\label{the-model}
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
 
-We compared three models 1) a full model with prevalence surveys and
-aggregated incidence data 2) the submodel with only prevalence data and
-3) the submodel with only aggregated incidence data.
+%% END MACROS SECTION
 
-The full, joint likelihood model is described as follows. Values at the
-aggregate, polygon level are given the subscript \(a\) while pixel or
-point level below are indexed with \(b\). The polygon case count data,
-\(y_j\) is given a Poisson likelihood
+\begin{document}
+\vspace*{0.2in}
 
-\[y_a \sim \operatorname{Pois}(i_a\mathrm{pop_a})\]
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{A comparison of models for polygon data, point data or both for malaria mapping} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Tim C.D. Lucas\textsuperscript{1},
+et al\textsuperscript{1},
+\\
+\bigskip
+\textbf{1} BDI, Oxford
+\\
+\bigskip
 
-where \(i_a\) is the estimated polygon incidence rate and
-\(\mathrm{pop_a}\) is the observed polygon population-at-risk.
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
+% 
+% Remove or comment out the author notes below if they aren't used.
+%
 
-The point-level prevalence data, \(z_b\), is given a binomial likelihood
+% Current address notes
 
-\[z_b \sim \operatorname{Binom}(p_b, n_b) \]
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* timcdlucas@gmail.com
 
-where \(p_b\) is the estimated prevalence and \(n_b\) is the observed
-survey sample size.
+\end{flushleft}
+% Please keep the abstract below 300 words
+\section*{Abstract}
+malaria is bad but decreasing
+moving to strategy of elimination country by country
+elimination requires maps of low prevalence areas
+but maps in low prevalence areas are difficult
+sometimes little data
+traditional prevalence mapping won't work
+we need new sources of data.
 
-The two quantities are linked to each other and to the predictor
-variables by the following system of equations.
+% Please keep the Author Summary between 150 and 200 words
+% Use first person. PLOS ONE authors please skip this step. 
+% Author Summary not valid for PLOS ONE submissions.   
+\section*{Author summary}
+malaria is bad but decreasing
+moving to strategy of elimination country by country
+elimination requires maps of low prevalence areas
+but maps in low prevalence areas are difficult
+sometimes little data
+traditional prevalence mapping won't work
+we need new sources of data.
 
-\[i_a = \frac{ \sum(i_b \mathrm{pop}_b)}{\sum  \mathrm{pop}_b} \]
+\linenumbers
 
-\[i_b = \mathrm{p2i}(p_b)\]
+% Use "Eq" instead of "Equation" for equation citations.
+\section*{Introduction}
+malaria is bad but decreasing
+moving to strategy of elimination country by country
+elimination requires maps of low prevalence areas
+but maps in low prevalence areas are difficult
+sometimes little data
+traditional prevalence mapping won't work
+we need new sources of data.
 
-where \(\mathrm{p2i}\) is a from a model that was published previously.
-{[}@cameron2015defining{]} After fitting, this model defines a function
-\[\mathrm{p2i}: f\left(P\right) = 2.616P - 3.596P^2 + 1.594P^3\].
+\section*{Materials and methods}
 
-The linear predictor of the model, \(\eta_b\), is related to prevalence
-by a typical logit link function.
+% Results and Discussion can be combined.
+\section*{Results}
 
-\[p_b = \operatorname{logit}^{-1}(\eta_b)\]
+\section*{Discussion}
 
-The linear predictor is composed of an intercept, covariates and a
-spatial, Gaussian random field.
+\section*{Conclusion}
 
-\[\eta_b = \beta_0 + \beta X  + u(s, \tau, \kappa)\]
+\section*{Supporting information}
 
-The spatial effect \(u(s, \tau, \kappa)\) has a Mat'ern covariance
-function and two hyper parameters. blah.
+% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
+\paragraph*{S1 Fig.}
+\label{S1_Fig}
+{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
 
-Finally, we complete the model by setting priors on the parameters
-\(\beta_0, \beta, \tau\) and \(\kappa\).
+\section*{Acknowledgments}
+Thanks everyone.
+\nolinenumbers
 
-We set
+% Either type in your references using
+% \begin{thebibliography}{}
+% \bibitem{}
+% Text
+% \end{thebibliography}
+%
+% or
+%
+% Compile your BiBTeX database using our plos2015.bst
+% style file and paste the contents of your .bbl file
+% here. See http://journals.plos.org/plosone/s/latex for 
+% step-by-step instructions.
+% 
+\begin{thebibliography}{10}
 
-\[\log(\tau)\sim \operatorname{ Norm}(2, 6)\]
+\end{thebibliography}
 
-which corresponds to a mean nominal range \(r = \frac{\tau}{\sqrt{2}}\)
-of one fifth of the range of the study area.
-
-We set \[\log(\kappa)\sim \operatorname{ Norm}(2, 6)\]
-
-for some reason. Finally, we set regularising priors on the regression
-coefficients
-
-\[\beta_i \sim \operatorname{ Norm}(0, \sigma)\]
-
-where we try the values for \(\sigma\), 0.2, 1 and 2.
-
-Given this setup, we get predictions of prevalence and incidence
-simultaneously whether we used both data types or just one.
-
-\subsubsection{experiments}\label{experiments}
-
-To compare the three models we used two cross validation schemes. In the
-first, the combined data set of prevalence and incidence data was split
-into five cross-validation folds stratified by data type. This reflects
-real world data where we sometimes have incidence data but no prevalence
-data and visa versa. In the second validation scheme the incidence data
-was split into five spatial cross-validation folds (see
-Figure\textasciitilde{}\ref{fig:data}b). Then, any prevalence data
-within the hold out incidence polygons was also withheld. This scheme is
-testing the models' ability to predict into new areas with no
-information from the spatial random field.
-
-In both cases we examined performance metrics for both the withheld
-prevalence data and the withheld incidence data. As there is no good way
-of combining predictive error from both types of data into one
-performance metric, we considered performance separately throughout. Our
-main performance metric was Pearson's correlation. However, we also
-considered Spearman's correlation. If the prevalence-incidence
-relationship is poorly estimated, this will strongly affect the
-Pearson's correlation while the Spearman's correlation will be
-relatively robust to this source of poor model performance.
-
-\subsection{results}\label{results}
-
-\subsection{discussion}\label{discussion}
-
-what did and didn't work application to global maps further ml work
-potential way to refine prevalence incidence relationship.
+\end{document}

### 2018-06-29 ms.tex
More first pass through latex with plos style.

@@
 \\
-Tim C.D. Lucas\textsuperscript{1},
+Tim C.D. Lucas*\textsuperscript{1},
 et al\textsuperscript{1},
@@
 % Use "Eq" instead of "Equation" for equation citations.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 malaria is bad but decreasing
@@
 
+however surveillance data is sometimes high quality in these areas
+pixel level maps from aggregates data is difficult (sturrock, inla, Leon, others)
+not much information for covariates 
+sturrock used two.
+undeveloped area of statistics but see Leon.
+
+Ideal situation is to combine data
+benefits of both
+but data are on different scales
+Ewan says there's a relationship.
+
+here we compared 3 models, point only, polygon only and joint models
+we use Madagascar and Indonesia as case studies as they have good surveillance data and good pr data.
+we find that...
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Materials and methods}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection*{Malaria data}
+
+We used two data sources that reflect malaria burden; point prevalence surveys and polygon-level, aggregated incidence data.
+We selected Madagascar and Indonesia as case examples as they have both good surveillance data and good country wide surveys from approximately the same time.
+Given the available data we chose to focus our analysis on 2012-2015 for Indonesia and 2013-2014 for Madagascar.
+
+\subsection*{Prevalence survey data}
+
+The prevalence survey data were extracted from the MAP prevalence survey database [@].
+As the prevalence surveys cover different are ranges they were standardisePars using the model from [@].
+
+\subsection*{Polygon incidence data}
+
+\subsection*{Population data}
+
+\subsection*{Covariate data}
+
+\subsection*{The model}
+
+We compared three models 1) a full model with prevalence surveys and aggregated incidence data 2) the submodel with only prevalence data and 3) the submodel with only aggregated incidence data.
+
+The full, joint likelihood model is described as follows. 
+Values at the aggregate, polygon level are given the subscript $a$ while pixel or point level below are indexed with $b$.
+The polygon case count data, $y_j$ is given a Poisson likelihood
+
+$$y_a \sim \operatorname{Pois}(i_a\mathrm{pop_a})$$
+
+where $i_a$ is the estimated polygon incidence rate and $\mathrm{pop_a}$ is the observed polygon population-at-risk.
+
+The point-level prevalence data, $z_b$, is given a binomial likelihood
+
+$$z_b \sim \operatorname{Binom}(p_b, n_b) $$
+
+where $p_b$ is the estimated prevalence and $n_b$ is the observed survey sample size.
+
+The two quantities are linked to each other and to the predictor variables by the following system of equations.
+
+$$i_a = \frac{ \sum(i_b \mathrm{pop}_b)}{\sum  \mathrm{pop}_b} $$
+
+$$i_b = \mathrm{p2i}(p_b)$$
+
+where $\mathrm{p2i}$ is a from a model that was published previously. [@cameron2015defining]
+After fitting, this model defines a function
+$$\mathrm{p2i}: f\left(P\right) = 2.616P - 3.596P^2 + 1.594P^3$$.
+
+The linear predictor of the model, $\eta_b$, is related to prevalence by a typical logit link function.
+
+$$p_b = \operatorname{logit}^{-1}(\eta_b)$$
+
+The linear predictor is composed of an intercept, covariates and a spatial, Gaussian random field.
+
+$$\eta_b = \beta_0 + \beta X  + u(s, \tau, \kappa)$$
+
+The spatial effect $u(s, \tau, \kappa)$ has a Mat\'ern covariance function and two hyper parameters. blah.
+
+Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \tau$ and $\kappa$.
+
+We set
+
+$$\log(\tau)\sim \operatorname{ Norm}(2, 6)$$
+
+which corresponds to a mean nominal range $r = \frac{\tau}{\sqrt{2}}$ of one fifth of the range of the study area.
+
+We set
+$$\log(\kappa)\sim \operatorname{ Norm}(2, 6)$$
+
+for some reason.
+Finally, we set regularising priors on the regression coefficients
+
+$$\beta_i \sim \operatorname{ Norm}(0, \sigma)$$
+
+where we try the values for $\sigma$, 0.2, 1 and 2.
+
+Given this setup, we get predictions of prevalence and incidence simultaneously whether we used both data types or just one.
+
+\subsection*{Experiments}
+
+To compare the three models we used two cross validation schemes. 
+In the first, the combined data set of prevalence and incidence data was split into five cross-validation folds stratified by data type.
+This reflects real world data where we sometimes have incidence data but no prevalence data and visa versa.
+In the second validation scheme the incidence data was split into five spatial cross-validation folds (see Figure~\ref{fig:data}b).
+Then, any prevalence data within the hold out incidence polygons was also withheld.
+This scheme is testing the models' ability to predict into new areas with no information from the spatial random field.
+
+In both cases we examined performance metrics for both the withheld prevalence data and the withheld incidence data.
+As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
+Our main performance metric was Pearson's correlation.
+However, we also considered Spearman's correlation.
+If the prevalence-incidence relationship is poorly estimated, this will strongly affect the Pearson's correlation while the Spearman's correlation will be relatively robust to this source of poor model performance.
 
 % Results and Discussion can be combined.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+\begin{figure}[!h]
+% to be removed before submission
+\includegraphics{figures/mdg_points_and_polygons.png}
+\caption{{\bf Bold the figure title.}
+Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
+\label{fig1}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Conclusion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2018-06-29 ms.tex
Add some figures  for placeholders.

@@
 The prevalence survey data were extracted from the MAP prevalence survey database [@].
-As the prevalence surveys cover different are ranges they were standardisePars using the model from [@].
+As the prevalence surveys cover different are ranges they were standardised using the model from [@].
 
@@
 % to be removed before submission
-\includegraphics{figures/mdg_points_and_polygons.png}
-\caption{{\bf Bold the figure title.}
+\includegraphics[width = 0.9\textwidth]{figures/mdg_points_and_polygons.png}
+\caption{{\bf Madagascar polygon data and predictions from the combined model.}
+Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
+\label{fig1}
+\end{figure}
+
+\begin{figure}[!h]
+% to be removed before submission
+\includegraphics[width = 0.9\textwidth]{figures/pred_obs_map.png}
+\caption{{\bf Indonesia polygon data and predictions from the combined model.}
 Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}

### 2018-07-31 ms.tex
Working bib.
A load of edits to main manuscript. Authors, priors, spatial cv, and introduction.

--- 2018-06-29 ms.tex
@@
 {\Large
-\textbf\newline{A comparison of models for polygon data, point data or both for malaria mapping} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Joint modelling of aggregated incidence data and point prevalence surveys for malaria mapping} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 \\
-Tim C.D. Lucas*\textsuperscript{1},
-et al\textsuperscript{1},
+Tim C.D.
+Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Dan Weiss\textsuperscript{1},
 \\
@@
 
+Despite major reductions in incidence over the last fifteen years, malaria still causes millions of deaths and loads of DALYs annually \cite{gbd2016}.
+Elimination of malaria, country-by-county has become a central goal in the global malaria strategy \cite{wmr2016}.
+Elimination of malaria requires high resolution maps of malaria risk, in low prevalence areas in order to optimise interventions and minimise costs \cite{pete_elim_paper}.
+
 % Please keep the Author Summary between 150 and 200 words
@@
 
-malaria is bad but decreasing
-moving to strategy of elimination country by country
-elimination requires maps of low prevalence areas
-but maps in low prevalence areas are difficult
-sometimes little data
-traditional prevalence mapping won't work
-we need new sources of data.
+Global malaria incidence has decreased dramatically over the last 20 years \cite{gbd2017}.
+This has been accompanied by a strategic shift towards aiming for elimination in low burden countries \cite{wmr?}.
+Accurate, high-resolution maps of malaria risk are vital in these countries in the elimination and pre-elimination phases \cite{Gething map op-ed?}.
+However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite {Gething op-ed, sturrock}.
+In low burden areas, very large sample sizes are needed before a prevalence survey is informative.
+Furthermore, large, countrywide surveys of prevalence, such as DHS or MIS, are rare in low burden countries due to costs and percieved low utility \cite{dunno}.
+We therefore need new data sources and associated statistical methods.
 
-however surveillance data is sometimes high quality in these areas
-pixel level maps from aggregates data is difficult (sturrock, inla, Leon, others)
-not much information for covariates 
+Routine surveillance data, of disease case counts, is becoming more widely available and of better quality.
+This data is commonly aggregated, reporting disease case counts that occurred within a certain geographic region defined by a polygon.
+This type of data is more sensitive than prevalence surveys in low transmission areas as three entire health system is being used to passively monitor disease risk.
+Routine surveillance is also often timely, with reports being released annually or monthly, while large prevalence surveys are performed on a more decadely time scale.
+However, the unstructured nature of the data collection means that dealing with biases and data gaps is an ongoing research priority \cite{battlets, cibulski}.
+
+%however surveillance data is sometimes high quality in these areas
+%pixel level maps from aggregates data is difficult (sturrock, inla, Leon, others)
+%not much information for covariates 
 sturrock used two.
-undeveloped area of statistics but see Leon.
+%undeveloped area of statistics but see Leon.
 
-Ideal situation is to combine data
+Furthermore, using aggregated data to estimate malaria risk for high resolution maps presents further modelling difficulties \cite{sturrock, inla, Leon, others}.
+The aggregated nature of the data means that each data point does not necessarily contain much information, especially if the case counts are aggregated over a large or heterogenous area.
+For example, \cite{sturrock} use only two covariates do to the lack of information in their data.
+
+A model that could combine point surveys and aggregated surveillance has great potential if it could leverage the strengths of both aggregated surveillance data and point survey data.
+One major barrier to this modelling approved us that these two data sources are on different scales: point surveys are a measurement of prevalence $\[0, 1\]$ while routine surveillance measures incidence $\[0, \infty\]$.
+One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015}.
+
+%Ideal situation is to combine data
 benefits of both
-but data are on different scales
-Ewan says there's a relationship.
+%but data are on different scales
+%Ewan says there's a relationship.
 
-here we compared 3 models, point only, polygon only and joint models
-we use Madagascar and Indonesia as case studies as they have good surveillance data and good pr data.
+Here we formulate a joint model that combines aggregated surveillance data and point prevalence surveys of \emph{Plasmodium falciparum}.
+We compare the joint model to models fitted with only one type of data.
+As case studies we use three countries with good routine surveillance data as well as good coverage of prevalence point surveys.
+
+%here we compared 3 models, point only, polygon only and joint models
+%we use Madagascar and Indonesia as case studies as they have good %surveillance data and good pr data.
 we find that...
@@
 
-The prevalence survey data were extracted from the MAP prevalence survey database [@].
-As the prevalence surveys cover different are ranges they were standardisePars using the model from [@].
+The prevalence survey data were extracted from the MAP prevalence survey database \cite{}.
+As the prevalence surveys cover different are ranges they were standardised using the model from \cite{}.
 
@@
 \subsection*{Covariate data}
+
+We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres that included land surface temperature annual mean and standard deviation, enhanced vegetation index, mosquito temperature suitability index, elevation, tassel cap brightness, tassel cap wetness, accessibility to cities, night lights and proportion of urban land cover.
+Elevation, land surface temperature standard deviation, accessibility to cities and night lights were all log transformed to reduce skewness.
+After preliminary analyses, tassel cap brightness and urban land cover were removed as they were highly correlated with other variables.
+The covariates are standardised to have a mean of zero and a standard deviation of one.
 
@@
 
-where $\mathrm{p2i}$ is a from a model that was published previously. [@cameron2015defining]
+where $\mathrm{p2i}$ is a from a model that was published previously. \cite{cameron2015defining}
 After fitting, this model defines a function
@@
 
-The linear predictor is composed of an intercept, covariates and a spatial, Gaussian random field.
+The form of the link function means we get predictions of prevalence and incidence simultaneously whether we used both data types or just one.
+The linear predictor is composed of an intercept, covariates a spatial, Gaussian random field two iid random effects.
 
-$$\eta_b = \beta_0 + \beta X  + u(s, \tau, \kappa)$$
+$$\eta_b = \beta_0 + \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) + w_i(\sigma_w)$$
 
-The spatial effect $u(s, \tau, \kappa)$ has a Mat\'ern covariance function and two hyper parameters. blah.
+The Gaussian spatial effect $u(s, \tau, \kappa)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range (behind which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
+The first iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  is grouped by polygon, with all pixels and point surveys within polygon $j$ being grouped together.
+This random effect models both missing covariates and extra-Poisson sampling error. 
+The second iid random effect, $w_i \sim \operatorname{Norm}(0, \sigma_w)$, is applied to each point survey.
+This effect models extra-binomial sampling noise.
+As such, this random effect is not included in the predicted uncertainty in the incidence or prevalence layers.
+However, it is included in predictions of out-of-sample point surveys.
 
-Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \tau$ and $\kappa$.
+Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
+We assign $\rho$ and $\sigma_u$ a joint penalised complexity prior \ref{notSimpson} such that $P(\rho < 3) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
+We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected, so we set this prior such that the girls could explain most of the range of the data.
 
-We set
+We assign \rho$ and $\sigma_u$ penalised complexity priors as well such that $P(\sigma_v > 0.05) = 0.00001$ and $P(\sigma_w > 0.05) = 0.00001$. 
+The former is based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for three case counts \ref{cibulskis}.
+We found that an iid effect with a standard deviation of 0.05 would be able to account for the discrepancy.
 
-$$\log(\tau)\sim \operatorname{ Norm}(2, 6)$$
-
-which corresponds to a mean nominal range $r = \frac{\tau}{\sqrt{2}}$ of one fifth of the range of the study area.
-
-We set
-$$\log(\kappa)\sim \operatorname{ Norm}(2, 6)$$
-
-for some reason.
-Finally, we set regularising priors on the regression coefficients
-
-$$\beta_i \sim \operatorname{ Norm}(0, \sigma)$$
-
-where we try the values for $\sigma$, 0.2, 1 and 2.
-
-Given this setup, we get predictions of prevalence and incidence simultaneously whether we used both data types or just one.
+Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{ Norm}(0, 0.04)$. 
+Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of 3, I've covariate would be able to predict prevalences between 0.004 and 0.27. 
+This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularised our model.
 
@@
 This reflects real world data where we sometimes have incidence data but no prevalence data and visa versa.
-In the second validation scheme the incidence data was split into five spatial cross-validation folds (see Figure~\ref{fig:data}b).
-Then, any prevalence data within the hold out incidence polygons was also withheld.
-This scheme is testing the models' ability to predict into new areas with no information from the spatial random field.
+Thus this cross-validation scheme can be seen as asking whether aggregated incidence data provides a viable or preferable alternative to using just prevalence data as in previous modelling efforts \cite{bhatt2016nature}.
+
+%figure 1.cross validation. %%columns country. rows: CV  Indonesia and Senegal only.
+
+\begin{figure}[!h]
+% to be removed before submission
+\centering
+\begin{minipage}{0.45\textwidth} \centering 
+\includegraphics[width = 0.9\textwidth]{figures/idn_cv_random.png} \caption{Indonesia random crossvalidation} 
+\end{minipage}
+
+\begin{minipage}{0.45\textwidth} \centering 
+\includegraphics[width = 0.9\textwidth]{figures/idn_cv_spatial.png} \caption{Indonesia random crossvalidation} 
+\end{minipage}
+
+\caption{{\bf Input incidence and prevalence data and predicted incidence maps.
+} The incidence and prevalence data (left) and (spatially) out-of-sample predictions (right) for Indonesia (top) and Senagal (bottom).}
+\label{fig1}
+\end{figure}
+
+In the second validation scheme the data was split into five spatial cross-validation folds (see Figure~\ref{fig:data}b).
+The data was divided by combining the point locations and the centroids of the polygons and performing k means clustering.
+This scheme is testing the models' ability to predict into new areas with little information from the spatial random field.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
+\section*{Results and Discussion}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%figure 2. data and predicted incidence maps. Indonesia and Senegal only. spatial CV only.
+
+%figure 3 predicted Vs observed. colour by %country facet by prev inc and cv scheme? best model only.
 
@@
 % to be removed before submission
-\includegraphics{figures/mdg_points_and_polygons.png}
-\caption{{\bf Bold the figure title.}
-Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
-\label{fig1}
+\includegraphics[width = 0.9\textwidth]{figures/pred_obs_map.png}
+\caption{{\bf Input incidence and prevalence data and predicted incidence maps.
+} The incidence and prevalence data (left) and (spatially) out-of-sample predictions (right) for Indonesia (top) and Senagal (bottom).}
+\label{predobsmap}
 \end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{
+{\bf Summary of out-of-sample accuracy.}}
+\begin{tabular}{l|l|l|l|l}
+\hline
+{\bf Holdout data} & {\bf Metric} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
+\thickhline \\
+\multirow{6}{Incidence} & \multirow{3}{Pearson} & Indonesia & 0.1 &. 0.2 & {\bf 0.3}\\
+                   & Madagascar & 0.1 &. 0.2 & {\bf 0.3}\\
+                   & Senagal & 0.1 &. 0.2 & {\bf 0.3}\\
+                                          & \multirow{3}{Spearman} & Indonesia & 0.1 &. 0.2 & {\bf 0.3}\\
+                   & Madagascar & 0.1 &. 0.2 & {\bf 0.3}\\
+                   & Senagal & 0.1 &. 0.2 & {\bf 0.3}\\
+\multirow{6}{Prevalence} & \multirow{3}{Pearson} & Indonesia & 0.1 &. 0.2 & {\bf 0.3}\\
+                   & Madagascar & 0.1 &. 0.2 & {\bf 0.3}\\
+                   & Senagal & 0.1 &. 0.2 & {\bf 0.3}\\
+                                         & \multirow{3}{Spearman} & Indonesia & 0.1 &. 0.2 & {\bf 0.3}\\
+                   & Madagascar & 0.1 &. 0.2 & {\bf 0.3}\\
+                   & Senagal & 0.1 &. 0.2 & {\bf 0.3}\\
+\end{tabular}
+\begin{flushleft}
+Correlation (Spearman's and Pearson's) of predicted incidence rate and prevalence against out-of-sample observed data for three countries.
+\end{flushleft}
+\label{table1}
+\end{adjustwidth}
+\end{table}
+
+\begin{figure}[!h]
+% to be removed before submission
+\includegraphics[width = 0.9\textwidth]{figures/joint_idn_cv_log_results}
+\caption{{\bf Observed-predicted plots for cross-validated data.}
+Error bars include uncertainty of the fitted parameters and from sampling error.
+100 realisations of the predictions were calculated taking a draw of all parameters from the posterior and the iid random effect $v_j$ and then sampling from the assumed sampling models (binomial and Poisson) each time.
+The 90\% quantiles were them taken and plotted as error bars.
+}
+\label{predobsscatter}
+\end{figure}
 
@@
 % 
-\begin{thebibliography}{10}
+\bibliography{Malaria}
 
-\end{thebibliography}
+%\begin{thebibliography}{10}
+
+%\end{thebibliography}
 

### 2018-07-31 ms.tex
Fix up ms errors.

@@
 \usepackage{array}
+
+% multirow for multiple row tables. 
+\usepackage{multirow}
 
@@
 A model that could combine point surveys and aggregated surveillance has great potential if it could leverage the strengths of both aggregated surveillance data and point survey data.
-One major barrier to this modelling approved us that these two data sources are on different scales: point surveys are a measurement of prevalence $\[0, 1\]$ while routine surveillance measures incidence $\[0, \infty\]$.
+One major barrier to this modelling approved us that these two data sources are on different scales: point surveys are a measurement of prevalence $\lbrack 0, 1\rbrack$ while routine surveillance measures incidence $\lbrack 0, \infty\rbrack$.
 One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015}.
@@
 
-We assign \rho$ and $\sigma_u$ penalised complexity priors as well such that $P(\sigma_v > 0.05) = 0.00001$ and $P(\sigma_w > 0.05) = 0.00001$. 
+We assign $\rho$ and $\sigma_u$ penalised complexity priors as well such that $P(\sigma_v > 0.05) = 0.00001$ and $P(\sigma_w > 0.05) = 0.00001$. 
 The former is based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for three case counts \ref{cibulskis}.
@@
 {\bf Summary of out-of-sample accuracy.}}
-\begin{tabular}{l|l|l|l|l}
+\begin{tabular}{llllll}
 \hline
 {\bf Holdout data} & {\bf Metric} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
-\thickhline \\
-\multirow{6}{Incidence} & \multirow{3}{Pearson} & Indonesia & 0.1 &. 0.2 & {\bf 0.3}\\
-                   & Madagascar & 0.1 &. 0.2 & {\bf 0.3}\\
-                   & Senagal & 0.1 &. 0.2 & {\bf 0.3}\\
-                                          & \multirow{3}{Spearman} & Indonesia & 0.1 &. 0.2 & {\bf 0.3}\\
-                   & Madagascar & 0.1 &. 0.2 & {\bf 0.3}\\
-                   & Senagal & 0.1 &. 0.2 & {\bf 0.3}\\
-\multirow{6}{Prevalence} & \multirow{3}{Pearson} & Indonesia & 0.1 &. 0.2 & {\bf 0.3}\\
-                   & Madagascar & 0.1 &. 0.2 & {\bf 0.3}\\
-                   & Senagal & 0.1 &. 0.2 & {\bf 0.3}\\
-                                         & \multirow{3}{Spearman} & Indonesia & 0.1 &. 0.2 & {\bf 0.3}\\
-                   & Madagascar & 0.1 &. 0.2 & {\bf 0.3}\\
-                   & Senagal & 0.1 &. 0.2 & {\bf 0.3}\\
+\thickhline 
+Incidence & Pearson & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{1mm}\\ 
+          & Spearman & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{3mm} \\ 
+Prevalence & Pearson & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{1mm}\\ 
+            & Spearman & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\\
 \end{tabular}

### 2018-08-02 ms.tex
Add place holder for spatial cv table.

@@
 
-where $\mathrm{p2i}$ is a from a model that was published previously. \cite{cameron2015defining}
+where $\mathrm{p2i}$ is from a model that was published previously. \cite{cameron2015defining}
 After fitting, this model defines a function
@@
 
-The Gaussian spatial effect $u(s, \tau, \kappa)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range (behind which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
-The first iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  is grouped by polygon, with all pixels and point surveys within polygon $j$ being grouped together.
-This random effect models both missing covariates and extra-Poisson sampling error. 
-The second iid random effect, $w_i \sim \operatorname{Norm}(0, \sigma_w)$, is applied to each point survey.
-This effect models extra-binomial sampling noise.
+The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
+The first iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all pixels and point surveys within polygon $j$ being grouped together.
+This random effect modelled both missing covariates and extra-Poisson sampling error. 
+The second iid random effect, $w_i \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
+This effect modelled extra-binomial sampling noise.
 As such, this random effect is not included in the predicted uncertainty in the incidence or prevalence layers.
@@
 Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
-We assign $\rho$ and $\sigma_u$ a joint penalised complexity prior \ref{notSimpson} such that $P(\rho < 3) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
-We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected, so we set this prior such that the girls could explain most of the range of the data.
+We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \ref{notSimpson} such that $P(\rho < 3) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
+We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected, so we set this prior such that the randome field could explain most of the range of the data.
 
-We assign $\rho$ and $\sigma_u$ penalised complexity priors as well such that $P(\sigma_v > 0.05) = 0.00001$ and $P(\sigma_w > 0.05) = 0.00001$. 
-The former is based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for three case counts \ref{cibulskis}.
-We found that an iid effect with a standard deviation of 0.05 would be able to account for the discrepancy.
+We assigned $\sigma_v$ a penalised complexity prior such that $P(\sigma_v > 0.05) = 0.0000001$
+This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for three case counts \ref{cibulskis}.
+We found that an iid effect with a standard deviation of 0.05 would be able to account for the discrepancy between the assumed Poisson error and the independently derived error.
+We assigned $\sigma_w$ a penalised complexity prior such that $P(\sigma_w > 0.3) = 0.0000001$. 
+This was chosen by finding the maximum difference in prevalence between survey points (with a sample size greater than 500) within the same raster pixel.
+The differences between points within the same pixel can only be accounted for by the binomial error and this iid effect.
+Given that the error on a prevalence estimate with sample size greater than 500 is quite small, the iid effect needs to be able to explain this difference.
 
@@
 \begin{minipage}{0.45\textwidth} \centering 
-\includegraphics[width = 0.9\textwidth]{figures/idn_cv_random.png} \caption{Indonesia random crossvalidation} 
+\includegraphics[width = 0.9\textwidth]{figures/idn_cv_random.png} %\caption{Indonesia random crossvalidation} 
 \end{minipage}
-
 \begin{minipage}{0.45\textwidth} \centering 
-\includegraphics[width = 0.9\textwidth]{figures/idn_cv_spatial.png} \caption{Indonesia random crossvalidation} 
+\includegraphics[width = 0.9\textwidth]{figures/idn_cv_spatial.png} %\caption{Indonesia spatial crossvalidation} 
 \end{minipage}
@@
 \caption{
-{\bf Summary of out-of-sample accuracy.}}
+{\bf Summary of out-of-sample accuracy for random crossvalidation experiment.}}
 \begin{tabular}{llllll}
@@
 Correlation (Spearman's and Pearson's) of predicted incidence rate and prevalence against out-of-sample observed data for three countries.
+The data were split randomly into 10 groups stratified by data type (incidence polygon and prevalence points).
+\end{flushleft}
+\label{table1}
+\end{adjustwidth}
+\end{table}
+
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{
+{\bf Summary of out-of-sample accuracy for spatial crossvalidation experiment.}}
+\begin{tabular}{llllll}
+\hline
+{\bf Holdout data} & {\bf Metric} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
+\thickhline 
+Incidence & Pearson & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{1mm}\\ 
+          & Spearman & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{3mm} \\ 
+Prevalence & Pearson & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{1mm}\\ 
+            & Spearman & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
+                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\\
+\end{tabular}
+\begin{flushleft}
+Correlation (Spearman's and Pearson's) of predicted incidence rate and prevalence against out-of-sample observed data for three countries.
+The data were split spatiall into 5 groups.
 \end{flushleft}

### 2018-08-02 ms.tex
Fill in citation placeholders. Still pretty poorly referenced.

@@
 
-Despite major reductions in incidence over the last fifteen years, malaria still causes millions of deaths and loads of DALYs annually \cite{gbd2016}.
-Elimination of malaria, country-by-county has become a central goal in the global malaria strategy \cite{wmr2016}.
-Elimination of malaria requires high resolution maps of malaria risk, in low prevalence areas in order to optimise interventions and minimise costs \cite{pete_elim_paper}.
+Despite major reductions in incidence over the last fifteen years, malaria still causes millions of deaths and loads of DALYs annually \cite{abajobir2017global}.
+Elimination of malaria, country-by-county has become a central goal in the global malaria strategy \cite{world2016world}.
+Elimination of malaria requires high resolution maps of malaria risk, in low prevalence areas in order to optimise interventions and minimise costs \cite{sturrock2016mapping}.
 
@@
 
-Global malaria incidence has decreased dramatically over the last 20 years \cite{gbd2017}.
-This has been accompanied by a strategic shift towards aiming for elimination in low burden countries \cite{wmr?}.
-Accurate, high-resolution maps of malaria risk are vital in these countries in the elimination and pre-elimination phases \cite{Gething map op-ed?}.
-However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite {Gething op-ed, sturrock}.
+Global malaria incidence has decreased dramatically over the last 20 years \cite{abajobir2017global}.
+This has been accompanied by a strategic shift towards aiming for elimination in low burden countries \cite{world2016world}.
+Accurate, high-resolution maps of malaria risk are vital in these countries in the elimination and pre-elimination phases \cite{sturrock2016mapping}.
+However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite {sturrock2016mapping, sturrock2014fine}.
 In low burden areas, very large sample sizes are needed before a prevalence survey is informative.
@@
 Routine surveillance is also often timely, with reports being released annually or monthly, while large prevalence surveys are performed on a more decadely time scale.
-However, the unstructured nature of the data collection means that dealing with biases and data gaps is an ongoing research priority \cite{battlets, cibulski}.
+However, the unstructured nature of the data collection means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.
 
 %however surveillance data is sometimes high quality in these areas
-%pixel level maps from aggregates data is difficult (sturrock, inla, Leon, others)
+%pixel level maps from aggregates data is difficult (sturrock2014fine, wilson2017pointless, law2018variational, others)
 %not much information for covariates 
@@
 
-Furthermore, using aggregated data to estimate malaria risk for high resolution maps presents further modelling difficulties \cite{sturrock, inla, Leon, others}.
+Furthermore, using aggregated data to estimate malaria risk for high resolution maps presents further modelling difficulties \cite{sturrock2014fine, wilson2017pointless, law2018variational, others}.
 The aggregated nature of the data means that each data point does not necessarily contain much information, especially if the case counts are aggregated over a large or heterogenous area.
-For example, \cite{sturrock} use only two covariates do to the lack of information in their data.
+For example, \cite{sturrock2014fine} use only two covariates do to the lack of information in their data.
 
@@
 One major barrier to this modelling approved us that these two data sources are on different scales: point surveys are a measurement of prevalence $\lbrack 0, 1\rbrack$ while routine surveillance measures incidence $\lbrack 0, \infty\rbrack$.
-One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015}.
+One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015defining}.
 
@@
 
-The prevalence survey data were extracted from the MAP prevalence survey database \cite{}.
-As the prevalence surveys cover different are ranges they were standardised using the model from \cite{}.
+The prevalence survey data were extracted from the MAP prevalence survey database \cite{bhatt2015effect}.
+As the prevalence surveys cover different age ranges they were standardised using the model from \cite{smith2007standardizing}.
 
@@
 After fitting, this model defines a function
-$$\mathrm{p2i}: f\left(P\right) = 2.616P - 3.596P^2 + 1.594P^3$$.
+$$\mathrm{p2i}: f\left(P\right) = 2.616P - 3.596P^2 + 1.594P^3.$$
 
@@
 This reflects real world data where we sometimes have incidence data but no prevalence data and visa versa.
-Thus this cross-validation scheme can be seen as asking whether aggregated incidence data provides a viable or preferable alternative to using just prevalence data as in previous modelling efforts \cite{bhatt2016nature}.
+Thus this cross-validation scheme can be seen as asking whether aggregated incidence data provides a viable or preferable alternative to using just prevalence data as in previous modelling efforts \cite{bhatt2015effect}.
 

### 2018-08-02 ms.tex
Add tmb and R reference.
Add some pop methods.

@@
 %Ideal situation is to combine data
-benefits of both
+%benefits of both
 %but data are on different scales
@@
 \subsection*{Population data}
+
+Raster surfaces of population for the years 2005, 2010 and 2015, were created using a hybrid of data from GPWv4 \cite{gpw4} and WorldPop \cite{tatem2017worldpop}, with the latter taking priority for those pixels where both had population data.
+Final population rasters were created by linear interpolation of the surrounding five-yearly rasters
 
@@
 This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularised our model.
+
+The models were implemented and fitted using Template Model Builder \cite{TMB} in R \cite{R}
 

### 2018-08-29 ms.tex
Bump up lit on disaggregation.

@@
 
-Global malaria incidence has decreased dramatically over the last 20 years \cite{abajobir2017global}.
-This has been accompanied by a strategic shift towards aiming for elimination in low burden countries \cite{world2016world}.
-Accurate, high-resolution maps of malaria risk are vital in these countries in the elimination and pre-elimination phases \cite{sturrock2016mapping}.
-However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite {sturrock2016mapping, sturrock2014fine}.
+Global malaria incidence has decreased dramatically over the last 20 years \cite{abajobir2017global, bhatt2015effect}.
+This has been accompanied by a strategic shift towards aiming for elimination in low burden countries \cite{world2016world, newby2016path}.
+Accurate, high-resolution maps of malaria risk are vital in these countries in the elimination and pre-elimination phases \cite{sturrock2016mapping, cohen2017mapping}.
+However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \cite{gething2011new, bhatt2017improved, gething2012long} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite {sturrock2016mapping, sturrock2014fine}.
 In low burden areas, very large sample sizes are needed before a prevalence survey is informative.
-Furthermore, large, countrywide surveys of prevalence, such as DHS or MIS, are rare in low burden countries due to costs and percieved low utility \cite{dunno}.
+Furthermore, large, countrywide surveys of prevalence, such as DHS or MIS, are rare in low burden countries due to costs and percieved low utility \cite{dhs}.
 We therefore need new data sources and associated statistical methods.
 
-Routine surveillance data, of disease case counts, is becoming more widely available and of better quality.
+%cohen2017mapping Different metrics are useful for different things. Most maps use prevalence. Govts do use maps.
+
+Routine surveillance data, of disease case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information}.
 This data is commonly aggregated, reporting disease case counts that occurred within a certain geographic region defined by a polygon.
-This type of data is more sensitive than prevalence surveys in low transmission areas as three entire health system is being used to passively monitor disease risk.
+This type of data is more sensitive than prevalence surveys in low transmission areas as the entire health system is being used to passively monitor disease risk.
 Routine surveillance is also often timely, with reports being released annually or monthly, while large prevalence surveys are performed on a more decadely time scale.
@@
 %not much information for covariates 
-sturrock used two.
+%sturrock used two.
 %undeveloped area of statistics but see Leon.
 
-Furthermore, using aggregated data to estimate malaria risk for high resolution maps presents further modelling difficulties \cite{sturrock2014fine, wilson2017pointless, law2018variational, others}.
+Furthermore, using aggregated data to estimate malaria risk for high resolution maps presents further modelling difficulties \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
 The aggregated nature of the data means that each data point does not necessarily contain much information, especially if the case counts are aggregated over a large or heterogenous area.
-For example, \cite{sturrock2014fine} use only two covariates do to the lack of information in their data.
+For example, Sturrock \emph{et al.} use only two covariates due to the lack of information in their data \cite{sturrock2014fine}.
 
 A model that could combine point surveys and aggregated surveillance has great potential if it could leverage the strengths of both aggregated surveillance data and point survey data.
-One major barrier to this modelling approved us that these two data sources are on different scales: point surveys are a measurement of prevalence $\lbrack 0, 1\rbrack$ while routine surveillance measures incidence $\lbrack 0, \infty\rbrack$.
+One major barrier to this modelling approach us that these two data sources are on different scales: point surveys are a measurement of prevalence $\lbrack 0, 1\rbrack$ while routine surveillance measures incidence $\lbrack 0, \infty\rbrack$.
 One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015defining}.
@@
 Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
-We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \ref{notSimpson} such that $P(\rho < 3) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
+We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < 3) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
 We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected, so we set this prior such that the randome field could explain most of the range of the data.
 
-We assigned $\sigma_v$ a penalised complexity prior such that $P(\sigma_v > 0.05) = 0.0000001$
-This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for three case counts \ref{cibulskis}.
+We assigned $\sigma_v$ a penalised complexity prior \cite{simpson2017penalising} such that $P(\sigma_v > 0.05) = 0.0000001$
+This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for the case counts using the approach defined in \cite{cibulskis2011worldwide}.
 We found that an iid effect with a standard deviation of 0.05 would be able to account for the discrepancy between the assumed Poisson error and the independently derived error.

### 2018-08-29 ms.tex
Fix fig reference.

@@
 
-Routine surveillance data, of disease case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information}.
+Routine surveillance data, of disease case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
 This data is commonly aggregated, reporting disease case counts that occurred within a certain geographic region defined by a polygon.
-This type of data is more sensitive than prevalence surveys in low transmission areas as the entire health system is being used to passively monitor disease risk.
+This type of data is more sensitive than prevalence surveys in low transmission areas as typically the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
 Routine surveillance is also often timely, with reports being released annually or monthly, while large prevalence surveys are performed on a more decadely time scale.
@@
 } The incidence and prevalence data (left) and (spatially) out-of-sample predictions (right) for Indonesia (top) and Senagal (bottom).}
-\label{fig1}
+\label{fig:data}
 \end{figure}

### 2018-08-29 ms.tex
More intro edits.

@@
 Furthermore, using aggregated data to estimate malaria risk for high resolution maps presents further modelling difficulties \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
-The aggregated nature of the data means that each data point does not necessarily contain much information, especially if the case counts are aggregated over a large or heterogenous area.
-For example, Sturrock \emph{et al.} use only two covariates due to the lack of information in their data \cite{sturrock2014fine}.
+The aggregated of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
+For example, Sturrock \emph{et al.} used only two covariates in their model \cite{sturrock2014fine}.
+These models are also simply an underrepresented class of models in the statistical literature and statistical software.
+Wilson \emph{et al.} \cite{wilson2017pointless} use an approximation to represent a downscaling model as a convolution matrix within R-INLA \cite{INLA} but more generally, downscaling models are not available in popular software packages and must be programmed explicitely.
 
 A model that could combine point surveys and aggregated surveillance has great potential if it could leverage the strengths of both aggregated surveillance data and point survey data.
-One major barrier to this modelling approach us that these two data sources are on different scales: point surveys are a measurement of prevalence $\lbrack 0, 1\rbrack$ while routine surveillance measures incidence $\lbrack 0, \infty\rbrack$.
+Joint modelling of the two data types has the potential to increase statistical power for learning relationships between malaria risk and covariates.
+Furthermore, using two complimentary datasets potentially allows better spatial coverage. 
+One major barrier to this modelling approach is that these two data sources are on different scales: point surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ while routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$.
 One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015defining}.
@@
 
-Here we formulate a joint model that combines aggregated surveillance data and point prevalence surveys of \emph{Plasmodium falciparum}.
-We compare the joint model to models fitted with only one type of data.
-As case studies we use three countries with good routine surveillance data as well as good coverage of prevalence point surveys.
+Here we formulate a joint model that combines aggregated surveillance data and point prevalence-surveys of \emph{Plasmodium falciparum}.
+The model has seperate likelihood functions for the two data types.
+We relate the two malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
+We compare the joint model to two benchmark models, a prevalence-survey only model and an aggregated-incidence disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless}.
+As case studies we use data from Indonesia, Senegal and Madagascar as these countries have both good routine surveillance data and good coverage of prevalence point surveys.
 

### 2018-08-30 ms.tex
Small additions to data methods.

@@
 We used two data sources that reflect malaria burden; point prevalence surveys and polygon-level, aggregated incidence data.
-We selected Madagascar and Indonesia as case examples as they have both good surveillance data and good country wide surveys from approximately the same time.
+We selected Madagascar, Senegal and Indonesia as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
 Given the available data we chose to focus our analysis on 2012-2015 for Indonesia and 2013-2014 for Madagascar.
@@
 
-The prevalence survey data were extracted from the MAP prevalence survey database \cite{bhatt2015effect}.
+The prevalence survey data were extracted from the Malaria Atlas Project prevalence survey database \cite{bhatt2015effect}.
 As the prevalence surveys cover different age ranges they were standardised using the model from \cite{smith2007standardizing}.
@@
 \subsection*{Polygon incidence data}
+
+The polygon level surveillance data were collated from various government reports.
+To account for underreporting of clinical cases due to lack of treatment seeking, missed case reports and cases that sought medical attention outside the public health systems, the methods in \cite{cibulskis2011worldwide} were used.
+Where species specific reports were given, these were used. 
+When reports were no species specific, national estimates of the ratio between \emph{P. falciparum} and \emph{P. vivax} cases were used to calculate \emph{P. falciparum} only cases.
 

### 2018-08-30 ms.tex
More intro edits.

@@
 This has been accompanied by a strategic shift towards aiming for elimination in low burden countries \cite{world2016world, newby2016path}.
-Accurate, high-resolution maps of malaria risk are vital in these countries in the elimination and pre-elimination phases \cite{sturrock2016mapping, cohen2017mapping}.
+Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases \cite{sturrock2016mapping, cohen2017mapping}.
 However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \cite{gething2011new, bhatt2017improved, gething2012long} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite {sturrock2016mapping, sturrock2014fine}.
@@
 Routine surveillance data, of disease case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
-This data is commonly aggregated, reporting disease case counts that occurred within a certain geographic region defined by a polygon.
-This type of data is more sensitive than prevalence surveys in low transmission areas as typically the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
-Routine surveillance is also often timely, with reports being released annually or monthly, while large prevalence surveys are performed on a more decadely time scale.
-However, the unstructured nature of the data collection means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.
+Surveillance data is commonly aggregated, reporting disease case counts that occurred within a certain geographic region defined by a polygon.
+Ths surveillance data can be more sensitive than prevalence surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
+Furthermore, surveillance data is also often timely, with reports being released annually or monthly, while large prevalence surveys are performed on a more decadely time scale.
+However, the unstructured nature data collection and reporting from national disease surveillance systems means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.
 
@@
 
-Furthermore, using aggregated data to estimate malaria risk for high resolution maps presents further modelling difficulties \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
-The aggregated of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
-For example, Sturrock \emph{et al.} used only two covariates in their model \cite{sturrock2014fine}.
-These models are also simply an underrepresented class of models in the statistical literature and statistical software.
+Further to issues with the data itself, using aggregated data to estimate malaria risk for high resolution maps presents particular modelling difficulties \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
+The class of models that aim to estimate high-resolution maps from aggregated data are called disaggregation models and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
+The aggregating of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
+For example, Sturrock \emph{et al.} used only two environmental covariates in their model \cite{sturrock2014fine}.
+Disaggregation models are also simply an underrepresented class of models in the statistical literature and statistical software.
 Wilson \emph{et al.} \cite{wilson2017pointless} use an approximation to represent a downscaling model as a convolution matrix within R-INLA \cite{INLA} but more generally, downscaling models are not available in popular software packages and must be programmed explicitely.
 
-A model that could combine point surveys and aggregated surveillance has great potential if it could leverage the strengths of both aggregated surveillance data and point survey data.
-Joint modelling of the two data types has the potential to increase statistical power for learning relationships between malaria risk and covariates.
+A model that combines point surveys and aggregated surveillance data, and therefore leverages the strength of both, has great potential.
+Joint modelling of the two data types has the potential to increase statistical power for learning relationships between malaria risk and covariates both by simply making more data available and because the point survey has a one-to-one relationship with the environment at the location of the survey.
 Furthermore, using two complimentary datasets potentially allows better spatial coverage. 

### 2018-08-31 ms.tex
Edits to methods.

@@
 We used two data sources that reflect malaria burden; point prevalence surveys and polygon-level, aggregated incidence data.
-We selected Madagascar, Senegal and Indonesia as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
-Given the available data we chose to focus our analysis on 2012-2015 for Indonesia and 2013-2014 for Madagascar.
+We selected Indonesia, Senegal and Madagascar as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
+To minimise temporal effects we select, for each country, one year of prevalence survey data and one year of surveillance data.
+For Indonesia we selected 2010 for prevalence data (n = ) and 2012 for surveillance data (n =).
+For Senegal we selected todo for prevalence data (n = ) and todo for surveillance data (n =).
+Finally, for Madagascar we selected 2013 for both prevalence (n = ) and surveillance (n = ) data.
 
@@
 Where species specific reports were given, these were used. 
-When reports were no species specific, national estimates of the ratio between \emph{P. falciparum} and \emph{P. vivax} cases were used to calculate \emph{P. falciparum} only cases.
+For reports where no species specific, national estimates of the ratio between \emph{P. falciparum} and \emph{P. vivax} cases were used to calculate \emph{P. falciparum} only cases.
 
@@
 Raster surfaces of population for the years 2005, 2010 and 2015, were created using a hybrid of data from GPWv4 \cite{gpw4} and WorldPop \cite{tatem2017worldpop}, with the latter taking priority for those pixels where both had population data.
-Final population rasters were created by linear interpolation of the surrounding five-yearly rasters
+Final population rasters were created by linear interpolation of the surrounding five-yearly rasters.
+Finally, for each year, national population estimates from the UN were raked over the interpolated population surfaces.
 
@@
 After preliminary analyses, tassel cap brightness and urban land cover were removed as they were highly correlated with other variables.
-The covariates are standardised to have a mean of zero and a standard deviation of one.
+The covariates were standardised to have a mean of zero and a standard deviation of one.
 
@@
 We compared three models 1) a full model with prevalence surveys and aggregated incidence data 2) the submodel with only prevalence data and 3) the submodel with only aggregated incidence data. 
+The models were implemented and fitted using Template Model Builder \cite{TMB} in R \cite{R}
 
@@
 Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
-We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < 3) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
-We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected, so we set this prior such that the randome field could explain most of the range of the data.
+We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
+We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = todo$ and Madagascar $\zeta = 1$.
+We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \cite{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.
 
@@
 Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{ Norm}(0, 0.04)$. 
-Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of 3, I've covariate would be able to predict prevalences between 0.004 and 0.27. 
+Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of 3, each covariate would be able to predict prevalences between 0.004 and 0.27. 
 This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularised our model.
-
-The models were implemented and fitted using Template Model Builder \cite{TMB} in R \cite{R}
 
@@
 To compare the three models we used two cross validation schemes. 
-In the first, the combined data set of prevalence and incidence data was split into five cross-validation folds stratified by data type.
-This reflects real world data where we sometimes have incidence data but no prevalence data and visa versa.
+In the first, the combined data set of prevalence and incidence data was split into ten cross-validation folds stratified by data type.
+This reflects real world data where we in some locations we have incidence data but no prevalence data and visa versa.
 Thus this cross-validation scheme can be seen as asking whether aggregated incidence data provides a viable or preferable alternative to using just prevalence data as in previous modelling efforts \cite{bhatt2015effect}.
@@
 
-In the second validation scheme the data was split into five spatial cross-validation folds (see Figure~\ref{fig:data}b).
+In the second validation scheme the data was split into spatial cross-validation folds (see Figure~\ref{fig:data}b).
+The number of folds was seven for Indonesia, todo for Senegal and three for Madagascar due to their differing size and geography.
 The data was divided by combining the point locations and the centroids of the polygons and performing k means clustering.
@@
 If the prevalence-incidence relationship is poorly estimated, this will strongly affect the Pearson's correlation while the Spearman's correlation will be relatively robust to this source of poor model performance.
+Finally, we considered coverage of the 80\% credible intervals.
 

### 2018-09-17 ms.tex
Update tables and figure labels.

@@
 To compare the three models we used two cross validation schemes. 
-In the first, the combined data set of prevalence and incidence data was split into ten cross-validation folds stratified by data type.
+In the first, the combined data set of prevalence and incidence data was split into ten cross-validation folds stratified by data type (Figure~\ref{fig:cv_random}).
 This reflects real world data where we in some locations we have incidence data but no prevalence data and visa versa.
@@
 
-%figure 1.cross validation. %%columns country. rows: CV  Indonesia and Senegal only.
+%figure 1.cross validation. %% Do fig 1 and 2, random and spatial cv. IDN on top, MDG and SEN below in each.
 
@@
 \centering
-\begin{minipage}{0.45\textwidth} \centering 
-\includegraphics[width = 0.9\textwidth]{figures/idn_cv_random.png} %\caption{Indonesia random crossvalidation} 
-\end{minipage}
-\begin{minipage}{0.45\textwidth} \centering 
-\includegraphics[width = 0.9\textwidth]{figures/idn_cv_spatial.png} %\caption{Indonesia spatial crossvalidation} 
-\end{minipage}
 
-\caption{{\bf Input incidence and prevalence data and predicted incidence maps.
-} The incidence and prevalence data (left) and (spatially) out-of-sample predictions (right) for Indonesia (top) and Senagal (bottom).}
-\label{fig:data}
+\includegraphics[width = 0.9\textwidth]{figures/random_crossvalidation_full.png} %\caption{Indonesia random crossvalidation}
+
+\caption{{\bf Random cross-validation scheme for Indonesia, Senegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+\label{fig:cv_random}
 \end{figure}
 
-In the second validation scheme the data was split into spatial cross-validation folds (see Figure~\ref{fig:data}b).
+\begin{figure}[!h]
+% to be removed before submission
+\centering
+
+\includegraphics[width = 0.9\textwidth]{figures/spatial_crossvalidation_full.png} %\caption{Indonesia random crossvalidation}
+
+\caption{{\bf Spatial cross-validation scheme for Indonesia, Senegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+\label{fig:cv_spatial}
+\end{figure}
+
+In the second validation scheme the data was split into spatial cross-validation folds (see Figure~\ref{fig:cv_spatial}).
 The number of folds was seven for Indonesia, todo for Senegal and three for Madagascar due to their differing size and geography.
@@
 
-%figure 2. data and predicted incidence maps. Indonesia and Senegal only. spatial CV only.
-
-%figure 3 predicted Vs observed. colour by %country facet by prev inc and cv scheme? best model only.
+%figure 3 and 4. data and predicted incidence maps. Indonesia and Senegal only. Fig 3 ind, fig 4 rand. Data, Rand, Spatial for best model? Joint model?
 
@@
 % to be removed before submission
-\includegraphics[width = 0.9\textwidth]{figures/pred_obs_map.png}
-\caption{{\bf Input incidence and prevalence data and predicted incidence maps.
-} The incidence and prevalence data (left) and (spatially) out-of-sample predictions (right) for Indonesia (top) and Senagal (bottom).}
-\label{predobsmap}
+\includegraphics[width = 0.9\textwidth]{figures/idn_both_cv12_preds.png}
+\caption{{\bf Input incidence and prevalence data and predicted incidence maps. } 
+The incidence (log10) and prevalence data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
+}
+\label{predobsmapidn}
+\end{figure}
+
+\begin{figure}[!h]
+% to be removed before submission
+\includegraphics[width = 0.9\textwidth]{figures/sen_both_cv12_preds.png}
+\caption{{\bf Input incidence and prevalence data and predicted incidence maps. } 
+The incidence (log10) and prevalence data (left), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (right) for Senegal.
+}
+\label{predobsmapsen}
 \end{figure}
@@
 \thickhline 
-Incidence & Pearson & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{1mm}\\ 
-          & Spearman & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{3mm} \\ 
-Prevalence & Pearson & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{1mm}\\ 
-            & Spearman & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\\
+Incidence & Pearson & Indonesia & 0.28 & 0.46 &  0.42\\
+&& Senegal & 0.28 & 0.79 &  0.83\\
+&& Madagascar & 0.69 & 0.72 &  0.75\vspace{1mm}\\
+& Spearman & Indonesia & 0.39 & 0.75 &  0.75\\
+&& Senegal & 0.46 & 0.69 &  0.66\\
+&& Madagascar & 0.81 & 0.83 &  0.85\vspace{3mm} \\
+Prevalence & Pearson & Indonesia & 0.32 & 0.31 &  0.19\\
+&& Senegal & 0.06 & 0.04 &  0.04\\
+&& Madagascar & 0.57 & 0.55 &  0.59\vspace{1mm}\\
+& Spearman & Indonesia & 0.54 & 0.38 &  0.39\\
+&& Senegal & 0.03 & 0.12 &  0.12\\
+&& Madagascar & 0.57 & 0.55 &  0.58\\
 \end{tabular}
@@
 \thickhline 
-Incidence & Pearson & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{1mm}\\ 
-          & Spearman & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{3mm} \\ 
-Prevalence & Pearson & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{1mm}\\ 
-            & Spearman & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
-                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\\
+Incidence & Pearson & Indonesia &  0.07 &  0.09 &   0.16\\
+&& Senegal &  0.20 &  0.23 &   0.53\\
+&& Madagascar &  0.20 &  0.16 &   0.24\vspace{1mm}\\
+& Spearman & Indonesia &  0.40 &  0.47 &   0.39\\
+&& Senegal &  0.36 &  0.30 &   0.56\\
+&& Madagascar &  0.49 &  0.50 &   0.52\vspace{3mm} \\
+Prevalence & Pearson & Indonesia & -0.23 & -0.07 &   0.06\\
+&& Senegal &  0.16 &  0.19 &   0.16\\
+&& Madagascar &  0.23 &  0.17 &   0.21\vspace{1mm}\\
+& Spearman & Indonesia & -0.35 & -0.05 &  -0.01\\
+&& Senegal &  0.02 &  0.16 &   0.13\\
+&& Madagascar &  0.44 &  0.38 &   0.43\\
 \end{tabular}
@@
 \end{flushleft}
-\label{table1}
+\label{table2}
 \end{adjustwidth}
@@
 
+%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
 \begin{figure}[!h]
 % to be removed before submission
-\includegraphics[width = 0.9\textwidth]{figures/joint_idn_cv_log_results}
-\caption{{\bf Observed-predicted plots for cross-validated data.}
-Error bars include uncertainty of the fitted parameters and from sampling error.
-100 realisations of the predictions were calculated taking a draw of all parameters from the posterior and the iid random effect $v_j$ and then sampling from the assumed sampling models (binomial and Poisson) each time.
-The 90\% quantiles were them taken and plotted as error bars.
+\includegraphics[width = 0.9\textwidth]{figures/random_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
+\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
+A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) log10 aggregated incidence, B, D, F) prevalence.
+Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
 }
@@
 \end{figure}
+
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{
+{\bf Summary of coverage of 80\% credible intervals for.}}
+\begin{tabular}{llllll}
+\hline
+{\bf Holdout data} & {\bf crossvalidation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
+\thickhline 
+Incidence & Random & Indonesia &  0.11 &  0.77 &   0.79\\
+&& Senegal &  0.11 &  0.80 &   0.85\\
+&& Madagascar &  0.59 &  0.82 &   0.77\vspace{1mm}\\
+& Spatial & Indonesia &  0.11 &  0.77 &   0.79\\
+&& Senegal &  0.11 &  0.80 &   0.85\\
+&& Madagascar &  0.59 &  0.82 &   0.77\vspace{3mm} \\
+Prevalence & Random & Indonesia &  0.83 &  0.66 &   0.85\\
+&& Senegal &  0.90 &  0.88 &   0.79\\
+&& Madagascar &  0.93 &  0.68 &   0.83\vspace{1mm}\\
+& Spatial & Indonesia & -0.35 & -0.05 &  -0.01\\
+&& Senegal &  0.90 &  0.88 &   0.79\\
+&& Madagascar &  0.93 &  0.68 &   0.83\\
+\end{tabular}
+\begin{flushleft}
+
+\end{flushleft}
+\label{table3}
+\end{adjustwidth}
+\end{table}
 

### 2018-09-17 ms.tex
Fix table3.

@@
 \thickhline 
-Incidence & Random & Indonesia &  0.11 &  0.77 &   0.79\\
-&& Senegal &  0.11 &  0.80 &   0.85\\
-&& Madagascar &  0.59 &  0.82 &   0.77\vspace{1mm}\\
-& Spatial & Indonesia &  0.11 &  0.77 &   0.79\\
-&& Senegal &  0.11 &  0.80 &   0.85\\
-&& Madagascar &  0.59 &  0.82 &   0.77\vspace{3mm} \\
-Prevalence & Random & Indonesia &  0.83 &  0.66 &   0.85\\
-&& Senegal &  0.90 &  0.88 &   0.79\\
-&& Madagascar &  0.93 &  0.68 &   0.83\vspace{1mm}\\
-& Spatial & Indonesia & -0.35 & -0.05 &  -0.01\\
-&& Senegal &  0.90 &  0.88 &   0.79\\
-&& Madagascar &  0.93 &  0.68 &   0.83\\
+Incidence & Random & Indonesia & 0.10 & 0.76 &  0.77\\
+&& Senegal & 0.69 & 0.82 &  0.78\\
+&& Madagascar & 0.73 & 0.82 &  0.78\vspace{1mm}\\
+& Spatial & Indonesia & 0.10 & 0.76 &  0.77\\
+&& Senegal & 0.69 & 0.82 &  0.78\\
+&& Madagascar & 0.73 & 0.82 &  0.78\vspace{3mm} \\
+Prevalence & Random & Indonesia & 0.83 & 0.59 &  0.77\\
+&& Senegal & 0.87 & 0.69 &  0.80\\
+&& Madagascar & 0.83 & 0.69 &  0.80\vspace{1mm}\\
+& Spatial & Indonesia & 0.54 & 0.36 &  0.38\\
+&& Senegal & 0.87 & 0.69 &  0.80\\
+&& Madagascar & 0.83 & 0.69 &  0.80\\
 \end{tabular}

### 2018-09-27 ms.tex
Update cov table.

@@
 
-Despite major reductions in incidence over the last fifteen years, malaria still causes millions of deaths and loads of DALYs annually \cite{abajobir2017global}.
-Elimination of malaria, country-by-county has become a central goal in the global malaria strategy \cite{world2016world}.
-Elimination of malaria requires high resolution maps of malaria risk, in low prevalence areas in order to optimise interventions and minimise costs \cite{sturrock2016mapping}.
-
 % Please keep the Author Summary between 150 and 200 words
@@
 Global malaria incidence has decreased dramatically over the last 20 years \cite{abajobir2017global, bhatt2015effect}.
-This has been accompanied by a strategic shift towards aiming for elimination in low burden countries \cite{world2016world, newby2016path}.
+This decrease has been accompanied by a strategic shift towards aiming for elimination in low incidence countries \cite{world2016world, newby2016path}.
 Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases \cite{sturrock2016mapping, cohen2017mapping}.
@@
 
+%Despite major reductions in incidence over the last fifteen years, malaria still causes millions of deaths and loads of DALYs annually \cite{abajobir2017global}.
+%Elimination of malaria, country-by-county has become a central goal in the global malaria strategy \cite{world2016world}.
+%Elimination of malaria requires high resolution maps of malaria risk, in low prevalence areas in order to optimise interventions and minimise costs \cite{sturrock2016mapping}.
+
 %cohen2017mapping Different metrics are useful for different things. Most maps use prevalence. Govts do use maps.
 
-Routine surveillance data, of disease case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
-Surveillance data is commonly aggregated, reporting disease case counts that occurred within a certain geographic region defined by a polygon.
+Routine surveillance data, of malaria case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
+Surveillance data is commonly aggregated, reporting the number of cases that occurred within a certain geographic or administrative region defined by a polygon.
 Ths surveillance data can be more sensitive than prevalence surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
 Furthermore, surveillance data is also often timely, with reports being released annually or monthly, while large prevalence surveys are performed on a more decadely time scale.
-However, the unstructured nature data collection and reporting from national disease surveillance systems means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.
+However, the unstructured nature of data collection and reporting from national disease surveillance systems means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.
 
@@
 Further to issues with the data itself, using aggregated data to estimate malaria risk for high resolution maps presents particular modelling difficulties \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
-The class of models that aim to estimate high-resolution maps from aggregated data are called disaggregation models and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
+%Disaggregation models aim to estimate high-resolution maps from aggregated data and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
 The aggregating of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
@@
 Disaggregation models are also simply an underrepresented class of models in the statistical literature and statistical software.
-Wilson \emph{et al.} \cite{wilson2017pointless} use an approximation to represent a downscaling model as a convolution matrix within R-INLA \cite{INLA} but more generally, downscaling models are not available in popular software packages and must be programmed explicitely.
+Wilson \emph{et al.} \cite{wilson2017pointless} used an approximation to represent a downscaling model as a convolution matrix within R-INLA \cite{INLA} but more generally, downscaling models are not available in popular software packages and must be programmed explicitely.
+Furthermore, disaggregation models are relatively difficult to implement as they have more rows of covariate data than response data.
 
@@
 Here we formulate a joint model that combines aggregated surveillance data and point prevalence-surveys of \emph{Plasmodium falciparum}.
-The model has seperate likelihood functions for the two data types.
+The model has seperate likelihoods for the two data types.
 We relate the two malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
@@
 \hline
-{\bf Holdout data} & {\bf Metric} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
+{\bf Holdout data} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
 \thickhline 
-Incidence & Pearson & Indonesia & 0.28 & 0.46 &  0.42\\
-&& Senegal & 0.28 & 0.79 &  0.83\\
-&& Madagascar & 0.69 & 0.72 &  0.75\vspace{1mm}\\
-& Spearman & Indonesia & 0.39 & 0.75 &  0.75\\
-&& Senegal & 0.46 & 0.69 &  0.66\\
-&& Madagascar & 0.81 & 0.83 &  0.85\vspace{3mm} \\
-Prevalence & Pearson & Indonesia & 0.32 & 0.31 &  0.19\\
-&& Senegal & 0.06 & 0.04 &  0.04\\
-&& Madagascar & 0.57 & 0.55 &  0.59\vspace{1mm}\\
-& Spearman & Indonesia & 0.54 & 0.38 &  0.39\\
-&& Senegal & 0.03 & 0.12 &  0.12\\
-&& Madagascar & 0.57 & 0.55 &  0.58\\
+Incidence & Indonesia & 18.33 & 14.02 &  14.09\\
+& Senegal & 51.24 & 26.74 &  28.45\\
+& Madagascar & 85.54 & 37.45 &  34.49\vspace{3mm}\\
+Prevalence & Indonesia & 0.010 & 0.010 &  0.010\\
+& Senegal & 0.015 & 0.024 &  0.024\\
+& Madagascar & 0.054 & 0.059 &  0.059\\
 \end{tabular}
 \begin{flushleft}
-Correlation (Spearman's and Pearson's) of predicted incidence rate and prevalence against out-of-sample observed data for three countries.
+Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
 The data were split randomly into 10 groups stratified by data type (incidence polygon and prevalence points).
@@
 \hline
-{\bf Holdout data} & {\bf Metric} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
+{\bf Holdout data} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
 \thickhline 
-Incidence & Pearson & Indonesia &  0.07 &  0.09 &   0.16\\
-&& Senegal &  0.20 &  0.23 &   0.53\\
-&& Madagascar &  0.20 &  0.16 &   0.24\vspace{1mm}\\
-& Spearman & Indonesia &  0.40 &  0.47 &   0.39\\
-&& Senegal &  0.36 &  0.30 &   0.56\\
-&& Madagascar &  0.49 &  0.50 &   0.52\vspace{3mm} \\
-Prevalence & Pearson & Indonesia & -0.23 & -0.07 &   0.06\\
-&& Senegal &  0.16 &  0.19 &   0.16\\
-&& Madagascar &  0.23 &  0.17 &   0.21\vspace{1mm}\\
-& Spearman & Indonesia & -0.35 & -0.05 &  -0.01\\
-&& Senegal &  0.02 &  0.16 &   0.13\\
-&& Madagascar &  0.44 &  0.38 &   0.43\\
+Incidence & Indonesia &  18.13 &  14.77 &   15.02\\
+& Senegal &  51.17 &  41.43 &   36.76\\
+& Madagascar & 107.32 &  71.44 &   65.50\vspace{3mm}\\
+Prevalence & Indonesia & 0.011 & 0.010 &  0.010\\
+& Senegal & 0.015 & 0.019 &  0.019\\
+& Madagascar & 0.069 & 0.066 &  0.065\\
 \end{tabular}
 \begin{flushleft}
-Correlation (Spearman's and Pearson's) of predicted incidence rate and prevalence against out-of-sample observed data for three countries.
+Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
 The data were split spatiall into 5 groups.
@@
 \caption{{\bf Observed-predicted plots for random cross-validation experiments.}
-A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) log10 aggregated incidence, B, D, F) prevalence.
+A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
+Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
+}
+\label{predobsscatter}
+\end{figure}
+
+%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
+\begin{figure}[!h]
+% to be removed before submission
+\includegraphics[width = 0.9\textwidth]{figures/spatial_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
+\caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
+A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
 Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
@@
 \thickhline 
-Incidence & Random & Indonesia & 0.10 & 0.76 &  0.77\\
-&& Senegal & 0.69 & 0.82 &  0.78\\
-&& Madagascar & 0.73 & 0.82 &  0.78\vspace{1mm}\\
-& Spatial & Indonesia & 0.10 & 0.76 &  0.77\\
-&& Senegal & 0.69 & 0.82 &  0.78\\
-&& Madagascar & 0.73 & 0.82 &  0.78\vspace{3mm} \\
-Prevalence & Random & Indonesia & 0.83 & 0.59 &  0.77\\
-&& Senegal & 0.87 & 0.69 &  0.80\\
-&& Madagascar & 0.83 & 0.69 &  0.80\vspace{1mm}\\
-& Spatial & Indonesia & 0.54 & 0.36 &  0.38\\
-&& Senegal & 0.87 & 0.69 &  0.80\\
-&& Madagascar & 0.83 & 0.69 &  0.80\\
+Incidence & Random & Indonesia & 0.13 & 0.72 &  0.73\\
+&& Senegal & 0.11 & 0.80 &  0.85\\
+&& Madagascar & 0.59 & 0.82 &  0.77\vspace{1mm}\\
+& Spatial & Indonesia & 0.14 & 0.76 &  0.68\\
+&& Senegal & 0.30 & 0.67 &  0.70\\
+&& Madagascar & 0.68 & 0.65 &  0.68\vspace{3mm} \\
+Prevalence & Random & Indonesia & 0.90 & 0.50 &  0.80\\
+&& Senegal & 0.80 & 0.71 &  0.91\\
+&& Madagascar & 0.83 & 0.53 &  0.74\vspace{1mm}\\
+& Spatial & Indonesia & 0.87 & 0.62 &  0.96\\
+&& Senegal & 0.90 & 0.88 &  0.79\\
+&& Madagascar & 0.93 & 0.68 &  0.83\\
 \end{tabular}

### 2018-09-27 ms.tex
Add some covs references.

@@
 
-We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres that included land surface temperature annual mean and standard deviation, enhanced vegetation index, mosquito temperature suitability index, elevation, tassel cap brightness, tassel cap wetness, accessibility to cities, night lights and proportion of urban land cover.
+We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres at the equator that included land surface temperature annual mean and standard deviation \cite{LST}, enhanced vegetation index \cite{TCB}, mosquito temperature suitability index \cite{weiss2014air}, elevation \cite{SRTMElev}, tassel cap brightness \cite{TCB}, tassel cap wetness \cite{TCB}, accessibility to cities \cite{weiss2018global}, night lights \cite{} and proportion of urban land cover \cite{}.
 Elevation, land surface temperature standard deviation, accessibility to cities and night lights were all log transformed to reduce skewness.
@@
 \includegraphics[width = 0.9\textwidth]{figures/idn_both_cv12_preds.png}
-\caption{{\bf Input incidence and prevalence data and predicted incidence maps. } 
-The incidence (log10) and prevalence data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
+\caption{{\bf Input incidence data and predicted incidence maps. } 
+The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
 }
@@
 \includegraphics[width = 0.9\textwidth]{figures/sen_both_cv12_preds.png}
-\caption{{\bf Input incidence and prevalence data and predicted incidence maps. } 
-The incidence (log10) and prevalence data (left), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (right) for Senegal.
+\caption{{\bf Input incidence data and predicted incidence maps. } 
+The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
 }

### 2018-09-27 ms.tex
Small methods edits.

@@
 For Indonesia we selected 2010 for prevalence data (n = ) and 2012 for surveillance data (n =).
-For Senegal we selected todo for prevalence data (n = ) and todo for surveillance data (n =).
+For Senegal we selected 2015 for both prevalence data (n = ) and surveillance data (n =).
 Finally, for Madagascar we selected 2013 for both prevalence (n = ) and surveillance (n = ) data.
@@
 
-where $\mathrm{p2i}$ is from a model that was published previously. \cite{cameron2015defining}
-After fitting, this model defines a function
+where $\mathrm{p2i}$ is a function from a previously fitted model \cite{cameron2015defining} 
 $$\mathrm{p2i}: f\left(P\right) = 2.616P - 3.596P^2 + 1.594P^3.$$
@@
 The form of the link function means we get predictions of prevalence and incidence simultaneously whether we used both data types or just one.
-The linear predictor is composed of an intercept, covariates a spatial, Gaussian random field two iid random effects.
+The linear predictor is composed of an intercept, covariates, a spatial, Gaussian random field and two iid random effects.
 
@@
 We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
-We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = todo$ and Madagascar $\zeta = 1$.
+We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = 1$ and Madagascar $\zeta = 1$.
 We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \cite{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.
@@
 In the second validation scheme the data was split into spatial cross-validation folds (see Figure~\ref{fig:cv_spatial}).
-The number of folds was seven for Indonesia, todo for Senegal and three for Madagascar due to their differing size and geography.
+The number of folds was seven for Indonesia, seven for Senegal and three for Madagascar due to their differing size and geographies.
 The data was divided by combining the point locations and the centroids of the polygons and performing k means clustering.

### 2018-09-27 ms.tex
Small methods edits.

@@
 As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
-Our main performance metric was Pearson's correlation.
-However, we also considered Spearman's correlation.
-If the prevalence-incidence relationship is poorly estimated, this will strongly affect the Pearson's correlation while the Spearman's correlation will be relatively robust to this source of poor model performance.
-Finally, we considered coverage of the 80\% credible intervals.
+Our main performance metric was mean absolute error.
+To assess how well the models are calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.
 

### 2018-09-27 ms.tex
Bold best result.

@@
 \thickhline 
-Incidence & Indonesia & 18.33 & 14.02 &  14.09\\
-& Senegal & 51.24 & 26.74 &  28.45\\
-& Madagascar & 85.54 & 37.45 &  34.49\vspace{3mm}\\
+Incidence & Indonesia & 18.33 & {\bf 14.02} &  14.09\\
+& Senegal & 51.24 & {\bf 26.74} &  28.45\\
+& Madagascar & 85.54 & 37.45 &  {\bf 34.49}\vspace{3mm}\\
 Prevalence & Indonesia & 0.010 & 0.010 &  0.010\\
-& Senegal & 0.015 & 0.024 &  0.024\\
-& Madagascar & 0.054 & 0.059 &  0.059\\
+& Senegal & {\bf 0.015} & 0.024 &  0.024\\
+& Madagascar & {\bf 0.054} & 0.059 &  0.059\\
 \end{tabular}
@@
 \thickhline 
-Incidence & Indonesia &  18.13 &  14.77 &   15.02\\
-& Senegal &  51.17 &  41.43 &   36.76\\
-& Madagascar & 107.32 &  71.44 &   65.50\vspace{3mm}\\
+Incidence & Indonesia &  18.13 &  {\bf 14.77} &   15.02\\
+& Senegal &  51.17 &  41.43 &   {\bf 36.76}\\
+& Madagascar & 107.32 &  71.44 &   {\bf 65.50}\vspace{3mm}\\
 Prevalence & Indonesia & 0.011 & 0.010 &  0.010\\
-& Senegal & 0.015 & 0.019 &  0.019\\
-& Madagascar & 0.069 & 0.066 &  0.065\\
+& Senegal & {\bf 0.015} & 0.019 &  0.019\\
+& Madagascar & 0.069 & 0.066 &  {\bf 0.065}\\
 \end{tabular}

### 2018-09-27 ms.tex
First go at results.

@@
 
-The polygon level surveillance data were collated from various government reports.
-To account for underreporting of clinical cases due to lack of treatment seeking, missed case reports and cases that sought medical attention outside the public health systems, the methods in \cite{cibulskis2011worldwide} were used.
+The polygon level surveillance data were collated from various government reports (Figures~\ref{predobsmapidn}A and \ref{predobsmapsen}A).
+To account for underreporting of clinical cases due to lack of treatment seeking, missed case reports and cases that sought medical attention outside the public health systems, the methods in \cite{cibulskis2011worldwide} were used using estimates of treatment seeking from \cite{battle2016treatment}.
 Where species specific reports were given, these were used. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results and Discussion}
+\section*{Results}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Random results
+% Maps, reasonable for both
+% MAE performance.
+
+For the random cross-validation experiments, the polygon-only model had the lowest mean absolute error, with respect to predicting incidence, for Indonesia (14.02) and Senegal (26.74) (Table~\ref{table1}).
+Incidence in Madagascar was best predicted by the join model (34.49).
+However, the difference between the two models in Indonesia was small (polygons-only 14.02, joint model 14.09).
+Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter}A, C and E.
+
+The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both Senegal (0.015) and  Madagascar (0.054) while the wighted MAE was the same for all three models in Indonesia (0.010) (Table~\ref{table1}).
+The more pertinent comparison is whether the addition of the prevalence data improves the ability of the disaggregation models to predict pixel level prevalence.
+However, weighted MAE was unchanged between the polygon model and the joint model for Indonesia (0.010), Senegal (0.024) or Madagascar (0.059).
+Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and Senegal.
+
+Maps of the Indonesian input data_and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
+Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for Senegal show broad agreement with malaria incidence being higher in the South.
+
+% Spatial results
+% Maps, reasonable for india, get's broad pattern even far away from data. Poor for SEN, wrong overall pattern. Different covariates.
+% MAE performance.
+
+For the spatial cross-validation experiments, the polygon-only model again had the lowest mean absolute error between observed and predicted incidence for Indonesia (14.77) (Table~\ref{table2}).
+However, for both Senegal (36.76) and Madagascar (65.50) the joint model had the best predictive performance.
+Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{spatialpredobsscatter}A, C and E.
+
+Again, the benchmark points-only model had the lowest weighted MAE between spatially cross-validated observed and predicted prevalence for Senegal (0.015).
+However, for Indonesia, both the disaggration models marginally outperformed the points-only model (polygons-only 0.010, joint model 0.010). 
+For Senegal, the joint model (0.065) had the lowest weighted MAE for predicted prevalence though this was again marginal (points-only 0.069, polygons-only 0.066).
+Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and Senegal.
+
+Maps of the Indonesian input data_and spatially out-of-sample predictions (Figures~\ref{predobsmapidn}A and C) suggest the that the broad spatial patterns were once again recovered.
+This acceptable performance is notable given the very large areas held out-of-sample (Fig~\ref{fig:cv_spatial}).
+For example, the whole of Papua and West Papua the the East are held out in a single fold.
+In contrast the predictions for Senegal do not match those observed in the input data (Figures~\ref{predobsmapsen}A and C).
+
+% Coverage results
+
+The polygon-only model and the joint model seem to be fairly well calibrated.
+The proportion of out-of-sample incidence datapoints being within their 80\% credible intervals ranged between 0.65 and 0.85.
+The proportion of out-of-sample prevalence datapoints being within their 80\% credible intervals ranged from 0.50 to 0.96.
+The points only model was reasonably well calibrated for predictions of prevalence (coverage ranging from 0.8 to 0.93) but was poorly calibrated for predicting incidence with coverage values as low as 0.11 and the best coverage value being 0.68 for spatial crossvalidation in Madagascar.
+
+% Overall
 
@@
 The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
+The values plotted for areas with no polygon data are the means across all cross-validation folds.
 }
@@
 & Madagascar & 107.32 &  71.44 &   {\bf 65.50}\vspace{3mm}\\
-Prevalence & Indonesia & 0.011 & 0.010 &  0.010\\
+Prevalence & Indonesia & 0.011 & {\bf 0.010} &  {\bf 0.010}\\
 & Senegal & {\bf 0.015} & 0.019 &  0.019\\
@@
 }
-\label{predobsscatter}
+\label{randompredobsscatter}
 \end{figure}
@@
 }
-\label{predobsscatter}
+\label{spatialpredobsscatter}
 \end{figure}
@@
 \end{table}
+
+% Results and Discussion can be combined.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2018-09-28 ms.tex
Minor edits.

@@
 
-Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{ Norm}(0, 0.04)$. 
+Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
 Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of 3, each covariate would be able to predict prevalences between 0.004 and 0.27. 
@@
 Our main performance metric was mean absolute error.
+% Why not correlation
 To assess how well the models are calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.
@@
 
-Maps of the Indonesian input data_and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
+Maps of the Indonesian input data and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
 Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for Senegal show broad agreement with malaria incidence being higher in the South.
@@
 
+%Summarise results
+
+% Discuss and interpret. Generalise
+
+% Short comings
+
+% Future work
+
+% Temporal model
+
+% nonlinearities
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Fig.}
-\label{S1_Fig}
-{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
+%\paragraph*{S1 Fig.}
+%\label{S1_Fig}
+%{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
 
@@
 Thanks everyone.
+
 \nolinenumbers

### 2018-09-28 ms.tex
Add n for all analyses.

@@
 To minimise temporal effects we select, for each country, one year of prevalence survey data and one year of surveillance data.
-For Indonesia we selected 2010 for prevalence data (n = ) and 2012 for surveillance data (n =).
-For Senegal we selected 2015 for both prevalence data (n = ) and surveillance data (n =).
-Finally, for Madagascar we selected 2013 for both prevalence (n = ) and surveillance (n = ) data.
+For Indonesia we selected 2012 for surveillance data ($n = 380$) and 2010 for  prevalence data ($n = 969$).
+For Senegal we selected 2015 for both surveillance data ($n = 46$) and prevalence data ($n = 216$). % update todo
+Finally, for Madagascar we selected 2013 for both surveillance ($n = 110$) and prevalence ($n = 290$) data.
 

### 2018-09-28 ms.tex
Add why we didnot do correlation.

--- 2018-09-28 ms.tex
@@
 To minimise temporal effects we select, for each country, one year of prevalence survey data and one year of surveillance data.
-For Indonesia we selected 2010 for prevalence data (n = ) and 2012 for surveillance data (n =).
-For Senegal we selected 2015 for both prevalence data (n = ) and surveillance data (n =).
-Finally, for Madagascar we selected 2013 for both prevalence (n = ) and surveillance (n = ) data.
+For Indonesia we selected 2012 for surveillance data (380 regions) and 2010 for  prevalence data (969 surveys, 128537 individuals).
+For Senegal we selected 2015 for both surveillance data (46 regions) and prevalence data (216 surveys, 8114). % update todo
+Finally, for Madagascar we selected 2013 for both surveillance (110 regions) and prevalence (290 surveys, 7244 individuals) data.
 
@@
 In the second validation scheme the data was split into spatial cross-validation folds (see Figure~\ref{fig:cv_spatial}).
-The number of folds was seven for Indonesia, seven for Senegal and three for Madagascar due to their differing size and geographies.
-The data was divided by combining the point locations and the centroids of the polygons and performing k means clustering.
+The number of folds was seven for Indonesia, four for Senegal and three for Madagascar due to their differing sizes and geographies.
+The data was divided by combining the point locations and the centroids of the incidence polygons and performing k means clustering.
 This scheme is testing the models' ability to predict into new areas with little information from the spatial random field.
@@
 As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
-Our main performance metric was mean absolute error.
+Our main performance metric was mean absolute error (MAE) for incidence and MAE weighted by survey sample size for prevalence.
+While other metrics could have been used, we specifically did not use correlation as correlation measures linear dependance without regard to slope or intercept.
+As the models are being fitted on data on difference scales we found that predictions were sometimes correlated but strongly displaced from the one-one line and therefore correlation metrics were misleading.
 % Why not correlation
-To assess how well the models are calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.
+To assess how well the models were calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.
 
@@
 
-Maps of the Indonesian input data_and spatially out-of-sample predictions (Figures~\ref{predobsmapidn}A and C) suggest the that the broad spatial patterns were once again recovered.
+Maps of the Indonesian input data and spatially out-of-sample predictions (Figures~\ref{predobsmapidn}A and C) suggest the that the broad spatial patterns were once again recovered.
 This acceptable performance is notable given the very large areas held out-of-sample (Fig~\ref{fig:cv_spatial}).
@@
 Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
-The data were split spatiall into 5 groups.
+The data were split spatially into 7 groups (Indonesia.
 \end{flushleft}
@@
 \hline
-{\bf Holdout data} & {\bf crossvalidation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
+{\bf Holdout data} & {\bf Crossvalidation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
 \thickhline 
@@
 
+% Relative amaounts of data
+
+% Geographies.
+
+% Data size. In spat inc, countries with few polys improve. In random madagascar improves.
+% Senegal points mostly zero. MAtters?
+
+% Clear benefits, when some areas have polygon and some have PR.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-28 ms.tex
Move tables.
First pass at discussion.

@@
 We relate the two malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
-We compare the joint model to two benchmark models, a prevalence-survey only model and an aggregated-incidence disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless}.
+We compare the joint model to an aggregated-incidence disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and a further benchmark model that contains on;y prevalence-survey data.
 As case studies we use data from Indonesia, Senegal and Madagascar as these countries have both good routine surveillance data and good coverage of prevalence point surveys.
@@
 To minimise temporal effects we select, for each country, one year of prevalence survey data and one year of surveillance data.
-For Indonesia we selected 2012 for surveillance data (380 regions) and 2010 for  prevalence data (969 surveys, 128537 individuals).
-For Senegal we selected 2015 for both surveillance data (46 regions) and prevalence data (216 surveys, 8114). % update todo
-Finally, for Madagascar we selected 2013 for both surveillance (110 regions) and prevalence (290 surveys, 7244 individuals) data.
+For Indonesia we selected 2012 for surveillance data (380 regions) and 2010 for  prevalence data (969 surveys, 128,537 individuals).
+For Senegal we selected 2015 for both surveillance data (46 regions) and prevalence data (216 surveys, 8,114). % update todo
+Finally, for Madagascar we selected 2013 for both surveillance (110 regions) and prevalence (290 surveys, 7,244 individuals) data.
 
@@
 The prevalence survey data were extracted from the Malaria Atlas Project prevalence survey database \cite{bhatt2015effect}.
-As the prevalence surveys cover different age ranges they were standardised using the model from \cite{smith2007standardizing}.
+As the prevalence surveys cover different age ranges they were standardised to an age-range of 2--10 using the model from \cite{smith2007standardizing}.
 
@@
 
-We compared three models 1) a full model with prevalence surveys and aggregated incidence data 2) the submodel with only prevalence data and 3) the submodel with only aggregated incidence data. 
+We compared three models 1) a full model with prevalence surveys and aggregated incidence data 2) the submodel with only aggregated incidence data and 3) the benchmark submodel with only prevalence point-survey data.
 The models were implemented and fitted using Template Model Builder \cite{TMB} in R \cite{R}
@@
 Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
-Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of 3, each covariate would be able to predict prevalences between 0.004 and 0.27. 
-This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularised our model.
+Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of -3, each covariate would be able to predict prevalences between 0.004 and 0.27. 
+This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularise our model.
+This regularisation is particularly important given the small number of observations in Senegal (n = 46) and Madagascar (n = 110).
 
@@
 As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
+We considered the ability to predict incidence correctly out main objective.
+However, a problem with using polygon data in a cross-validation scheme is that a model can perform well at the polygon level but not correctly predict the pixel-level malaria risk.
+Predictive performance on prevalence points is one way to measure how well a model can predict pixel-level malaria risk.
+However, in areas of low prevalence, small or moderately sized prevalence surveys can be noisey or unsensitive and so care must be taken when interpreting predictive performance on these data.
 Our main performance metric was mean absolute error (MAE) for incidence and MAE weighted by survey sample size for prevalence.
@@
 
-The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both Senegal (0.015) and  Madagascar (0.054) while the wighted MAE was the same for all three models in Indonesia (0.010) (Table~\ref{table1}).
-The more pertinent comparison is whether the addition of the prevalence data improves the ability of the disaggregation models to predict pixel level prevalence.
-However, weighted MAE was unchanged between the polygon model and the joint model for Indonesia (0.010), Senegal (0.024) or Madagascar (0.059).
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and Senegal.
-
-Maps of the Indonesian input data and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
-Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for Senegal show broad agreement with malaria incidence being higher in the South.
-
-% Spatial results
-% Maps, reasonable for india, get's broad pattern even far away from data. Poor for SEN, wrong overall pattern. Different covariates.
-% MAE performance.
-
-For the spatial cross-validation experiments, the polygon-only model again had the lowest mean absolute error between observed and predicted incidence for Indonesia (14.77) (Table~\ref{table2}).
-However, for both Senegal (36.76) and Madagascar (65.50) the joint model had the best predictive performance.
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{spatialpredobsscatter}A, C and E.
-
-Again, the benchmark points-only model had the lowest weighted MAE between spatially cross-validated observed and predicted prevalence for Senegal (0.015).
-However, for Indonesia, both the disaggration models marginally outperformed the points-only model (polygons-only 0.010, joint model 0.010). 
-For Senegal, the joint model (0.065) had the lowest weighted MAE for predicted prevalence though this was again marginal (points-only 0.069, polygons-only 0.066).
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and Senegal.
-
-Maps of the Indonesian input data and spatially out-of-sample predictions (Figures~\ref{predobsmapidn}A and C) suggest the that the broad spatial patterns were once again recovered.
-This acceptable performance is notable given the very large areas held out-of-sample (Fig~\ref{fig:cv_spatial}).
-For example, the whole of Papua and West Papua the the East are held out in a single fold.
-In contrast the predictions for Senegal do not match those observed in the input data (Figures~\ref{predobsmapsen}A and C).
-
-% Coverage results
-
-The polygon-only model and the joint model seem to be fairly well calibrated.
-The proportion of out-of-sample incidence datapoints being within their 80\% credible intervals ranged between 0.65 and 0.85.
-The proportion of out-of-sample prevalence datapoints being within their 80\% credible intervals ranged from 0.50 to 0.96.
-The points only model was reasonably well calibrated for predictions of prevalence (coverage ranging from 0.8 to 0.93) but was poorly calibrated for predicting incidence with coverage values as low as 0.11 and the best coverage value being 0.68 for spatial crossvalidation in Madagascar.
-
-% Overall
-
-%figure 3 and 4. data and predicted incidence maps. Indonesia and Senegal only. Fig 3 ind, fig 4 rand. Data, Rand, Spatial for best model? Joint model?
-
-\begin{figure}[!h]
-% to be removed before submission
-\includegraphics[width = 0.9\textwidth]{figures/idn_both_cv12_preds.png}
-\caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
-The values plotted for areas with no polygon data are the means across all cross-validation folds.
-}
-\label{predobsmapidn}
-\end{figure}
-
-\begin{figure}[!h]
-% to be removed before submission
-\includegraphics[width = 0.9\textwidth]{figures/sen_both_cv12_preds.png}
-\caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
-}
-\label{predobsmapsen}
-\end{figure}
-
 \begin{table}[!ht]
@@
 \caption{
-{\bf Summary of out-of-sample accuracy for random crossvalidation experiment.}}
+{\bf Summary of out-of-sample accuracy for random cross-validation experiment.}}
 \begin{tabular}{llllll}
@@
 \caption{
-{\bf Summary of out-of-sample accuracy for spatial crossvalidation experiment.}}
+{\bf Summary of out-of-sample accuracy for spatial cross-validation experiment.}}
 \begin{tabular}{llllll}
@@
 Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
-The data were split spatially into 7 groups (Indonesia.
+The data were split into seven, four and three groups in Indonesia, Senegal and Madagascar respectively.
 \end{flushleft}
@@
 
+The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both Senegal (0.015) and  Madagascar (0.054) while the wighted MAE was the same for all three models in Indonesia (0.010) (Table~\ref{table1}).
+The more pertinent comparison is whether the addition of the prevalence data improves the ability of the disaggregation models to predict pixel level prevalence.
+However, weighted MAE was unchanged between the polygon model and the joint model for Indonesia (0.010), Senegal (0.024) or Madagascar (0.059).
+Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and Senegal.
+
+Maps of the Indonesian input data and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
+Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for Senegal show broad agreement with malaria incidence being higher in the South.
+
+% Further results. Accuracy or recall of Sen. Correlation for some?
+
+% Spatial results
+% Maps, reasonable for india, get's broad pattern even far away from data. Poor for SEN, wrong overall pattern. Different covariates.
+% MAE performance.
+
+For the spatial cross-validation experiments, the polygon-only model again had the lowest mean absolute error between observed and predicted incidence for Indonesia (14.77) (Table~\ref{table2}).
+However, for both Senegal (36.76) and Madagascar (65.50) the joint model had the best predictive performance.
+Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{spatialpredobsscatter}A, C and E.
+
+Again, the benchmark points-only model had the lowest weighted MAE between spatially cross-validated observed and predicted prevalence for Senegal (0.015).
+However, for Indonesia, both the disaggration models marginally outperformed the points-only model (polygons-only 0.010, joint model 0.010). 
+For Senegal, the joint model (0.065) had the lowest weighted MAE for predicted prevalence though this was again marginal (points-only 0.069, polygons-only 0.066).
+Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and Senegal.
+
+Maps of the Indonesian input data and spatially out-of-sample predictions (Figures~\ref{predobsmapidn}A and C) suggest the that the broad spatial patterns were once again recovered.
+This acceptable performance is notable given the very large areas held out-of-sample (Fig~\ref{fig:cv_spatial}).
+For example, the whole of Papua and West Papua the the East are held out in a single fold.
+In contrast the predictions for Senegal do not match those observed in the input data (Figures~\ref{predobsmapsen}A and C).
+
+% Coverage results
+
+The polygon-only model and the joint model seem to be fairly well calibrated (Table~\ref{table3}).
+The proportion of out-of-sample incidence datapoints being within their 80\% credible intervals ranged between 0.65 and 0.85.
+The proportion of out-of-sample prevalence datapoints being within their 80\% credible intervals ranged from 0.50 to 0.96.
+The points only model was reasonably well calibrated for predictions of prevalence (coverage ranging from 0.8 to 0.93) but was poorly calibrated for predicting incidence with coverage values as low as 0.11 and the best coverage value being 0.68 for spatial cross-validation in Madagascar.
+With respect to uncertainty in incidence predictions, the polygon-only model and joint model were similar; adding the points sometimes improved coverage and sometimes made it worse.
+However, with respect to uncertainty in prevalence predictions, the coverage was substantially improved in three of six cases and marginally improved in one case.
+Coverage improved in the random cross-validation in Indonesia (polygon-only 0.50, joint 0.80) and Madagascar (polygon-only 0.53, joint 0.74) and spatial cross-validation in Madagascar (polygon-only 0.68, joint 0.83) and marginally improved in the spatial cross-validation in Senegal (polygon-only 0.88, joint 0.79).
+In the remaining two cases, adding points did not substantially improve coverage, but did make the model more conservative, with coverage of 0.91 rather than 0.71 in the random cross-validation Senegal experiment and 0.96 instead of 0.62 in the spatial cross-validation Indonesia experiment.
+
+% Overall
+
+%figure 3 and 4. data and predicted incidence maps. Indonesia and Senegal only. Fig 3 ind, fig 4 rand. Data, Rand, Spatial for best model? Joint model?
+
+\begin{figure}[!t]
+% to be removed before submission
+\includegraphics[width = 0.9\textwidth]{figures/idn_both_cv12_preds.png}
+\caption{{\bf Input incidence data and predicted incidence maps. } 
+The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
+The values plotted for areas with no polygon data are the means across all cross-validation folds.
+}
+\label{predobsmapidn}
+\end{figure}
+
+\begin{figure}[!t]
+% to be removed before submission
+\includegraphics[width = 0.9\textwidth]{figures/sen_both_cv12_preds.png}
+\caption{{\bf Input incidence data and predicted incidence maps. } 
+The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
+}
+\label{predobsmapsen}
+\end{figure}
+
 %figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
-\begin{figure}[!h]
+\begin{figure}[!t]
 % to be removed before submission
@@
 %figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
-\begin{figure}[!h]
+\begin{figure}[!t]
 % to be removed before submission
@@
 
-\begin{table}[!ht]
+\begin{table}[!t]
 \begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
@@
 \hline
-{\bf Holdout data} & {\bf Crossvalidation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
+{\bf Holdout data} & {\bf Cross-validation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
 \thickhline 
@@
 
+We have compared the predictive performance of a disaggration model and a model that jointly learns from aggregated incidence data and point prevalence surveys.
+With regards to a random cross-validation scheme, adding points to the disaggregation model improved performance in one of three countries (Madagascar).
+With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the point surveys improved the disaggregation models in both Senegal and Madagascar.
+
+A problem with using cross-validation on polygon data is that models can correctly predict polygon-level incidence while incorrectly predicting the within-polygon, pixel-level risk.
+Of the four cases where polygon predictions were improved or similar (Indonesia and Madagascar random cross-validation and Senegal and Madagascar spatial cross validation) the predictive performance on prevalence points was always unchanged or marginally improved.
+However, the points only model was the top or equal top model at predicting point level prevalence in four out of six cases and only marginally worse in one further case.
+Only in the Madagascar, spatial cross-validation experiment was the points-only model notably worse at predicting prevalence.
+
 % Discuss and interpret. Generalise
 
-% Short comings
-
-% Future work
-
-% Temporal model
-
-% nonlinearities
-
-% Relative amaounts of data
-
-% Geographies.
-
-% Data size. In spat inc, countries with few polys improve. In random madagascar improves.
-% Senegal points mostly zero. MAtters?
+The joint model improved the prediction of incidence in two of three countries under the spatial cross-validation scheme but only one country in the random cross-validation scheme.
+Furthermore, in the spatial cross-validation scheme, the two countries where performance was improved by using the joint model are the two countries with the least data.
+The joint model seems to be helping in the cases where predictions have little information from the random field and when there is little data to estimate regression parameters.
+In contrast, the joint model does not in general improve on the polygon-only model in the random cross-validation scheme.
+A noticable element of this scheme was that locations where polygon data was removed for validation could still potentially have prevalence data.
+Figure~\ref{fig:cv_random} implies that this situation is the norm.
+Yes this spatial information did not improve performance in Indonesia or Senegal.
 
 % Clear benefits, when some areas have polygon and some have PR.
+%   Where?
+
+There are large potential benefits to models that combine data in the context of large scale studies over multiple countries.
+In these cases there is often different data types in different countries and being able to make malaria estimates of the countries together increases spatial coverage and statistical power.
+Further cases where this joint model may be particularly beneficial is in countries where prevalence surveys are strongly clustered in one area --- typically an area of high malaria risk --- but without high resolution surveillance data.
+In these regions, fitting a model on just the points requires predictions far away from the survey locations whlie fitting a model just on the surveillance data will be underpowered.
+
+However, the benefits of these methods do not come for free, as indicated by the reduced performance in some cases.
+Two main aspects of prevalence point data have the potential to reduce the predictive ability of a polygon-only model.
+Firstly, the data are on a difference scale.
+Here we have used a previously fitted model \cite{cameron2015defining} in order to be able to fit the joint model.
+However, this model is imperfect in that it is calibrated with a relatively small amount of matched prevalence and incidence data.
+Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, nutrition and health care will be different.
+In using a joint model we are accepting these failings in the hope that the benefits of including additional data are stronger than the costs of using mismatched data.
+The second aspect of prevalence point data that could reduce the predictive ability of a polygon-only model by adding point data is if the point data is of low quality.
+In particular, non-random sampling of individuals can produce biased estimates of prevalence and this will decrease model performance.
+In countries with lots of high quality, high resolution incidence data, the potential benefits of including point data in the model are reduced while the potential costs remain.
+
+For a model to be robust to shortcomings in the prevalence-incidence relationship from \cite{cameron2015defining}, future models could be more flexible in the way they use this relationship.
+This could be by estimating the parameters of the polynomial jointly with the rest of the model.
+Informative priors based on the original model should be used to regularise this joint fit both to prevent unbelievable inferences but also because if the relationship is too flexible, the information from the prevalence data might not be used by the incidence level model.
+This is particularly true for even more flexible model forms that could be used such as a spline or a Gaussian process on the relationship between prevalence and incidence.
+
+For the model to handle noisey or biased prevalence data points, the modeller can control the iid random effect on the point surveys, $w_i$. 
+Here we have tried to maximise the influence of the prevalence data by setting the prior based on the belief that the random effect should only explain extra-binomial variation that is impossible to explain with the covariates (i.e.
+based on the differences in prevalence surveys within the same pixel).
+Weakening this prior will allow the iid effect to explain more of the point survey variation which both reduces the potential statistical power gained by adding the point data but also reduces the effects of biased or noisey estimates.
+
+In order to specifically compare the affects of combining the data types, we have aimed to keep the models fitted here as simple as possible.
+However, a number of improvements could be made.
+Data from multiple years are available for many countries.
+Simply combining data collected at different times is not recommended as malaria incidence is changing rapidly.
+However, fitting a full spatio-temporal model would be a suitable way to combine data from different periods but would be computationally more expensive.
+This is an avenue of work that should be pursued.
+Furthermore, it has been clearly established that simple linear combinations of environmental covariates cannot fully explain malaria risk \cite{bhatt2017improved}.
+A number of methods could be used to include non-linear effects of covariates and interactions into the model.
+Firstly, as in \cite{bhatt2017improved}, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model.
+This approach is feasible but does not allow any information from the polygons to inform non-linear relationships.
+To directly model non-linear effects in the full model could be achieved by including simple non-linear functions such as splines, though the increased model complexity would require more data than was used in Senegal and Madagascar in this study.
+Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \cite{law2018variational}.
+These are computational expensive without careful approximations via variational Bayes or other approximations.
+Again these models need a lot of data and careful regularisation for good predictive performance.
 

### 2018-10-01 ms.tex
Add ros as an author.

@@
 Tim C.D.
-Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Dan Weiss\textsuperscript{1},
+Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Rosalind Howes \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Dan Weiss\textsuperscript{1},
 \\

### 2018-10-01 ms.tex
Add TMB integration and empirical bayes details.

@@
 We compared three models 1) a full model with prevalence surveys and aggregated incidence data 2) the submodel with only aggregated incidence data and 3) the benchmark submodel with only prevalence point-survey data.
-The models were implemented and fitted using Template Model Builder \cite{TMB} in R \cite{R}
+The models were implemented and fitted in R \cite{R} using Template Model Builder \cite{TMB} which allows a Laplace approximation of the posterior to be calculated.
 
@@
 However, it is included in predictions of out-of-sample point surveys.
+The randoms effects are all integrated out during the TMB model fitting.
+The hyperparameters are fitted during model fitting using empirical Bayes.
+In this empirical Bayes scheme the hyperparameters are learned from the data but are treated as point estimates rather than the model using the full posterior of the hyperparameters.
 

### 2018-10-01 ms.tex
Some attempted to help model definition.

@@
 We compare the joint model to an aggregated-incidence disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and a further benchmark model that contains on;y prevalence-survey data.
-As case studies we use data from Indonesia, Senegal and Madagascar as these countries have both good routine surveillance data and good coverage of prevalence point surveys.
+As case studies we use data from Indonesia, PseudoSenegal and Madagascar as these countries have both good routine surveillance data and good coverage of prevalence point surveys.
 
@@
 We used two data sources that reflect malaria burden; point prevalence surveys and polygon-level, aggregated incidence data.
-We selected Indonesia, Senegal and Madagascar as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
+We selected Indonesia, PseudoSenegal and Madagascar as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
 To minimise temporal effects we select, for each country, one year of prevalence survey data and one year of surveillance data.
 For Indonesia we selected 2012 for surveillance data (380 regions) and 2010 for  prevalence data (969 surveys, 128,537 individuals).
-For Senegal we selected 2015 for both surveillance data (46 regions) and prevalence data (216 surveys, 8,114). % update todo
+For PseudoSenegal we selected 2015 for both surveillance data (46 regions) and prevalence data (216 surveys, 8,114). % update todo
 Finally, for Madagascar we selected 2013 for both surveillance (110 regions) and prevalence (290 surveys, 7,244 individuals) data.
@@
 
-$$i_a = \frac{ \sum(i_b \mathrm{pop}_b)}{\sum  \mathrm{pop}_b} $$
+$$i_a = \frac{ \sum_{b \in a}(i_b \mathrm{pop}_b)}{\sum_{b \in a}\mathrm{pop}_b} $$
 
-$$i_b = \mathrm{p2i}(p_b)$$
+where
 
-where $\mathrm{p2i}$ is a function from a previously fitted model \cite{cameron2015defining} 
-$$\mathrm{p2i}: f\left(P\right) = 2.616P - 3.596P^2 + 1.594P^3.$$
+$$i_b = \mathrm{PrevInc}(p_b)$$
+
+where $\mathrm{PrevInc}$ is a function from a previously fitted model \cite{cameron2015defining} 
+$$\mathrm{PrevInc}: f\left(p_b\right) = 2.616p_b - 3.596{p_b}^2 + 1.594{p_b}^3.$$
 
@@
 We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
-We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = 1$ and Madagascar $\zeta = 1$.
+We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, PseudoSenegal $\zeta = 1$ and Madagascar $\zeta = 1$.
 We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \cite{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.
@@
 This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularise our model.
-This regularisation is particularly important given the small number of observations in Senegal (n = 46) and Madagascar (n = 110).
+This regularisation is particularly important given the small number of observations in PseudoSenegal (n = 46) and Madagascar (n = 110).
 
@@
 
-\caption{{\bf Random cross-validation scheme for Indonesia, Senegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+\caption{{\bf Random cross-validation scheme for Indonesia, PseudoSenegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
 \label{fig:cv_random}
@@
 
-\caption{{\bf Spatial cross-validation scheme for Indonesia, Senegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+\caption{{\bf Spatial cross-validation scheme for Indonesia, PseudoSenegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
 \label{fig:cv_spatial}
@@
 In the second validation scheme the data was split into spatial cross-validation folds (see Figure~\ref{fig:cv_spatial}).
-The number of folds was seven for Indonesia, four for Senegal and three for Madagascar due to their differing sizes and geographies.
+The number of folds was seven for Indonesia, four for PseudoSenegal and three for Madagascar due to their differing sizes and geographies.
 The data was divided by combining the point locations and the centroids of the incidence polygons and performing k means clustering.
@@
 Predictive performance on prevalence points is one way to measure how well a model can predict pixel-level malaria risk.
-However, in areas of low prevalence, small or moderately sized prevalence surveys can be noisey or unsensitive and so care must be taken when interpreting predictive performance on these data.
+However, in areas of low prevalence, small or moderately sized prevalence surveys can be noisy or unsensitive and so care must be taken when interpreting predictive performance on these data.
 Our main performance metric was mean absolute error (MAE) for incidence and MAE weighted by survey sample size for prevalence.
@@
 
-For the random cross-validation experiments, the polygon-only model had the lowest mean absolute error, with respect to predicting incidence, for Indonesia (14.02) and Senegal (26.74) (Table~\ref{table1}).
+For the random cross-validation experiments, the polygon-only model had the lowest mean absolute error, with respect to predicting incidence, for Indonesia (14.02) and PseudoSenegal (26.74) (Table~\ref{table1}).
 Incidence in Madagascar was best predicted by the join model (34.49).
@@
 Incidence & Indonesia & 18.33 & {\bf 14.02} &  14.09\\
-& Senegal & 51.24 & {\bf 26.74} &  28.45\\
+& PseudoSenegal & 51.24 & {\bf 26.74} &  28.45\\
 & Madagascar & 85.54 & 37.45 &  {\bf 34.49}\vspace{3mm}\\
 Prevalence & Indonesia & 0.010 & 0.010 &  0.010\\
-& Senegal & {\bf 0.015} & 0.024 &  0.024\\
+& PseudoSenegal & {\bf 0.015} & 0.024 &  0.024\\
 & Madagascar & {\bf 0.054} & 0.059 &  0.059\\
@@
 Incidence & Indonesia &  18.13 &  {\bf 14.77} &   15.02\\
-& Senegal &  51.17 &  41.43 &   {\bf 36.76}\\
+& PseudoSenegal &  51.17 &  41.43 &   {\bf 36.76}\\
 & Madagascar & 107.32 &  71.44 &   {\bf 65.50}\vspace{3mm}\\
 Prevalence & Indonesia & 0.011 & {\bf 0.010} &  {\bf 0.010}\\
-& Senegal & {\bf 0.015} & 0.019 &  0.019\\
+& PseudoSenegal & {\bf 0.015} & 0.019 &  0.019\\
 & Madagascar & 0.069 & 0.066 &  {\bf 0.065}\\
@@
 Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
-The data were split into seven, four and three groups in Indonesia, Senegal and Madagascar respectively.
+The data were split into seven, four and three groups in Indonesia, PseudoSenegal and Madagascar respectively.
 \end{flushleft}
@@
 
-The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both Senegal (0.015) and  Madagascar (0.054) while the wighted MAE was the same for all three models in Indonesia (0.010) (Table~\ref{table1}).
+The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both PseudoSenegal (0.015) and  Madagascar (0.054) while the wighted MAE was the same for all three models in Indonesia (0.010) (Table~\ref{table1}).
 The more pertinent comparison is whether the addition of the prevalence data improves the ability of the disaggregation models to predict pixel level prevalence.
-However, weighted MAE was unchanged between the polygon model and the joint model for Indonesia (0.010), Senegal (0.024) or Madagascar (0.059).
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and Senegal.
+However, weighted MAE was unchanged between the polygon model and the joint model for Indonesia (0.010), PseudoSenegal (0.024) or Madagascar (0.059).
+Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and PseudoSenegal.
 
 Maps of the Indonesian input data and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
-Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for Senegal show broad agreement with malaria incidence being higher in the South.
+Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for PseudoSenegal show broad agreement with malaria incidence being higher in the South.
 
@@
 For the spatial cross-validation experiments, the polygon-only model again had the lowest mean absolute error between observed and predicted incidence for Indonesia (14.77) (Table~\ref{table2}).
-However, for both Senegal (36.76) and Madagascar (65.50) the joint model had the best predictive performance.
+However, for both PseudoSenegal (36.76) and Madagascar (65.50) the joint model had the best predictive performance.
 Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{spatialpredobsscatter}A, C and E.
 
-Again, the benchmark points-only model had the lowest weighted MAE between spatially cross-validated observed and predicted prevalence for Senegal (0.015).
+Again, the benchmark points-only model had the lowest weighted MAE between spatially cross-validated observed and predicted prevalence for PseudoSenegal (0.015).
 However, for Indonesia, both the disaggration models marginally outperformed the points-only model (polygons-only 0.010, joint model 0.010). 
-For Senegal, the joint model (0.065) had the lowest weighted MAE for predicted prevalence though this was again marginal (points-only 0.069, polygons-only 0.066).
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and Senegal.
+For PseudoSenegal, the joint model (0.065) had the lowest weighted MAE for predicted prevalence though this was again marginal (points-only 0.069, polygons-only 0.066).
+Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and PseudoSenegal.
 
@@
 For example, the whole of Papua and West Papua the the East are held out in a single fold.
-In contrast the predictions for Senegal do not match those observed in the input data (Figures~\ref{predobsmapsen}A and C).
+In contrast the predictions for PseudoSenegal do not match those observed in the input data (Figures~\ref{predobsmapsen}A and C).
 
@@
 However, with respect to uncertainty in prevalence predictions, the coverage was substantially improved in three of six cases and marginally improved in one case.
-Coverage improved in the random cross-validation in Indonesia (polygon-only 0.50, joint 0.80) and Madagascar (polygon-only 0.53, joint 0.74) and spatial cross-validation in Madagascar (polygon-only 0.68, joint 0.83) and marginally improved in the spatial cross-validation in Senegal (polygon-only 0.88, joint 0.79).
-In the remaining two cases, adding points did not substantially improve coverage, but did make the model more conservative, with coverage of 0.91 rather than 0.71 in the random cross-validation Senegal experiment and 0.96 instead of 0.62 in the spatial cross-validation Indonesia experiment.
+Coverage improved in the random cross-validation in Indonesia (polygon-only 0.50, joint 0.80) and Madagascar (polygon-only 0.53, joint 0.74) and spatial cross-validation in Madagascar (polygon-only 0.68, joint 0.83) and marginally improved in the spatial cross-validation in PseudoSenegal (polygon-only 0.88, joint 0.79).
+In the remaining two cases, adding points did not substantially improve coverage, but did make the model more conservative, with coverage of 0.91 rather than 0.71 in the random cross-validation PseudoSenegal experiment and 0.96 instead of 0.62 in the spatial cross-validation Indonesia experiment.
 
@@
 
-%figure 3 and 4. data and predicted incidence maps. Indonesia and Senegal only. Fig 3 ind, fig 4 rand. Data, Rand, Spatial for best model? Joint model?
+%figure 3 and 4. data and predicted incidence maps. Indonesia and PseudoSenegal only. Fig 3 ind, fig 4 rand. Data, Rand, Spatial for best model? Joint model?
 
@@
 \caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
+The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for PseudoSenegal.
 }
@@
 \caption{{\bf Observed-predicted plots for random cross-validation experiments.}
-A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
+A-B) Indonesia, C-D) PseudoSenegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
 Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
@@
 \caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
-A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
+A-B) Indonesia, C-D) PseudoSenegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
 Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
@@
 Incidence & Random & Indonesia & 0.13 & 0.72 &  0.73\\
-&& Senegal & 0.11 & 0.80 &  0.85\\
+&& PseudoSenegal & 0.11 & 0.80 &  0.85\\
 && Madagascar & 0.59 & 0.82 &  0.77\vspace{1mm}\\
 & Spatial & Indonesia & 0.14 & 0.76 &  0.68\\
-&& Senegal & 0.30 & 0.67 &  0.70\\
+&& PseudoSenegal & 0.30 & 0.67 &  0.70\\
 && Madagascar & 0.68 & 0.65 &  0.68\vspace{3mm} \\
 Prevalence & Random & Indonesia & 0.90 & 0.50 &  0.80\\
-&& Senegal & 0.80 & 0.71 &  0.91\\
+&& PseudoSenegal & 0.80 & 0.71 &  0.91\\
 && Madagascar & 0.83 & 0.53 &  0.74\vspace{1mm}\\
 & Spatial & Indonesia & 0.87 & 0.62 &  0.96\\
-&& Senegal & 0.90 & 0.88 &  0.79\\
+&& PseudoSenegal & 0.90 & 0.88 &  0.79\\
 && Madagascar & 0.93 & 0.68 &  0.83\\
@@
 With regards to a random cross-validation scheme, adding points to the disaggregation model improved performance in one of three countries (Madagascar).
-With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the point surveys improved the disaggregation models in both Senegal and Madagascar.
+With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the point surveys improved the disaggregation models in both PseudoSenegal and Madagascar but not Indonesia.
 
-A problem with using cross-validation on polygon data is that models can correctly predict polygon-level incidence while incorrectly predicting the within-polygon, pixel-level risk.
-Of the four cases where polygon predictions were improved or similar (Indonesia and Madagascar random cross-validation and Senegal and Madagascar spatial cross validation) the predictive performance on prevalence points was always unchanged or marginally improved.
+A problem with using cross-validation on polygon data is that a model could correctly predict polygon-level incidence while incorrectly predicting the within-polygon, pixel-level risk which is the real target of inference.
+Of the four cases where polygon predictions were improved or similar (Indonesia and Madagascar random cross-validation and PseudoSenegal and Madagascar spatial cross validation) the predictive performance on prevalence points was always unchanged or marginally improved.
 However, the points only model was the top or equal top model at predicting point level prevalence in four out of six cases and only marginally worse in one further case.
@@
 Figure~\ref{fig:cv_random} implies that this situation is the norm.
-Yes this spatial information did not improve performance in Indonesia or Senegal.
+Yes this spatial information did not improve performance in Indonesia or PseudoSenegal.
 
@@
 
-For the model to handle noisey or biased prevalence data points, the modeller can control the iid random effect on the point surveys, $w_i$. 
+For the model to handle noisy or biased prevalence data points, the modeller can control the iid random effect on the point surveys, $w_i$. 
 Here we have tried to maximise the influence of the prevalence data by setting the prior based on the belief that the random effect should only explain extra-binomial variation that is impossible to explain with the covariates (i.e.
 based on the differences in prevalence surveys within the same pixel).
-Weakening this prior will allow the iid effect to explain more of the point survey variation which both reduces the potential statistical power gained by adding the point data but also reduces the effects of biased or noisey estimates.
+Weakening this prior will allow the iid effect to explain more of the point survey variation which both reduces the potential statistical power gained by adding the point data but also reduces the effects of biased or noisy estimates.
 
@@
 This approach is feasible but does not allow any information from the polygons to inform non-linear relationships.
-To directly model non-linear effects in the full model could be achieved by including simple non-linear functions such as splines, though the increased model complexity would require more data than was used in Senegal and Madagascar in this study.
+To directly model non-linear effects in the full model could be achieved by including simple non-linear functions such as splines, though the increased model complexity would require more data than was used in PseudoSenegal and Madagascar in this study.
 Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \cite{law2018variational}.

### 2018-10-01 ms.tex
Add some refs to discussion.

@@
 
-The polygon level surveillance data were collated from various government reports (Figures~\ref{predobsmapidn}A and \ref{predobsmapsen}A).
+% (Figures~\ref{predobsmapidn}A and \ref{predobsmapsen}A)
+
+The polygon level surveillance data were collated from various government reports.
 To account for underreporting of clinical cases due to lack of treatment seeking, missed case reports and cases that sought medical attention outside the public health systems, the methods in \cite{cibulskis2011worldwide} were used using estimates of treatment seeking from \cite{battle2016treatment}.
@@
 For the random cross-validation experiments, the polygon-only model had the lowest mean absolute error, with respect to predicting incidence, for Indonesia (14.02) and PseudoSenegal (26.74) (Table~\ref{table1}).
-Incidence in Madagascar was best predicted by the join model (34.49).
+Incidence in Madagascar was best predicted by the joint model (34.49).
 However, the difference between the two models in Indonesia was small (polygons-only 14.02, joint model 14.09).
@@
 A problem with using cross-validation on polygon data is that a model could correctly predict polygon-level incidence while incorrectly predicting the within-polygon, pixel-level risk which is the real target of inference.
-Of the four cases where polygon predictions were improved or similar (Indonesia and Madagascar random cross-validation and PseudoSenegal and Madagascar spatial cross validation) the predictive performance on prevalence points was always unchanged or marginally improved.
-However, the points only model was the top or equal top model at predicting point level prevalence in four out of six cases and only marginally worse in one further case.
+Of the four cases where polygon predictions were improved or remained similar after adding point data (Indonesia and Madagascar random cross-validation and PseudoSenegal and Madagascar spatial cross validation) the predictive performance on prevalence points was always unchanged or marginally improved.
+However, the benchmark points-only model was the top or equal top model at predicting point level prevalence in four out of six cases and only marginally worse in one further case.
 Only in the Madagascar, spatial cross-validation experiment was the points-only model notably worse at predicting prevalence.
@@
 The joint model improved the prediction of incidence in two of three countries under the spatial cross-validation scheme but only one country in the random cross-validation scheme.
-Furthermore, in the spatial cross-validation scheme, the two countries where performance was improved by using the joint model are the two countries with the least data.
-The joint model seems to be helping in the cases where predictions have little information from the random field and when there is little data to estimate regression parameters.
+The two countries where the joint model performed best in the spatial cross-validation scheme are the two countries with the least data.
+The joint model seemed to perform comparatively well in the cases where predictions had little information from the random field and when there is little data to estimate regression parameters.
+Far-from-data predictions are particularly susceptible to overfitting.
+Given the simple linear model, adding prevalence data may protect against overfitting simply by increasing the amount of data available.
+Alternatively, a model that learns from two datasets, on different scales, with different biases, is also less likely to overfit.
+
 In contrast, the joint model does not in general improve on the polygon-only model in the random cross-validation scheme.
@@
 Figure~\ref{fig:cv_random} implies that this situation is the norm.
-Yes this spatial information did not improve performance in Indonesia or PseudoSenegal.
+Yet this spatial information did not improve performance in Indonesia or PseudoSenegal.
 
@@
 
-There are large potential benefits to models that combine data in the context of large scale studies over multiple countries.
-In these cases there is often different data types in different countries and being able to make malaria estimates of the countries together increases spatial coverage and statistical power.
-Further cases where this joint model may be particularly beneficial is in countries where prevalence surveys are strongly clustered in one area --- typically an area of high malaria risk --- but without high resolution surveillance data.
-In these regions, fitting a model on just the points requires predictions far away from the survey locations whlie fitting a model just on the surveillance data will be underpowered.
-
-However, the benefits of these methods do not come for free, as indicated by the reduced performance in some cases.
-Two main aspects of prevalence point data have the potential to reduce the predictive ability of a polygon-only model.
-Firstly, the data are on a difference scale.
+There are two main reasons why a model fitted jointly on prevalence and polygon incidence data may perform worse than a polygon-only mode.
+Firstly, the data are on difference scales.
 Here we have used a previously fitted model \cite{cameron2015defining} in order to be able to fit the joint model.
 However, this model is imperfect in that it is calibrated with a relatively small amount of matched prevalence and incidence data.
-Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, nutrition and health care will be different.
+Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality and age-structure are not constant \cite{cameron2015defining, battle2015defining,reiner2015seasonality}.
 In using a joint model we are accepting these failings in the hope that the benefits of including additional data are stronger than the costs of using mismatched data.
@@
 In particular, non-random sampling of individuals can produce biased estimates of prevalence and this will decrease model performance.
-In countries with lots of high quality, high resolution incidence data, the potential benefits of including point data in the model are reduced while the potential costs remain.
 
@@
 
+There are large potential benefits to models that combine data in the context of large scale studies over multiple countries.
+In these cases there is often different data types in different countries and being able to make malaria estimates of the countries together increases spatial coverage and statistical power.
+Further cases where this joint model may be particularly beneficial is in countries where prevalence surveys are strongly clustered in one area --- typically an area of high malaria risk --- but without high resolution surveillance data.
+In these regions, fitting a model on just the points requires predictions far away from the survey locations whlie fitting a model just on the surveillance data will be underpowered. 
+However, the benefits of these methods do not come for free, as indicated by the reduced performance in some cases.
+
 In order to specifically compare the affects of combining the data types, we have aimed to keep the models fitted here as simple as possible.
@@
 Simply combining data collected at different times is not recommended as malaria incidence is changing rapidly.
-However, fitting a full spatio-temporal model would be a suitable way to combine data from different periods but would be computationally more expensive.
+However, fitting a full spatio-temporal model would be a suitable way to combine data from different periods but would be computationally more expensive \cite{bhatt2015effect, taylor2017continuous}.
 This is an avenue of work that should be pursued.
@@
 This approach is feasible but does not allow any information from the polygons to inform non-linear relationships.
-To directly model non-linear effects in the full model could be achieved by including simple non-linear functions such as splines, though the increased model complexity would require more data than was used in PseudoSenegal and Madagascar in this study.
+To directly model non-linear effects in the full model could be achieved by including simple non-linear functions such as splines \cite{sissoko2017temporal, sewe2017using, hundessa2018projecting}, though the increased model complexity would require more data than was used in PseudoSenegal and Madagascar in this study.
 Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \cite{law2018variational}.

### 2018-10-01 ms.tex
Add an internal glossary.

@@
 
+% Glossary
+% Models:
+%   Joint model
+%   Polygon-only model
+%   Point-only model
+% Data:
+%   Prevalence point-surveys
+%   Polygon incidence
+% Variables:
+%   Pixel-level prevalence
+%   Polygon-level incidence
+%   Pixel-level incidence
+
 Global malaria incidence has decreased dramatically over the last 20 years \cite{abajobir2017global, bhatt2015effect}.
@@
 As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
-We considered the ability to predict incidence correctly out main objective.
+We considered the ability to predict aggregated incidence correctly our main objective and our performance metric was mean absolute error (MAE)..
 However, a problem with using polygon data in a cross-validation scheme is that a model can perform well at the polygon level but not correctly predict the pixel-level malaria risk.
@@
 However, in areas of low prevalence, small or moderately sized prevalence surveys can be noisy or unsensitive and so care must be taken when interpreting predictive performance on these data.
-Our main performance metric was mean absolute error (MAE) for incidence and MAE weighted by survey sample size for prevalence.
+Therefore our secondary metric was, MAE weighted by survey sample size, of prevalence point surveys.
 While other metrics could have been used, we specifically did not use correlation as correlation measures linear dependance without regard to slope or intercept.
@@
 We have compared the predictive performance of a disaggration model and a model that jointly learns from aggregated incidence data and point prevalence surveys.
-With regards to a random cross-validation scheme, adding points to the disaggregation model improved performance in one of three countries (Madagascar).
-With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the point surveys improved the disaggregation models in both PseudoSenegal and Madagascar but not Indonesia.
+We found that neither model was clearly superior to the other but that both models recovered the broad spatial pattern of malaria risk (Figures \ref{predobsmapidn} and \ref{predobsmapidn}).
+With regards to a random cross-validation scheme, adding points to the disaggregation model only improved performance in  Madagascar (Table~\ref{table1}).
+With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the point surveys improved the disaggregation models in both PseudoSenegal and Madagascar but not Indonesia  (Table~\ref{table2}).
 
-A problem with using cross-validation on polygon data is that a model could correctly predict polygon-level incidence while incorrectly predicting the within-polygon, pixel-level risk which is the real target of inference.
-Of the four cases where polygon predictions were improved or remained similar after adding point data (Indonesia and Madagascar random cross-validation and PseudoSenegal and Madagascar spatial cross validation) the predictive performance on prevalence points was always unchanged or marginally improved.
-However, the benchmark points-only model was the top or equal top model at predicting point level prevalence in four out of six cases and only marginally worse in one further case.
+We used held-out prevalence point-surveys to measure how well model were predicting the within-polygon, pixel-level malaria risk.
+
+Of the four cases where polygon predictions were improved or remained similar after adding point data (Indonesia and Madagascar random cross-validation and PseudoSenegal and Madagascar spatial cross validation) the predictive performance on prevalence point-surveys was always unchanged or marginally improved.
+However, the benchmark points-only model was the top or equal top model at predicting point-level prevalence in four out of six cases and only marginally worse in one further case.
 Only in the Madagascar, spatial cross-validation experiment was the points-only model notably worse at predicting prevalence.

### 2018-10-01 ms.tex
Make data and model terminology more consistent.

@@
 Surveillance data is commonly aggregated, reporting the number of cases that occurred within a certain geographic or administrative region defined by a polygon.
-Ths surveillance data can be more sensitive than prevalence surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
-Furthermore, surveillance data is also often timely, with reports being released annually or monthly, while large prevalence surveys are performed on a more decadely time scale.
-However, the unstructured nature of data collection and reporting from national disease surveillance systems means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.
+This polygon incidence data can be more sensitive than prevalence point-surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
+Furthermore, polygon incidence data is also often timely, with reports being released annually or monthly, while countrywide collection of prevalence point-surveys is performed on a more decadely time scale.
+However, the unstructured nature of data collection and reporting of polygon incidence data from national disease surveillance systems means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.
 
@@
 
-Further to issues with the data itself, using aggregated data to estimate malaria risk for high resolution maps presents particular modelling difficulties \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
+Disaggregation regression methods have been proposed to handle polygon incidence data \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
+However using polygon incidence data to estimate malaria risk for high resolution maps presents particular modelling difficulties. 
 %Disaggregation models aim to estimate high-resolution maps from aggregated data and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
-The aggregating of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
+The aggregation of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
 For example, Sturrock \emph{et al.} used only two environmental covariates in their model \cite{sturrock2014fine}.
@@
 
-A model that combines point surveys and aggregated surveillance data, and therefore leverages the strength of both, has great potential.
-Joint modelling of the two data types has the potential to increase statistical power for learning relationships between malaria risk and covariates both by simply making more data available and because the point survey has a one-to-one relationship with the environment at the location of the survey.
+A model that combines prevalence point-surveys and polygon incidence data, and therefore leverages the strength of both, has great potential.
+Joint modelling of the two data types has the potential to increase statistical power for learning relationships between malaria risk and covariates both by simply making more data available and because point-surveys have a one-to-one relationship with the environment at the location of the survey.
 Furthermore, using two complimentary datasets potentially allows better spatial coverage. 
@@
 
-Here we formulate a joint model that combines aggregated surveillance data and point prevalence-surveys of \emph{Plasmodium falciparum}.
+Here we formulate a joint model that combines polygon incidence data and prevalence point-surveys of \emph{Plasmodium falciparum}.
 The model has seperate likelihoods for the two data types.
 We relate the two malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
-We compare the joint model to an aggregated-incidence disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and a further benchmark model that contains on;y prevalence-survey data.
-As case studies we use data from Indonesia, PseudoSenegal and Madagascar as these countries have both good routine surveillance data and good coverage of prevalence point surveys.
+We compare the joint model to an polygon-only disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and a further benchmark model that contains only prevalence point-survey data.
+As case studies we use data from Indonesia, PseudoSenegal and Madagascar as these countries have both good routine surveillance data and good coverage of prevalence point-surveys.
 
@@
 
-We used two data sources that reflect malaria burden; point prevalence surveys and polygon-level, aggregated incidence data.
+We used two data sources that reflect malaria burden; prevalence point-surveys and polygon incidence data.
 We selected Indonesia, PseudoSenegal and Madagascar as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
-To minimise temporal effects we select, for each country, one year of prevalence survey data and one year of surveillance data.
-For Indonesia we selected 2012 for surveillance data (380 regions) and 2010 for  prevalence data (969 surveys, 128,537 individuals).
-For PseudoSenegal we selected 2015 for both surveillance data (46 regions) and prevalence data (216 surveys, 8,114). % update todo
-Finally, for Madagascar we selected 2013 for both surveillance (110 regions) and prevalence (290 surveys, 7,244 individuals) data.
+To minimise temporal effects we select, for each country, one year of prevalence point-survey data and one year of polygon incidence data.
+For Indonesia we selected 2012 for polygon incidence data (380 regions) and 2010 for prevalence data (969 surveys, 128,537 individuals).
+For PseudoSenegal we selected 2015 for both polygon incidence data (46 regions) and prevalence data (216 surveys, 8,114). % update todo
+Finally, for Madagascar we selected 2013 for both polygon incidence (110 regions) and prevalence (290 surveys, 7,244 individuals) data.
 
@@
 
-The prevalence survey data were extracted from the Malaria Atlas Project prevalence survey database \cite{bhatt2015effect}.
-As the prevalence surveys cover different age ranges they were standardised to an age-range of 2--10 using the model from \cite{smith2007standardizing}.
+The prevalence point-survey data were extracted from the Malaria Atlas Project prevalence survey database \cite{bhatt2015effect}.
+As the prevalence point-surveys cover different age ranges they were standardised to an age-range of 2--10 using the model from \cite{smith2007standardizing}.
 
@@
 
-The polygon level surveillance data were collated from various government reports.
+The polygon incidence data were collated from various government reports.
 To account for underreporting of clinical cases due to lack of treatment seeking, missed case reports and cases that sought medical attention outside the public health systems, the methods in \cite{cibulskis2011worldwide} were used using estimates of treatment seeking from \cite{battle2016treatment}.
@@
 
-We compared three models 1) a full model with prevalence surveys and aggregated incidence data 2) the submodel with only aggregated incidence data and 3) the benchmark submodel with only prevalence point-survey data.
+We compared three models 1) a full model with prevalence point-surveys and polygon incidence data 2) the submodel with only polygon incidence data and 3) the benchmark submodel with only prevalence point-survey data.
 The models were implemented and fitted in R \cite{R} using Template Model Builder \cite{TMB} which allows a Laplace approximation of the posterior to be calculated.
@@
 The full, joint likelihood model is described as follows. 
-Values at the aggregate, polygon level are given the subscript $a$ while pixel or point level below are indexed with $b$.
-The polygon case count data, $y_j$ is given a Poisson likelihood
+Values at the aggregate, polygon level are given the subscript $a$ while pixel or point level variables are indexed with $b$.
+The polygon incidence case count data, $y_j$ is given a Poisson likelihood
 
@@
 
-The point-level prevalence data, $z_b$, is given a binomial likelihood
+The prevalence point-survey data, $z_b$, is given a binomial likelihood
 
@@
 We assigned $\sigma_w$ a penalised complexity prior such that $P(\sigma_w > 0.3) = 0.0000001$. 
-This was chosen by finding the maximum difference in prevalence between survey points (with a sample size greater than 500) within the same raster pixel.
+This was chosen by finding the maximum difference in prevalence between point-surveys (with a sample size greater than 500) within the same raster pixel.
 The differences between points within the same pixel can only be accounted for by the binomial error and this iid effect.
@@
 This reflects real world data where we in some locations we have incidence data but no prevalence data and visa versa.
-Thus this cross-validation scheme can be seen as asking whether aggregated incidence data provides a viable or preferable alternative to using just prevalence data as in previous modelling efforts \cite{bhatt2015effect}.
+Thus this cross-validation scheme can be seen as asking whether the joint model is preferable to using just polygon incidence data.
 
@@
 The number of folds was seven for Indonesia, four for PseudoSenegal and three for Madagascar due to their differing sizes and geographies.
-The data was divided by combining the point locations and the centroids of the incidence polygons and performing k means clustering.
+The data was divided by combining the prevalence point-survey locations and the centroids of the incidence polygons and performing k means clustering.
 This scheme is testing the models' ability to predict into new areas with little information from the spatial random field.
 
-In both cases we examined performance metrics for both the withheld prevalence data and the withheld incidence data.
+In both cases we examined performance metrics for both the withheld prevalence point-survey data and the withheld incidence polygon data.
 As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
-We considered the ability to predict aggregated incidence correctly our main objective and our performance metric was mean absolute error (MAE)..
+We considered the ability to predict polygon incidence correctly our main objective and our performance metric was mean absolute error (MAE).
 However, a problem with using polygon data in a cross-validation scheme is that a model can perform well at the polygon level but not correctly predict the pixel-level malaria risk.
-Predictive performance on prevalence points is one way to measure how well a model can predict pixel-level malaria risk.
-However, in areas of low prevalence, small or moderately sized prevalence surveys can be noisy or unsensitive and so care must be taken when interpreting predictive performance on these data.
-Therefore our secondary metric was, MAE weighted by survey sample size, of prevalence point surveys.
+Predictive performance on prevalence survey-points is one way to measure how well a model can predict pixel-level malaria risk.
+However, in areas of low prevalence, small or moderately sized prevalence point-surveys can be noisy or unsensitive and so care must be taken when interpreting predictive performance on these data.
+Therefore our secondary metric was MAE, weighted by survey sample size, of prevalence point-surveys.
 While other metrics could have been used, we specifically did not use correlation as correlation measures linear dependance without regard to slope or intercept.
-As the models are being fitted on data on difference scales we found that predictions were sometimes correlated but strongly displaced from the one-one line and therefore correlation metrics were misleading.
+As the models are being fitted on data on difference scales we found that observations and predictions were sometimes correlated but strongly displaced from the one-one line and therefore correlation metrics were misleading.
 % Why not correlation
@@
 The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both PseudoSenegal (0.015) and  Madagascar (0.054) while the wighted MAE was the same for all three models in Indonesia (0.010) (Table~\ref{table1}).
-The more pertinent comparison is whether the addition of the prevalence data improves the ability of the disaggregation models to predict pixel level prevalence.
-However, weighted MAE was unchanged between the polygon model and the joint model for Indonesia (0.010), PseudoSenegal (0.024) or Madagascar (0.059).
+The more pertinent comparison is whether the addition of the prevalence data improves the ability of the polygon-only models to predict pixel level prevalence.
+However, weighted MAE was unchanged between the polygon-only model and the joint model for Indonesia (0.010), PseudoSenegal (0.024) or Madagascar (0.059).
 Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and PseudoSenegal.
@@
 The proportion of out-of-sample prevalence datapoints being within their 80\% credible intervals ranged from 0.50 to 0.96.
-The points only model was reasonably well calibrated for predictions of prevalence (coverage ranging from 0.8 to 0.93) but was poorly calibrated for predicting incidence with coverage values as low as 0.11 and the best coverage value being 0.68 for spatial cross-validation in Madagascar.
-With respect to uncertainty in incidence predictions, the polygon-only model and joint model were similar; adding the points sometimes improved coverage and sometimes made it worse.
-However, with respect to uncertainty in prevalence predictions, the coverage was substantially improved in three of six cases and marginally improved in one case.
+The points-only model was reasonably well calibrated for predictions of prevalence (coverage ranging from 0.8 to 0.93) but was poorly calibrated for predicting incidence with coverage values as low as 0.11 and the best coverage value being 0.68 for spatial cross-validation in Madagascar.
+With respect to uncertainty in polygon incidence predictions, the polygon-only model and joint model were similar; adding the prevalence point-survey data sometimes improved coverage and sometimes made it worse.
+However, with respect to uncertainty in prevalence point-survey predictions, the coverage was substantially improved in three of six cases and marginally improved in one case.
 Coverage improved in the random cross-validation in Indonesia (polygon-only 0.50, joint 0.80) and Madagascar (polygon-only 0.53, joint 0.74) and spatial cross-validation in Madagascar (polygon-only 0.68, joint 0.83) and marginally improved in the spatial cross-validation in PseudoSenegal (polygon-only 0.88, joint 0.79).
-In the remaining two cases, adding points did not substantially improve coverage, but did make the model more conservative, with coverage of 0.91 rather than 0.71 in the random cross-validation PseudoSenegal experiment and 0.96 instead of 0.62 in the spatial cross-validation Indonesia experiment.
+In the remaining two cases, adding prevalence point-surveys did not substantially improve coverage, but did make the model more conservative, with coverage of 0.91 rather than 0.71 in the random cross-validation PseudoSenegal experiment and 0.96 instead of 0.62 in the spatial cross-validation Indonesia experiment.
 
@@
 \caption{
-{\bf Summary of coverage of 80\% credible intervals for.}}
+{\bf Summary of coverage of 80\% credible intervals.}}
 \begin{tabular}{llllll}
@@
 
-We have compared the predictive performance of a disaggration model and a model that jointly learns from aggregated incidence data and point prevalence surveys.
+We have compared the predictive performance of a polygon-only model and a model that jointly learns from polygon incidence data and prevalence point-surveys.
 We found that neither model was clearly superior to the other but that both models recovered the broad spatial pattern of malaria risk (Figures \ref{predobsmapidn} and \ref{predobsmapidn}).
-With regards to a random cross-validation scheme, adding points to the disaggregation model only improved performance in  Madagascar (Table~\ref{table1}).
-With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the point surveys improved the disaggregation models in both PseudoSenegal and Madagascar but not Indonesia  (Table~\ref{table2}).
+With regards to a random cross-validation scheme, adding prevalence point-surveys to the disaggregation model only improved performance in  Madagascar (Table~\ref{table1}).
+With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the prevalence point-surveys improved on the polygon-only models in both PseudoSenegal and Madagascar but not Indonesia (Table~\ref{table2}).
 
@@
 
-Of the four cases where polygon predictions were improved or remained similar after adding point data (Indonesia and Madagascar random cross-validation and PseudoSenegal and Madagascar spatial cross validation) the predictive performance on prevalence point-surveys was always unchanged or marginally improved.
-However, the benchmark points-only model was the top or equal top model at predicting point-level prevalence in four out of six cases and only marginally worse in one further case.
-Only in the Madagascar, spatial cross-validation experiment was the points-only model notably worse at predicting prevalence.
+Of the four cases where predictions of polygon incidence were improved or remained similar after adding prevalence point-survey data (Indonesia and Madagascar random cross-validation and PseudoSenegal and Madagascar spatial cross validation) the predictive performance on prevalence point-surveys was always unchanged or marginally improved.
+However, the benchmark points-only model was the top or equal top model at predicting prevalence point-surveys in four out of six cases and only marginally worse in one further case.
+Only in the Madagascar, spatial cross-validation, experiment was the points-only model notably worse at predicting prevalence point surveys.
 
@@
 
-The joint model improved the prediction of incidence in two of three countries under the spatial cross-validation scheme but only one country in the random cross-validation scheme.
+The joint model improved the prediction of polygon incidence in two of three countries under the spatial cross-validation scheme but only one country in the random cross-validation scheme.
 The two countries where the joint model performed best in the spatial cross-validation scheme are the two countries with the least data.
@@
 Far-from-data predictions are particularly susceptible to overfitting.
-Given the simple linear model, adding prevalence data may protect against overfitting simply by increasing the amount of data available.
-Alternatively, a model that learns from two datasets, on different scales, with different biases, is also less likely to overfit.
+Given the simple linear model, adding prevalence point-surveys may protect against overfitting by increasing the amount of data available.
+Alternatively, the improved perforamance could be because a model that learns from two datasets, on different scales, with different biases, is also less likely to overfit.
 
 In contrast, the joint model does not in general improve on the polygon-only model in the random cross-validation scheme.
-A noticable element of this scheme was that locations where polygon data was removed for validation could still potentially have prevalence data.
+A noticable element of this scheme was that locations where polygon incidence data was removed for validation could still potentially have prevalence point-survey data.
 Figure~\ref{fig:cv_random} implies that this situation is the norm.
@@
 
-There are two main reasons why a model fitted jointly on prevalence and polygon incidence data may perform worse than a polygon-only mode.
+There are two main reasons why a model fitted jointly on prevalence point-surveys and polygon incidence data may perform worse than a polygon-only mode.
 Firstly, the data are on difference scales.
@@
 In using a joint model we are accepting these failings in the hope that the benefits of including additional data are stronger than the costs of using mismatched data.
-The second aspect of prevalence point data that could reduce the predictive ability of a polygon-only model by adding point data is if the point data is of low quality.
+The second aspect of prevalence point-survey data that could reduce the predictive ability of a polygon-only model by adding point data is if the point data is of low quality.
 In particular, non-random sampling of individuals can produce biased estimates of prevalence and this will decrease model performance.
@@
 
-For the model to handle noisy or biased prevalence data points, the modeller can control the iid random effect on the point surveys, $w_i$. 
+For the model to handle noisy or biased prevalence point-surveys, the modeller can control the iid random effect on the point-surveys, $w_i$. 
 Here we have tried to maximise the influence of the prevalence data by setting the prior based on the belief that the random effect should only explain extra-binomial variation that is impossible to explain with the covariates (i.e.
 based on the differences in prevalence surveys within the same pixel).
-Weakening this prior will allow the iid effect to explain more of the point survey variation which both reduces the potential statistical power gained by adding the point data but also reduces the effects of biased or noisy estimates.
+Weakening this prior will allow the iid effect to explain more of the prevalence point-survey variation which both reduces the potential statistical power gained by adding the point-surveys but also reduces the effects of biased or noisy estimates.
 
@@
 Further cases where this joint model may be particularly beneficial is in countries where prevalence surveys are strongly clustered in one area --- typically an area of high malaria risk --- but without high resolution surveillance data.
-In these regions, fitting a model on just the points requires predictions far away from the survey locations whlie fitting a model just on the surveillance data will be underpowered. 
+In these regions, fitting a model on just the prevalence point-surveys requires predictions far away from the survey locations whlie fitting a model just on the polygon incidence data will be underpowered.
 However, the benefits of these methods do not come for free, as indicated by the reduced performance in some cases.

### 2018-10-01 ms.tex
Mess around with fig placement.

@@
 
+\begin{figure}[t!]
+% to be removed before submission
+\centering
+
+\includegraphics[width = 0.9\textwidth]{figures/random_crossvalidation_full.png} %\caption{Indonesia random crossvalidation}
+
+\caption{{\bf Random cross-validation scheme for Indonesia, PseudoSenegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+\label{fig:cv_random}
+\end{figure}
+
+\begin{figure}[!t]
+% to be removed before submission
+\centering
+
+\includegraphics[width = 0.9\textwidth]{figures/spatial_crossvalidation_full.png} %\caption{Indonesia random crossvalidation}
+
+\caption{{\bf Spatial cross-validation scheme for Indonesia, PseudoSenegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+\label{fig:cv_spatial}
+\end{figure}
+
 Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
@@
 %figure 1.cross validation. %% Do fig 1 and 2, random and spatial cv. IDN on top, MDG and SEN below in each.
-
-\begin{figure}[!h]
-% to be removed before submission
-\centering
-
-\includegraphics[width = 0.9\textwidth]{figures/random_crossvalidation_full.png} %\caption{Indonesia random crossvalidation}
-
-\caption{{\bf Random cross-validation scheme for Indonesia, PseudoSenegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
-\label{fig:cv_random}
-\end{figure}
-
-\begin{figure}[!h]
-% to be removed before submission
-\centering
-
-\includegraphics[width = 0.9\textwidth]{figures/spatial_crossvalidation_full.png} %\caption{Indonesia random crossvalidation}
-
-\caption{{\bf Spatial cross-validation scheme for Indonesia, PseudoSenegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
-\label{fig:cv_spatial}
-\end{figure}
 
@@
 
-% Results and Discussion can be combined.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Random results
-% Maps, reasonable for both
-% MAE performance.
-
-For the random cross-validation experiments, the polygon-only model had the lowest mean absolute error, with respect to predicting incidence, for Indonesia (14.02) and PseudoSenegal (26.74) (Table~\ref{table1}).
-Incidence in Madagascar was best predicted by the joint model (34.49).
-However, the difference between the two models in Indonesia was small (polygons-only 14.02, joint model 14.09).
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter}A, C and E.
-
-\begin{table}[!ht]
+\begin{table}[!t]
 \begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
@@
 
+% Results and Discussion can be combined.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Random results
+% Maps, reasonable for both
+% MAE performance.
+
+For the random cross-validation experiments, the polygon-only model had the lowest mean absolute error, with respect to predicting incidence, for Indonesia (14.02) and PseudoSenegal (26.74) (Table~\ref{table1}).
+Incidence in Madagascar was best predicted by the joint model (34.49).
+However, the difference between the two models in Indonesia was small (polygons-only 14.02, joint model 14.09).
+Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter}A, C and E.
+
 The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both PseudoSenegal (0.015) and  Madagascar (0.054) while the wighted MAE was the same for all three models in Indonesia (0.010) (Table~\ref{table1}).
@@
 Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for PseudoSenegal show broad agreement with malaria incidence being higher in the South.
+
+%figure 3 and 4. data and predicted incidence maps. Indonesia and PseudoSenegal only. Fig 3 ind, fig 4 rand. Data, Rand, Spatial for best model? Joint model?
+
+\begin{figure}[!t]
+% to be removed before submission
+\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_preds.png}
+\caption{{\bf Input incidence data and predicted incidence maps. } 
+The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
+The values plotted for areas with no polygon data are the means across all cross-validation folds.
+}
+\label{predobsmapidn}
+\end{figure}
+
+\begin{figure}[!t]
+% to be removed before submission
+\includegraphics[width = 0.7\textwidth]{figures/sen_both_cv12_preds.png}
+\caption{{\bf Input incidence data and predicted incidence maps. } 
+The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for PseudoSenegal.
+}
+\label{predobsmapsen}
+\end{figure}
+
+%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
+\begin{figure}[!t]
+% to be removed before submission
+\includegraphics[width = \textwidth]{figures/random_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
+\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
+A-B) Indonesia, C-D) PseudoSenegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
+Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
+}
+\label{randompredobsscatter}
+\end{figure}
+
+%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
+\begin{figure}[!t]
+% to be removed before submission
+\includegraphics[width = \textwidth]{figures/spatial_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
+\caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
+A-B) Indonesia, C-D) PseudoSenegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
+Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
+}
+\label{spatialpredobsscatter}
+\end{figure}
 
@@
 % Overall
-
-%figure 3 and 4. data and predicted incidence maps. Indonesia and PseudoSenegal only. Fig 3 ind, fig 4 rand. Data, Rand, Spatial for best model? Joint model?
-
-\begin{figure}[!t]
-% to be removed before submission
-\includegraphics[width = 0.9\textwidth]{figures/idn_both_cv12_preds.png}
-\caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
-The values plotted for areas with no polygon data are the means across all cross-validation folds.
-}
-\label{predobsmapidn}
-\end{figure}
-
-\begin{figure}[!t]
-% to be removed before submission
-\includegraphics[width = 0.9\textwidth]{figures/sen_both_cv12_preds.png}
-\caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for PseudoSenegal.
-}
-\label{predobsmapsen}
-\end{figure}
-
-%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
-\begin{figure}[!t]
-% to be removed before submission
-\includegraphics[width = 0.9\textwidth]{figures/random_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
-\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
-A-B) Indonesia, C-D) PseudoSenegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
-Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
-}
-\label{randompredobsscatter}
-\end{figure}
-
-%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
-\begin{figure}[!t]
-% to be removed before submission
-\includegraphics[width = 0.9\textwidth]{figures/spatial_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
-\caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
-A-B) Indonesia, C-D) PseudoSenegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
-Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
-}
-\label{spatialpredobsscatter}
-\end{figure}
 
@@
 We used held-out prevalence point-surveys to measure how well model were predicting the within-polygon, pixel-level malaria risk.
-
+Given the poor performance by all models (Figures~\ref{randompredobsscatter} and \ref{spatialpredobsscatter}) these results must be interpreted with care.
 Of the four cases where predictions of polygon incidence were improved or remained similar after adding prevalence point-survey data (Indonesia and Madagascar random cross-validation and PseudoSenegal and Madagascar spatial cross validation) the predictive performance on prevalence point-surveys was always unchanged or marginally improved.

### 2018-10-01 ms.tex
Explain more small sample size.

@@
 As the prevalence point-surveys cover different age ranges they were standardised to an age-range of 2--10 using the model from \cite{smith2007standardizing}.
+Many of the points have relatively small sample sizes.
+285 surveys out of 290 in Senegal have a sample size less than 50 while 618 out of 969 surveys in Indonesia have a sample size less than 100.
+Furthermore, due to the small sample sizes and low malaria prevalence in these countries, many of the surveys have find very few malaria infections.
+Amongst the Senegal surveys, 189 out of 290 have zero positive cases while a further 30 have only one positive case.
+In Indonesia 620 out of 969 surveys have zero positive cases and 195 have one positive case.
+Finally, in Madagascar 189 out of 290 surveys have zero positive cases and 30 have one positive case.
+The age standardisation model gives the surveys with zero positive cases a small positive prevalence.
 
@@
 
-To compare the three models we used two cross validation schemes. 
+To compare the three models we used two cross-validation schemes. 
 In the first, the combined data set of prevalence and incidence data was split into ten cross-validation folds stratified by data type (Figure~\ref{fig:cv_random}).
@@
 % to be removed before submission
-\includegraphics[width = \textwidth]{figures/random_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
+\includegraphics[width = 1.05\textwidth]{figures/random_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
 \caption{{\bf Observed-predicted plots for random cross-validation experiments.}
@@
 Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
+The bimodal distribution in observed prevalence in Indonesia is caused by the large number of surveys with exactly one positive case.
 }
@@
 % to be removed before submission
-\includegraphics[width = \textwidth]{figures/spatial_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
+\includegraphics[width = 1.05\textwidth]{figures/spatial_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
 \caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
@@
 We used held-out prevalence point-surveys to measure how well model were predicting the within-polygon, pixel-level malaria risk.
-Given the poor performance by all models (Figures~\ref{randompredobsscatter} and \ref{spatialpredobsscatter}) these results must be interpreted with care.
-Of the four cases where predictions of polygon incidence were improved or remained similar after adding prevalence point-survey data (Indonesia and Madagascar random cross-validation and PseudoSenegal and Madagascar spatial cross validation) the predictive performance on prevalence point-surveys was always unchanged or marginally improved.
-However, the benchmark points-only model was the top or equal top model at predicting prevalence point-surveys in four out of six cases and only marginally worse in one further case.
-Only in the Madagascar, spatial cross-validation, experiment was the points-only model notably worse at predicting prevalence point surveys.
+Given the poor performance by all models including the points-only model (Figures~\ref{randompredobsscatter} and \ref{spatialpredobsscatter}), particularly in Indonesia and PseudoSenegal these results must be interpreted with care.
+% Add sample size, comparisons etc.
+In particular, nearly all of the prevalence point-surveys in PseudoSenegal found zero malaria infections (though the age standardisation moves these to slightly non-zero values).
+Given the poor performance of the points-only model, it is not useful to interpret these results as a direct measure of a models ability to predict within-polygon, pixel level risk.
+Instead we can, with care, interpret the relative performance of models.
+In five cases, the polygon-only and joint model had the same predictive performance on the prevalence point-surveys.
+In only one cases, the joint model was marginally better.
+Therefore we have no evidence that the joint model is better than the polygon-only model at predicting within-polygon, pixel-level malaria risk.
 

### 2018-10-01 ms.tex
More messing with fig placement.

@@
 
-The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both PseudoSenegal (0.015) and  Madagascar (0.054) while the wighted MAE was the same for all three models in Indonesia (0.010) (Table~\ref{table1}).
-The more pertinent comparison is whether the addition of the prevalence data improves the ability of the polygon-only models to predict pixel level prevalence.
-However, weighted MAE was unchanged between the polygon-only model and the joint model for Indonesia (0.010), PseudoSenegal (0.024) or Madagascar (0.059).
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and PseudoSenegal.
-
-Maps of the Indonesian input data and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
-Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for PseudoSenegal show broad agreement with malaria incidence being higher in the South.
-
-%figure 3 and 4. data and predicted incidence maps. Indonesia and PseudoSenegal only. Fig 3 ind, fig 4 rand. Data, Rand, Spatial for best model? Joint model?
-
-\begin{figure}[!t]
-% to be removed before submission
-\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_preds.png}
-\caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
-The values plotted for areas with no polygon data are the means across all cross-validation folds.
-}
-\label{predobsmapidn}
-\end{figure}
-
-\begin{figure}[!t]
-% to be removed before submission
-\includegraphics[width = 0.7\textwidth]{figures/sen_both_cv12_preds.png}
-\caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for PseudoSenegal.
-}
-\label{predobsmapsen}
-\end{figure}
-
 %figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
-\begin{figure}[!t]
+\begin{figure}
 % to be removed before submission
@@
 %figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
-\begin{figure}[!t]
+\begin{figure}
 % to be removed before submission
@@
 \end{figure}
+
+\begin{table}[t]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{
+{\bf Summary of coverage of 80\% credible intervals.}}
+\begin{tabular}{llllll}
+\hline
+{\bf Holdout data} & {\bf Cross-validation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
+\thickhline 
+Incidence & Random & Indonesia & 0.13 & 0.72 &  0.73\\
+&& PseudoSenegal & 0.11 & 0.80 &  0.85\\
+&& Madagascar & 0.59 & 0.82 &  0.77\vspace{1mm}\\
+& Spatial & Indonesia & 0.14 & 0.76 &  0.68\\
+&& PseudoSenegal & 0.30 & 0.67 &  0.70\\
+&& Madagascar & 0.68 & 0.65 &  0.68\vspace{3mm} \\
+Prevalence & Random & Indonesia & 0.90 & 0.50 &  0.80\\
+&& PseudoSenegal & 0.80 & 0.71 &  0.91\\
+&& Madagascar & 0.83 & 0.53 &  0.74\vspace{1mm}\\
+& Spatial & Indonesia & 0.87 & 0.62 &  0.96\\
+&& PseudoSenegal & 0.90 & 0.88 &  0.79\\
+&& Madagascar & 0.93 & 0.68 &  0.83\\
+\end{tabular}
+\begin{flushleft}
+
+\end{flushleft}
+\label{table3}
+\end{adjustwidth}
+\end{table}
+
+The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both PseudoSenegal (0.015) and  Madagascar (0.054) while the wighted MAE was the same for all three models in Indonesia (0.010) (Table~\ref{table1}).
+The more pertinent comparison is whether the addition of the prevalence data improves the ability of the polygon-only models to predict pixel level prevalence.
+However, weighted MAE was unchanged between the polygon-only model and the joint model for Indonesia (0.010), PseudoSenegal (0.024) or Madagascar (0.059).
+Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and PseudoSenegal.
+
+Maps of the Indonesian input data and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
+Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for PseudoSenegal show broad agreement with malaria incidence being higher in the South.
 
@@
 
-\begin{table}[!t]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\caption{
-{\bf Summary of coverage of 80\% credible intervals.}}
-\begin{tabular}{llllll}
-\hline
-{\bf Holdout data} & {\bf Cross-validation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
-\thickhline 
-Incidence & Random & Indonesia & 0.13 & 0.72 &  0.73\\
-&& PseudoSenegal & 0.11 & 0.80 &  0.85\\
-&& Madagascar & 0.59 & 0.82 &  0.77\vspace{1mm}\\
-& Spatial & Indonesia & 0.14 & 0.76 &  0.68\\
-&& PseudoSenegal & 0.30 & 0.67 &  0.70\\
-&& Madagascar & 0.68 & 0.65 &  0.68\vspace{3mm} \\
-Prevalence & Random & Indonesia & 0.90 & 0.50 &  0.80\\
-&& PseudoSenegal & 0.80 & 0.71 &  0.91\\
-&& Madagascar & 0.83 & 0.53 &  0.74\vspace{1mm}\\
-& Spatial & Indonesia & 0.87 & 0.62 &  0.96\\
-&& PseudoSenegal & 0.90 & 0.88 &  0.79\\
-&& Madagascar & 0.93 & 0.68 &  0.83\\
-\end{tabular}
-\begin{flushleft}
+%figure 3 and 4. data and predicted incidence maps. Indonesia and PseudoSenegal only. Fig 3 ind, fig 4 rand. Data, Rand, Spatial for best model? Joint model?
 
-\end{flushleft}
-\label{table3}
-\end{adjustwidth}
-\end{table}
+\begin{figure}
+% to be removed before submission
+\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_preds.png}
+\caption{{\bf Input incidence data and predicted incidence maps. } 
+The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
+The values plotted for areas with no polygon data are the means across all cross-validation folds.
+}
+\label{predobsmapidn}
+\end{figure}
+
+\begin{figure}
+% to be removed before submission
+\includegraphics[width = 0.7\textwidth]{figures/sen_both_cv12_preds.png}
+\caption{{\bf Input incidence data and predicted incidence maps. } 
+The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for PseudoSenegal.
+}
+\label{predobsmapsen}
+\end{figure}
 
@@
 We have compared the predictive performance of a polygon-only model and a model that jointly learns from polygon incidence data and prevalence point-surveys.
-We found that neither model was clearly superior to the other but that both models recovered the broad spatial pattern of malaria risk (Figures \ref{predobsmapidn} and \ref{predobsmapidn}).
+We found that neither model was clearly superior to the other but that both models recovered the broad spatial pattern of malaria risk (Figures \ref{predobsmapidn} and \ref{predobsmapsen}).
 With regards to a random cross-validation scheme, adding prevalence point-surveys to the disaggregation model only improved performance in  Madagascar (Table~\ref{table1}).

### 2018-10-01 ms.tex
Rewrite abstract.

@@
 \section*{Abstract}
-malaria is bad but decreasing
-moving to strategy of elimination country by country
-elimination requires maps of low prevalence areas
-but maps in low prevalence areas are difficult
-sometimes little data
-traditional prevalence mapping won't work
-we need new sources of data.
+As malaria incidence decreases and more contries move towards elimination, maps of malaria risk in low prevalence areas are becoming increasingly needed.
+However, traditional mapping using prevalence point-surveys are often ineffective in low prevalence areas due to low statistical power and a lack of data.
+Therefore, models must be developed that can estimate risk at high spatial resolution from surveillance data that reports incidence aggregated to a geographic polygon.
+Current models formulated for polygon incidence data suffer from lower statistical power for learning relationships between malaria risk and environmental covariates.
+Here we present a joint model that uses both polygon incidence and prevalence point-surveys.
 

### 2018-10-01 ms.tex
Add we find to intro.

@@
 \section*{Author summary}
-malaria is bad but decreasing
-moving to strategy of elimination country by country
-elimination requires maps of low prevalence areas
-but maps in low prevalence areas are difficult
-sometimes little data
-traditional prevalence mapping won't work
-we need new sources of data.
+Todo
 
@@
 
-Here we formulate a joint model that combines polygon incidence data and prevalence point-surveys of \emph{Plasmodium falciparum}.
-The model has seperate likelihoods for the two data types.
+Here we formulate a joint model that combines polygon incidence data and prevalence point-surveys of \emph{Plasmodium falciparum} using seperate likelihoods for the two data types.
 We relate the two malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
-We compare the joint model to an polygon-only disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and a further benchmark model that contains only prevalence point-survey data.
-As case studies we use data from Indonesia, PseudoSenegal and Madagascar as these countries have both good routine surveillance data and good coverage of prevalence point-surveys.
+We compare the joint model to a polygon-only, disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and a further benchmark model that contains only prevalence point-survey data using data from Indonesia, PseudoSenegal and Madagascar as case studies.
+We find that the joint model performs better than the polygon-only model in cases where predictions are needed far from the location of the data or when little data is available for learning relationships between covariates and malaria risk.
 
@@
 %we use Madagascar and Indonesia as case studies as they have good %surveillance data and good pr data.
-we find that...
 

### 2018-10-01 ms.tex
Tidy up of methods.

@@
 Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases \cite{sturrock2016mapping, cohen2017mapping}.
-However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \cite{gething2011new, bhatt2017improved, gething2012long} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite {sturrock2016mapping, sturrock2014fine}.
+However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \cite{gething2011new, bhatt2017improved, gething2012long} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite{sturrock2016mapping, sturrock2014fine}.
 In low burden areas, very large sample sizes are needed before a prevalence survey is informative.
@@
 Joint modelling of the two data types has the potential to increase statistical power for learning relationships between malaria risk and covariates both by simply making more data available and because point-surveys have a one-to-one relationship with the environment at the location of the survey.
-Furthermore, using two complimentary datasets potentially allows better spatial coverage. 
+Furthermore, using two complimentary datasets potentially allows better spatial coverage \cite{sturrock2016mapping}. 
 One major barrier to this modelling approach is that these two data sources are on different scales: point surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ while routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$.
@@
 
-For the random cross-validation experiments, the polygon-only model had the lowest mean absolute error, with respect to predicting incidence, for Indonesia (14.02) and PseudoSenegal (26.74) (Table~\ref{table1}).
-Incidence in Madagascar was best predicted by the joint model (34.49).
-However, the difference between the two models in Indonesia was small (polygons-only 14.02, joint model 14.09).
+For the random cross-validation experiments, the polygon-only model had the lowest mean absolute error, with respect to predicting incidence, for Indonesia and PseudoSenegal (Table~\ref{table1}).
+Incidence in Madagascar was best predicted by the joint model.
+However, the difference between the two models in Indonesia was small.
 Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter}A, C and E.
+From the scatter plots it can be seen that the point-only model is strongly biased, overestimating incidence in Indonesia and Madagascar and underestimating incidence in Senegal.
 
@@
 
-The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both PseudoSenegal (0.015) and  Madagascar (0.054) while the wighted MAE was the same for all three models in Indonesia (0.010) (Table~\ref{table1}).
+The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both PseudoSenegal and  Madagascar while the wighted MAE was the same for all three models in Indonesia (Table~\ref{table1}).
 The more pertinent comparison is whether the addition of the prevalence data improves the ability of the polygon-only models to predict pixel level prevalence.
-However, weighted MAE was unchanged between the polygon-only model and the joint model for Indonesia (0.010), PseudoSenegal (0.024) or Madagascar (0.059).
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and PseudoSenegal.
+However, weighted MAE was unchanged between the polygon-only model and the joint model for Indonesia, PseudoSenegal or Madagascar.
+Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F.
+All models show poor predictive performance in Indonesia and PseudoSenegal with none of the models being able to accurately predict the large number of points with zero prevalence.
+The predictions in Madagascar are better though the large number of surveys with measured prevalence of zero are still problematic.
 
@@
 
-For the spatial cross-validation experiments, the polygon-only model again had the lowest mean absolute error between observed and predicted incidence for Indonesia (14.77) (Table~\ref{table2}).
-However, for both PseudoSenegal (36.76) and Madagascar (65.50) the joint model had the best predictive performance.
+For the spatial cross-validation experiments, the joint model had the best predictive performance for both PseudoSenegal and Madagascar.
+The polygon-only model again had the lowest mean absolute error between observed and predicted incidence for Indonesia (Table~\ref{table2}).
 Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{spatialpredobsscatter}A, C and E.
 
-Again, the benchmark points-only model had the lowest weighted MAE between spatially cross-validated observed and predicted prevalence for PseudoSenegal (0.015).
-However, for Indonesia, both the disaggration models marginally outperformed the points-only model (polygons-only 0.010, joint model 0.010). 
+Again, the benchmark points-only model had the lowest weighted MAE between spatially cross-validated observed and predicted prevalence for PseudoSenegal.
+However, for Indonesia, both the polygon-model and the joint model marginally outperformed the points-only model. 
+However, scatter plots of the out-of-sample predictions show that there is almost no correlation between observed and predicted values (Figures~\ref{randompredobsscatter} B, D and F).
 For PseudoSenegal, the joint model (0.065) had the lowest weighted MAE for predicted prevalence though this was again marginal (points-only 0.069, polygons-only 0.066).
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F and show poor predictive performance for all models in both Indonesia and PseudoSenegal.
+Again the survey-points with prevalence of zero were difficult to correctly predict.
 
@@
 The points-only model was reasonably well calibrated for predictions of prevalence (coverage ranging from 0.8 to 0.93) but was poorly calibrated for predicting incidence with coverage values as low as 0.11 and the best coverage value being 0.68 for spatial cross-validation in Madagascar.
+
 With respect to uncertainty in polygon incidence predictions, the polygon-only model and joint model were similar; adding the prevalence point-survey data sometimes improved coverage and sometimes made it worse.

### 2018-10-01 ms.tex
Tidy up of coverage results.

@@
 However, with respect to uncertainty in prevalence point-survey predictions, the coverage was substantially improved in three of six cases and marginally improved in one case.
-Coverage improved in the random cross-validation in Indonesia (polygon-only 0.50, joint 0.80) and Madagascar (polygon-only 0.53, joint 0.74) and spatial cross-validation in Madagascar (polygon-only 0.68, joint 0.83) and marginally improved in the spatial cross-validation in PseudoSenegal (polygon-only 0.88, joint 0.79).
+Coverage improved in the random cross-validation in Indonesia and Madagascar and spatial cross-validation in Madagascar and marginally improved in the spatial cross-validation in PseudoSenegal.
 In the remaining two cases, adding prevalence point-surveys did not substantially improve coverage, but did make the model more conservative, with coverage of 0.91 rather than 0.71 in the random cross-validation PseudoSenegal experiment and 0.96 instead of 0.62 in the spatial cross-validation Indonesia experiment.

### 2018-10-01 ms.tex
Small edits to discussion.

@@
 
-We used held-out prevalence point-surveys to measure how well model were predicting the within-polygon, pixel-level malaria risk.
-Given the poor performance by all models including the points-only model (Figures~\ref{randompredobsscatter} and \ref{spatialpredobsscatter}), particularly in Indonesia and PseudoSenegal these results must be interpreted with care.
+We used held-out prevalence point-surveys to measure how well the models predicted within-polygon, pixel-level malaria risk.
+Given the poor performance by all models, including the points-only model (Figures~\ref{randompredobsscatter} and \ref{spatialpredobsscatter}), particularly in Indonesia and PseudoSenegal these results must be interpreted with care.
 % Add sample size, comparisons etc.
-In particular, nearly all of the prevalence point-surveys in PseudoSenegal found zero malaria infections (though the age standardisation moves these to slightly non-zero values).
+In particular, a majority of the prevalence point-surveys in all countries found zero malaria infections (though the age standardisation moves these to slightly non-zero values) and small sample sizes were common in the Senegal and Indonesia data.
 Given the poor performance of the points-only model, it is not useful to interpret these results as a direct measure of a models ability to predict within-polygon, pixel level risk.

### 2018-11-19 ms.tex
Start adding some dan w comments.

@@
 \usepackage{lastpage,fancyhdr,graphicx}
+\DeclareGraphicsExtensions{.pdf,.png}   
 \usepackage{epstopdf}
@@
 Tim C.D.
-Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Rosalind Howes \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Dan Weiss\textsuperscript{1},
+Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Rosalind Howes \textsuperscript{1}, Katherine Battle \textsuperscript{1}, Andre Python \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Dan Weiss\textsuperscript{1},
 \\
@@
 Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases \cite{sturrock2016mapping, cohen2017mapping}.
-However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \cite{gething2011new, bhatt2017improved, gething2012long} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite{sturrock2016mapping, sturrock2014fine}.
-In low burden areas, very large sample sizes are needed before a prevalence survey is informative.
-Furthermore, large, countrywide surveys of prevalence, such as DHS or MIS, are rare in low burden countries due to costs and percieved low utility \cite{dhs}.
+However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \cite{gething2011new, bhatt2017improved, gething2012long, bhatt2015effect} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite{sturrock2016mapping, sturrock2014fine}.
+In low burden areas, very large sample sizes are needed before a prevalence survey is informative because so few individuals have parasitaemia that most sample points will have no cases.
+As a result, large, countrywide surveys of prevalence, such as DHS or MIS, are rare in low burden countries due to costs and percieved low utility \cite{dhs}.
 We therefore need new data sources and associated statistical methods.
@@
 Routine surveillance data, of malaria case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
-Surveillance data is commonly aggregated, reporting the number of cases that occurred within a certain geographic or administrative region defined by a polygon.
+Surveillance data is commonly aggregated from information collected at healthcare facilities or by community health workers, reporting the number of cases that occurred within a certain geographic or administrative region defined by a polygon.
 This polygon incidence data can be more sensitive than prevalence point-surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
-Furthermore, polygon incidence data is also often timely, with reports being released annually or monthly, while countrywide collection of prevalence point-surveys is performed on a more decadely time scale.
+Furthermore, polygon incidence data is also often timely, with reports being released annually or monthly with little lag, while countrywide collection of prevalence point-surveys are both rare and often released one to two years after field data collection is completed.
 However, the unstructured nature of data collection and reporting of polygon incidence data from national disease surveillance systems means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.
@@
 
-Disaggregation regression methods have been proposed to handle polygon incidence data \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
-However using polygon incidence data to estimate malaria risk for high resolution maps presents particular modelling difficulties. 
+Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level incidence \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
+However using polygon incidence data to estimate malaria risk for high resolution maps presents several noteworthy modelling difficulties. 
 %Disaggregation models aim to estimate high-resolution maps from aggregated data and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
 The aggregation of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
-For example, Sturrock \emph{et al.} used only two environmental covariates in their model \cite{sturrock2014fine}.
-Disaggregation models are also simply an underrepresented class of models in the statistical literature and statistical software.
-Wilson \emph{et al.} \cite{wilson2017pointless} used an approximation to represent a downscaling model as a convolution matrix within R-INLA \cite{INLA} but more generally, downscaling models are not available in popular software packages and must be programmed explicitely.
+For example, Sturrock \emph{et al.} used only two environmental covariates in their model as although they had a reasonable number of data points, the data were not informative enough to support retaining more covariates \cite{sturrock2014fine}.
+Disaggregation models are also simply an underrepresented class of models in the statistical literature and statistical software relative to model-based geostatistical approaches.
+Likewise, downscaling models are not available in popular software packages and must typically be programmed explicitly though Wilson \emph{et al.} \cite{wilson2017pointless} used an approximation to represent a downscaling model as a convolution matrix within R-INLA \cite{INLA}.
 Furthermore, disaggregation models are relatively difficult to implement as they have more rows of covariate data than response data.
@@
 
-\begin{figure}[t!]
-% to be removed before submission
-\centering
-
-\includegraphics[width = 0.9\textwidth]{figures/random_crossvalidation_full.png} %\caption{Indonesia random crossvalidation}
-
-\caption{{\bf Random cross-validation scheme for Indonesia, PseudoSenegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
-\label{fig:cv_random}
-\end{figure}
-
-\begin{figure}[!t]
-% to be removed before submission
-\centering
-
-\includegraphics[width = 0.9\textwidth]{figures/spatial_crossvalidation_full.png} %\caption{Indonesia random crossvalidation}
-
-\caption{{\bf Spatial cross-validation scheme for Indonesia, PseudoSenegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
-\label{fig:cv_spatial}
-\end{figure}
+%\begin{figure}[t!]
+%% to be removed before submission
+%\centering
+%
+%\includegraphics[width = 0.9\textwidth]{figures/random_crossvalidation_full.png} %\caption{Indonesia random crossvalidation} 
+%
+%\caption{{\bf Random cross-validation scheme for Indonesia, PseudoSenegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+%\label{fig:cv_random}
+%\end{figure}
+%
+%
+%\begin{figure}[!t]
+%% to be removed before submission
+%\centering
+%
+%\includegraphics[width = 0.9\textwidth]{figures/spatial_crossvalidation_full.png} %\caption{Indonesia random crossvalidation} 
+%
+%\caption{{\bf Spatial cross-validation scheme for Indonesia, PseudoSenegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+%\label{fig:cv_spatial}
+%\end{figure}
+%
 
@@
 % to be removed before submission
-\includegraphics[width = 1.05\textwidth]{figures/random_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
+\includegraphics[width = 1.05\textwidth]{figures/random_cv_poly_facet} %\caption{Indonesia spatial crossvalidation} 
 \caption{{\bf Observed-predicted plots for random cross-validation experiments.}
-A-B) Indonesia, C-D) PseudoSenegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
+A) Indonesia, B) PseudoSenegal, C) Madagascar. Square root aggregated incidence (per 1,000).
 Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
-The bimodal distribution in observed prevalence in Indonesia is caused by the large number of surveys with exactly one positive case.
 }
-\label{randompredobsscatter}
+\label{randompredobspolyfacet}
+\end{figure}
+
+\begin{figure}
+% to be removed before submission
+\includegraphics[width = 1.05\textwidth]{figures/random_cv_points_facet} %\caption{Indonesia spatial crossvalidation} 
+\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
+A) Indonesia, B) PseudoSenegal, C) Madagascar. Square root prevalence.
+Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
+}
+\label{randompredobspointfacet}
 \end{figure}
@@
 % to be removed before submission
-\includegraphics[width = 1.05\textwidth]{figures/spatial_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
+\includegraphics[width = 1.05\textwidth]{figures/spatial_cv_scatter} %\caption{Indonesia spatial crossvalidation} 
 \caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
@@
 In only one cases, the joint model was marginally better.
-Therefore we have no evidence that the joint model is better than the polygon-only model at predicting within-polygon, pixel-level malaria risk.
+Therefore we conclude that the joint model is no better than the polygon-only model at predicting within-polygon, pixel-level malaria risk.
 

### 2018-11-20 ms.tex
More dan w edits.

@@
 The aggregation of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
-For example, Sturrock \emph{et al.} used only two environmental covariates in their model as although they had a reasonable number of data points, the data were not informative enough to support retaining more covariates \cite{sturrock2014fine}.
+This lack of statistical power puts constraints on the models that can be fitted for example requiring variable selection and simple linear terms \cite{sturrock2014fine}.
 Disaggregation models are also simply an underrepresented class of models in the statistical literature and statistical software relative to model-based geostatistical approaches.
@@
 
-A model that combines prevalence point-surveys and polygon incidence data, and therefore leverages the strength of both, has great potential.
-Joint modelling of the two data types has the potential to increase statistical power for learning relationships between malaria risk and covariates both by simply making more data available and because point-surveys have a one-to-one relationship with the environment at the location of the survey.
+Given the differing strengths of prevalence point-surveys and polygon incidence data, a model that simultaneously leverages both data types has great potential to improve malaria burden mapping.
+Joint modelling of the two data types could provide increased statistical power for learning relationships between malaria risk and covariates by making more data available and because point-surveys have a one-to-one relationship with gridded environmental covariates at the location and time of the survey.
 Furthermore, using two complimentary datasets potentially allows better spatial coverage \cite{sturrock2016mapping}. 
-One major barrier to this modelling approach is that these two data sources are on different scales: point surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ while routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$.
-One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015defining}.
+One major barrier to a joint modelling approach, however, is that these two data types capture different scales.
+Point surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ that quantify parasite rate at a single moment. In contrast,
+In contrast, routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$ as it spans a period of time (e.g., a year) over which individuals can have multiple malaria infections..
+%One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015defining}.
 
@@
 
-Here we formulate a joint model that combines polygon incidence data and prevalence point-surveys of \emph{Plasmodium falciparum} using seperate likelihoods for the two data types.
-We relate the two malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
-We compare the joint model to a polygon-only, disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and a further benchmark model that contains only prevalence point-survey data using data from Indonesia, PseudoSenegal and Madagascar as case studies.
-We find that the joint model performs better than the polygon-only model in cases where predictions are needed far from the location of the data or when little data is available for learning relationships between covariates and malaria risk.
+Here we formulate a joint model that combines polygon incidence data and prevalence point-surveys of \emph{Plasmodium falciparum} using seperate likelihoods for both data types.
+We relate the differing malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
+We then compare results from the joint model with those made using (a) a polygon-only, disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and (b) a model created using prevalence point-survey data similar to the model used by Bhatt \emph{et al.}\cite{bhatt2015effect}.
+Each set of three models is applied to data from Indonesia, Senegal and Madagascar to provide a set of case studies with disparate geographic settings and levels of malaria endemicity.
+We find that the joint model performs better than the polygon-only model in cases where predictions are needed far from the location of the data or when there are few polygon incidence datapoints available for learning relationships between covariates and malaria risk.
 
@@
 We used two data sources that reflect malaria burden; prevalence point-surveys and polygon incidence data.
-We selected Indonesia, PseudoSenegal and Madagascar as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
+We selected Indonesia, Senegal and Madagascar as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
 To minimise temporal effects we select, for each country, one year of prevalence point-survey data and one year of polygon incidence data.
 For Indonesia we selected 2012 for polygon incidence data (380 regions) and 2010 for prevalence data (969 surveys, 128,537 individuals).
-For PseudoSenegal we selected 2015 for both polygon incidence data (46 regions) and prevalence data (216 surveys, 8,114). % update todo
+For Senegal we selected 2015 for both polygon incidence data (46 regions) and prevalence data (216 surveys, 8,114). % update todo
 Finally, for Madagascar we selected 2013 for both polygon incidence (110 regions) and prevalence (290 surveys, 7,244 individuals) data.
@@
 We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
-We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, PseudoSenegal $\zeta = 1$ and Madagascar $\zeta = 1$.
+We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = 1$ and Madagascar $\zeta = 1$.
 We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \cite{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.
@@
 %
-%\caption{{\bf Random cross-validation scheme for Indonesia, PseudoSenegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+%\caption{{\bf Random cross-validation scheme for Indonesia, Senegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
 %\label{fig:cv_random}
@@
 %
-%\caption{{\bf Spatial cross-validation scheme for Indonesia, PseudoSenegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+%\caption{{\bf Spatial cross-validation scheme for Indonesia, Senegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
 %\label{fig:cv_spatial}
@@
 This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularise our model.
-This regularisation is particularly important given the small number of observations in PseudoSenegal (n = 46) and Madagascar (n = 110).
+This regularisation is particularly important given the small number of observations in Senegal (n = 46) and Madagascar (n = 110).
 
@@
 In the second validation scheme the data was split into spatial cross-validation folds (see Figure~\ref{fig:cv_spatial}).
-The number of folds was seven for Indonesia, four for PseudoSenegal and three for Madagascar due to their differing sizes and geographies.
+The number of folds was seven for Indonesia, four for Senegal and three for Madagascar due to their differing sizes and geographies.
 The data was divided by combining the prevalence point-survey locations and the centroids of the incidence polygons and performing k means clustering.
@@
 Incidence & Indonesia & 18.33 & {\bf 14.02} &  14.09\\
-& PseudoSenegal & 51.24 & {\bf 26.74} &  28.45\\
+& Senegal & 51.24 & {\bf 26.74} &  28.45\\
 & Madagascar & 85.54 & 37.45 &  {\bf 34.49}\vspace{3mm}\\
 Prevalence & Indonesia & 0.010 & 0.010 &  0.010\\
-& PseudoSenegal & {\bf 0.015} & 0.024 &  0.024\\
+& Senegal & {\bf 0.015} & 0.024 &  0.024\\
 & Madagascar & {\bf 0.054} & 0.059 &  0.059\\
@@
 Incidence & Indonesia &  18.13 &  {\bf 14.77} &   15.02\\
-& PseudoSenegal &  51.17 &  41.43 &   {\bf 36.76}\\
+& Senegal &  51.17 &  41.43 &   {\bf 36.76}\\
 & Madagascar & 107.32 &  71.44 &   {\bf 65.50}\vspace{3mm}\\
 Prevalence & Indonesia & 0.011 & {\bf 0.010} &  {\bf 0.010}\\
-& PseudoSenegal & {\bf 0.015} & 0.019 &  0.019\\
+& Senegal & {\bf 0.015} & 0.019 &  0.019\\
 & Madagascar & 0.069 & 0.066 &  {\bf 0.065}\\
@@
 Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
-The data were split into seven, four and three groups in Indonesia, PseudoSenegal and Madagascar respectively.
+The data were split into seven, four and three groups in Indonesia, Senegal and Madagascar respectively.
 \end{flushleft}
@@
 
-For the random cross-validation experiments, the polygon-only model had the lowest mean absolute error, with respect to predicting incidence, for Indonesia and PseudoSenegal (Table~\ref{table1}).
+For the random cross-validation experiments, the polygon-only model had the lowest mean absolute error, with respect to predicting incidence, for Indonesia and Senegal (Table~\ref{table1}).
 Incidence in Madagascar was best predicted by the joint model.
@@
 \caption{{\bf Observed-predicted plots for random cross-validation experiments.}
-A) Indonesia, B) PseudoSenegal, C) Madagascar. Square root aggregated incidence (per 1,000).
+A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (per 1,000).
 Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
@@
 \caption{{\bf Observed-predicted plots for random cross-validation experiments.}
-A) Indonesia, B) PseudoSenegal, C) Madagascar. Square root prevalence.
+A) Indonesia, B) Senegal, C) Madagascar. Square root prevalence.
 Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
@@
 \caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
-A-B) Indonesia, C-D) PseudoSenegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
+A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
 Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
@@
 Incidence & Random & Indonesia & 0.13 & 0.72 &  0.73\\
-&& PseudoSenegal & 0.11 & 0.80 &  0.85\\
+&& Senegal & 0.11 & 0.80 &  0.85\\
 && Madagascar & 0.59 & 0.82 &  0.77\vspace{1mm}\\
 & Spatial & Indonesia & 0.14 & 0.76 &  0.68\\
-&& PseudoSenegal & 0.30 & 0.67 &  0.70\\
+&& Senegal & 0.30 & 0.67 &  0.70\\
 && Madagascar & 0.68 & 0.65 &  0.68\vspace{3mm} \\
 Prevalence & Random & Indonesia & 0.90 & 0.50 &  0.80\\
-&& PseudoSenegal & 0.80 & 0.71 &  0.91\\
+&& Senegal & 0.80 & 0.71 &  0.91\\
 && Madagascar & 0.83 & 0.53 &  0.74\vspace{1mm}\\
 & Spatial & Indonesia & 0.87 & 0.62 &  0.96\\
-&& PseudoSenegal & 0.90 & 0.88 &  0.79\\
+&& Senegal & 0.90 & 0.88 &  0.79\\
 && Madagascar & 0.93 & 0.68 &  0.83\\
@@
 
-The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both PseudoSenegal and  Madagascar while the wighted MAE was the same for all three models in Indonesia (Table~\ref{table1}).
+The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both Senegal and  Madagascar while the wighted MAE was the same for all three models in Indonesia (Table~\ref{table1}).
 The more pertinent comparison is whether the addition of the prevalence data improves the ability of the polygon-only models to predict pixel level prevalence.
-However, weighted MAE was unchanged between the polygon-only model and the joint model for Indonesia, PseudoSenegal or Madagascar.
+However, weighted MAE was unchanged between the polygon-only model and the joint model for Indonesia, Senegal or Madagascar.
 Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F.
-All models show poor predictive performance in Indonesia and PseudoSenegal with none of the models being able to accurately predict the large number of points with zero prevalence.
+All models show poor predictive performance in Indonesia and Senegal with none of the models being able to accurately predict the large number of points with zero prevalence.
 The predictions in Madagascar are better though the large number of surveys with measured prevalence of zero are still problematic.
@@
 Maps of the Indonesian input data and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
-Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for PseudoSenegal show broad agreement with malaria incidence being higher in the South.
+Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for Senegal show broad agreement with malaria incidence being higher in the South.
 
@@
 
-For the spatial cross-validation experiments, the joint model had the best predictive performance for both PseudoSenegal and Madagascar.
+For the spatial cross-validation experiments, the joint model had the best predictive performance for both Senegal and Madagascar.
 The polygon-only model again had the lowest mean absolute error between observed and predicted incidence for Indonesia (Table~\ref{table2}).
@@
 
-Again, the benchmark points-only model had the lowest weighted MAE between spatially cross-validated observed and predicted prevalence for PseudoSenegal.
+Again, the benchmark points-only model had the lowest weighted MAE between spatially cross-validated observed and predicted prevalence for Senegal.
 However, for Indonesia, both the polygon-model and the joint model marginally outperformed the points-only model. 
 However, scatter plots of the out-of-sample predictions show that there is almost no correlation between observed and predicted values (Figures~\ref{randompredobsscatter} B, D and F).
-For PseudoSenegal, the joint model (0.065) had the lowest weighted MAE for predicted prevalence though this was again marginal (points-only 0.069, polygons-only 0.066).
+For Senegal, the joint model (0.065) had the lowest weighted MAE for predicted prevalence though this was again marginal (points-only 0.069, polygons-only 0.066).
 Again the survey-points with prevalence of zero were difficult to correctly predict.
@@
 For example, the whole of Papua and West Papua the the East are held out in a single fold.
-In contrast the predictions for PseudoSenegal do not match those observed in the input data (Figures~\ref{predobsmapsen}A and C).
+In contrast the predictions for Senegal do not match those observed in the input data (Figures~\ref{predobsmapsen}A and C).
 
@@
 However, with respect to uncertainty in prevalence point-survey predictions, the coverage was substantially improved in three of six cases and marginally improved in one case.
-Coverage improved in the random cross-validation in Indonesia and Madagascar and spatial cross-validation in Madagascar and marginally improved in the spatial cross-validation in PseudoSenegal.
-In the remaining two cases, adding prevalence point-surveys did not substantially improve coverage, but did make the model more conservative, with coverage of 0.91 rather than 0.71 in the random cross-validation PseudoSenegal experiment and 0.96 instead of 0.62 in the spatial cross-validation Indonesia experiment.
+Coverage improved in the random cross-validation in Indonesia and Madagascar and spatial cross-validation in Madagascar and marginally improved in the spatial cross-validation in Senegal.
+In the remaining two cases, adding prevalence point-surveys did not substantially improve coverage, but did make the model more conservative, with coverage of 0.91 rather than 0.71 in the random cross-validation Senegal experiment and 0.96 instead of 0.62 in the spatial cross-validation Indonesia experiment.
 
@@
 
-%figure 3 and 4. data and predicted incidence maps. Indonesia and PseudoSenegal only. Fig 3 ind, fig 4 rand. Data, Rand, Spatial for best model? Joint model?
+%figure 3 and 4. data and predicted incidence maps. Indonesia and Senegal only. Fig 3 ind, fig 4 rand. Data, Rand, Spatial for best model? Joint model?
 
@@
 \caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for PseudoSenegal.
+The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
 }
@@
 With regards to a random cross-validation scheme, adding prevalence point-surveys to the disaggregation model only improved performance in  Madagascar (Table~\ref{table1}).
-With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the prevalence point-surveys improved on the polygon-only models in both PseudoSenegal and Madagascar but not Indonesia (Table~\ref{table2}).
+With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the prevalence point-surveys improved on the polygon-only models in both Senegal and Madagascar but not Indonesia (Table~\ref{table2}).
 
 We used held-out prevalence point-surveys to measure how well the models predicted within-polygon, pixel-level malaria risk.
-Given the poor performance by all models, including the points-only model (Figures~\ref{randompredobsscatter} and \ref{spatialpredobsscatter}), particularly in Indonesia and PseudoSenegal these results must be interpreted with care.
+Given the poor performance by all models, including the points-only model (Figures~\ref{randompredobsscatter} and \ref{spatialpredobsscatter}), particularly in Indonesia and Senegal these results must be interpreted with care.
 % Add sample size, comparisons etc.
@@
 Figure~\ref{fig:cv_random} implies that this situation is the norm.
-Yet this spatial information did not improve performance in Indonesia or PseudoSenegal.
+Yet this spatial information did not improve performance in Indonesia or Senegal.
 
@@
 This approach is feasible but does not allow any information from the polygons to inform non-linear relationships.
-To directly model non-linear effects in the full model could be achieved by including simple non-linear functions such as splines \cite{sissoko2017temporal, sewe2017using, hundessa2018projecting}, though the increased model complexity would require more data than was used in PseudoSenegal and Madagascar in this study.
+To directly model non-linear effects in the full model could be achieved by including simple non-linear functions such as splines \cite{sissoko2017temporal, sewe2017using, hundessa2018projecting}, though the increased model complexity would require more data than was used in Senegal and Madagascar in this study.
 Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \cite{law2018variational}.

### 2018-11-22 ms.tex
Add si and make fig refs in text point to si.

@@
 
+\usepackage{xr}
+\externaldocument{si}
+
 %% END MACROS SECTION
@@
 Tim C.D.
-Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Rosalind Howes \textsuperscript{1}, Katherine Battle \textsuperscript{1}, Andre Python \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Dan Weiss\textsuperscript{1},
+Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Rosalind Howes \textsuperscript{1}, Katherine Battle \textsuperscript{1}, Andre Python \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Dan Weiss\textsuperscript{1}
 \\

### 2018-11-22 si.tex
Add si and make fig refs in text point to si.

--- 2018-11-22 ms.tex
@@
 
-\usepackage{xr}
-\externaldocument{si}
-
+\renewcommand\thefigure{S\arabic{figure}} 
+\renewcommand\thetable{S\arabic{table}} 
 %% END MACROS SECTION
@@
 {\Large
-\textbf\newline{Joint modelling of aggregated incidence data and point prevalence surveys for malaria mapping} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Supplementary Material: Joint modelling of aggregated incidence data and point prevalence surveys for malaria mapping} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 
+\end{flushleft}
+
 % Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
@@
 
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* timcdlucas@gmail.com
+\clearpage
 
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-As malaria incidence decreases and more contries move towards elimination, maps of malaria risk in low prevalence areas are becoming increasingly needed.
-However, traditional mapping using prevalence point-surveys are often ineffective in low prevalence areas due to low statistical power and a lack of data.
-Therefore, models must be developed that can estimate risk at high spatial resolution from surveillance data that reports incidence aggregated to a geographic polygon.
-Current models formulated for polygon incidence data suffer from lower statistical power for learning relationships between malaria risk and environmental covariates.
-Here we present a joint model that uses both polygon incidence and prevalence point-surveys.
+\begin{figure}[h!]
 
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-\section*{Author summary}
-Todo
+\centering
 
-\linenumbers
+\includegraphics[width = 0.9\textwidth]{figures/random_crossvalidation_full.png}
 
-% Use "Eq" instead of "Equation" for equation citations.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Glossary
-% Models:
-%   Joint model
-%   Polygon-only model
-%   Point-only model
-% Data:
-%   Prevalence point-surveys
-%   Polygon incidence
-% Variables:
-%   Pixel-level prevalence
-%   Polygon-level incidence
-%   Pixel-level incidence
-
-Global malaria incidence has decreased dramatically over the last 20 years \cite{abajobir2017global, bhatt2015effect}.
-This decrease has been accompanied by a strategic shift towards aiming for elimination in low incidence countries \cite{world2016world, newby2016path}.
-Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases \cite{sturrock2016mapping, cohen2017mapping}.
-However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \cite{gething2011new, bhatt2017improved, gething2012long, bhatt2015effect} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite{sturrock2016mapping, sturrock2014fine}.
-In low burden areas, very large sample sizes are needed before a prevalence survey is informative because so few individuals have parasitaemia that most sample points will have no cases.
-As a result, large, countrywide surveys of prevalence, such as DHS or MIS, are rare in low burden countries due to costs and percieved low utility \cite{dhs}.
-We therefore need new data sources and associated statistical methods.
-
-%Despite major reductions in incidence over the last fifteen years, malaria still causes millions of deaths and loads of DALYs annually \cite{abajobir2017global}.
-%Elimination of malaria, country-by-county has become a central goal in the global malaria strategy \cite{world2016world}.
-%Elimination of malaria requires high resolution maps of malaria risk, in low prevalence areas in order to optimise interventions and minimise costs \cite{sturrock2016mapping}.
-
-%cohen2017mapping Different metrics are useful for different things. Most maps use prevalence. Govts do use maps.
-
-Routine surveillance data, of malaria case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
-Surveillance data is commonly aggregated from information collected at healthcare facilities or by community health workers, reporting the number of cases that occurred within a certain geographic or administrative region defined by a polygon.
-This polygon incidence data can be more sensitive than prevalence point-surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
-Furthermore, polygon incidence data is also often timely, with reports being released annually or monthly with little lag, while countrywide collection of prevalence point-surveys are both rare and often released one to two years after field data collection is completed.
-However, the unstructured nature of data collection and reporting of polygon incidence data from national disease surveillance systems means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.
-
-%however surveillance data is sometimes high quality in these areas
-%pixel level maps from aggregates data is difficult (sturrock2014fine, wilson2017pointless, law2018variational, others)
-%not much information for covariates 
-%sturrock used two.
-%undeveloped area of statistics but see Leon.
-
-Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level incidence \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
-However using polygon incidence data to estimate malaria risk for high resolution maps presents several noteworthy modelling difficulties. 
-%Disaggregation models aim to estimate high-resolution maps from aggregated data and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
-The aggregation of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
-This lack of statistical power puts constraints on the models that can be fitted for example requiring variable selection and simple linear terms \cite{sturrock2014fine}.
-Disaggregation models are also simply an underrepresented class of models in the statistical literature and statistical software relative to model-based geostatistical approaches.
-Likewise, downscaling models are not available in popular software packages and must typically be programmed explicitly though Wilson \emph{et al.} \cite{wilson2017pointless} used an approximation to represent a downscaling model as a convolution matrix within R-INLA \cite{INLA}.
-Furthermore, disaggregation models are relatively difficult to implement as they have more rows of covariate data than response data.
-
-Given the differing strengths of prevalence point-surveys and polygon incidence data, a model that simultaneously leverages both data types has great potential to improve malaria burden mapping.
-Joint modelling of the two data types could provide increased statistical power for learning relationships between malaria risk and covariates by making more data available and because point-surveys have a one-to-one relationship with gridded environmental covariates at the location and time of the survey.
-Furthermore, using two complimentary datasets potentially allows better spatial coverage \cite{sturrock2016mapping}. 
-One major barrier to a joint modelling approach, however, is that these two data types capture different scales.
-Point surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ that quantify parasite rate at a single moment. In contrast,
-In contrast, routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$ as it spans a period of time (e.g., a year) over which individuals can have multiple malaria infections..
-%One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015defining}.
-
-%Ideal situation is to combine data
-%benefits of both
-%but data are on different scales
-%Ewan says there's a relationship.
-
-Here we formulate a joint model that combines polygon incidence data and prevalence point-surveys of \emph{Plasmodium falciparum} using seperate likelihoods for both data types.
-We relate the differing malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
-We then compare results from the joint model with those made using (a) a polygon-only, disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and (b) a model created using prevalence point-survey data similar to the model used by Bhatt \emph{et al.}\cite{bhatt2015effect}.
-Each set of three models is applied to data from Indonesia, Senegal and Madagascar to provide a set of case studies with disparate geographic settings and levels of malaria endemicity.
-We find that the joint model performs better than the polygon-only model in cases where predictions are needed far from the location of the data or when there are few polygon incidence datapoints available for learning relationships between covariates and malaria risk.
-
-%here we compared 3 models, point only, polygon only and joint models
-%we use Madagascar and Indonesia as case studies as they have good %surveillance data and good pr data.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Materials and methods}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Malaria data}
-
-We used two data sources that reflect malaria burden; prevalence point-surveys and polygon incidence data.
-We selected Indonesia, Senegal and Madagascar as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
-To minimise temporal effects we select, for each country, one year of prevalence point-survey data and one year of polygon incidence data.
-For Indonesia we selected 2012 for polygon incidence data (380 regions) and 2010 for prevalence data (969 surveys, 128,537 individuals).
-For Senegal we selected 2015 for both polygon incidence data (46 regions) and prevalence data (216 surveys, 8,114). % update todo
-Finally, for Madagascar we selected 2013 for both polygon incidence (110 regions) and prevalence (290 surveys, 7,244 individuals) data.
-
-\subsection*{Prevalence survey data}
-
-The prevalence point-survey data were extracted from the Malaria Atlas Project prevalence survey database \cite{bhatt2015effect}.
-As the prevalence point-surveys cover different age ranges they were standardised to an age-range of 2--10 using the model from \cite{smith2007standardizing}.
-Many of the points have relatively small sample sizes.
-285 surveys out of 290 in Senegal have a sample size less than 50 while 618 out of 969 surveys in Indonesia have a sample size less than 100.
-Furthermore, due to the small sample sizes and low malaria prevalence in these countries, many of the surveys have find very few malaria infections.
-Amongst the Senegal surveys, 189 out of 290 have zero positive cases while a further 30 have only one positive case.
-In Indonesia 620 out of 969 surveys have zero positive cases and 195 have one positive case.
-Finally, in Madagascar 189 out of 290 surveys have zero positive cases and 30 have one positive case.
-The age standardisation model gives the surveys with zero positive cases a small positive prevalence.
-
-\subsection*{Polygon incidence data}
-
-% (Figures~\ref{predobsmapidn}A and \ref{predobsmapsen}A)
-
-The polygon incidence data were collated from various government reports.
-To account for underreporting of clinical cases due to lack of treatment seeking, missed case reports and cases that sought medical attention outside the public health systems, the methods in \cite{cibulskis2011worldwide} were used using estimates of treatment seeking from \cite{battle2016treatment}.
-Where species specific reports were given, these were used. 
-For reports where no species specific, national estimates of the ratio between \emph{P. falciparum} and \emph{P. vivax} cases were used to calculate \emph{P. falciparum} only cases.
-
-\subsection*{Population data}
-
-Raster surfaces of population for the years 2005, 2010 and 2015, were created using a hybrid of data from GPWv4 \cite{gpw4} and WorldPop \cite{tatem2017worldpop}, with the latter taking priority for those pixels where both had population data.
-Final population rasters were created by linear interpolation of the surrounding five-yearly rasters.
-Finally, for each year, national population estimates from the UN were raked over the interpolated population surfaces.
-
-\subsection*{Covariate data}
-
-We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres at the equator that included land surface temperature annual mean and standard deviation \cite{LST}, enhanced vegetation index \cite{TCB}, mosquito temperature suitability index \cite{weiss2014air}, elevation \cite{SRTMElev}, tassel cap brightness \cite{TCB}, tassel cap wetness \cite{TCB}, accessibility to cities \cite{weiss2018global}, night lights \cite{} and proportion of urban land cover \cite{}.
-Elevation, land surface temperature standard deviation, accessibility to cities and night lights were all log transformed to reduce skewness.
-After preliminary analyses, tassel cap brightness and urban land cover were removed as they were highly correlated with other variables.
-The covariates were standardised to have a mean of zero and a standard deviation of one.
-
-\subsection*{The model}
-
-We compared three models 1) a full model with prevalence point-surveys and polygon incidence data 2) the submodel with only polygon incidence data and 3) the benchmark submodel with only prevalence point-survey data.
-The models were implemented and fitted in R \cite{R} using Template Model Builder \cite{TMB} which allows a Laplace approximation of the posterior to be calculated.
-
-The full, joint likelihood model is described as follows. 
-Values at the aggregate, polygon level are given the subscript $a$ while pixel or point level variables are indexed with $b$.
-The polygon incidence case count data, $y_j$ is given a Poisson likelihood
-
-$$y_a \sim \operatorname{Pois}(i_a\mathrm{pop_a})$$
-
-where $i_a$ is the estimated polygon incidence rate and $\mathrm{pop_a}$ is the observed polygon population-at-risk.
-
-The prevalence point-survey data, $z_b$, is given a binomial likelihood
-
-$$z_b \sim \operatorname{Binom}(p_b, n_b) $$
-
-where $p_b$ is the estimated prevalence and $n_b$ is the observed survey sample size.
-
-The two quantities are linked to each other and to the predictor variables by the following system of equations.
-
-$$i_a = \frac{ \sum_{b \in a}(i_b \mathrm{pop}_b)}{\sum_{b \in a}\mathrm{pop}_b} $$
-
-where
-
-$$i_b = \mathrm{PrevInc}(p_b)$$
-
-where $\mathrm{PrevInc}$ is a function from a previously fitted model \cite{cameron2015defining} 
-$$\mathrm{PrevInc}: f\left(p_b\right) = 2.616p_b - 3.596{p_b}^2 + 1.594{p_b}^3.$$
-
-The linear predictor of the model, $\eta_b$, is related to prevalence by a typical logit link function.
-
-$$p_b = \operatorname{logit}^{-1}(\eta_b)$$
-
-The form of the link function means we get predictions of prevalence and incidence simultaneously whether we used both data types or just one.
-The linear predictor is composed of an intercept, covariates, a spatial, Gaussian random field and two iid random effects.
-
-$$\eta_b = \beta_0 + \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) + w_i(\sigma_w)$$
-
-The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
-The first iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all pixels and point surveys within polygon $j$ being grouped together.
-This random effect modelled both missing covariates and extra-Poisson sampling error. 
-The second iid random effect, $w_i \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
-This effect modelled extra-binomial sampling noise.
-As such, this random effect is not included in the predicted uncertainty in the incidence or prevalence layers.
-However, it is included in predictions of out-of-sample point surveys.
-The randoms effects are all integrated out during the TMB model fitting.
-The hyperparameters are fitted during model fitting using empirical Bayes.
-In this empirical Bayes scheme the hyperparameters are learned from the data but are treated as point estimates rather than the model using the full posterior of the hyperparameters.
-
-Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
-We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
-We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = 1$ and Madagascar $\zeta = 1$.
-We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \cite{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.
-
-We assigned $\sigma_v$ a penalised complexity prior \cite{simpson2017penalising} such that $P(\sigma_v > 0.05) = 0.0000001$
-This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for the case counts using the approach defined in \cite{cibulskis2011worldwide}.
-We found that an iid effect with a standard deviation of 0.05 would be able to account for the discrepancy between the assumed Poisson error and the independently derived error.
-We assigned $\sigma_w$ a penalised complexity prior such that $P(\sigma_w > 0.3) = 0.0000001$. 
-This was chosen by finding the maximum difference in prevalence between point-surveys (with a sample size greater than 500) within the same raster pixel.
-The differences between points within the same pixel can only be accounted for by the binomial error and this iid effect.
-Given that the error on a prevalence estimate with sample size greater than 500 is quite small, the iid effect needs to be able to explain this difference.
-
-%\begin{figure}[t!]
-%% to be removed before submission
-%\centering
-%
-%\includegraphics[width = 0.9\textwidth]{figures/random_crossvalidation_full.png} %\caption{Indonesia random crossvalidation} 
-%
-%\caption{{\bf Random cross-validation scheme for Indonesia, Senegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
-%\label{fig:cv_random}
-%\end{figure}
-%
-%
-%\begin{figure}[!t]
-%% to be removed before submission
-%\centering
-%
-%\includegraphics[width = 0.9\textwidth]{figures/spatial_crossvalidation_full.png} %\caption{Indonesia random crossvalidation} 
-%
-%\caption{{\bf Spatial cross-validation scheme for Indonesia, Senegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
-%\label{fig:cv_spatial}
-%\end{figure}
-%
-
-Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
-Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of -3, each covariate would be able to predict prevalences between 0.004 and 0.27. 
-This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularise our model.
-This regularisation is particularly important given the small number of observations in Senegal (n = 46) and Madagascar (n = 110).
-
-\subsection*{Experiments}
-
-To compare the three models we used two cross-validation schemes. 
-In the first, the combined data set of prevalence and incidence data was split into ten cross-validation folds stratified by data type (Figure~\ref{fig:cv_random}).
-This reflects real world data where we in some locations we have incidence data but no prevalence data and visa versa.
-Thus this cross-validation scheme can be seen as asking whether the joint model is preferable to using just polygon incidence data.
-
-%figure 1.cross validation. %% Do fig 1 and 2, random and spatial cv. IDN on top, MDG and SEN below in each.
-
-In the second validation scheme the data was split into spatial cross-validation folds (see Figure~\ref{fig:cv_spatial}).
-The number of folds was seven for Indonesia, four for Senegal and three for Madagascar due to their differing sizes and geographies.
-The data was divided by combining the prevalence point-survey locations and the centroids of the incidence polygons and performing k means clustering.
-This scheme is testing the models' ability to predict into new areas with little information from the spatial random field.
-
-In both cases we examined performance metrics for both the withheld prevalence point-survey data and the withheld incidence polygon data.
-As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
-We considered the ability to predict polygon incidence correctly our main objective and our performance metric was mean absolute error (MAE).
-However, a problem with using polygon data in a cross-validation scheme is that a model can perform well at the polygon level but not correctly predict the pixel-level malaria risk.
-Predictive performance on prevalence survey-points is one way to measure how well a model can predict pixel-level malaria risk.
-However, in areas of low prevalence, small or moderately sized prevalence point-surveys can be noisy or unsensitive and so care must be taken when interpreting predictive performance on these data.
-Therefore our secondary metric was MAE, weighted by survey sample size, of prevalence point-surveys.
-While other metrics could have been used, we specifically did not use correlation as correlation measures linear dependance without regard to slope or intercept.
-As the models are being fitted on data on difference scales we found that observations and predictions were sometimes correlated but strongly displaced from the one-one line and therefore correlation metrics were misleading.
-% Why not correlation
-To assess how well the models were calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.
-
-\begin{table}[!t]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\caption{
-{\bf Summary of out-of-sample accuracy for random cross-validation experiment.}}
-\begin{tabular}{llllll}
-\hline
-{\bf Holdout data} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
-\thickhline 
-Incidence & Indonesia & 18.33 & {\bf 14.02} &  14.09\\
-& Senegal & 51.24 & {\bf 26.74} &  28.45\\
-& Madagascar & 85.54 & 37.45 &  {\bf 34.49}\vspace{3mm}\\
-Prevalence & Indonesia & 0.010 & 0.010 &  0.010\\
-& Senegal & {\bf 0.015} & 0.024 &  0.024\\
-& Madagascar & {\bf 0.054} & 0.059 &  0.059\\
-\end{tabular}
-\begin{flushleft}
-Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
-The data were split randomly into 10 groups stratified by data type (incidence polygon and prevalence points).
-\end{flushleft}
-\label{table1}
-\end{adjustwidth}
-\end{table}
-
-\begin{table}[!t]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\caption{
-{\bf Summary of out-of-sample accuracy for spatial cross-validation experiment.}}
-\begin{tabular}{llllll}
-\hline
-{\bf Holdout data} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
-\thickhline 
-Incidence & Indonesia &  18.13 &  {\bf 14.77} &   15.02\\
-& Senegal &  51.17 &  41.43 &   {\bf 36.76}\\
-& Madagascar & 107.32 &  71.44 &   {\bf 65.50}\vspace{3mm}\\
-Prevalence & Indonesia & 0.011 & {\bf 0.010} &  {\bf 0.010}\\
-& Senegal & {\bf 0.015} & 0.019 &  0.019\\
-& Madagascar & 0.069 & 0.066 &  {\bf 0.065}\\
-\end{tabular}
-\begin{flushleft}
-Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
-The data were split into seven, four and three groups in Indonesia, Senegal and Madagascar respectively.
-\end{flushleft}
-\label{table2}
-\end{adjustwidth}
-\end{table}
-
-% Results and Discussion can be combined.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Random results
-% Maps, reasonable for both
-% MAE performance.
-
-For the random cross-validation experiments, the polygon-only model had the lowest mean absolute error, with respect to predicting incidence, for Indonesia and Senegal (Table~\ref{table1}).
-Incidence in Madagascar was best predicted by the joint model.
-However, the difference between the two models in Indonesia was small.
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter}A, C and E.
-From the scatter plots it can be seen that the point-only model is strongly biased, overestimating incidence in Indonesia and Madagascar and underestimating incidence in Senegal.
-
-%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
-\begin{figure}
-% to be removed before submission
-\includegraphics[width = 1.05\textwidth]{figures/random_cv_poly_facet} %\caption{Indonesia spatial crossvalidation} 
-\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
-A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (per 1,000).
-Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
-}
-\label{randompredobspolyfacet}
+\caption{{\bf Random cross-validation scheme for Indonesia, Senegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+\label{fig:cv_random}
 \end{figure}
 
-\begin{figure}
-% to be removed before submission
-\includegraphics[width = 1.05\textwidth]{figures/random_cv_points_facet} %\caption{Indonesia spatial crossvalidation} 
-\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
-A) Indonesia, B) Senegal, C) Madagascar. Square root prevalence.
-Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
-}
-\label{randompredobspointfacet}
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.9\textwidth]{figures/spatial_crossvalidation_full.png}
+
+\caption{{\bf Spatial cross-validation scheme for Indonesia, Senegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+\label{fig:cv_spatial}
 \end{figure}
 
-%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
-\begin{figure}
-% to be removed before submission
-\includegraphics[width = 1.05\textwidth]{figures/spatial_cv_scatter} %\caption{Indonesia spatial crossvalidation} 
-\caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
-A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
-Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
-The bimodal distribution in observed prevalence in Indonesia is caused by the large number of surveys with exactly one positive case.
-}
-\label{spatialpredobsscatter}
-\end{figure}
-
-\begin{table}[t]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\caption{
-{\bf Summary of coverage of 80\% credible intervals.}}
-\begin{tabular}{llllll}
-\hline
-{\bf Holdout data} & {\bf Cross-validation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
-\thickhline 
-Incidence & Random & Indonesia & 0.13 & 0.72 &  0.73\\
-&& Senegal & 0.11 & 0.80 &  0.85\\
-&& Madagascar & 0.59 & 0.82 &  0.77\vspace{1mm}\\
-& Spatial & Indonesia & 0.14 & 0.76 &  0.68\\
-&& Senegal & 0.30 & 0.67 &  0.70\\
-&& Madagascar & 0.68 & 0.65 &  0.68\vspace{3mm} \\
-Prevalence & Random & Indonesia & 0.90 & 0.50 &  0.80\\
-&& Senegal & 0.80 & 0.71 &  0.91\\
-&& Madagascar & 0.83 & 0.53 &  0.74\vspace{1mm}\\
-& Spatial & Indonesia & 0.87 & 0.62 &  0.96\\
-&& Senegal & 0.90 & 0.88 &  0.79\\
-&& Madagascar & 0.93 & 0.68 &  0.83\\
-\end{tabular}
-\begin{flushleft}
-
-\end{flushleft}
-\label{table3}
-\end{adjustwidth}
-\end{table}
-
-The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both Senegal and  Madagascar while the wighted MAE was the same for all three models in Indonesia (Table~\ref{table1}).
-The more pertinent comparison is whether the addition of the prevalence data improves the ability of the polygon-only models to predict pixel level prevalence.
-However, weighted MAE was unchanged between the polygon-only model and the joint model for Indonesia, Senegal or Madagascar.
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F.
-All models show poor predictive performance in Indonesia and Senegal with none of the models being able to accurately predict the large number of points with zero prevalence.
-The predictions in Madagascar are better though the large number of surveys with measured prevalence of zero are still problematic.
-
-Maps of the Indonesian input data and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
-Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for Senegal show broad agreement with malaria incidence being higher in the South.
-
-% Further results. Accuracy or recall of Sen. Correlation for some?
-
-% Spatial results
-% Maps, reasonable for india, get's broad pattern even far away from data. Poor for SEN, wrong overall pattern. Different covariates.
-% MAE performance.
-
-For the spatial cross-validation experiments, the joint model had the best predictive performance for both Senegal and Madagascar.
-The polygon-only model again had the lowest mean absolute error between observed and predicted incidence for Indonesia (Table~\ref{table2}).
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{spatialpredobsscatter}A, C and E.
-
-Again, the benchmark points-only model had the lowest weighted MAE between spatially cross-validated observed and predicted prevalence for Senegal.
-However, for Indonesia, both the polygon-model and the joint model marginally outperformed the points-only model. 
-However, scatter plots of the out-of-sample predictions show that there is almost no correlation between observed and predicted values (Figures~\ref{randompredobsscatter} B, D and F).
-For Senegal, the joint model (0.065) had the lowest weighted MAE for predicted prevalence though this was again marginal (points-only 0.069, polygons-only 0.066).
-Again the survey-points with prevalence of zero were difficult to correctly predict.
-
-Maps of the Indonesian input data and spatially out-of-sample predictions (Figures~\ref{predobsmapidn}A and C) suggest the that the broad spatial patterns were once again recovered.
-This acceptable performance is notable given the very large areas held out-of-sample (Fig~\ref{fig:cv_spatial}).
-For example, the whole of Papua and West Papua the the East are held out in a single fold.
-In contrast the predictions for Senegal do not match those observed in the input data (Figures~\ref{predobsmapsen}A and C).
-
-% Coverage results
-
-The polygon-only model and the joint model seem to be fairly well calibrated (Table~\ref{table3}).
-The proportion of out-of-sample incidence datapoints being within their 80\% credible intervals ranged between 0.65 and 0.85.
-The proportion of out-of-sample prevalence datapoints being within their 80\% credible intervals ranged from 0.50 to 0.96.
-The points-only model was reasonably well calibrated for predictions of prevalence (coverage ranging from 0.8 to 0.93) but was poorly calibrated for predicting incidence with coverage values as low as 0.11 and the best coverage value being 0.68 for spatial cross-validation in Madagascar.
-
-With respect to uncertainty in polygon incidence predictions, the polygon-only model and joint model were similar; adding the prevalence point-survey data sometimes improved coverage and sometimes made it worse.
-However, with respect to uncertainty in prevalence point-survey predictions, the coverage was substantially improved in three of six cases and marginally improved in one case.
-Coverage improved in the random cross-validation in Indonesia and Madagascar and spatial cross-validation in Madagascar and marginally improved in the spatial cross-validation in Senegal.
-In the remaining two cases, adding prevalence point-surveys did not substantially improve coverage, but did make the model more conservative, with coverage of 0.91 rather than 0.71 in the random cross-validation Senegal experiment and 0.96 instead of 0.62 in the spatial cross-validation Indonesia experiment.
-
-% Overall
-
-%figure 3 and 4. data and predicted incidence maps. Indonesia and Senegal only. Fig 3 ind, fig 4 rand. Data, Rand, Spatial for best model? Joint model?
-
-\begin{figure}
-% to be removed before submission
-\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_preds.png}
-\caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
-The values plotted for areas with no polygon data are the means across all cross-validation folds.
-}
-\label{predobsmapidn}
-\end{figure}
-
-\begin{figure}
-% to be removed before submission
-\includegraphics[width = 0.7\textwidth]{figures/sen_both_cv12_preds.png}
-\caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
-}
-\label{predobsmapsen}
-\end{figure}
-
-% Results and Discussion can be combined.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%Summarise results
-
-We have compared the predictive performance of a polygon-only model and a model that jointly learns from polygon incidence data and prevalence point-surveys.
-We found that neither model was clearly superior to the other but that both models recovered the broad spatial pattern of malaria risk (Figures \ref{predobsmapidn} and \ref{predobsmapsen}).
-With regards to a random cross-validation scheme, adding prevalence point-surveys to the disaggregation model only improved performance in  Madagascar (Table~\ref{table1}).
-With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the prevalence point-surveys improved on the polygon-only models in both Senegal and Madagascar but not Indonesia (Table~\ref{table2}).
-
-We used held-out prevalence point-surveys to measure how well the models predicted within-polygon, pixel-level malaria risk.
-Given the poor performance by all models, including the points-only model (Figures~\ref{randompredobsscatter} and \ref{spatialpredobsscatter}), particularly in Indonesia and Senegal these results must be interpreted with care.
-% Add sample size, comparisons etc.
-In particular, a majority of the prevalence point-surveys in all countries found zero malaria infections (though the age standardisation moves these to slightly non-zero values) and small sample sizes were common in the Senegal and Indonesia data.
-Given the poor performance of the points-only model, it is not useful to interpret these results as a direct measure of a models ability to predict within-polygon, pixel level risk.
-Instead we can, with care, interpret the relative performance of models.
-In five cases, the polygon-only and joint model had the same predictive performance on the prevalence point-surveys.
-In only one cases, the joint model was marginally better.
-Therefore we conclude that the joint model is no better than the polygon-only model at predicting within-polygon, pixel-level malaria risk.
-
-% Discuss and interpret. Generalise
-
-The joint model improved the prediction of polygon incidence in two of three countries under the spatial cross-validation scheme but only one country in the random cross-validation scheme.
-The two countries where the joint model performed best in the spatial cross-validation scheme are the two countries with the least data.
-The joint model seemed to perform comparatively well in the cases where predictions had little information from the random field and when there is little data to estimate regression parameters.
-Far-from-data predictions are particularly susceptible to overfitting.
-Given the simple linear model, adding prevalence point-surveys may protect against overfitting by increasing the amount of data available.
-Alternatively, the improved perforamance could be because a model that learns from two datasets, on different scales, with different biases, is also less likely to overfit.
-
-In contrast, the joint model does not in general improve on the polygon-only model in the random cross-validation scheme.
-A noticable element of this scheme was that locations where polygon incidence data was removed for validation could still potentially have prevalence point-survey data.
-Figure~\ref{fig:cv_random} implies that this situation is the norm.
-Yet this spatial information did not improve performance in Indonesia or Senegal.
-
-% Clear benefits, when some areas have polygon and some have PR.
-%   Where?
-
-There are two main reasons why a model fitted jointly on prevalence point-surveys and polygon incidence data may perform worse than a polygon-only mode.
-Firstly, the data are on difference scales.
-Here we have used a previously fitted model \cite{cameron2015defining} in order to be able to fit the joint model.
-However, this model is imperfect in that it is calibrated with a relatively small amount of matched prevalence and incidence data.
-Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality and age-structure are not constant \cite{cameron2015defining, battle2015defining,reiner2015seasonality}.
-In using a joint model we are accepting these failings in the hope that the benefits of including additional data are stronger than the costs of using mismatched data.
-The second aspect of prevalence point-survey data that could reduce the predictive ability of a polygon-only model by adding point data is if the point data is of low quality.
-In particular, non-random sampling of individuals can produce biased estimates of prevalence and this will decrease model performance.
-
-For a model to be robust to shortcomings in the prevalence-incidence relationship from \cite{cameron2015defining}, future models could be more flexible in the way they use this relationship.
-This could be by estimating the parameters of the polynomial jointly with the rest of the model.
-Informative priors based on the original model should be used to regularise this joint fit both to prevent unbelievable inferences but also because if the relationship is too flexible, the information from the prevalence data might not be used by the incidence level model.
-This is particularly true for even more flexible model forms that could be used such as a spline or a Gaussian process on the relationship between prevalence and incidence.
-
-For the model to handle noisy or biased prevalence point-surveys, the modeller can control the iid random effect on the point-surveys, $w_i$. 
-Here we have tried to maximise the influence of the prevalence data by setting the prior based on the belief that the random effect should only explain extra-binomial variation that is impossible to explain with the covariates (i.e.
-based on the differences in prevalence surveys within the same pixel).
-Weakening this prior will allow the iid effect to explain more of the prevalence point-survey variation which both reduces the potential statistical power gained by adding the point-surveys but also reduces the effects of biased or noisy estimates.
-
-There are large potential benefits to models that combine data in the context of large scale studies over multiple countries.
-In these cases there is often different data types in different countries and being able to make malaria estimates of the countries together increases spatial coverage and statistical power.
-Further cases where this joint model may be particularly beneficial is in countries where prevalence surveys are strongly clustered in one area --- typically an area of high malaria risk --- but without high resolution surveillance data.
-In these regions, fitting a model on just the prevalence point-surveys requires predictions far away from the survey locations whlie fitting a model just on the polygon incidence data will be underpowered.
-However, the benefits of these methods do not come for free, as indicated by the reduced performance in some cases.
-
-In order to specifically compare the affects of combining the data types, we have aimed to keep the models fitted here as simple as possible.
-However, a number of improvements could be made.
-Data from multiple years are available for many countries.
-Simply combining data collected at different times is not recommended as malaria incidence is changing rapidly.
-However, fitting a full spatio-temporal model would be a suitable way to combine data from different periods but would be computationally more expensive \cite{bhatt2015effect, taylor2017continuous}.
-This is an avenue of work that should be pursued.
-Furthermore, it has been clearly established that simple linear combinations of environmental covariates cannot fully explain malaria risk \cite{bhatt2017improved}.
-A number of methods could be used to include non-linear effects of covariates and interactions into the model.
-Firstly, as in \cite{bhatt2017improved}, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model.
-This approach is feasible but does not allow any information from the polygons to inform non-linear relationships.
-To directly model non-linear effects in the full model could be achieved by including simple non-linear functions such as splines \cite{sissoko2017temporal, sewe2017using, hundessa2018projecting}, though the increased model complexity would require more data than was used in Senegal and Madagascar in this study.
-Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \cite{law2018variational}.
-These are computational expensive without careful approximations via variational Bayes or other approximations.
-Again these models need a lot of data and careful regularisation for good predictive performance.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Supporting information}
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-%\paragraph*{S1 Fig.}
-%\label{S1_Fig}
-%{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
-
-\section*{Acknowledgments}
-Thanks everyone.
-
-\nolinenumbers
-
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% or
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here. See http://journals.plos.org/plosone/s/latex for 
-% step-by-step instructions.
-% 
-\bibliography{Malaria}
-
-%\begin{thebibliography}{10}
-
-%\end{thebibliography}
-
 \end{document}

### 2018-11-22 ms.tex
More dan edits.

@@
 Tim C.D.
-Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Rosalind Howes \textsuperscript{1}, Katherine Battle \textsuperscript{1}, Andre Python \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Dan Weiss\textsuperscript{1}
+Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Rosalind Howes \textsuperscript{1}, Katherine E.
+Battle \textsuperscript{1}, Andre Python \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Daniel J.
+Weiss\textsuperscript{1}
 \\
@@
 We used two data sources that reflect malaria burden; prevalence point-surveys and polygon incidence data.
-We selected Indonesia, Senegal and Madagascar as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
-To minimise temporal effects we select, for each country, one year of prevalence point-survey data and one year of polygon incidence data.
-For Indonesia we selected 2012 for polygon incidence data (380 regions) and 2010 for prevalence data (969 surveys, 128,537 individuals).
+We selected Indonesia, Senegal and Madagascar as case examples as they all have abundant subnational surveillance data and country wide surveys from approximately the same period.
+To minimise temporal effects we selected, for each country, one year of prevalence point-survey data and one year of polygon incidence data.
+For Indonesia we selected polygon incidence data from 2012 that covers 380 regions, and prevalence data from 2010 that consists of 969 surveys, accounting for 128,537 individuals.
 For Senegal we selected 2015 for both polygon incidence data (46 regions) and prevalence data (216 surveys, 8,114). % update todo
@@
 
-The prevalence point-survey data were extracted from the Malaria Atlas Project prevalence survey database \cite{bhatt2015effect}.
+The prevalence point-survey data were extracted from the Malaria Atlas Project prevalence survey database \cite{bhatt2015effect, guerra2007assembling, gething2011new}.
 As the prevalence point-surveys cover different age ranges they were standardised to an age-range of 2--10 using the model from \cite{smith2007standardizing}.
-Many of the points have relatively small sample sizes.
-285 surveys out of 290 in Senegal have a sample size less than 50 while 618 out of 969 surveys in Indonesia have a sample size less than 100.
+A challenge associated with using the prevalence points is that many of them have relatively small sample sizes.
+For example, 285 surveys out of 290 in Senegal have a sample size less than 50 while 618 out of 969 surveys in Indonesia have a sample size less than 100.
 Furthermore, due to the small sample sizes and low malaria prevalence in these countries, many of the surveys have find very few malaria infections.
 Amongst the Senegal surveys, 189 out of 290 have zero positive cases while a further 30 have only one positive case.
-In Indonesia 620 out of 969 surveys have zero positive cases and 195 have one positive case.
+In Indonesia 620 out of 969 surveys have zero positive cases and 195 have only one positive case.
 Finally, in Madagascar 189 out of 290 surveys have zero positive cases and 30 have one positive case.
@@
 
-The polygon incidence data were collated from various government reports.
-To account for underreporting of clinical cases due to lack of treatment seeking, missed case reports and cases that sought medical attention outside the public health systems, the methods in \cite{cibulskis2011worldwide} were used using estimates of treatment seeking from \cite{battle2016treatment}.
-Where species specific reports were given, these were used. 
-For reports where no species specific, national estimates of the ratio between \emph{P. falciparum} and \emph{P. vivax} cases were used to calculate \emph{P. falciparum} only cases.
+The polygon incidence data were collated from various government reports and adjusted to a standard metric using methods defined in \cite{cibulskis2011worldwide}.
+These adjustments account for underreporting of clinical cases due to lack of treatment seeking, missed case reports, and cases that sought medical attention outside the public health systems, and treatment seeking behaviour \cite{battle2016treatment}.
+Where species specific reports were given, these were used, and in reports that did not distinguish between species of \emph{Plasmodium} the national estimate of the ratio between \emph{P.
+falciparum} and \emph{P.
+vivax} cases were used to estimate \emph{P.
+falciparum} only cases.
 

### 2018-11-25 ms.tex
Update tables.

@@
 \thickhline 
-Incidence & Indonesia & 18.33 & {\bf 14.02} &  14.09\\
-& Senegal & 51.24 & {\bf 26.74} &  28.45\\
-& Madagascar & 85.54 & 37.45 &  {\bf 34.49}\vspace{3mm}\\
+Incidence & Indonesia & 18.33 & 14.02 &  14.09\\
+& Senegal & 85.73 & 12.52 &  12.63\\
+& Madagascar & 85.54 & 37.45 &  34.49\vspace{3mm}\\
 Prevalence & Indonesia & 0.010 & 0.010 &  0.010\\
-& Senegal & {\bf 0.015} & 0.024 &  0.024\\
-& Madagascar & {\bf 0.054} & 0.059 &  0.059\\
+& Senegal & 0.052 & 0.059 &  0.058\\
+& Madagascar & 0.054 & 0.059 &  0.059\\
 \end{tabular}
@@
 \thickhline 
-Incidence & Indonesia &  18.13 &  {\bf 14.77} &   15.02\\
-& Senegal &  51.17 &  41.43 &   {\bf 36.76}\\
-& Madagascar & 107.32 &  71.44 &   {\bf 65.50}\vspace{3mm}\\
-Prevalence & Indonesia & 0.011 & {\bf 0.010} &  {\bf 0.010}\\
-& Senegal & {\bf 0.015} & 0.019 &  0.019\\
-& Madagascar & 0.069 & 0.066 &  {\bf 0.065}\\
+Incidence & Indonesia &  18.13 &  14.77 &   15.02\\
+& Senegal &  62.71 &  13.53 &   17.62\\
+& Madagascar & 107.32 &  71.44 &   65.50\vspace{3mm}\\
+Prevalence & Indonesia & 0.011 & 0.010 &  0.010\\
+& Senegal & 0.062 & 0.060 &  0.060\\
+& Madagascar & 0.069 & 0.066 &  0.065\\
 \end{tabular}
@@
 % to be removed before submission
-\includegraphics[width = 1.05\textwidth]{figures/spatial_cv_scatter} %\caption{Indonesia spatial crossvalidation} 
+\includegraphics[width = 1.05\textwidth]{figures/spatial_cv_poly_facet} %\caption{Indonesia spatial crossvalidation} 
 \caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
-A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
+A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (per 1,000).
 Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
-The bimodal distribution in observed prevalence in Indonesia is caused by the large number of surveys with exactly one positive case.
 }
-\label{spatialpredobsscatter}
+\label{spatialpredobspolyfacet}
+\end{figure}
+
+\begin{figure}
+% to be removed before submission
+\includegraphics[width = 1.05\textwidth]{figures/spatial_cv_points_facet} %\caption{Indonesia spatial crossvalidation} 
+\caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
+A) Indonesia, B) Senegal, C) Madagascar. Square root prevalence.
+Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
+}
+\label{spatialpredobspointfacet}
 \end{figure}
@@
 Incidence & Random & Indonesia & 0.13 & 0.72 &  0.73\\
-&& Senegal & 0.11 & 0.80 &  0.85\\
+&& Senegal & 0.20 & 0.78 &  0.71\\
 && Madagascar & 0.59 & 0.82 &  0.77\vspace{1mm}\\
 & Spatial & Indonesia & 0.14 & 0.76 &  0.68\\
-&& Senegal & 0.30 & 0.67 &  0.70\\
+&& Senegal & 0.34 & 0.90 &  0.78\\
 && Madagascar & 0.68 & 0.65 &  0.68\vspace{3mm} \\
 Prevalence & Random & Indonesia & 0.90 & 0.50 &  0.80\\
-&& Senegal & 0.80 & 0.71 &  0.91\\
+&& Senegal & 0.83 & 0.19 &  0.77\\
 && Madagascar & 0.83 & 0.53 &  0.74\vspace{1mm}\\
 & Spatial & Indonesia & 0.87 & 0.62 &  0.96\\
-&& Senegal & 0.90 & 0.88 &  0.79\\
+&& Senegal & 0.85 & 0.26 &  0.79\\
 && Madagascar & 0.93 & 0.68 &  0.83\\

### 2019-02-07 ms.tex
Add malariaAtlas ref.

@@
 Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Rosalind Howes \textsuperscript{1}, Katherine E.
-Battle \textsuperscript{1}, Andre Python \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Daniel J.
+Battle \textsuperscript{1}, Penelope Hancock \textsuperscript{1}, Andre Python \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Daniel J.
 Weiss\textsuperscript{1}
@@
 
-The prevalence point-survey data were extracted from the Malaria Atlas Project prevalence survey database \cite{bhatt2015effect, guerra2007assembling, gething2011new}.
+The prevalence point-survey data were extracted from the Malaria Atlas Project prevalence survey database \cite{bhatt2015effect, guerra2007assembling, gething2011new, pfeffer2018ma}.
 As the prevalence point-surveys cover different age ranges they were standardised to an age-range of 2--10 using the model from \cite{smith2007standardizing}.
@@
 The polygon incidence data were collated from various government reports and adjusted to a standard metric using methods defined in \cite{cibulskis2011worldwide}.
-These adjustments account for underreporting of clinical cases due to lack of treatment seeking, missed case reports, and cases that sought medical attention outside the public health systems, and treatment seeking behaviour \cite{battle2016treatment}.
+These adjustments account for underreporting of clinical cases due to lack of treatment seeking, missed case reports, and cases that sought medical attention outside the public health systems \cite{battle2016treatment}.
 Where species specific reports were given, these were used, and in reports that did not distinguish between species of \emph{Plasmodium} the national estimate of the ratio between \emph{P.
@@
 We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres at the equator that included land surface temperature annual mean and standard deviation \cite{LST}, enhanced vegetation index \cite{TCB}, mosquito temperature suitability index \cite{weiss2014air}, elevation \cite{SRTMElev}, tassel cap brightness \cite{TCB}, tassel cap wetness \cite{TCB}, accessibility to cities \cite{weiss2018global}, night lights \cite{} and proportion of urban land cover \cite{}.
-Elevation, land surface temperature standard deviation, accessibility to cities and night lights were all log transformed to reduce skewness.
-After preliminary analyses, tassel cap brightness and urban land cover were removed as they were highly correlated with other variables.
+Some covariates were log-transformed to remove skewness or removed due to multicollineariy with other predictor variables using the threshold of 0.8.
+% think we decided this on indonesia data only.
+Sen is currently 0.81...
+just a bit messy.
 The covariates were standardised to have a mean of zero and a standard deviation of one.
@@
 
-We compared three models 1) a full model with prevalence point-surveys and polygon incidence data 2) the submodel with only polygon incidence data and 3) the benchmark submodel with only prevalence point-survey data.
+We compared three models 1) a joint model using both  prevalence point-surveys and polygon incidence data as the response variable 2) a submodel using only polygon incidence data and 3) a benchmark submodel using only prevalence point-survey data.
 The models were implemented and fitted in R \cite{R} using Template Model Builder \cite{TMB} which allows a Laplace approximation of the posterior to be calculated.
@@
 This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for the case counts using the approach defined in \cite{cibulskis2011worldwide}.
-We found that an iid effect with a standard deviation of 0.05 would be able to account for the discrepancy between the assumed Poisson error and the independently derived error.
+We found that an iid effect with a standard deviation of 0.05 is able to account for the discrepancy between the assumed Poisson error and the independently derived error.
 We assigned $\sigma_w$ a penalised complexity prior such that $P(\sigma_w > 0.3) = 0.0000001$. 
-This was chosen by finding the maximum difference in prevalence between point-surveys (with a sample size greater than 500) within the same raster pixel.
+This was chosen by finding the maximum difference in prevalence between point-surveys (with a sample size greater than 500 individuals) within the same raster pixel.
 The differences between points within the same pixel can only be accounted for by the binomial error and this iid effect.
@@
 Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
-Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of -3, each covariate would be able to predict prevalences between 0.004 and 0.27. 
-This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularise our model.
+Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of -3, each covariate is able to predict prevalences between 0.004 and 0.27. 
+This prior encodes our desire to regularise our model and and belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularise our model.
 This regularisation is particularly important given the small number of observations in Senegal (n = 46) and Madagascar (n = 110).
@@
 This reflects real world data where we in some locations we have incidence data but no prevalence data and visa versa.
-Thus this cross-validation scheme can be seen as asking whether the joint model is preferable to using just polygon incidence data.
+Thus this cross-validation scheme directly addresses the question of whether the joint model is preferable to using just polygon incidence data.
 
@@
 In the second validation scheme the data was split into spatial cross-validation folds (see Figure~\ref{fig:cv_spatial}).
-The number of folds was seven for Indonesia, four for Senegal and three for Madagascar due to their differing sizes and geographies.
+The number of folds was seven for Indonesia, four for Senegal and three for Madagascar due to their differing sizes and and epidemiological settings.
 The data was divided by combining the prevalence point-survey locations and the centroids of the incidence polygons and performing k means clustering.
@@
 Predictive performance on prevalence survey-points is one way to measure how well a model can predict pixel-level malaria risk.
-However, in areas of low prevalence, small or moderately sized prevalence point-surveys can be noisy or unsensitive and so care must be taken when interpreting predictive performance on these data.
+However, in areas of low prevalence, small or moderately sized prevalence point-surveys can be noisy or insensitive and so care must be taken when interpreting predictive performance on these data.
 Therefore our secondary metric was MAE, weighted by survey sample size, of prevalence point-surveys.

### 2019-03-11 ms.tex
Refs tidy.
Update to new cv schemes and things.

@@
 To minimise temporal effects we selected, for each country, one year of prevalence point-survey data and one year of polygon incidence data.
-For Indonesia we selected polygon incidence data from 2012 that covers 380 regions, and prevalence data from 2010 that consists of 969 surveys, accounting for 128,537 individuals.
-For Senegal we selected 2015 for both polygon incidence data (46 regions) and prevalence data (216 surveys, 8,114). % update todo
-Finally, for Madagascar we selected 2013 for both polygon incidence (110 regions) and prevalence (290 surveys, 7,244 individuals) data.
+For Indonesia we selected polygon incidence data from 2012 that covers 380 regions, and prevalence data from 2010 to 2014 that consists of todo surveys, accounting for todo individuals.
+For Senegal we selected 2015 for polygon incidence data (46 regions) and 2013 to 2017 for prevalence data (todo surveys, todo).
+Finally, for Madagascar we selected 2013 for polygon incidence (110 regions) and 2011 to 2015 prevalence (todo surveys, todo individuals) data.
 
@@
 As the prevalence point-surveys cover different age ranges they were standardised to an age-range of 2--10 using the model from \cite{smith2007standardizing}.
-A challenge associated with using the prevalence points is that many of them have relatively small sample sizes.
-For example, 285 surveys out of 290 in Senegal have a sample size less than 50 while 618 out of 969 surveys in Indonesia have a sample size less than 100.
-Furthermore, due to the small sample sizes and low malaria prevalence in these countries, many of the surveys have find very few malaria infections.
-Amongst the Senegal surveys, 189 out of 290 have zero positive cases while a further 30 have only one positive case.
-In Indonesia 620 out of 969 surveys have zero positive cases and 195 have only one positive case.
-Finally, in Madagascar 189 out of 290 surveys have zero positive cases and 30 have one positive case.
 The age standardisation model gives the surveys with zero positive cases a small positive prevalence.
@@
 We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres at the equator that included land surface temperature annual mean and standard deviation \cite{LST}, enhanced vegetation index \cite{TCB}, mosquito temperature suitability index \cite{weiss2014air}, elevation \cite{SRTMElev}, tassel cap brightness \cite{TCB}, tassel cap wetness \cite{TCB}, accessibility to cities \cite{weiss2018global}, night lights \cite{} and proportion of urban land cover \cite{}.
+% change to table
 Some covariates were log-transformed to remove skewness or removed due to multicollineariy with other predictor variables using the threshold of 0.8.
@@
 
-To compare the three models we used two cross-validation schemes. 
-In the first, the combined data set of prevalence and incidence data was split into ten cross-validation folds stratified by data type (Figure~\ref{fig:cv_random}).
-This reflects real world data where we in some locations we have incidence data but no prevalence data and visa versa.
-Thus this cross-validation scheme directly addresses the question of whether the joint model is preferable to using just polygon incidence data.
-
-%figure 1.cross validation. %% Do fig 1 and 2, random and spatial cv. IDN on top, MDG and SEN below in each.
-
-In the second validation scheme the data was split into spatial cross-validation folds (see Figure~\ref{fig:cv_spatial}).
+To compare the three models we used three cross-validation schemes. 
+In the first, the incidence data was split into ten cross-validation folds while all the prevalence data was used in each case.
+%This cross-validation scheme directly addresses the question of whethe
+In the second validation scheme, the incidence data was split into spatial cross-validation folds (see Figure~\ref{fig:cv_spatial}) while again all prevalence points were used in all folds.
 The number of folds was seven for Indonesia, four for Senegal and three for Madagascar due to their differing sizes and and epidemiological settings.
 The data was divided by combining the prevalence point-survey locations and the centroids of the incidence polygons and performing k means clustering.
+This scheme is specifically testing whether the joint model can improve predictions by increasing geographic coverage.
+This situation is particularly common in continental scale models where done countries will have large DHS style surveys while others will not.
+In the final scheme the data is again split  spatially but the prevalence surveys from the hold-out areas are also witheld.
 This scheme is testing the models' ability to predict into new areas with little information from the spatial random field.
+It is therefore testing how well the models learn the parameters that relate the environment to malaria risk.
 
-In both cases we examined performance metrics for both the withheld prevalence point-survey data and the withheld incidence polygon data.
-As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
 We considered the ability to predict polygon incidence correctly our main objective and our performance metric was mean absolute error (MAE).
-However, a problem with using polygon data in a cross-validation scheme is that a model can perform well at the polygon level but not correctly predict the pixel-level malaria risk.
-Predictive performance on prevalence survey-points is one way to measure how well a model can predict pixel-level malaria risk.
-However, in areas of low prevalence, small or moderately sized prevalence point-surveys can be noisy or insensitive and so care must be taken when interpreting predictive performance on these data.
-Therefore our secondary metric was MAE, weighted by survey sample size, of prevalence point-surveys.
-While other metrics could have been used, we specifically did not use correlation as correlation measures linear dependance without regard to slope or intercept.
 As the models are being fitted on data on difference scales we found that observations and predictions were sometimes correlated but strongly displaced from the one-one line and therefore correlation metrics were misleading.

### 2019-03-19 ms.tex
Order spatial cvs properly.

@@
 To compare the three models we used three cross-validation schemes. 
-In the first, the incidence data was split into ten cross-validation folds while all the prevalence data was used in each case.
+In the first (random), the incidence data was split into ten cross-validation folds while all the prevalence data was used in each case.
 %This cross-validation scheme directly addresses the question of whethe
-In the second validation scheme, the incidence data was split into spatial cross-validation folds (see Figure~\ref{fig:cv_spatial}) while again all prevalence points were used in all folds.
-The number of folds was seven for Indonesia, four for Senegal and three for Madagascar due to their differing sizes and and epidemiological settings.
+In the second validation scheme (spatial a), the incidence data was split into spatial cross-validation folds while again all prevalence points were used in all folds.
+The number of folds was seven for Indonesia, five for Senegal and three for Madagascar due to their differing sizes and epidemiological settings.
 The data was divided by combining the prevalence point-survey locations and the centroids of the incidence polygons and performing k means clustering.
-This scheme is specifically testing whether the joint model can improve predictions by increasing geographic coverage.
-This situation is particularly common in continental scale models where done countries will have large DHS style surveys while others will not.
-In the final scheme the data is again split  spatially but the prevalence surveys from the hold-out areas are also witheld.
+This scheme is specifically testing whether the joint model can improve predictions by increasing geographic data coverage.
+This situation is particularly common in continental scale models where some countries will have large DHS style surveys but little incidence data.
+In the final scheme (spatial b) the data is again split  spatially but the prevalence surveys from the hold-out areas are also witheld.
 This scheme is testing the models' ability to predict into new areas with little information from the spatial random field.
@@
 \caption{
-{\bf Summary of out-of-sample accuracy for random cross-validation experiment.}}
-\begin{tabular}{llllll}
+{\bf Summary of out-of-sample accuracy for all three cross-validation experiments.}}
+\begin{tabular}{llll}
 \hline
-{\bf Holdout data} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
+{\bf CV scheme} & {\bf Country} &  {\bf Polygons} & {\bf Joint} \\
 \thickhline 
-Incidence & Indonesia & 18.33 & 14.02 &  14.09\\
-& Senegal & 85.73 & 12.52 &  12.63\\
-& Madagascar & 85.54 & 37.45 &  34.49\vspace{3mm}\\
-Prevalence & Indonesia & 0.010 & 0.010 &  0.010\\
-& Senegal & 0.052 & 0.059 &  0.058\\
-& Madagascar & 0.054 & 0.059 &  0.059\\
+Random & Indonesia  & 13.95 &  {\bf 13.88}\\
+& Senegal  & {\bf 12.41} &  12.81\\
+& Madagascar  & 39.06 &  {\bf 36.36}\vspace{3mm}\\
+Spatial a & Indonesia & {\bf 14.81} &  16.45\\
+& Senegal  & {\bf 12.31} &  30.12\\
+& Madagascar & 67.73 &  {\bf 44.05} \vspace{3mm}\\
+Spatial b & Indonesia & {\bf 14.77} &  15.02\\
+& Senegal  & {\bf 12.39} &  18.75\\
+& Madagascar  & 70.72 &  {\bf 61.05}\\
 \end{tabular}
 \begin{flushleft}
-Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
-The data were split randomly into 10 groups stratified by data type (incidence polygon and prevalence points).
+Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.
 \end{flushleft}
 \label{table1}
-\end{adjustwidth}
-\end{table}
-
-\begin{table}[!t]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\caption{
-{\bf Summary of out-of-sample accuracy for spatial cross-validation experiment.}}
-\begin{tabular}{llllll}
-\hline
-{\bf Holdout data} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
-\thickhline 
-Incidence & Indonesia &  18.13 &  14.77 &   15.02\\
-& Senegal &  62.71 &  13.53 &   17.62\\
-& Madagascar & 107.32 &  71.44 &   65.50\vspace{3mm}\\
-Prevalence & Indonesia & 0.011 & 0.010 &  0.010\\
-& Senegal & 0.062 & 0.060 &  0.060\\
-& Madagascar & 0.069 & 0.066 &  0.065\\
-\end{tabular}
-\begin{flushleft}
-Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
-The data were split into seven, four and three groups in Indonesia, Senegal and Madagascar respectively.
-\end{flushleft}
-\label{table2}
 \end{adjustwidth}
@@
 
-%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
 \begin{figure}
 % to be removed before submission
-\includegraphics[width = 1.05\textwidth]{figures/random_cv_poly_facet} %\caption{Indonesia spatial crossvalidation} 
+\includegraphics[width = 1.05\textwidth]{figures/random_cv_poly_facet}  
 \caption{{\bf Observed-predicted plots for random cross-validation experiments.}
 A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (per 1,000).
-Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
+Results from the standard downscaling model are shown in blue and the combined model is shown in green.
 }
@@
 
+%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
+
 \begin{figure}
 % to be removed before submission
-\includegraphics[width = 1.05\textwidth]{figures/random_cv_points_facet} %\caption{Indonesia spatial crossvalidation} 
-\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
-A) Indonesia, B) Senegal, C) Madagascar. Square root prevalence.
-Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
+\includegraphics[width = 1.05\textwidth]{figures/spatialkeeppr_cv_poly_facet}  
+\caption{{\bf Observed-predicted plots for spatial a cross-validation experiments where all prevalence points are used in model fitting.}
+A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (per 1,000).
+Results from the standard downscaling model are shown in blue and the combined model is shown in green.
 }
-\label{randompredobspointfacet}
-\end{figure}
-
-%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
-\begin{figure}
-% to be removed before submission
-\includegraphics[width = 1.05\textwidth]{figures/spatial_cv_poly_facet} %\caption{Indonesia spatial crossvalidation} 
-\caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
-A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (per 1,000).
-Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
-}
-\label{spatialpredobspolyfacet}
+\label{spatial2predobspolyfacet}
 \end{figure}
@@
 % to be removed before submission
-\includegraphics[width = 1.05\textwidth]{figures/spatial_cv_points_facet} %\caption{Indonesia spatial crossvalidation} 
-\caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
-A) Indonesia, B) Senegal, C) Madagascar. Square root prevalence.
-Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
+\includegraphics[width = 1.05\textwidth]{figures/spatial_cv_poly_facet} 
+\caption{{\bf Observed-predicted plots for spatial b cross-validation experiments where prevalence points are spatially witheld.}
+A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (per 1,000).
+Results from the standard downscaling model are shown in blue and the combined model is shown in green.
 }
-\label{spatialpredobspointfacet}
+\label{spatialpredobspolyfacet}
 \end{figure}
@@
 {\bf Summary of coverage of 80\% credible intervals.}}
-\begin{tabular}{llllll}
+\begin{tabular}{llll}
 \hline
-{\bf Holdout data} & {\bf Cross-validation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
+{\bf Cross-validation} & {\bf Country}  & {\bf Polygons} & {\bf Joint} \\
 \thickhline 
-Incidence & Random & Indonesia & 0.13 & 0.72 &  0.73\\
-&& Senegal & 0.20 & 0.78 &  0.71\\
-&& Madagascar & 0.59 & 0.82 &  0.77\vspace{1mm}\\
-& Spatial & Indonesia & 0.14 & 0.76 &  0.68\\
-&& Senegal & 0.34 & 0.90 &  0.78\\
-&& Madagascar & 0.68 & 0.65 &  0.68\vspace{3mm} \\
-Prevalence & Random & Indonesia & 0.90 & 0.50 &  0.80\\
-&& Senegal & 0.83 & 0.19 &  0.77\\
-&& Madagascar & 0.83 & 0.53 &  0.74\vspace{1mm}\\
-& Spatial & Indonesia & 0.87 & 0.62 &  0.96\\
-&& Senegal & 0.85 & 0.26 &  0.79\\
-&& Madagascar &   0.93 & 0.68 &  0.83\\
+Random & Indonesia  & 0.73 &  0.74\\
+& Senegal  & 0.76 &  0.73\\
+& Madagascar  & 0.78 &  0.78\vspace{1mm}\\
+ Spatial a & Indonesia  & {\bf 0.69} &  {\bf 0.54}\\
+& Senegal  & 0.83 &  {\bf 0.59}\\
+& Madagascar  & {\bf 0.67} &  0.72 \vspace{1mm} \\
+Spatial b & Indonesia & 0.74 &  0.70\\
+& Senegal  & {\bf 0.90} &  0.73\\
+& Madagascar  & {\bf 0.61} &  {\bf 0.69}\\
+
 \end{tabular}

### 2019-03-22 ms.tex
Bring rest of ms up to date with new cv schemes.

@@
 We relate the differing malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
-We then compare results from the joint model with those made using (a) a polygon-only, disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and (b) a model created using prevalence point-survey data similar to the model used by Bhatt \emph{et al.}\cite{bhatt2015effect}.
-Each set of three models is applied to data from Indonesia, Senegal and Madagascar to provide a set of case studies with disparate geographic settings and levels of malaria endemicity.
-We find that the joint model performs better than the polygon-only model in cases where predictions are needed far from the location of the data or when there are few polygon incidence datapoints available for learning relationships between covariates and malaria risk.
+We then compare results from the joint model with those made using a polygon-only, disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless}.
+Both models are fitted to data from Indonesia, Senegal and Madagascar to provide a set of case studies with disparate geographic settings and levels of malaria endemicity.
 
@@
 
-% Random results
-% Maps, reasonable for both
-% MAE performance.
+% Random cv
 
-For the random cross-validation experiments, the polygon-only model had the lowest mean absolute error, with respect to predicting incidence, for Indonesia and Senegal (Table~\ref{table1}).
-Incidence in Madagascar was best predicted by the joint model.
-However, the difference between the two models in Indonesia was small.
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter}A, C and E.
-From the scatter plots it can be seen that the point-only model is strongly biased, overestimating incidence in Indonesia and Madagascar and underestimating incidence in Senegal.
+Under the random cross-validation scheme, the joint model performed best in Indonesia and Madagascar while the polygon only model performed best in Senegal (Table \ref{table1}).
+The differences were relatively small in all three countries.
+This lack of strong differences is highlighted by the fact that there are no clear differences in scatter plots of observed and predicted data (Figure \ref{randompredobspolyfacet}).
+
+% spatial 1
+
+Under the spatial a cross-validation scheme, the polygon only model performed best in Indonesia and Senegal while the joint model performed best in Madagascar (Table \ref{table1}).
+In contrast to the random cross-validation results, the differences between models is quite strong.
+Furthermore, notable difference can be seen in the scattor plots of observed and predicted values (Figure \ref{spatial2predobspolyfacet}).
+In Indonesia it can be seen the the joint model is more strongly biased at low incidence values with many data points being overpredicted.
+In Senegal the predictions from the joint model do not appear biased but are often far from the observed value.
+However, the joint model clearly performs better in Madagascar with the polygon only model particularly struggling to predict high incidence observations correctly.
+
+% spatial b
+
+Under the spatial b cross-validation scheme, in which the prevalence data are spatially withheld, the polygon model again performs the best in Indonesia and Senegal while the joint model performs best in Madagascar (Table \ref{table1}).
+The bias in the low incidence observations in Indonesia is no longer present (Figure \ref{spatial1predobspolyfacet}).
+In Indonesia and Senegal the joint model performs worse in the spatial a cross-validation than in the spatial b cross-validation scheme.
+Given that more data is being witheld in spatial b this implies that the bias caused by the prevalence points is so severe that models perform worse with this spatial information than with just information from the covariates.
 
@@
 
-The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both Senegal and  Madagascar while the wighted MAE was the same for all three models in Indonesia (Table~\ref{table1}).
-The more pertinent comparison is whether the addition of the prevalence data improves the ability of the polygon-only models to predict pixel level prevalence.
-However, weighted MAE was unchanged between the polygon-only model and the joint model for Indonesia, Senegal or Madagascar.
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F.
-All models show poor predictive performance in Indonesia and Senegal with none of the models being able to accurately predict the large number of points with zero prevalence.
-The predictions in Madagascar are better though the large number of surveys with measured prevalence of zero are still problematic.
-
-Maps of the Indonesian input data and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
-Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for Senegal show broad agreement with malaria incidence being higher in the South.
-
-% Further results. Accuracy or recall of Sen. Correlation for some?
-
-% Spatial results
-% Maps, reasonable for india, get's broad pattern even far away from data. Poor for SEN, wrong overall pattern. Different covariates.
-% MAE performance.
-
-For the spatial cross-validation experiments, the joint model had the best predictive performance for both Senegal and Madagascar.
-The polygon-only model again had the lowest mean absolute error between observed and predicted incidence for Indonesia (Table~\ref{table2}).
-Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{spatialpredobsscatter}A, C and E.
-
-Again, the benchmark points-only model had the lowest weighted MAE between spatially cross-validated observed and predicted prevalence for Senegal.
-However, for Indonesia, both the polygon-model and the joint model marginally outperformed the points-only model. 
-However, scatter plots of the out-of-sample predictions show that there is almost no correlation between observed and predicted values (Figures~\ref{randompredobsscatter} B, D and F).
-For Senegal, the joint model (0.065) had the lowest weighted MAE for predicted prevalence though this was again marginal (points-only 0.069, polygons-only 0.066).
-Again the survey-points with prevalence of zero were difficult to correctly predict.
-
-Maps of the Indonesian input data and spatially out-of-sample predictions (Figures~\ref{predobsmapidn}A and C) suggest the that the broad spatial patterns were once again recovered.
-This acceptable performance is notable given the very large areas held out-of-sample (Fig~\ref{fig:cv_spatial}).
-For example, the whole of Papua and West Papua the the East are held out in a single fold.
-In contrast the predictions for Senegal do not match those observed in the input data (Figures~\ref{predobsmapsen}A and C).
-
 % Coverage results
@@
 The polygon-only model and the joint model seem to be fairly well calibrated (Table~\ref{table3}).
-The proportion of out-of-sample incidence datapoints being within their 80\% credible intervals ranged between 0.65 and 0.85.
-The proportion of out-of-sample prevalence datapoints being within their 80\% credible intervals ranged from 0.50 to 0.96.
-The points-only model was reasonably well calibrated for predictions of prevalence (coverage ranging from 0.8 to 0.93) but was poorly calibrated for predicting incidence with coverage values as low as 0.11 and the best coverage value being 0.68 for spatial cross-validation in Madagascar.
-
-With respect to uncertainty in polygon incidence predictions, the polygon-only model and joint model were similar; adding the prevalence point-survey data sometimes improved coverage and sometimes made it worse.
-However, with respect to uncertainty in prevalence point-survey predictions, the coverage was substantially improved in three of six cases and marginally improved in one case.
-Coverage improved in the random cross-validation in Indonesia and Madagascar and spatial cross-validation in Madagascar and marginally improved in the spatial cross-validation in Senegal.
-In the remaining two cases, adding prevalence point-surveys did not substantially improve coverage, but did make the model more conservative, with coverage of 0.91 rather than 0.71 in the random cross-validation Senegal experiment and 0.96 instead of 0.62 in the spatial cross-validation Indonesia experiment.
+The proportion of out-of-sample incidence datapoints being within their 80\% credible intervals ranged between 0.54 and 0.9.
+However, in most cases coverage was between 0.7 and 0.8 implying the models were a little overconfident in their predictions.
 
@@
 We have compared the predictive performance of a polygon-only model and a model that jointly learns from polygon incidence data and prevalence point-surveys.
-We found that neither model was clearly superior to the other but that both models recovered the broad spatial pattern of malaria risk (Figures \ref{predobsmapidn} and \ref{predobsmapsen}).
-With regards to a random cross-validation scheme, adding prevalence point-surveys to the disaggregation model only improved performance in  Madagascar (Table~\ref{table1}).
-With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the prevalence point-surveys improved on the polygon-only models in both Senegal and Madagascar but not Indonesia (Table~\ref{table2}).
-
-We used held-out prevalence point-surveys to measure how well the models predicted within-polygon, pixel-level malaria risk.
-Given the poor performance by all models, including the points-only model (Figures~\ref{randompredobsscatter} and \ref{spatialpredobsscatter}), particularly in Indonesia and Senegal these results must be interpreted with care.
-% Add sample size, comparisons etc.
-In particular, a majority of the prevalence point-surveys in all countries found zero malaria infections (though the age standardisation moves these to slightly non-zero values) and small sample sizes were common in the Senegal and Indonesia data.
-Given the poor performance of the points-only model, it is not useful to interpret these results as a direct measure of a models ability to predict within-polygon, pixel level risk.
-Instead we can, with care, interpret the relative performance of models.
-In five cases, the polygon-only and joint model had the same predictive performance on the prevalence point-surveys.
-In only one cases, the joint model was marginally better.
-Therefore we conclude that the joint model is no better than the polygon-only model at predicting within-polygon, pixel-level malaria risk.
-
-% Discuss and interpret. Generalise
-
-The joint model improved the prediction of polygon incidence in two of three countries under the spatial cross-validation scheme but only one country in the random cross-validation scheme.
-The two countries where the joint model performed best in the spatial cross-validation scheme are the two countries with the least data.
-The joint model seemed to perform comparatively well in the cases where predictions had little information from the random field and when there is little data to estimate regression parameters.
-Far-from-data predictions are particularly susceptible to overfitting.
-Given the simple linear model, adding prevalence point-surveys may protect against overfitting by increasing the amount of data available.
-Alternatively, the improved perforamance could be because a model that learns from two datasets, on different scales, with different biases, is also less likely to overfit.
-
-In contrast, the joint model does not in general improve on the polygon-only model in the random cross-validation scheme.
-A noticable element of this scheme was that locations where polygon incidence data was removed for validation could still potentially have prevalence point-survey data.
-Figure~\ref{fig:cv_random} implies that this situation is the norm.
-Yet this spatial information did not improve performance in Indonesia or Senegal.
-
-% Clear benefits, when some areas have polygon and some have PR.
-%   Where?
-
-There are two main reasons why a model fitted jointly on prevalence point-surveys and polygon incidence data may perform worse than a polygon-only mode.
-Firstly, the data are on difference scales.
-Here we have used a previously fitted model \cite{cameron2015defining} in order to be able to fit the joint model.
-However, this model is imperfect in that it is calibrated with a relatively small amount of matched prevalence and incidence data.
-Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality and age-structure are not constant \cite{cameron2015defining, battle2015defining,reiner2015seasonality}.
-In using a joint model we are accepting these failings in the hope that the benefits of including additional data are stronger than the costs of using mismatched data.
-The second aspect of prevalence point-survey data that could reduce the predictive ability of a polygon-only model by adding point data is if the point data is of low quality.
-In particular, non-random sampling of individuals can produce biased estimates of prevalence and this will decrease model performance.
-
-For a model to be robust to shortcomings in the prevalence-incidence relationship from \cite{cameron2015defining}, future models could be more flexible in the way they use this relationship.
-This could be by estimating the parameters of the polynomial jointly with the rest of the model.
-Informative priors based on the original model should be used to regularise this joint fit both to prevent unbelievable inferences but also because if the relationship is too flexible, the information from the prevalence data might not be used by the incidence level model.
-This is particularly true for even more flexible model forms that could be used such as a spline or a Gaussian process on the relationship between prevalence and incidence.
-
-For the model to handle noisy or biased prevalence point-surveys, the modeller can control the iid random effect on the point-surveys, $w_i$. 
-Here we have tried to maximise the influence of the prevalence data by setting the prior based on the belief that the random effect should only explain extra-binomial variation that is impossible to explain with the covariates (i.e.
-based on the differences in prevalence surveys within the same pixel).
-Weakening this prior will allow the iid effect to explain more of the prevalence point-survey variation which both reduces the potential statistical power gained by adding the point-surveys but also reduces the effects of biased or noisy estimates.
-
-There are large potential benefits to models that combine data in the context of large scale studies over multiple countries.
-In these cases there is often different data types in different countries and being able to make malaria estimates of the countries together increases spatial coverage and statistical power.
-Further cases where this joint model may be particularly beneficial is in countries where prevalence surveys are strongly clustered in one area --- typically an area of high malaria risk --- but without high resolution surveillance data.
-In these regions, fitting a model on just the prevalence point-surveys requires predictions far away from the survey locations whlie fitting a model just on the polygon incidence data will be underpowered.
-However, the benefits of these methods do not come for free, as indicated by the reduced performance in some cases.
-
-In order to specifically compare the affects of combining the data types, we have aimed to keep the models fitted here as simple as possible.
-However, a number of improvements could be made.
-Data from multiple years are available for many countries.
-Simply combining data collected at different times is not recommended as malaria incidence is changing rapidly.
-However, fitting a full spatio-temporal model would be a suitable way to combine data from different periods but would be computationally more expensive \cite{bhatt2015effect, taylor2017continuous}.
-This is an avenue of work that should be pursued.
-Furthermore, it has been clearly established that simple linear combinations of environmental covariates cannot fully explain malaria risk \cite{bhatt2017improved}.
-A number of methods could be used to include non-linear effects of covariates and interactions into the model.
-Firstly, as in \cite{bhatt2017improved}, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model.
-This approach is feasible but does not allow any information from the polygons to inform non-linear relationships.
-To directly model non-linear effects in the full model could be achieved by including simple non-linear functions such as splines \cite{sissoko2017temporal, sewe2017using, hundessa2018projecting}, though the increased model complexity would require more data than was used in Senegal and Madagascar in this study.
-Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \cite{law2018variational}.
-These are computational expensive without careful approximations via variational Bayes or other approximations.
-Again these models need a lot of data and careful regularisation for good predictive performance.
 

### 2019-03-30 ms.tex
Edits to add fit p2i in.

@@
 
-$$i_b = \mathrm{PrevInc}(p_b)$$
+$$i_b = \exp(\alpha)\mathrm{PrevInc}(p_b).$$
 
-where $\mathrm{PrevInc}$ is a function from a previously fitted model \cite{cameron2015defining} 
+Here $\mathrm{PrevInc}$ is a function from a previously fitted model \cite{cameron2015defining} 
 $$\mathrm{PrevInc}: f\left(p_b\right) = 2.616p_b - 3.596{p_b}^2 + 1.594{p_b}^3.$$
+$\alpha$ is a parameter to be fitted that adjusts the previously fitted function.
 
@@
 The form of the link function means we get predictions of prevalence and incidence simultaneously whether we used both data types or just one.
-The linear predictor is composed of an intercept, covariates, a spatial, Gaussian random field and two iid random effects.
+The linear predictor is composed of a global intercept, $b_0$, and a prevalence survey only intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point survey is being considered.
+The linear predictor also includes covariates, $X$, and a vector of regression coefficients $\beta$.
+Finally we include a spatial, Gaussian random field and two iid random effects.
 
-$$\eta_b = \beta_0 + \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) + w_i(\sigma_w)$$
+$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) + w_i(\sigma_w)$$
 
@@
 
-Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
+Finally, we complete the model by setting priors on the parameters $\beta_0, \brta_p, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
 We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
@@
 
+The intercept was given a wide prior, $b_0 \sim \operatorname{Norm}(-2, 4)$ with a mean less than zero as we know \emph{a priori} that these countries have low or medium levels of malaria transmission.
+The prevalence only intercept was given a wide, zero-mean prior, $b_0 \sim \operatorname{Norm}(0, 4)$. % check
 Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
@@
 & Madagascar  & 39.06 &  {\bf 36.36}\vspace{3mm}\\
-Spatial a & Indonesia & {\bf 14.81} &  16.45\\
-& Senegal  & {\bf 12.31} &  30.12\\
-& Madagascar & 67.73 &  {\bf 44.05} \vspace{3mm}\\
-Spatial b & Indonesia & {\bf 14.77} &  15.02\\
-& Senegal  & {\bf 12.39} &  18.75\\
-& Madagascar  & 70.72 &  {\bf 61.05}\\
+Spatial 1 & Indonesia & {\bf 14.77} &  15.08\\
+& Senegal  & {\bf 12.39} &  16.56\\
+& Madagascar  & 70.72 &  {\bf 61.05}\vspace{3mm}\\
+Spatial 2 & Indonesia & {\bf 14.81} &  16.36\\
+& Senegal  & {\bf 12.31} &  15.91\\
+& Madagascar & 67.73 &  {\bf 44.05}\\
 \end{tabular}
@@
 & Madagascar  & 0.78 &  0.78\vspace{1mm}\\
- Spatial a & Indonesia  & {\bf 0.69} &  {\bf 0.54}\\
-& Senegal  & 0.83 &  {\bf 0.59}\\
-& Madagascar  & {\bf 0.67} &  0.72 \vspace{1mm} \\
-Spatial b & Indonesia & 0.74 &  0.70\\
-& Senegal  & {\bf 0.90} &  0.73\\
-& Madagascar  & {\bf 0.61} &  {\bf 0.69}\\
+ Spatial 1 & Indonesia & 0.74 &  0.68\\
+& Senegal  & 0.90 &  0.83\\
+& Madagascar  & 0.61 &  0.69\vspace{1mm} \\
+ Spatial 2 & Indonesia  & 0.69 &  0.53\\
+& Senegal  & 0.83 &  0.73\\
+& Madagascar  & 0.67 &  0.72\\
 

### 2019-05-03 ms.tex
Typo.
Add zambia prelim results.

@@
 
-Finally, we complete the model by setting priors on the parameters $\beta_0, \brta_p, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
+Finally, we complete the model by setting priors on the parameters $\beta_0, \beta_p, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
 We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
@@
 %This cross-validation scheme directly addresses the question of whethe
-In the second validation scheme (spatial a), the incidence data was split into spatial cross-validation folds while again all prevalence points were used in all folds.
+In the second validation scheme (spatial a), the incidence data was split into spatial cross-validation folds, using k means clustering on polygon centroids, while again all prevalence points were used in all folds.
 The number of folds was seven for Indonesia, five for Senegal and three for Madagascar due to their differing sizes and epidemiological settings.
-The data was divided by combining the prevalence point-survey locations and the centroids of the incidence polygons and performing k means clustering.
 This scheme is specifically testing whether the joint model can improve predictions by increasing geographic data coverage.
@@
 & Senegal  & {\bf 12.41} &  12.81\\
+& Zambia  & {\bf 154.59} &  154.96\\
 & Madagascar  & 39.06 &  {\bf 36.36}\vspace{3mm}\\
@@
 & Senegal  & {\bf 12.39} &  16.56\\
+& Zambia  & {\bf 162.74} &  163.74\\
 & Madagascar  & 70.72 &  {\bf 61.05}\vspace{3mm}\\
@@
 & Senegal  & {\bf 12.31} &  15.91\\
+& Zambia  & {\bf 135.39} &  184.14\\
 & Madagascar & 67.73 &  {\bf 44.05}\\

### 2019-05-03 ms.tex
Add extra prev snegal results.

@@
 \hline
-{\bf CV scheme} & {\bf Country} &  {\bf Polygons} & {\bf Joint} \\
+{\bf CV scheme} & {\bf Country} &  {\bf Polygons} & {\bf Joint} & {\bf Joint extra} \\
 \thickhline 
-Random & Indonesia  & 13.95 &  {\bf 13.88}\\
-& Senegal  & {\bf 12.41} &  12.81\\
-& Zambia  & {\bf 154.59} &  154.96\\
-& Madagascar  & 39.06 &  {\bf 36.36}\vspace{3mm}\\
-Spatial 1 & Indonesia & {\bf 14.77} &  15.08\\
-& Senegal  & {\bf 12.39} &  16.56\\
-& Zambia  & {\bf 162.74} &  163.74\\
-& Madagascar  & 70.72 &  {\bf 61.05}\vspace{3mm}\\
-Spatial 2 & Indonesia & {\bf 14.81} &  16.36\\
-& Senegal  & {\bf 12.31} &  15.91\\
-& Zambia  & {\bf 135.39} &  184.14\\
-& Madagascar & 67.73 &  {\bf 44.05}\\
+Random & Indonesia  & 13.95 &  {\bf 13.88} & \\
+& Senegal  & {\bf 12.41} &  12.81 &\\
+& Zambia  & {\bf 154.59} &  154.96 &\\
+& Madagascar  & 39.06 &  {\bf 36.36} &\vspace{3mm}\\
+Spatial 1 & Indonesia & {\bf 14.77} &  15.08&\\
+& Senegal  & {\bf 12.39} &  16.56 & 14.41\\
+& Zambia  & {\bf 162.74} &  163.74 &\\
+& Madagascar  & 70.72 &  {\bf 61.05} & \vspace{3mm}\\
+Spatial 2 & Indonesia & {\bf 14.81} &  16.36 &\\
+& Senegal  & {\bf 12.31} &  15.91 & 13.63\\
+& Zambia  & {\bf 135.39} &  184.14 &\\
+& Madagascar & 67.73 &  {\bf 44.05} &\\
 \end{tabular}

### 2019-05-04 ms.tex
New zambia with rng issue fixed.

@@
 {\bf Summary of out-of-sample accuracy for all three cross-validation experiments.}}
-\begin{tabular}{llll}
+\begin{tabular}{lllll}
 \hline
@@
 & Senegal  & {\bf 12.39} &  16.56 & 14.41\\
-& Zambia  & {\bf 162.74} &  163.74 &\\
+& Zambia  & {\bf 165.02} &  169.84 &\\
 & Madagascar  & 70.72 &  {\bf 61.05} & \vspace{3mm}\\
@@
 & Senegal  & {\bf 12.31} &  15.91 & 13.63\\
-& Zambia  & {\bf 135.39} &  184.14 &\\
+& Zambia  & {\bf 165.02} &  185.39 &\\
 & Madagascar & 67.73 &  {\bf 44.05} &\\

### 2019-05-30 ms.tex
Add pr gp to results table.

--- 2019-05-03 ms.tex
@@
 {\bf Summary of out-of-sample accuracy for all three cross-validation experiments.}}
-\begin{tabular}{llll}
+\begin{tabular}{lllll}
 \hline
-{\bf CV scheme} & {\bf Country} &  {\bf Polygons} & {\bf Joint} \\
+{\bf CV scheme} & {\bf Country} &  {\bf Polygons} & {\bf Joint} & {\bf Prevalence Cov} \\
 \thickhline 
-Random & Indonesia  & 13.95 &  {\bf 13.88}\\
-& Senegal  & {\bf 12.41} &  12.81\\
-& Zambia  & {\bf 154.59} &  154.96\\
-& Madagascar  & 39.06 &  {\bf 36.36}\vspace{3mm}\\
-Spatial 1 & Indonesia & {\bf 14.77} &  15.08\\
-& Senegal  & {\bf 12.39} &  16.56\\
-& Zambia  & {\bf 162.74} &  163.74\\
-& Madagascar  & 70.72 &  {\bf 61.05}\vspace{3mm}\\
-Spatial 2 & Indonesia & {\bf 14.81} &  16.36\\
-& Senegal  & {\bf 12.31} &  15.91\\
-& Zambia  & {\bf 135.39} &  184.14\\
-& Madagascar & 67.73 &  {\bf 44.05}\\
+Random & Indonesia  & 13.95 &  {\bf 13.88} & 14.09  \\
+& Senegal  & 12.41 &  12.81 &  {\bf 12.37}\\
+& Madagascar  & 39.06 &  36.36 &  {\bf 35.82} \vspace{3mm}\\
+Spatial 1 & Indonesia & {\bf 14.77} &  14.97 &   {\bf 14.77}\\
+& Senegal  & 13.07 &  15.15 &  {\bf 12.21}  \\
+& Madagascar  & 70.72 &  61.05 & {\bf 50.38}\vspace{3mm}\\
 \end{tabular}

### 2019-06-07 ms.tex
Add newest results table.

@@
 However, traditional mapping using prevalence point-surveys are often ineffective in low prevalence areas due to low statistical power and a lack of data.
-Therefore, models must be developed that can estimate risk at high spatial resolution from surveillance data that reports incidence aggregated to a geographic polygon.
-Current models formulated for polygon incidence data suffer from lower statistical power for learning relationships between malaria risk and environmental covariates.
-Here we present a joint model that uses both polygon incidence and prevalence point-surveys.
+More recently, dissagregation regression models have been developed that can estimate risk at high spatial resolution from surveillance data that reports incidence aggregated to a geographic polygon.
+However, there is generally low spatial overlap between prevalence point-surveys and polygon incidence data and therefore models that make use of the spatial information from prevalence point surveys have great potential.
+Here, using case studies in Indonesia, Senegal and Madagascar, we compare two methods for incorporating this spatial information into a disaggregation regression model.
+The first is a simple model that fits a Gaussian random field to prevalence point-surveys and then uses predictions from the random field as a covariate in the disaggregation regression model.
+The second is a more complex, multi-likelihood model that jointly fits a model using prevalence point-surveys and  polygon incidence data.
+We find that the simple model performs better than a baseline disaggregation model while the joint model performs similarly or slightly worse.
+Our results demonstrate that a simple method can be used to combine spatial information from prevalence point-surveys and polygon incdience data.
 
@@
 However using polygon incidence data to estimate malaria risk for high resolution maps presents several noteworthy modelling difficulties. 
+Firstly, especially when modelling at continental scales \cite{lancet}, there are often areas with better coverage of prevalence surveys than polygon incidence data.
 %Disaggregation models aim to estimate high-resolution maps from aggregated data and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
-The aggregation of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
-This lack of statistical power puts constraints on the models that can be fitted for example requiring variable selection and simple linear terms \cite{sturrock2014fine}.
-Disaggregation models are also simply an underrepresented class of models in the statistical literature and statistical software relative to model-based geostatistical approaches.
-Likewise, downscaling models are not available in popular software packages and must typically be programmed explicitly though Wilson \emph{et al.} \cite{wilson2017pointless} used an approximation to represent a downscaling model as a convolution matrix within R-INLA \cite{INLA}.
-Furthermore, disaggregation models are relatively difficult to implement as they have more rows of covariate data than response data.
+Furthermore, the aggregation of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
+This lack of statistical power puts constraints on the number of covariates that can be used \cite{sturrock2014fine}.
+Finally, both prevalence and incidence metrics are useful for policy makers \cite{cohen2017mapping} but typically models are fitted to observations of one metric and then a secondary model is used to convert to the other post hoc \cite{battlelancet, bhatt2015}.
+Models that combine observations of incidence and prevalence have the potential to provide better estimates than the post hoc conversion and could also learn the relationship between different metrics at the same time as making spatial estimates.
 
 Given the differing strengths of prevalence point-surveys and polygon incidence data, a model that simultaneously leverages both data types has great potential to improve malaria burden mapping.
-Joint modelling of the two data types could provide increased statistical power for learning relationships between malaria risk and covariates by making more data available and because point-surveys have a one-to-one relationship with gridded environmental covariates at the location and time of the survey.
-Furthermore, using two complimentary datasets potentially allows better spatial coverage \cite{sturrock2016mapping}. 
-One major barrier to a joint modelling approach, however, is that these two data types capture different scales.
-Point surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ that quantify parasite rate at a single moment. In contrast,
-In contrast, routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$ as it spans a period of time (e.g., a year) over which individuals can have multiple malaria infections..
+Joint modelling of the two data potentially allows better spatial coverage \cite{sturrock2016mapping}. 
+Using two datasets could also provide increased statistical power for learning relationships between malaria risk and covariates by making more data available and because point-surveys have a one-to-one relationship with gridded environmental covariates at the location and time of the survey.
+One major barrier to a joint modelling approach, however, is that these two data types measure metrics disease transmission on different scales.
+Point surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ that quantify parasite rate at a single moment.
+In contrast, routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$ as it spans a period of time (e.g., a year) over which individuals can have multiple malaria infections.
 %One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015defining}.
@@
 
-Here we formulate a joint model that combines polygon incidence data and prevalence point-surveys of \emph{Plasmodium falciparum} using seperate likelihoods for both data types.
-We relate the differing malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
-We then compare results from the joint model with those made using a polygon-only, disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless}.
+Here we compare two methods for using spatial information from prevalence surveys to inform a disaggregation model of fitted to polygon incidence data.
+The first model fits a Gaussian process to prevalence point surveys then uses predictions from this model as a covariate in the disaggregation model.
+Secondly, we formulate a joint model that combines polygon incidence data and prevalence point-surveys of \emph{Plasmodium falciparum} using seperate likelihoods for both data types.
+We relate the differing malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining} which is then adjusted as part of the model fitting process.
+We then compare results from the two models with those made using a polygon-only, disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless}.
 Both models are fitted to data from Indonesia, Senegal and Madagascar to provide a set of case studies with disparate geographic settings and levels of malaria endemicity.
@@
 
-\subsection*{The model}
+\subsection*{Baseline Disaggregation Model}
 
-We compared three models 1) a joint model using both  prevalence point-surveys and polygon incidence data as the response variable 2) a submodel using only polygon incidence data and 3) a benchmark submodel using only prevalence point-survey data.
-The models were implemented and fitted in R \cite{R} using Template Model Builder \cite{TMB} which allows a Laplace approximation of the posterior to be calculated.
-
-The full, joint likelihood model is described as follows. 
 Values at the aggregate, polygon level are given the subscript $a$ while pixel or point level variables are indexed with $b$.
@@
 
-The prevalence point-survey data, $z_b$, is given a binomial likelihood
-
-$$z_b \sim \operatorname{Binom}(p_b, n_b) $$
-
-where $p_b$ is the estimated prevalence and $n_b$ is the observed survey sample size.
-
-The two quantities are linked to each other and to the predictor variables by the following system of equations.
+Incidence rate is linked to a latent prevalence $p_b$ and to the predictor variables by the following system of equations.
 
@@
 $$\mathrm{PrevInc}: f\left(p_b\right) = 2.616p_b - 3.596{p_b}^2 + 1.594{p_b}^3.$$
-$\alpha$ is a parameter to be fitted that adjusts the previously fitted function.
+$\alpha$ is an unknown parameter that adjusts the previously fitted function.
 
-The linear predictor of the model, $\eta_b$, is related to prevalence by a typical logit link function.
+The linear predictor of the model, $\eta_b$, is related to the latent prevalence scale by a typical logit link function.
 
@@
 The form of the link function means we get predictions of prevalence and incidence simultaneously whether we used both data types or just one.
-The linear predictor is composed of a global intercept, $b_0$, and a prevalence survey only intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point survey is being considered.
-The linear predictor also includes covariates, $X$, and a vector of regression coefficients $\beta$.
-Finally we include a spatial, Gaussian random field and two iid random effects.
+The linear predictor is composed of a global intercept, $b_0$, covariates, $X$, and a vector of regression coefficients $\beta$.
+Finally we include a spatial, Gaussian random field and one iid random effect.
 
-$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) + w_i(\sigma_w)$$
+$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) $$
 
 The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
-The first iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all pixels and point surveys within polygon $j$ being grouped together.
+The iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $j$ being grouped together.
 This random effect modelled both missing covariates and extra-Poisson sampling error. 
-The second iid random effect, $w_i \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
-This effect modelled extra-binomial sampling noise.
-As such, this random effect is not included in the predicted uncertainty in the incidence or prevalence layers.
-However, it is included in predictions of out-of-sample point surveys.
 The randoms effects are all integrated out during the TMB model fitting.
@@
 We found that an iid effect with a standard deviation of 0.05 is able to account for the discrepancy between the assumed Poisson error and the independently derived error.
-We assigned $\sigma_w$ a penalised complexity prior such that $P(\sigma_w > 0.3) = 0.0000001$. 
-This was chosen by finding the maximum difference in prevalence between point-surveys (with a sample size greater than 500 individuals) within the same raster pixel.
-The differences between points within the same pixel can only be accounted for by the binomial error and this iid effect.
-Given that the error on a prevalence estimate with sample size greater than 500 is quite small, the iid effect needs to be able to explain this difference.
 
@@
 
+The models were implemented and fitted in R \cite{R} using Template Model Builder \cite{TMB} which allows a Laplace approximation of the posterior to be calculated.
+
+\subsection*{Prevalence Gaussian process covariate model}
+
+\subsection*{Full joint model}
+
+The prevalence point-survey data, $z_b$, is given a binomial likelihood
+
+$$z_b \sim \operatorname{Binom}(p_b, n_b) $$
+
+where $p_b$ is the estimated prevalence and $n_b$ is the observed survey sample size.
+
+and a prevalence survey only intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point survey is being considered.
+
+The iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $j$ being grouped together.
+
+The second iid random effect, $w_i \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
+This effect modelled extra-binomial sampling noise.
+As such, this random effect is not included in the predicted uncertainty in the incidence or prevalence layers.
+However, it is included in predictions of out-of-sample point surveys.
+
+We assigned $\sigma_w$ a penalised complexity prior such that $P(\sigma_w > 0.3) = 0.0000001$. 
+This was chosen by finding the maximum difference in prevalence between point-surveys (with a sample size greater than 500 individuals) within the same raster pixel.
+The differences between points within the same pixel can only be accounted for by the binomial error and this iid effect.
+Given that the error on a prevalence estimate with sample size greater than 500 is quite small, the iid effect needs to be able to explain this difference.
+
 \subsection*{Experiments}
@@
 \hline
-{\bf CV scheme} & {\bf Country} &  {\bf Polygons} & {\bf Joint} & {\bf Prevalence Cov} \\
+{\bf Cross-validation} & {\bf Country}  & {\bf Baseline} & {\bf Prev GP} & {\bf Joint} \\
 \thickhline 
-Random & Indonesia  & 13.95 &  {\bf 13.88} & 14.09  \\
-& Senegal  & 12.41 &  12.81 &  {\bf 12.37}\\
-& Madagascar  & 39.06 &  36.36 &  {\bf 35.82} \vspace{3mm}\\
-Spatial 1 & Indonesia & {\bf 14.77} &  14.97 &   {\bf 14.77}\\
-& Senegal  & 13.07 &  15.15 &  {\bf 12.21}  \\
-& Madagascar  & 70.72 &  61.05 & {\bf 50.38}\vspace{3mm}\\
+Random & Indonesia  & 13.95 &  14.09 &  {\bf 13.79}\\
+& Senegal  & 12.41 &  {\bf 12.37} &  13.07\\
+& Madagascar  & 39.06 &  {\bf 35.82} &  36.36\vspace{3mm}\\
+Spatial & Indonesia & {\bf 14.77} &  {\bf 14.77} &  16.46\\
+& Senegal  & 13.09 &  {\bf 12.21} &  15.15\\
+& Madagascar & 67.73 &  50.38 &  {\bf 44.05}\\
 \end{tabular}
@@
 
-\begin{figure}
-% to be removed before submission
-\includegraphics[width = 1.05\textwidth]{figures/spatial_cv_poly_facet} 
-\caption{{\bf Observed-predicted plots for spatial b cross-validation experiments where prevalence points are spatially witheld.}
-A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (per 1,000).
-Results from the standard downscaling model are shown in blue and the combined model is shown in green.
-}
-\label{spatialpredobspolyfacet}
-\end{figure}
-
 \begin{table}[t]
@@
 {\bf Summary of coverage of 80\% credible intervals.}}
-\begin{tabular}{llll}
+\begin{tabular}{lllll}
 \hline
-{\bf Cross-validation} & {\bf Country}  & {\bf Polygons} & {\bf Joint} \\
+{\bf Cross-validation} & {\bf Country}  & {\bf Baseline} & {\bf Prev GP} & {\bf Joint} \\
 \thickhline 
-Random & Indonesia  & 0.73 &  0.74\\
-& Senegal  & 0.76 &  0.73\\
-& Madagascar  & 0.78 &  0.78\vspace{1mm}\\
- Spatial 1 & Indonesia & 0.74 &  0.68\\
-& Senegal  & 0.90 &  0.83\\
-& Madagascar  & 0.61 &  0.69\vspace{1mm} \\
- Spatial 2 & Indonesia  & 0.69 &  0.53\\
-& Senegal  & 0.83 &  0.73\\
-& Madagascar  & 0.67 &  0.72\\
+Random & Indonesia  & 13.95 &  14.09 &  {\bf 13.79}\\
+& Senegal  & 12.41 &  {\bf 12.37} &  13.07\\
+& Madagascar  & 39.06 &  {\bf 35.82} &  36.36\vspace{3mm}\\
+Spatial & Indonesia & {\bf 14.77} &  {\bf 14.77} &  16.46\\
+& Senegal  & 13.09 &  {\bf 12.21} &  15.15\\
+& Madagascar & 67.73 &  50.38 &  {\bf 44.05}\\
 
@@
 
+% simple model best
+% less fiddly, but none of these models are in packages
+%
+
+% joint model benefits
+% robust
+% lower sd of posteriors
+% learn relationship
+% disappointed that we couldn't get it to out perform
+
+There are two main reasons why a model fitted jointly on prevalence point-surveys and polygon incidence data may perform worse than a polygon-only mode.
+Firstly, the data are on difference scales.
+Here we have used a previously fitted model \cite{cameron2015defining} in order to be able to fit the joint model.
+However, this model is imperfect in that it is calibrated with a relatively small amount of matched prevalence and incidence data.
+Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality and age-structure are not constant \cite{cameron2015defining, battle2015defining,reiner2015seasonality}.
+In using a joint model we are accepting these failings in the hope that the benefits of including additional data are stronger than the costs of using mismatched data.
+The second aspect of prevalence point-survey data that could reduce the predictive ability of a polygon-only model by adding point data is if the point data is of low quality.
+In particular, non-random sampling of individuals can produce biased estimates of prevalence and this will decrease model performance.
+
+For a model to be robust to shortcomings in the prevalence-incidence relationship from \cite{cameron2015defining}, future models could be more flexible in the way they use this relationship.
+This could be by estimating the parameters of the polynomial jointly with the rest of the model.
+Informative priors based on the original model should be used to regularise this joint fit both to prevent unbelievable inferences but also because if the relationship is too flexible, the information from the prevalence data might not be used by the incidence level model.
+This is particularly true for even more flexible model forms that could be used such as a spline or a Gaussian process on the relationship between prevalence and incidence.
+
+For the model to handle noisy or biased prevalence point-surveys, the modeller can control the iid random effect on the point-surveys, $w_i$. 
+Here we have tried to maximise the influence of the prevalence data by setting the prior based on the belief that the random effect should only explain extra-binomial variation that is impossible to explain with the covariates (i.e.
+based on the differences in prevalence surveys within the same pixel).
+Weakening this prior will allow the iid effect to explain more of the prevalence point-survey variation which both reduces the potential statistical power gained by adding the point-surveys but also reduces the effects of biased or noisy estimates.
+
+However, fitting a full spatio-temporal model would be a suitable way to combine data from different periods but would be computationally more expensive \cite{bhatt2015effect, taylor2017continuous}.
+This is an avenue of work that should be pursued.
+Furthermore, it has been clearly established that simple linear combinations of environmental covariates cannot fully explain malaria risk \cite{bhatt2017improved}.
+A number of methods could be used to include non-linear effects of covariates and interactions into the model.
+Firstly, as in \cite{bhatt2017improved}, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model.
+This approach is feasible but does not allow any information from the polygons to inform non-linear relationships.
+To directly model non-linear effects in the full model could be achieved by including simple non-linear functions such as splines \cite{sissoko2017temporal, sewe2017using, hundessa2018projecting}, though the increased model complexity would require more data than was used in Senegal and Madagascar in this study.
+Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \cite{law2018variational}.
+These are computational expensive without variational Bayes or other approximations \cite{law2018variational,  randomFourier} which can be difficult to derive.
+Again these models need a lot of data and careful regularisation for good predictive performance.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-06-09 ms.tex
Add newest coverage table.
Add methods for prev gp.

@@
 This random effect modelled both missing covariates and extra-Poisson sampling error.
-The randoms effects are all integrated out during the TMB model fitting.
-The hyperparameters are fitted during model fitting using empirical Bayes.
-In this empirical Bayes scheme the hyperparameters are learned from the data but are treated as point estimates rather than the model using the full posterior of the hyperparameters.
+The hyperparameters are fitted using empirical Bayes whereby the hyperparameters are learned from the data but are treated as point estimates rather than using the full posterior of the hyperparameters.
 
@@
 \subsection*{Prevalence Gaussian process covariate model}
+
+This model is the same as the baseline disaggregation model except that it has one extra covariate.
+This covariate is created by fitting a Gaussian random field to the prevalence survey data.
+For each country we fitted a binomial likelihood, hierarchical Gaussian random field with the same hyperpriors as above.
+These models were fitted using R-INLA \cite{INLA}.
+To be in the correct scale for the dissagregation model, the inverse logit of the predicted Gaussian field (i.e. the liver predictor of the model) was used for the additional covariate.
 
@@
 \thickhline 
-Random & Indonesia  & 13.95 &  14.09 &  {\bf 13.79}\\
-& Senegal  & 12.41 &  {\bf 12.37} &  13.07\\
-& Madagascar  & 39.06 &  {\bf 35.82} &  36.36\vspace{3mm}\\
-Spatial & Indonesia & {\bf 14.77} &  {\bf 14.77} &  16.46\\
-& Senegal  & 13.09 &  {\bf 12.21} &  15.15\\
-& Madagascar & 67.73 &  50.38 &  {\bf 44.05}\\
+Random & Indonesia  & 0.73 &  0.72 &  0.72\\
+& Senegal  & 0.76 &  0.78 &  0.80\\
+& Madagascar  & 0.78 &  0.79 &  0.78\vspace{1mm}\\
+ Spatial  & Indonesia & 0.71 &  0.72 &  {\bf 0.51}\\
+& Senegal  & 0.78 &  0.88 &  0.71\\
+& Madagascar  & {\bf 0.67} &  0.70 &  0.72\\
 

### 2019-06-10 ms.tex
Fix joint model methods.

@@
 
-$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) $$
+$$\eta_b = \beta_0 + \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) $$
 
@@
 
-The prevalence point-survey data, $z_b$, is given a binomial likelihood
+The final model is a joint-likelihood model with separate likelihoods for prevalence point surveys and polygon incidence data.
+The polygon data are assigned a Poisson likelihood as before but the prevalence point-survey data, $z_b$, is given a binomial likelihood
 
@@
 where $p_b$ is the estimated prevalence and $n_b$ is the observed survey sample size. 
+The only further additions to the baseline model are in the linear predictor which becomes
 
-and a prevalence survey only intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point survey is being considered.
+$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) + w_i(\sigma_w).$$
 
-The iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $j$ being grouped together.
-
-The second iid random effect, $w_i \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
+As well as the global intercept, $\beta_0$, this model has a prevalence survey only intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point survey is being considered.
+The iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all point surveys within polygon $j$ being in the same group as polygon $j$.
+Finally, the second iid random effect, $w_i \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
 This effect modelled extra-binomial sampling noise.
 As such, this random effect is not included in the predicted uncertainty in the incidence or prevalence layers.
-However, it is included in predictions of out-of-sample point surveys.
 

### 2019-06-14 ms.tex
Bunch of edits to methods.

@@
 \section*{Abstract}
-As malaria incidence decreases and more contries move towards elimination, maps of malaria risk in low prevalence areas are becoming increasingly needed.
+As malaria incidence decreases and more countries move towards elimination, maps of malaria risk in low prevalence areas are becoming increasingly needed.
 However, traditional mapping using prevalence point-surveys are often ineffective in low prevalence areas due to low statistical power and a lack of data.
@@
 The second is a more complex, multi-likelihood model that jointly fits a model using prevalence point-surveys and  polygon incidence data.
-We find that the simple model performs better than a baseline disaggregation model while the joint model performs similarly or slightly worse.
-Our results demonstrate that a simple method can be used to combine spatial information from prevalence point-surveys and polygon incdience data.
+We find that the simple model generally performs better than a baseline disaggregation model while the joint model sometimes performs better than baseline but often worse.
+Our results demonstrate that a simple method can be used to combine spatial information from prevalence point-surveys and polygon incdience data and that more generally, combining these types of data improves estimates of malaria incidence.
 
@@
 In low burden areas, very large sample sizes are needed before a prevalence survey is informative because so few individuals have parasitaemia that most sample points will have no cases.
-As a result, large, countrywide surveys of prevalence, such as DHS or MIS, are rare in low burden countries due to costs and percieved low utility \cite{dhs}.
-We therefore need new data sources and associated statistical methods.
+Routine surveillance data, of malaria case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
+This polygon incidence data can be more sensitive than prevalence point-surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
 
@@
 %cohen2017mapping Different metrics are useful for different things. Most maps use prevalence. Govts do use maps.
-
-Routine surveillance data, of malaria case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
-Surveillance data is commonly aggregated from information collected at healthcare facilities or by community health workers, reporting the number of cases that occurred within a certain geographic or administrative region defined by a polygon.
-This polygon incidence data can be more sensitive than prevalence point-surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
-Furthermore, polygon incidence data is also often timely, with reports being released annually or monthly with little lag, while countrywide collection of prevalence point-surveys are both rare and often released one to two years after field data collection is completed.
-However, the unstructured nature of data collection and reporting of polygon incidence data from national disease surveillance systems means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.
 
@@
 However using polygon incidence data to estimate malaria risk for high resolution maps presents several noteworthy modelling difficulties. 
-Firstly, especially when modelling at continental scales \cite{lancet}, there are often areas with better coverage of prevalence surveys than polygon incidence data.
+Firstly, especially when modelling at continental scales \cite{lancet}, there are often some areas with better coverage of prevalence surveys than polygon incidence data.
 %Disaggregation models aim to estimate high-resolution maps from aggregated data and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
-Furthermore, the aggregation of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
-This lack of statistical power puts constraints on the number of covariates that can be used \cite{sturrock2014fine}.
-Finally, both prevalence and incidence metrics are useful for policy makers \cite{cohen2017mapping} but typically models are fitted to observations of one metric and then a secondary model is used to convert to the other post hoc \cite{battlelancet, bhatt2015}.
-Models that combine observations of incidence and prevalence have the potential to provide better estimates than the post hoc conversion and could also learn the relationship between different metrics at the same time as making spatial estimates.
-
-Given the differing strengths of prevalence point-surveys and polygon incidence data, a model that simultaneously leverages both data types has great potential to improve malaria burden mapping.
-Joint modelling of the two data potentially allows better spatial coverage \cite{sturrock2016mapping}. 
-Using two datasets could also provide increased statistical power for learning relationships between malaria risk and covariates by making more data available and because point-surveys have a one-to-one relationship with gridded environmental covariates at the location and time of the survey.
+Furthermore, the aggregation of cases over space means that it may be difficult to learn relationships between malaria risk and the environment from these data, especially if the case counts are aggregated over a large or heterogenous area.
+Finally, estimates of both prevalence and incidence metrics are useful for policy makers \cite{cohen2017mapping} but typically models are fitted to observations of one metric and then a secondary model is used to convert to the other \emph{post hoc} \cite{battlelancet, bhatt2015}.
+Models that combine observations of incidence and prevalence have the potential to provide better estimates than the \emph{post hoc} conversion and could also learn the relationship between different metrics at the same time as making spatial estimates.
 One major barrier to a joint modelling approach, however, is that these two data types measure metrics disease transmission on different scales.
@@
 We selected Indonesia, Senegal and Madagascar as case examples as they all have abundant subnational surveillance data and country wide surveys from approximately the same period.
-To minimise temporal effects we selected, for each country, one year of prevalence point-survey data and one year of polygon incidence data.
+To minimise temporal effects we selected five years of prevalence point-survey data and one year of polygon incidence data for each country.
 For Indonesia we selected polygon incidence data from 2012 that covers 380 regions, and prevalence data from 2010 to 2014 that consists of todo surveys, accounting for todo individuals.
 For Senegal we selected 2015 for polygon incidence data (46 regions) and 2013 to 2017 for prevalence data (todo surveys, todo).
-Finally, for Madagascar we selected 2013 for polygon incidence (110 regions) and 2011 to 2015 prevalence (todo surveys, todo individuals) data.
+Finally, for Madagascar we selected 2013 for polygon incidence (110 regions) and 2011 to 2015 for prevalence (todo surveys, todo individuals) data.
 
@@
 
-The polygon incidence data were collated from various government reports and adjusted to a standard metric using methods defined in \cite{cibulskis2011worldwide}.
+The polygon incidence data were collated from various government reports and adjusted to a standard metric using methods defined in \cite{cibulskis2011worldwide, weiss2019}.
 These adjustments account for underreporting of clinical cases due to lack of treatment seeking, missed case reports, and cases that sought medical attention outside the public health systems \cite{battle2016treatment}.
@@
 Raster surfaces of population for the years 2005, 2010 and 2015, were created using a hybrid of data from GPWv4 \cite{gpw4} and WorldPop \cite{tatem2017worldpop}, with the latter taking priority for those pixels where both had population data.
-Final population rasters were created by linear interpolation of the surrounding five-yearly rasters.
-Finally, for each year, national population estimates from the UN were raked over the interpolated population surfaces.
+Yearly population rasters were created by linear interpolation of the surrounding five-yearly rasters.
+For each year, national population estimates from the UN were raked over the interpolated population surfaces. 
+Finally a temperature suitability mask was used to created rasters of population at risk \cite{}. % todo
 
@@
 
-Incidence rate is linked to a latent prevalence $p_b$ and to the predictor variables by the following system of equations.
+Incidence rate is linked to latent pixel-level incidence, $i_b$, prevalence $p_b$ and to the predictor variables by the following system of equations.
 
-$$i_a = \frac{ \sum_{b \in a}(i_b \mathrm{pop}_b)}{\sum_{b \in a}\mathrm{pop}_b} $$
-
-where
-
-$$i_b = \exp(\alpha)\mathrm{PrevInc}(p_b).$$
-
+$$i_a = \frac{ \sum_{b \in a}i_b \mathrm{pop}_b}{\sum_{b \in a}\mathrm{pop}_b} $$
+Here, $b \in a$ denotes that the summation is over the pixels in polygon $a$. 
+Incidence is related to prevalence by
+$$i_b = \mathrm{PrevInc}(p_b).$$
 Here $\mathrm{PrevInc}$ is a function from a previously fitted model \cite{cameron2015defining} 
 $$\mathrm{PrevInc}: f\left(p_b\right) = 2.616p_b - 3.596{p_b}^2 + 1.594{p_b}^3.$$
-$\alpha$ is an unknown parameter that adjusts the previously fitted function.
+The linear predictor of the model, $\eta_b$, is related to the latent prevalence scale by a typical logit link function.
+$$p_b = \operatorname{logit}^{-1}(\eta_b)$$
+The form of this set of link functions means we get predictions of prevalence and incidence simultaneously whether we used both data types or just one.
 
-The linear predictor of the model, $\eta_b$, is related to the latent prevalence scale by a typical logit link function.
-
-$$p_b = \operatorname{logit}^{-1}(\eta_b)$$
-
-The form of the link function means we get predictions of prevalence and incidence simultaneously whether we used both data types or just one.
-The linear predictor is composed of a global intercept, $b_0$, covariates, $X$, and a vector of regression coefficients $\beta$.
-Finally we include a spatial, Gaussian random field and one iid random effect.
-
+The linear predictor is composed of an intercept, $b_0$, covariates, $X$, and a vector of regression coefficients $\beta$.
+We also include a spatial, Gaussian random field, $u(s, \rho, \sigma_u)$ and a polygon-level iid random effect, $ v_j(\sigma_v)$.
 $$\eta_b = \beta_0 + \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) $$
-
 The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
@@
 This random effect modelled both missing covariates and extra-Poisson sampling error.
-The hyperparameters are fitted using empirical Bayes whereby the hyperparameters are learned from the data but are treated as point estimates rather than using the full posterior of the hyperparameters.
 
-Finally, we complete the model by setting priors on the parameters $\beta_0, \beta_p, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
+Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho, \sigma_u$, $\sigma_v$ and $\sigma_w$.
+The intercept was given a wide prior, $b_0 \sim \operatorname{Norm}(-2, 4)$ with a mean less than zero as we know \emph{a priori} that these countries have low or medium levels of malaria transmission.
+We set independant, regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
+Given the standardised covariates and an intercept of -3, a regression coefficient from the 95\% interquartile range of this distribution, each covariate would be able to predict prevalences between 0.004 and 0.27.
+This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularise the model.
+This regularisation is particularly important given the small number of observations in Senegal (n = 46) and Madagascar (n = 110).
+
 We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
@@
 We found that an iid effect with a standard deviation of 0.05 is able to account for the discrepancy between the assumed Poisson error and the independently derived error.
+
+The models were implemented and fitted in R \cite{R} using Template Model Builder \cite{TMB} which allows a Laplace approximation of the posterior to be calculated.
+The hyperparameters are fitted using empirical Bayes whereby the hyperparameters are learned from the data but are treated as point estimates rather than using the full posterior of the hyperparameters.
 
@@
 
-The intercept was given a wide prior, $b_0 \sim \operatorname{Norm}(-2, 4)$ with a mean less than zero as we know \emph{a priori} that these countries have low or medium levels of malaria transmission.
-The prevalence only intercept was given a wide, zero-mean prior, $b_0 \sim \operatorname{Norm}(0, 4)$. % check
-Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
-Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of -3, each covariate is able to predict prevalences between 0.004 and 0.27. 
-This prior encodes our desire to regularise our model and and belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularise our model.
-This regularisation is particularly important given the small number of observations in Senegal (n = 46) and Madagascar (n = 110).
-
-The models were implemented and fitted in R \cite{R} using Template Model Builder \cite{TMB} which allows a Laplace approximation of the posterior to be calculated.
-
 \subsection*{Prevalence Gaussian process covariate model}
@@
 This covariate is created by fitting a Gaussian random field to the prevalence survey data.
-For each country we fitted a binomial likelihood, hierarchical Gaussian random field with the same hyperpriors as above.
+For each country we fitted a binomial likelihood, hierarchical Gaussian random field with the same hyperpriors for $\rho$ and $\sigma_u$ as above.
 These models were fitted using R-INLA \cite{INLA}.
-To be in the correct scale for the dissagregation model, the inverse logit of the predicted Gaussian field (i.e. the liver predictor of the model) was used for the additional covariate.
+To be in the correct scale for the dissagregation model, the inverse logit of the predicted Gaussian field (i.e. the linear predictor of the model) was used as the additional covariate.
 
@@
 The final model is a joint-likelihood model with separate likelihoods for prevalence point surveys and polygon incidence data.
-The polygon data are assigned a Poisson likelihood as before but the prevalence point-survey data, $z_b$, is given a binomial likelihood
+The polygon data are assigned a Poisson likelihood as before but the point-survey data, with positive cases $z_b$, is given a binomial likelihood
 
@@
 where $p_b$ is the estimated prevalence and $n_b$ is the observed survey sample size. 
+As this model has both prevalence and incidence data we add a parameter $\alpha$ that modifies the relationship between the two.
+$$i_b = \mathrm{PrevInc}(p_b).$$
 The only further additions to the baseline model are in the linear predictor which becomes
@@
 The iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all point surveys within polygon $j$ being in the same group as polygon $j$.
-Finally, the second iid random effect, $w_i \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
+The second iid random effect, $w_i \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
 This effect modelled extra-binomial sampling noise.
@@
 
+Given that the PrevInc relationship is fitted to the best available data, we have fairly strong \emph{a priori} confidence in it.
+Therefore, our prior belief is that $\exp(\alpha)$ is close to one (i.e.\thinspace the relationship remains unchanged) and therefore that $\alpha$ is close to zero.
+We set our prior that $\alpha \sim \operatorname{Norm}(0, 0.001)$.
+
 \subsection*{Experiments}
 
-To compare the three models we used three cross-validation schemes. 
+To compare the three models we used two cross-validation schemes. 
 In the first (random), the incidence data was split into ten cross-validation folds while all the prevalence data was used in each case.
 %This cross-validation scheme directly addresses the question of whethe
-In the second validation scheme (spatial a), the incidence data was split into spatial cross-validation folds, using k means clustering on polygon centroids, while again all prevalence points were used in all folds.
+In the second validation scheme , the incidence data was split into spatial cross-validation folds, using k means clustering on polygon centroids, while again all prevalence points were used in all folds.
 The number of folds was seven for Indonesia, five for Senegal and three for Madagascar due to their differing sizes and epidemiological settings.
@@
 This situation is particularly common in continental scale models where some countries will have large DHS style surveys but little incidence data.
-In the final scheme (spatial b) the data is again split spatially but the prevalence surveys from the hold-out areas are also witheld.
-This scheme is testing the models' ability to predict into new areas with little information from the spatial random field.
-It is therefore testing how well the models learn the parameters that relate the environment to malaria risk.
 
 We considered the ability to predict polygon incidence correctly our main objective and our performance metric was mean absolute error (MAE).
-As the models are being fitted on data on difference scales we found that observations and predictions were sometimes correlated but strongly displaced from the one-one line and therefore correlation metrics were misleading.
+As the models are being fitted on data on difference scales we found that observations and predictions were sometimes correlated but shifted from the one-one line (i.e.
+biased) and therefore correlation metrics were misleading.
 % Why not correlation

### 2019-07-08 ms.tex
Minor fig edits.

@@
 \caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
+The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
 The values plotted for areas with no polygon data are the means across all cross-validation folds.
@@
 \caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
+The incidence (log10) data, predicted log10 incidence from the prevalence GP model for spatially sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
+}
+\label{predobsmapsen}
+\end{figure}
+
+\begin{figure}
+% to be removed before submission
+\includegraphics[width = 1.1\textwidth]{figures/mdg_both_cv12_preds.png}
+\caption{{\bf Input incidence data and predicted incidence maps. } 
+The incidence (log10) data, predicted log10 incidence from the prevalence GP model for spatially sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
 }

### 2019-07-09 ms.tex
Fix references and start writing results and discussion.

@@
 However using polygon incidence data to estimate malaria risk for high resolution maps presents several noteworthy modelling difficulties. 
-Firstly, especially when modelling at continental scales \cite{lancet}, there are often some areas with better coverage of prevalence surveys than polygon incidence data.
+Firstly, especially when modelling at continental scales \cite{weiss2019mapping, battle2019mapping}, there are often some areas with better coverage of prevalence surveys than polygon incidence data.
 %Disaggregation models aim to estimate high-resolution maps from aggregated data and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
 Furthermore, the aggregation of cases over space means that it may be difficult to learn relationships between malaria risk and the environment from these data, especially if the case counts are aggregated over a large or heterogenous area.
-Finally, estimates of both prevalence and incidence metrics are useful for policy makers \cite{cohen2017mapping} but typically models are fitted to observations of one metric and then a secondary model is used to convert to the other \emph{post hoc} \cite{battlelancet, bhatt2015}.
+Finally, estimates of both prevalence and incidence metrics are useful for policy makers \cite{cohen2017mapping} but typically models are fitted to observations of one metric and then a secondary model is used to convert to the other \emph{post hoc} \cite{battle2019mapping, bhatt2015effect}.
 Models that combine observations of incidence and prevalence have the potential to provide better estimates than the \emph{post hoc} conversion and could also learn the relationship between different metrics at the same time as making spatial estimates.
@@
 
-The polygon incidence data were collated from various government reports and adjusted to a standard metric using methods defined in \cite{cibulskis2011worldwide, weiss2019}.
+The polygon incidence data were collated from various government reports and adjusted to a standard metric using methods defined in \cite{cibulskis2011worldwide, weiss2019mapping}.
 These adjustments account for underreporting of clinical cases due to lack of treatment seeking, missed case reports, and cases that sought medical attention outside the public health systems \cite{battle2016treatment}.
@@
 For each year, national population estimates from the UN were raked over the interpolated population surfaces.
-Finally a temperature suitability mask was used to created rasters of population at risk \cite{}. % todo
 
@@
 
-We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres at the equator that included land surface temperature annual mean and standard deviation \cite{LST}, enhanced vegetation index \cite{TCB}, mosquito temperature suitability index \cite{weiss2014air}, elevation \cite{SRTMElev}, tassel cap brightness \cite{TCB}, tassel cap wetness \cite{TCB}, accessibility to cities \cite{weiss2018global}, night lights \cite{} and proportion of urban land cover \cite{}.
+We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres at the equator that included land surface temperature annual mean and standard deviation \cite{LST}, enhanced vegetation index \cite{TCB}, mosquito temperature suitability index \cite{weiss2014air}, elevation \cite{SRTMElev}, tassel cap brightness \cite{TCB}, tassel cap wetness \cite{TCB}, accessibility to cities \cite{weiss2018global}, night lights \cite{elvidge2017viirs} and proportion of urban land cover \cite{GUF}.
 % change to table
@@
 
-Under the random cross-validation scheme, the joint model performed best in Indonesia and Madagascar while the polygon only model performed best in Senegal (Table \ref{table1}).
+Under the random cross-validation scheme, the prevalence GP model performed best in Senegal and Madagascar while the joint model performed best in Indonesia (Table \ref{table1}).
 The differences were relatively small in all three countries.
@@
 
-Under the spatial a cross-validation scheme, the polygon only model performed best in Indonesia and Senegal while the joint model performed best in Madagascar (Table \ref{table1}).
+Under the spatial a cross-validation scheme, the polygon only model and prevalence GP models performed equal best in Indonesia, the prevalence GP performaced best in Senegal while the joint model performed best in Madagascar (Table \ref{table1}).
 In contrast to the random cross-validation results, the differences between models is quite strong.
@@
 In Indonesia it can be seen the the joint model is more strongly biased at low incidence values with many data points being overpredicted.
-In Senegal the predictions from the joint model do not appear biased but are often far from the observed value.
 However, the joint model clearly performs better in Madagascar with the polygon only model particularly struggling to predict high incidence observations correctly.
-
-% spatial b
-
-Under the spatial b cross-validation scheme, in which the prevalence data are spatially withheld, the polygon model again performs the best in Indonesia and Senegal while the joint model performs best in Madagascar (Table \ref{table1}).
-The bias in the low incidence observations in Indonesia is no longer present (Figure \ref{spatial1predobspolyfacet}).
-In Indonesia and Senegal the joint model performs worse in the spatial a cross-validation than in the spatial b cross-validation scheme.
-Given that more data is being witheld in spatial b this implies that the bias caused by the prevalence points is so severe that models perform worse with this spatial information than with just information from the covariates.
 
@@
 A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (per 1,000).
-Results from the standard downscaling model are shown in blue and the combined model is shown in green.
+Results from the standard downscaling model are shown in red, the prevalence GP model is shown in green while the joint model is shown in blue.
 }
@@
 
-The polygon-only model and the joint model seem to be fairly well calibrated (Table~\ref{table3}).
-The proportion of out-of-sample incidence datapoints being within their 80\% credible intervals ranged between 0.54 and 0.9.
+All models seem to be fairly well calibrated (Table~\ref{table3}).
+The proportion of out-of-sample incidence datapoints being within their 80\% credible intervals ranged between 0.51 and 0.88.
 However, in most cases coverage was between 0.7 and 0.8 implying the models were a little overconfident in their predictions.
@@
 % Overall
+
+Overall, including the spatial information from prevalence surveys yields predictions that are as good or better than the baseline model in all six experiments (three countries and two cross-validation schemes).
+The prevalence GP model was as good or better than baseline in five out of six experiments.
+In contrast, the joint model was only better than baseline in three out of six experiments.
 
@@
 We have compared the predictive performance of a polygon-only model and a model that jointly learns from polygon incidence data and prevalence point-surveys.
+Overal the prevalence GP model appears to peform best.
+The joint model does sometimes perform best but also performs worse than baseline half of the time.
 
@@
 However, this model is imperfect in that it is calibrated with a relatively small amount of matched prevalence and incidence data.
-Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality and age-structure are not constant \cite{cameron2015defining, battle2015defining,reiner2015seasonality}.
+Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality and age-structure are not constant \cite{cameron2015defining, battle2015defining, reiner2015seasonality}.
 In using a joint model we are accepting these failings in the hope that the benefits of including additional data are stronger than the costs of using mismatched data.
@@
 Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \cite{law2018variational}.
-These are computational expensive without variational Bayes or other approximations \cite{law2018variational,  randomFourier} which can be difficult to derive.
+These are computational expensive without variational Bayes or other approximations \cite{law2018variational,  ton2018spatial} which can be difficult to derive.
 Again these models need a lot of data and careful regularisation for good predictive performance.

### 2019-07-12 ms.tex
Edit discussion.

@@
 $$z_b \sim \operatorname{Binom}(p_b, n_b) $$
-
 where $p_b$ is the estimated prevalence and $n_b$ is the observed survey sample size. 
 As this model has both prevalence and incidence data we add a parameter $\alpha$ that modifies the relationship between the two.
-$$i_b = \mathrm{PrevInc}(p_b).$$
+$$i_b = \exp(\alpha)\mathrm{PrevInc}(p_b).$$
+
 The only further additions to the baseline model are in the linear predictor which becomes
@@
 $$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) + w_i(\sigma_w).$$
-
 As well as the global intercept, $\beta_0$, this model has a prevalence survey only intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point survey is being considered.
@@
 Results from the standard downscaling model are shown in red, the prevalence GP model is shown in green while the joint model is shown in blue.
+The one-one line is shown with a black line and a simple linear regression through the points is shown by a coloured line.
 }
@@
 Overal the prevalence GP model appears to peform best.
-The joint model does sometimes perform best but also performs worse than baseline half of the time.
+While the joint model sometimes performs best it also performs worse than baseline half of the time.
+Therefore, fitting a spatial Gaussian process to prevalence points and including these predictions seems to be a more reliable way of using spatial information from prevalence points.
 
@@
 
-There are two main reasons why a model fitted jointly on prevalence point-surveys and polygon incidence data may perform worse than a polygon-only mode.
-Firstly, the data are on difference scales.
+A full joint model using both prevalence surveys and incidence data is gaining quite a large number of additional degrees of freedom compared to the baseline model and compared to the model that creates a new covariate from prevalence surveys.
+Therefore it is worth considering why the performance of this model was generally less good than the simpler prevalence GP model that did not benefit from the additional degrees of freedom.
+There are two main reasons why a model fitted jointly on prevalence point-surveys and polygon incidence data may perform worse than a model without that does not prevalence surveys as response data.
+Firstly, the data are on different scales.
 Here we have used a previously fitted model \cite{cameron2015defining} in order to be able to fit the joint model.
 However, this model is imperfect in that it is calibrated with a relatively small amount of matched prevalence and incidence data.
+Although we have added the parameter $\alpha$ that scales this relationship, it is a very simple scaling.
 Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality and age-structure are not constant \cite{cameron2015defining, battle2015defining, reiner2015seasonality}.
@@
 This could be by estimating the parameters of the polynomial jointly with the rest of the model.
-Informative priors based on the original model should be used to regularise this joint fit both to prevent unbelievable inferences but also because if the relationship is too flexible, the information from the prevalence data might not be used by the incidence level model.
+Informative priors based on the original model should be used to regularise this joint fit both to prevent unbelievable inferences but also because if the relationship is too flexible, the information from the prevalence data might not inform the predictions of incidence.
 This is particularly true for even more flexible model forms that could be used such as a spline or a Gaussian process on the relationship between prevalence and incidence.
 
-For the model to handle noisy or biased prevalence point-surveys, the modeller can control the iid random effect on the point-surveys, $w_i$. 
+For the model to handle noisy or biased prevalence point-surveys, the modeller can control the iid random effect on the point-surveys, $w_i$ and the prevalence-only intercept $\beta_p$. 
 Here we have tried to maximise the influence of the prevalence data by setting the prior based on the belief that the random effect should only explain extra-binomial variation that is impossible to explain with the covariates (i.e.
@@
 
-However, fitting a full spatio-temporal model would be a suitable way to combine data from different periods but would be computationally more expensive \cite{bhatt2015effect, taylor2017continuous}.
-This is an avenue of work that should be pursued.
-Furthermore, it has been clearly established that simple linear combinations of environmental covariates cannot fully explain malaria risk \cite{bhatt2017improved}.
+Here we have used purely linear covariates.
+It has been clearly established that simple linear combinations of environmental covariates cannot fully explain malaria risk \cite{bhatt2017improved}.
 A number of methods could be used to include non-linear effects of covariates and interactions into the model.
-Firstly, as in \cite{bhatt2017improved}, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model.
+Firstly, as in \cite{bhatt2017improved}, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model \cite{lucas2019model}.
 This approach is feasible but does not allow any information from the polygons to inform non-linear relationships.
-To directly model non-linear effects in the full model could be achieved by including simple non-linear functions such as splines \cite{sissoko2017temporal, sewe2017using, hundessa2018projecting}, though the increased model complexity would require more data than was used in Senegal and Madagascar in this study.
+Directly modelling non-linear effects in the full model could be achieved by including simple non-linear functions such as splines \cite{sissoko2017temporal, sewe2017using, hundessa2018projecting}, though the increased model complexity would require more data than was used in Senegal and Madagascar in this study.
 Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \cite{law2018variational}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Overall, we have shown that including spatial information from prevalence surveys generally improves the predictive performance of disaggregation regression of aggregated incidence data.
+However, we found that the more complex joint model was unreliable in its predictive performance.
+In contrast, summarising the spatial information from the prevalence surveys by fitting a spatial Gaussian process model and using predictions from this model as a new covariate nearly always improved predictive performance.
+As disaggregation regression becomes more widely used \cite{weiss2019mapping, battle2019mapping}, methods such as these to improve their performance are particularly needed
 

### 2019-07-12 ms.tex
Move figures around.

@@
 
+\begin{figure}
+% to be removed before submission
+\includegraphics[width = 0.6\textwidth]{figures/sen_both_cv12_preds.png}
+\caption{{\bf Input incidence data and predicted incidence maps. } 
+The incidence (log10) data, predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
+}
+\label{predobsmapsen}
+\end{figure}
+
+\begin{figure}
+% to be removed before submission
+\includegraphics[width = 1.1\textwidth]{figures/mdg_both_cv12_preds.png}
+\caption{{\bf Input incidence data and predicted incidence maps. } 
+The incidence (log10) data, predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
+}
+\label{predobsmapmdg}
+\end{figure}
+
 \subsection*{Prevalence survey data}
@@
 falciparum} only cases.
+The polygon incidence data for Senegal and Madagascar can be seen in Figures~\ref{predobsmapsen}A and \ref{predobsmapmdg}A)
 
@@
 
-This model is the same as the baseline disaggregation model except that it has one extra covariate.
+This model (henceforth the prevalence GP model) is the same as the baseline disaggregation model except that it has one extra covariate.
 This covariate is created by fitting a Gaussian random field to the prevalence survey data.
@@
 However, the joint model clearly performs better in Madagascar with the polygon only model particularly struggling to predict high incidence observations correctly.
+Out-of-sample predictions, under spatial cross validation, from the prevalence GP model and full joint model can be seen in Figures~\ref{predobsmapsen} and \ref{predobsmapmdg}.
 
@@
 \begin{flushleft}
-
+The proportion of held out data points that fall within their 80\% credible intervals. 
+Cases where this is below 0.7 are highlighted in bold.
 \end{flushleft}
@@
 
-\begin{figure}
+%\begin{figure}
 % to be removed before submission
-\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_preds.png}
-\caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
+%\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_preds.png}
+%\caption{{\bf Input incidence data and predicted incidence maps. } 
+%The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially sampled out-of-sample polygons (middle) and predicted log10 %incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia.
 The values plotted for areas with no polygon data are the means across all cross-validation folds.
-}
-\label{predobsmapidn}
-\end{figure}
-
-\begin{figure}
-% to be removed before submission
-\includegraphics[width = 0.7\textwidth]{figures/sen_both_cv12_preds.png}
-\caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data, predicted log10 incidence from the prevalence GP model for spatially sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
-}
-\label{predobsmapsen}
-\end{figure}
-
-\begin{figure}
-% to be removed before submission
-\includegraphics[width = 1.1\textwidth]{figures/mdg_both_cv12_preds.png}
-\caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data, predicted log10 incidence from the prevalence GP model for spatially sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
-}
-\label{predobsmapsen}
-\end{figure}
+%}
+%\label{predobsmapidn}
+%\end{figure}
 

### 2019-07-13 ms.tex
Another full round of edits.

@@
 {\Large
-\textbf\newline{Joint modelling of aggregated incidence data and point prevalence surveys for malaria mapping} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Mapping malaria by sharing spatial information between incidence and prevalence datasets} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 Tim C.D.
-Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Rosalind Howes \textsuperscript{1}, Katherine E.
-Battle \textsuperscript{1}, Penelope Hancock \textsuperscript{1}, Andre Python \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Daniel J.
+Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha\textsuperscript{1}, Rosalind Howes\textsuperscript{1}, Katherine E.
+Battle\textsuperscript{1}, Penelope Hancock\textsuperscript{1}, Andre Python\textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Daniel J.
 Weiss\textsuperscript{1}
@@
 We find that the simple model generally performs better than a baseline disaggregation model while the joint model sometimes performs better than baseline but often worse.
-Our results demonstrate that a simple method can be used to combine spatial information from prevalence point-surveys and polygon incdience data and that more generally, combining these types of data improves estimates of malaria incidence.
+Our results demonstrate that a simple method can be used to combine spatial information from prevalence point-surveys and polygon incidence data and that more generally, combining these types of data improves estimates of malaria incidence.
 
@@
 
-Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level incidence \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
-However using polygon incidence data to estimate malaria risk for high resolution maps presents several noteworthy modelling difficulties. 
-Firstly, especially when modelling at continental scales \cite{weiss2019mapping, battle2019mapping}, there are often some areas with better coverage of prevalence surveys than polygon incidence data.
+Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level, routine surveillance records of incidence \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
+However using polygon-level incidence data to estimate malaria risk for high resolution maps presents at least three noteworthy modelling difficulties. 
+(1) There are often some areas with better coverage of prevalence surveys than polygon incidence data.
+This is particularly true when modelling at continental scales \cite{weiss2019mapping, battle2019mapping}.
 %Disaggregation models aim to estimate high-resolution maps from aggregated data and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
-Furthermore, the aggregation of cases over space means that it may be difficult to learn relationships between malaria risk and the environment from these data, especially if the case counts are aggregated over a large or heterogenous area.
-Finally, estimates of both prevalence and incidence metrics are useful for policy makers \cite{cohen2017mapping} but typically models are fitted to observations of one metric and then a secondary model is used to convert to the other \emph{post hoc} \cite{battle2019mapping, bhatt2015effect}.
-Models that combine observations of incidence and prevalence have the potential to provide better estimates than the \emph{post hoc} conversion and could also learn the relationship between different metrics at the same time as making spatial estimates.
+(2) The aggregation of cases over space means that it may be difficult to learn relationships between malaria risk and the environment from aggregated incidence data, especially if the case counts are aggregated over a large or heterogenous area.
+(3) Finally, estimates of both prevalence and incidence metrics are useful for policy makers \cite{cohen2017mapping} but typically models are fitted to observations of one metric and then a secondary model is used to convert to the other \emph{post hoc} \cite{battle2019mapping, bhatt2015effect}.
+
+There are two broad ways that spatial information from prevalence surveys could be included in a dissaggregation regression model of incidence.
+Firstly, the spatial information from prevalence surveys could be summarised using a seperate model and then included as a covariate in the disaggregation model.
+If the model used to summarise the prevalence surveys is explicitely spatial, this approach would make the spatial information in the prevalence data available to be used by the disaggregation model, therefore solving issue (1) above.
+However, this approach does not provide additional degrees of freedom in order to more accurately learn relationships between malaria risk and the environment and therefore does not solve issue (2).
+Furthermore, it does not allow joint predictions of incidence and prevalence from a single model and so does not solve issue (3).
+This broad approach of summarising the information in a different data set using a separate model has previously been used in a number of contexts such as including information on animal hosts \cite{shearer2016estimating} or summarising temperature suitability of malaria parasites \cite{weiss2014air} and using this in models of malaria prevalence \cite{bhatt2015effect, weiss2019mapping}.
+However, previous uses have not typically summarised the spatial component of the secondary response data.
+
+Fully combining observations of incidence and prevalence in a joint model has the potential to alleviate all three of the above issues.
+As the prevalence surveys are directly used as response data, issue (1) is solved.
+Similar, as the additional data are being used as response data, they are providing additional degrees of freedom with which to learn relationships between malaria risk and the environment, therefore solving issue (2).
+Finally, a joint model that includes prevalence as a latent variable allows predictions of prevalence and incidence to be made jointly to provide better estimates than a \emph{post hoc} conversion.
+Such a model could also learn the relationship between different metrics at the same time as making spatial estimates.
+Therefore, a full joint model has the potential to solve issue (3) as well.
+
 One major barrier to a joint modelling approach, however, is that these two data types measure metrics disease transmission on different scales.
-Point surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ that quantify parasite rate at a single moment.
-In contrast, routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$ as it spans a period of time (e.g., a year) over which individuals can have multiple malaria infections.
+Point surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ that quantify parasite rate during a short period of time.
+In contrast, routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$ over a period of time (e.g., a year) during which individuals can have multiple malaria infections.
 %One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015defining}.
@@
 
-Here we compare two methods for using spatial information from prevalence surveys to inform a disaggregation model of fitted to polygon incidence data.
+Here we compare two methods for using spatial information from prevalence surveys to inform a disaggregation model fitted to polygon incidence data of \emph{Plasmodium falciparum}  malaria.
 The first model fits a Gaussian process to prevalence point surveys then uses predictions from this model as a covariate in the disaggregation model.
-Secondly, we formulate a joint model that combines polygon incidence data and prevalence point-surveys of \emph{Plasmodium falciparum} using seperate likelihoods for both data types.
+Secondly, we formulate a joint model that combines polygon incidence data and prevalence point-surveys using seperate likelihoods for both data types.
 We relate the differing malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining} which is then adjusted as part of the model fitting process.
@@
 We selected Indonesia, Senegal and Madagascar as case examples as they all have abundant subnational surveillance data and country wide surveys from approximately the same period.
-To minimise temporal effects we selected five years of prevalence point-survey data and one year of polygon incidence data for each country.
-For Indonesia we selected polygon incidence data from 2012 that covers 380 regions, and prevalence data from 2010 to 2014 that consists of todo surveys, accounting for todo individuals.
-For Senegal we selected 2015 for polygon incidence data (46 regions) and 2013 to 2017 for prevalence data (todo surveys, todo).
+To minimise temporal effects we selected one year of polygon incidence data and the surrounding five years of prevalence point-survey data for each country.
+For Indonesia we selected polygon incidence data from 2012 that covers 380 regions, and prevalence data from 2010 to 2014 that consists of todo surveys, representing todo individuals.
+For Senegal we selected 2015 for polygon incidence data (46 regions) and 2013 to 2017 for prevalence data (todo surveys, todo individuals).
 Finally, for Madagascar we selected 2013 for polygon incidence (110 regions) and 2011 to 2015 for prevalence (todo surveys, todo individuals) data.
@@
 \includegraphics[width = 0.6\textwidth]{figures/sen_both_cv12_preds.png}
-\caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data, predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
+\caption{{\bf Incidence data and predicted incidence maps. } 
+The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
 }
@@
 \caption{{\bf Input incidence data and predicted incidence maps. } 
-The incidence (log10) data, predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
+The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (right) for Senegal.
 }
@@
 falciparum} only cases.
-The polygon incidence data for Senegal and Madagascar can be seen in Figures~\ref{predobsmapsen}A and \ref{predobsmapmdg}A)
+These adjustments are uniform across each country.
+The polygon incidence data for Senegal and Madagascar can be seen in Figures~\ref{predobsmapsen}A and \ref{predobsmapmdg}A).
 
@@
 % change to table
-Some covariates were log-transformed to remove skewness or removed due to multicollineariy with other predictor variables using the threshold of 0.8.
+Some covariates were log-transformed to remove skewness or removed due to multicollinearity with other predictor variables using the threshold of 0.8.
 % think we decided this on indonesia data only.
@@
 
-Values at the aggregate, polygon level are given the subscript $a$ while pixel or point level variables are indexed with $b$.
-The polygon incidence case count data, $y_j$ is given a Poisson likelihood
+Values at the aggregated, polygon level are given the subscript $a$ while pixel or point level variables are indexed with $b$.
+The polygon incidence case count data, $y_a$ is given a Poisson likelihood
 
@@
 
-where $i_a$ is the estimated polygon incidence rate and $\mathrm{pop_a}$ is the observed polygon population-at-risk.
+where $i_a$ is the estimated polygon incidence rate and $\mathrm{pop_a}$ is the (assumed to be) known polygon population-at-risk.
 
-Incidence rate is linked to latent pixel-level incidence, $i_b$, prevalence $p_b$ and to the predictor variables by the following system of equations.
+Incidence rate is linked to latent pixel-level incidence ($i_b$), prevalence ($p_b$) and predictor variables by the following system of equations.
 
@@
 The linear predictor is composed of an intercept, $b_0$, covariates, $X$, and a vector of regression coefficients $\beta$.
-We also include a spatial, Gaussian random field, $u(s, \rho, \sigma_u)$ and a polygon-level iid random effect, $ v_j(\sigma_v)$.
-$$\eta_b = \beta_0 + \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) $$
+We also include a spatial, Gaussian random field, $u(s, \rho, \sigma_u)$ and a polygon-level iid random effect, $ v_a(\sigma_v)$.
+$$\eta_b = \beta_0 + \beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) $$
 The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
-The iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $j$ being grouped together.
+The iid random effect, $v_a \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $j$ being grouped together.
 This random effect modelled both missing covariates and extra-Poisson sampling error.
 
-Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho, \sigma_u$, $\sigma_v$ and $\sigma_w$.
+Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho, \sigma_u$ and $\sigma_v$.
 The intercept was given a wide prior, $b_0 \sim \operatorname{Norm}(-2, 4)$ with a mean less than zero as we know \emph{a priori} that these countries have low or medium levels of malaria transmission.
 We set independant, regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
-Given the standardised covariates and an intercept of -3, a regression coefficient from the 95\% interquartile range of this distribution, each covariate would be able to predict prevalences between 0.004 and 0.27.
+Given the standardised covariates, an intercept of -3 and a regression coefficient from the 95\% interquartile range of this distribution, each covariate would be able to predict prevalences between 0.004 and 0.27.
 This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularise the model.
@@
 The final model is a joint-likelihood model with separate likelihoods for prevalence point surveys and polygon incidence data.
-The polygon data are assigned a Poisson likelihood as before but the point-survey data, with positive cases $z_b$, is given a binomial likelihood
+The polygon data are assigned a Poisson likelihood as before.
+Additionally, the point-survey data, with positive cases $z_b$, are given a binomial likelihood
 
@@
 
-$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \beta X  + u(s, \rho, \sigma_u) + v_j(\sigma_v) + w_i(\sigma_w).$$
+$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) + w_b\sigma_w).$$
 As well as the global intercept, $\beta_0$, this model has a prevalence survey only intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point survey is being considered.
-The iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all point surveys within polygon $j$ being in the same group as polygon $j$.
-The second iid random effect, $w_i \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
+The iid random effect, $v_a \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point surveys within polygon $a$ being in the same group as polygon $a$.
+The second iid random effect, $w_b \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
 This effect modelled extra-binomial sampling noise.
@@
 Therefore, our prior belief is that $\exp(\alpha)$ is close to one (i.e.\thinspace the relationship remains unchanged) and therefore that $\alpha$ is close to zero.
-We set our prior that $\alpha \sim \operatorname{Norm}(0, 0.001)$.
+We set our prior as $\alpha \sim \operatorname{Norm}(0, 0.001)$.
 
@@
 This scheme is specifically testing whether the joint model can improve predictions by increasing geographic data coverage.
-This situation is particularly common in continental scale models where some countries will have large DHS style surveys but little incidence data.
+%This situation is particularly common in continental scale models where some countries will have large DHS style surveys but little incidence data.
 
 We considered the ability to predict polygon incidence correctly our main objective and our performance metric was mean absolute error (MAE).
-As the models are being fitted on data on difference scales we found that observations and predictions were sometimes correlated but shifted from the one-one line (i.e.
+As the models are being fitted on data on different scales we found that observations and predictions were sometimes correlated but shifted from the one-one line (i.e.
 biased) and therefore correlation metrics were misleading.
@@
 
-Under the spatial a cross-validation scheme, the polygon only model and prevalence GP models performed equal best in Indonesia, the prevalence GP performaced best in Senegal while the joint model performed best in Madagascar (Table \ref{table1}).
+Under the spatial cross-validation scheme, the baseline model and prevalence GP models performed equal best in Indonesia, the prevalence GP performaced best in Senegal while the joint model performed best in Madagascar (Table \ref{table1}).
 In contrast to the random cross-validation results, the differences between models is quite strong.
@@
 In Indonesia it can be seen the the joint model is more strongly biased at low incidence values with many data points being overpredicted.
-However, the joint model clearly performs better in Madagascar with the polygon only model particularly struggling to predict high incidence observations correctly.
+However, the joint model clearly performs better in Madagascar with the polygon only model unable to predict high incidence observations accurately.
 Out-of-sample predictions, under spatial cross validation, from the prevalence GP model and full joint model can be seen in Figures~\ref{predobsmapsen} and \ref{predobsmapmdg}.
@@
 \caption{{\bf Observed-predicted plots for random cross-validation experiments.}
-A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (per 1,000).
+A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (cases per 1,000).
 Results from the standard downscaling model are shown in red, the prevalence GP model is shown in green while the joint model is shown in blue.
@@
 \caption{{\bf Observed-predicted plots for spatial a cross-validation experiments where all prevalence points are used in model fitting.}
-A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (per 1,000).
+A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (cases per 1,000).
 Results from the standard downscaling model are shown in red, the prevalence GP model is shown in green while the joint model is shown in blue.
@@
 
-A full joint model using both prevalence surveys and incidence data is gaining quite a large number of additional degrees of freedom compared to the baseline model and compared to the model that creates a new covariate from prevalence surveys.
+A full joint model using both prevalence surveys and incidence data gains quite a large number of additional degrees of freedom compared to the baseline model and compared to the model that creates a new covariate from prevalence surveys.
 Therefore it is worth considering why the performance of this model was generally less good than the simpler prevalence GP model that did not benefit from the additional degrees of freedom.
-There are two main reasons why a model fitted jointly on prevalence point-surveys and polygon incidence data may perform worse than a model without that does not prevalence surveys as response data.
+There are two main reasons why a model fitted jointly on prevalence point-surveys and polygon incidence data may perform worse than a model that does not use prevalence surveys as additional response data.
 Firstly, the data are on different scales.
@@
 This could be by estimating the parameters of the polynomial jointly with the rest of the model.
-Informative priors based on the original model should be used to regularise this joint fit both to prevent unbelievable inferences but also because if the relationship is too flexible, the information from the prevalence data might not inform the predictions of incidence.
+Informative priors based on the original model should be used to regularise this joint fit both to prevent unbelievable inferences but also because if the relationship is too flexible, the information from the prevalence data might not contribute to learning the regression parameters and spatial random field.
 This is particularly true for even more flexible model forms that could be used such as a spline or a Gaussian process on the relationship between prevalence and incidence.
 
-For the model to handle noisy or biased prevalence point-surveys, the modeller can control the iid random effect on the point-surveys, $w_i$ and the prevalence-only intercept $\beta_p$. 
+For the model to handle noisy or biased prevalence point-surveys, the modeller can control the iid random effect on the point-surveys, $w_b$ and the prevalence-only intercept $\beta_p$. 
 Here we have tried to maximise the influence of the prevalence data by setting the prior based on the belief that the random effect should only explain extra-binomial variation that is impossible to explain with the covariates (i.e.

### 2019-07-14 ms.tex
Switch to r stat soc style.

@@
-% Template for PLoS
-% Version 3.5 March 2018
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended 
-% to minimize problems and delays during our production 
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Once your paper is accepted for publication, 
-% PLEASE REMOVE ALL TRACKED CHANGES in this file 
-% and leave only the final text of your manuscript. 
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that 
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file. 
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig" instead of "Figure".
-% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
-%
-% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column. 
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
+\documentclass{statsoc}
 
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+%\usepackage{hyperref}
 
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
+\usepackage[a4paper]{geometry}
+\usepackage{graphicx}
+\usepackage[textwidth=8em,textsize=small]{todonotes}
+\usepackage{amsmath}
 
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
+\usepackage[authoryear]{natbib}
 
-% Use Unicode characters when possible
-\usepackage[utf8x]{inputenc}
+\title[Mapping malaria by sharing spatial information]{Mapping malaria in pre-elimination settings by sharing spatial information between incidence and prevalence datasets}
+\author[Tim C.D. Lucas {\it et al.}]{Tim C.D. Lucas}
+\address{Big Data Institute,
+Oxford,
+UK.}
+\email{timcdlucas@gmail.com}
+\author{Anita Nandi}
+\address{Big Data Institute,
+Oxford,
+UK.}
 
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
+% Title must be 250 characters or less.
 
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% color can be used to apply background shading to table cells only
-\usepackage[table]{xcolor}
-
-% array package and thick rules for tables
-\usepackage{array}
-
-% multirow for multiple row tables. 
-\usepackage{multirow}
-
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-
-% create \thickcline for thick horizontal lines of variable length
-\newlength\savedwidth
-\newcommand\thickcline[1]{%
-  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-  \cline{#1}%
-  \noalign{\vskip\arrayrulewidth}%
-  \noalign{\global\arrayrulewidth\savedwidth}%
-}
-
-% \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-\hline
-\noalign{\global\arrayrulewidth\savedwidth}}
-
-% Remove comment for double spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-\renewcommand{\figurename}{Fig}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr,graphicx}
-\DeclareGraphicsExtensions{.pdf,.png}   
-\usepackage{epstopdf}
-%\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-%\setlength{\headheight}{27.023pt}
-%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\headrulewidth}{0pt}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\today}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-\usepackage{xr}
-\externaldocument{si}
-
-%% END MACROS SECTION
+%*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha\textsuperscript{1}, Rosalind Howes\textsuperscript{1}, Katherine E.
+Battle\textsuperscript{1}, Penelope Hancock\textsuperscript{1}, Andre Python\textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Daniel J.
+Weiss\textsuperscript{1}
 
 \begin{document}
-\vspace*{0.2in}
 
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{Mapping malaria by sharing spatial information between incidence and prevalence datasets} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Tim C.D.
-Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha\textsuperscript{1}, Rosalind Howes\textsuperscript{1}, Katherine E.
-Battle\textsuperscript{1}, Penelope Hancock\textsuperscript{1}, Andre Python\textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Daniel J.
-Weiss\textsuperscript{1}
-\\
-\bigskip
-\textbf{1} BDI, Oxford
-\\
-\bigskip
-
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-% 
-% Remove or comment out the author notes below if they aren't used.
-%
-
-% Current address notes
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* timcdlucas@gmail.com
-
-\end{flushleft}
 % Please keep the abstract below 300 words
-\section*{Abstract}
+\begin{abstract}
 As malaria incidence decreases and more countries move towards elimination, maps of malaria risk in low prevalence areas are becoming increasingly needed.
@@
 Our results demonstrate that a simple method can be used to combine spatial information from prevalence point-surveys and polygon incidence data and that more generally, combining these types of data improves estimates of malaria incidence.
+\end{abstract}
 
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-\section*{Author summary}
-Todo
-
-\linenumbers
+%\linenumbers
 
@@
 
-Global malaria incidence has decreased dramatically over the last 20 years \cite{abajobir2017global, bhatt2015effect}.
-This decrease has been accompanied by a strategic shift towards aiming for elimination in low incidence countries \cite{world2016world, newby2016path}.
-Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases \cite{sturrock2016mapping, cohen2017mapping}.
-However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \cite{gething2011new, bhatt2017improved, gething2012long, bhatt2015effect} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite{sturrock2016mapping, sturrock2014fine}.
+Global malaria incidence has decreased dramatically over the last 20 years \citep{abajobir2017global, bhatt2015effect}.
+This decrease has been accompanied by a strategic shift towards aiming for elimination in low incidence countries \citep{world2016world, newby2016path}.
+Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases \citep{sturrock2016mapping, cohen2017mapping}.
+However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \citep{gething2011new, bhatt2017improved, gething2012long, bhatt2015effect} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \citep{sturrock2016mapping, sturrock2014fine}.
 In low burden areas, very large sample sizes are needed before a prevalence survey is informative because so few individuals have parasitaemia that most sample points will have no cases.
-Routine surveillance data, of malaria case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
-This polygon incidence data can be more sensitive than prevalence point-surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
+Routine surveillance data, of malaria case counts, is becoming more widely available and of better quality \citep{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
+This polygon incidence data can be more sensitive than prevalence point-surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \citep{cibulskis2011worldwide}.
 
-%Despite major reductions in incidence over the last fifteen years, malaria still causes millions of deaths and loads of DALYs annually \cite{abajobir2017global}.
-%Elimination of malaria, country-by-county has become a central goal in the global malaria strategy \cite{world2016world}.
-%Elimination of malaria requires high resolution maps of malaria risk, in low prevalence areas in order to optimise interventions and minimise costs \cite{sturrock2016mapping}.
+%Despite major reductions in incidence over the last fifteen years, malaria still causes millions of deaths and loads of DALYs annually \citep{abajobir2017global}.
+%Elimination of malaria, country-by-county has become a central goal in the global malaria strategy \citep{world2016world}.
+%Elimination of malaria requires high resolution maps of malaria risk, in low prevalence areas in order to optimise interventions and minimise costs \citep{sturrock2016mapping}.
 
@@
 
-Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level, routine surveillance records of incidence \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
+Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level, routine surveillance records of incidence \citep{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
 However using polygon-level incidence data to estimate malaria risk for high resolution maps presents at least three noteworthy modelling difficulties. 
 (1) There are often some areas with better coverage of prevalence surveys than polygon incidence data.
-This is particularly true when modelling at continental scales \cite{weiss2019mapping, battle2019mapping}.
+This is particularly true when modelling at continental scales \citep{weiss2019mapping, battle2019mapping}.
 %Disaggregation models aim to estimate high-resolution maps from aggregated data and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
 (2) The aggregation of cases over space means that it may be difficult to learn relationships between malaria risk and the environment from aggregated incidence data, especially if the case counts are aggregated over a large or heterogenous area.
-(3) Finally, estimates of both prevalence and incidence metrics are useful for policy makers \cite{cohen2017mapping} but typically models are fitted to observations of one metric and then a secondary model is used to convert to the other \emph{post hoc} \cite{battle2019mapping, bhatt2015effect}.
+(3) Finally, estimates of both prevalence and incidence metrics are useful for policy makers \citep{cohen2017mapping} but typically models are fitted to observations of one metric and then a secondary model is used to convert to the other \emph{post hoc} \citep{battle2019mapping, bhatt2015effect}.
 
@@
 Firstly, the spatial information from prevalence surveys could be summarised using a seperate model and then included as a covariate in the disaggregation model.
-If the model used to summarise the prevalence surveys is explicitely spatial, this approach would make the spatial information in the prevalence data available to be used by the disaggregation model, therefore solving issue (1) above.
+If the model used to summarise the prevalence surveys is expliciteply spatial, this approach would make the spatial information in the prevalence data available to be used by the disaggregation model, therefore solving issue (1) above.
 However, this approach does not provide additional degrees of freedom in order to more accurately learn relationships between malaria risk and the environment and therefore does not solve issue (2).
 Furthermore, it does not allow joint predictions of incidence and prevalence from a single model and so does not solve issue (3).
-This broad approach of summarising the information in a different data set using a separate model has previously been used in a number of contexts such as including information on animal hosts \cite{shearer2016estimating} or summarising temperature suitability of malaria parasites \cite{weiss2014air} and using this in models of malaria prevalence \cite{bhatt2015effect, weiss2019mapping}.
+This broad approach of summarising the information in a different data set using a separate model has previously been used in a number of contexts such as including information on animal hosts \citep{shearer2016estimating} or summarising temperature suitability of malaria parasites \citep{weiss2014air} and using this in models of malaria prevalence \citep{bhatt2015effect, weiss2019mapping}.
 However, previous uses have not typically summarised the spatial component of the secondary response data.
@@
 In contrast, routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$ over a period of time (e.g., a year) during which individuals can have multiple malaria infections.
-%One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015defining}.
+%One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \citep{cameron2015defining}.
 
@@
 Secondly, we formulate a joint model that combines polygon incidence data and prevalence point-surveys using seperate likelihoods for both data types.
-We relate the differing malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining} which is then adjusted as part of the model fitting process.
-We then compare results from the two models with those made using a polygon-only, disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless}.
+We relate the differing malariometric measures by using a previously estimated relationship within the model \citep{cameron2015defining} which is then adjusted as part of the model fitting process.
+We then compare results from the two models with those made using a polygon-only, disaggregation model similar to previous models \citep{sturrock2014fine, wilson2017pointless}.
 Both models are fitted to data from Indonesia, Senegal and Madagascar to provide a set of case studies with disparate geographic settings and levels of malaria endemicity.
@@
 % to be removed before submission
-\includegraphics[width = 0.6\textwidth]{figures/sen_both_cv12_preds.png}
-\caption{{\bf Incidence data and predicted incidence maps. } 
+\makebox{\includegraphics[width = 0.6\textwidth]{figures/sen_both_cv12_preds.png}}
+\caption{\label{predobsmapsen}
+Incidence data and predicted incidence maps.
 The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
 }
-\label{predobsmapsen}
+
 \end{figure}
@@
 % to be removed before submission
-\includegraphics[width = 1.1\textwidth]{figures/mdg_both_cv12_preds.png}
-\caption{{\bf Input incidence data and predicted incidence maps. } 
+\makebox{\includegraphics[width = 1.1\textwidth]{figures/mdg_both_cv12_preds.png}}
+\caption{\label{predobsmapmdg}Input incidence data and predicted incidence maps.
 The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (right) for Senegal.
 }
-\label{predobsmapmdg}
+
 \end{figure}
@@
 
-The prevalence point-survey data were extracted from the Malaria Atlas Project prevalence survey database \cite{bhatt2015effect, guerra2007assembling, gething2011new, pfeffer2018ma}.
-As the prevalence point-surveys cover different age ranges they were standardised to an age-range of 2--10 using the model from \cite{smith2007standardizing}.
+The prevalence point-survey data were extracted from the Malaria Atlas Project prevalence survey database \citep{bhatt2015effect, guerra2007assembling, gething2011new, pfeffer2018ma}.
+As the prevalence point-surveys cover different age ranges they were standardised to an age-range of 2--10 using the model from \citep{smith2007standardizing}.
 The age standardisation model gives the surveys with zero positive cases a small positive prevalence.
@@
 
-The polygon incidence data were collated from various government reports and adjusted to a standard metric using methods defined in \cite{cibulskis2011worldwide, weiss2019mapping}.
-These adjustments account for underreporting of clinical cases due to lack of treatment seeking, missed case reports, and cases that sought medical attention outside the public health systems \cite{battle2016treatment}.
+The polygon incidence data were collated from various government reports and adjusted to a standard metric using methods defined in \citep{cibulskis2011worldwide, weiss2019mapping}.
+These adjustments account for underreporting of clinical cases due to lack of treatment seeking, missed case reports, and cases that sought medical attention outside the public health systems \citep{battle2016treatment}.
 Where species specific reports were given, these were used, and in reports that did not distinguish between species of \emph{Plasmodium} the national estimate of the ratio between \emph{P.
@@
 
-Raster surfaces of population for the years 2005, 2010 and 2015, were created using a hybrid of data from GPWv4 \cite{gpw4} and WorldPop \cite{tatem2017worldpop}, with the latter taking priority for those pixels where both had population data.
+Raster surfaces of population for the years 2005, 2010 and 2015, were created using a hybrid of data from GPWv4 \citep{gpw4} and WorldPop \citep{tatem2017worldpop}, with the latter taking priority for those pixels where both had population data.
 Yearly population rasters were created by linear interpolation of the surrounding five-yearly rasters.
@@
 
-We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres at the equator that included land surface temperature annual mean and standard deviation \cite{LST}, enhanced vegetation index \cite{TCB}, mosquito temperature suitability index \cite{weiss2014air}, elevation \cite{SRTMElev}, tassel cap brightness \cite{TCB}, tassel cap wetness \cite{TCB}, accessibility to cities \cite{weiss2018global}, night lights \cite{elvidge2017viirs} and proportion of urban land cover \cite{GUF}.
+We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres at the equator that included land surface temperature annual mean and standard deviation \citep{LST}, enhanced vegetation index \citep{TCB}, mosquito temperature suitability index \citep{weiss2014air}, elevation \citep{SRTMElev}, tassel cap brightness \citep{TCB}, tassel cap wetness \citep{TCB}, accessibility to cities \citep{weiss2018global}, night lights \citep{elvidge2017viirs} and proportion of urban land cover \citep{GUF}.
 % change to table
@@
 $$i_b = \mathrm{PrevInc}(p_b).$$
-Here $\mathrm{PrevInc}$ is a function from a previously fitted model \cite{cameron2015defining} 
+Here $\mathrm{PrevInc}$ is a function from a previously fitted model \citep{cameron2015defining} 
 $$\mathrm{PrevInc}: f\left(p_b\right) = 2.616p_b - 3.596{p_b}^2 + 1.594{p_b}^3.$$
@@
 
-We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
+We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \citep{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
 We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = 1$ and Madagascar $\zeta = 1$.
-We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \cite{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.
+We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \citep{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.
 
-We assigned $\sigma_v$ a penalised complexity prior \cite{simpson2017penalising} such that $P(\sigma_v > 0.05) = 0.0000001$
-This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for the case counts using the approach defined in \cite{cibulskis2011worldwide}.
+We assigned $\sigma_v$ a penalised complexity prior \citep{simpson2017penalising} such that $P(\sigma_v > 0.05) = 0.0000001$
+This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for the case counts using the approach defined in \citep{cibulskis2011worldwide}.
 We found that an iid effect with a standard deviation of 0.05 is able to account for the discrepancy between the assumed Poisson error and the independently derived error.
 
-The models were implemented and fitted in R \cite{R} using Template Model Builder \cite{TMB} which allows a Laplace approximation of the posterior to be calculated.
+The models were implemented and fitted in R \citep{R} using Template Model Builder \citep{TMB} which allows a Laplace approximation of the posterior to be calculated.
 The hyperparameters are fitted using empirical Bayes whereby the hyperparameters are learned from the data but are treated as point estimates rather than using the full posterior of the hyperparameters.
@@
 For each country we fitted a binomial likelihood, hierarchical Gaussian random field with the same hyperpriors for $\rho$ and $\sigma_u$ as above.
-These models were fitted using R-INLA \cite{INLA}.
+These models were fitted using R-INLA \citep{INLA}.
 To be in the correct scale for the dissagregation model, the inverse logit of the predicted Gaussian field (i.e. the linear predictor of the model) was used as the additional covariate.
@@
 
-\begin{table}[!t]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\begin{table}
+\caption{\label{table1}Summary of out-of-sample accuracy for all three cross-validation experiments.
+Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.}
 \centering
-\caption{
-{\bf Summary of out-of-sample accuracy for all three cross-validation experiments.}}
+\fbox{%
 \begin{tabular}{lllll}
@@
 {\bf Cross-validation} & {\bf Country}  & {\bf Baseline} & {\bf Prev GP} & {\bf Joint} \\
-\thickhline 
+\hline 
 Random & Indonesia  & 13.95 &  14.09 &  {\bf 13.79}\\
@@
 & Madagascar & 67.73 &  50.38 &  {\bf 44.05}\\
-\end{tabular}
-\begin{flushleft}
-Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.
-\end{flushleft}
-\label{table1}
-\end{adjustwidth}
+\end{tabular}}
 \end{table}
@@
 % to be removed before submission
-\includegraphics[width = 1.05\textwidth]{figures/random_cv_poly_facet}  
-\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
+\makebox{\includegraphics[width = 1.05\textwidth]{figures/random_cv_poly_facet.pdf}  }
+\caption{\label{randompredobspolyfacet} 
+Observed-predicted plots for random cross-validation experiments.
 A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (cases per 1,000).
@@
 }
-\label{randompredobspolyfacet}
+
 \end{figure}
@@
 % to be removed before submission
-\includegraphics[width = 1.05\textwidth]{figures/spatialkeeppr_cv_poly_facet}  
-\caption{{\bf Observed-predicted plots for spatial a cross-validation experiments where all prevalence points are used in model fitting.}
+\makebox{\includegraphics[width = 1.05\textwidth]{figures/spatialkeeppr_cv_poly_facet.pdf}}
+\caption{\label{spatial2predobspolyfacet} Observed-predicted plots for spatial a cross-validation experiments where all prevalence points are used in model fitting.
 A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (cases per 1,000).
@@
 }
-\label{spatial2predobspolyfacet}
+
 \end{figure}
 
-\begin{table}[t]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\begin{table}
+\caption{\label{table2}Summary of coverage of 80\% credible intervals. The proportion of held out data points that fall within their 80\% credible intervals. 
+Cases where this is below 0.7 are highlighted in bold.}
 \centering
-\caption{
-{\bf Summary of coverage of 80\% credible intervals.}}
+\fbox{%
 \begin{tabular}{lllll}
@@
 {\bf Cross-validation} & {\bf Country}  & {\bf Baseline} & {\bf Prev GP} & {\bf Joint} \\
-\thickhline 
+\hline 
 Random & Indonesia  & 0.73 &  0.72 &  0.72\\
@@
 & Madagascar  & {\bf 0.67} &  0.70 &  0.72\\
-
-\end{tabular}
-\begin{flushleft}
-The proportion of held out data points that fall within their 80\% credible intervals. 
-Cases where this is below 0.7 are highlighted in bold.
-\end{flushleft}
-\label{table3}
-\end{adjustwidth}
+\end{tabular}}
 \end{table}
@@
 Firstly, the data are on different scales.
-Here we have used a previously fitted model \cite{cameron2015defining} in order to be able to fit the joint model.
+Here we have used a previously fitted model \citep{cameron2015defining} in order to be able to fit the joint model.
 However, this model is imperfect in that it is calibrated with a relatively small amount of matched prevalence and incidence data.
 Although we have added the parameter $\alpha$ that scales this relationship, it is a very simple scaling.
-Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality and age-structure are not constant \cite{cameron2015defining, battle2015defining, reiner2015seasonality}.
+Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality and age-structure are not constant \citep{cameron2015defining, battle2015defining, reiner2015seasonality}.
 In using a joint model we are accepting these failings in the hope that the benefits of including additional data are stronger than the costs of using mismatched data.
@@
 
-For a model to be robust to shortcomings in the prevalence-incidence relationship from \cite{cameron2015defining}, future models could be more flexible in the way they use this relationship.
+For a model to be robust to shortcomings in the prevalence-incidence relationship from \citep{cameron2015defining}, future models could be more flexible in the way they use this relationship.
 This could be by estimating the parameters of the polynomial jointly with the rest of the model.
@@
 Here we have used purely linear covariates.
-It has been clearly established that simple linear combinations of environmental covariates cannot fully explain malaria risk \cite{bhatt2017improved}.
+It has been clearly established that simple linear combinations of environmental covariates cannot fully explain malaria risk \citep{bhatt2017improved}.
 A number of methods could be used to include non-linear effects of covariates and interactions into the model.
-Firstly, as in \cite{bhatt2017improved}, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model \cite{lucas2019model}.
+Firstly, as in \citep{bhatt2017improved}, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model.
 This approach is feasible but does not allow any information from the polygons to inform non-linear relationships.
-Directly modelling non-linear effects in the full model could be achieved by including simple non-linear functions such as splines \cite{sissoko2017temporal, sewe2017using, hundessa2018projecting}, though the increased model complexity would require more data than was used in Senegal and Madagascar in this study.
-Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \cite{law2018variational}.
-These are computational expensive without variational Bayes or other approximations \cite{law2018variational, ton2018spatial} which can be difficult to derive.
+Directly modelling non-linear effects in the full model could be achieved by including simple non-linear functions such as splines \citep{sissoko2017temporal, sewe2017using, hundessa2018projecting}, though the increased model complexity would require more data than was used in Senegal and Madagascar in this study.
+Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \citep{law2018variational}.
+These are computational expensive without variational Bayes or other approximations \citep{law2018variational, ton2018spatial} which can be difficult to derive.
 Again these models need a lot of data and careful regularisation for good predictive performance.
@@
 In contrast, summarising the spatial information from the prevalence surveys by fitting a spatial Gaussian process model and using predictions from this model as a new covariate nearly always improved predictive performance.
-As disaggregation regression becomes more widely used \cite{weiss2019mapping, battle2019mapping}, methods such as these to improve their performance are particularly needed
+As disaggregation regression becomes more widely used \citep{weiss2019mapping, battle2019mapping}, methods such as these to improve their performance are particularly needed
 
 \section*{Supporting information}
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-%\paragraph*{S1 Fig.}
-%\label{S1_Fig}
-%{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
 
@@
 
-\nolinenumbers
+%\bibliographystyle{apalike} %or any other style you like
 
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% or
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here. See http://journals.plos.org/plosone/s/latex for 
-% step-by-step instructions.
-% 
+\bibliographystyle{rss}
+
 \bibliography{Malaria}
 
-%\begin{thebibliography}{10}
-
-%\end{thebibliography}
-
 \end{document}

### 2019-07-16 ms.tex
Fix priors to match code. Closes #22.

@@
 \address{Big Data Institute,
+University of Oxford,
 Oxford,
@@
 \address{Big Data Institute,
+University of Oxford,
+Oxford,
+UK.}
+\author{Michele Nguyen}
+\address{Big Data Institute,
+University of Oxford,
+Oxford,
+UK.}
+\author{Susan Rumisha}
+\address{Big Data Institute,
+University of Oxford,
+Oxford,
+UK.}
+\author{Rosalind Howes}
+\address{Big Data Institute,
+University of Oxford,
+Oxford,
+UK.}
+\author{Katherine E. Battle}
+\address{Big Data Institute,
+University of Oxford,
+Oxford,
+UK.}
+\author{Penelope Hancock}
+\address{Big Data Institute,
+University of Oxford,
+Oxford,
+UK.}
+\author{Andre Python}
+\address{Big Data Institute,
+University of Oxford,
+Oxford,
+UK.}
+\author{Ewan Cameron}
+\address{Big Data Institute,
+University of Oxford,
+Oxford,
+UK.}
+\author{Pete Gething}
+\address{Big Data Institute,
+University of Oxford,
+Oxford,
+UK.}
+\author{Daniel J. Weiss}
+\address{Big Data Institute,
+University of Oxford,
 Oxford,
@@
 % to be removed before submission
-\makebox{\includegraphics[width = 0.6\textwidth]{figures/sen_both_cv12_preds.png}}
+\makebox{\includegraphics[width = 1.1\textwidth]{figures/sen_both_cv12_preds.png}}
 \caption{\label{predobsmapsen}
@@
 
-We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \citep{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
-We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = 1$ and Madagascar $\zeta = 1$.
+We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \citep{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > \xi) = 0.00001$.
+We used different $\zeta$  and $\xi$ values for each country: Indonesia $\zeta = 3, \xi = 1$, Senegal $\zeta = 1, \xi = 0.5$ and Madagascar $\zeta = 1, \xi = 1$.
 We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \citep{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.
+As Senegal has a lower range of incidences in the data we set $\xi$ to a smaller value for this country.
 
@@
 
-We assigned $\sigma_w$ a penalised complexity prior such that $P(\sigma_w > 0.3) = 0.0000001$. 
+We assigned $\sigma_w$ a penalised complexity prior such that $P(\sigma_w > \phi) = 0.0000001$. 
 This was chosen by finding the maximum difference in prevalence between point-surveys (with a sample size greater than 500 individuals) within the same raster pixel.
@@
 Given that the error on a prevalence estimate with sample size greater than 500 is quite small, the iid effect needs to be able to explain this difference.
+In Senegal and Madagascar this value was relatively small so we set $\phi = 0.05$. 
+In Indonesia however, there are many prevalence surveys in small areas and there is large differences in estimated prevalence within the same pixel.
+Therefore we set $\phi = 0.3$.
 
@@
 To assess how well the models were calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.
+%Finally, we fitted each model to the full data set and examine the parameter estimates for these models.
 
@@
 
+%\subsection{Parameter estimates}
+% We can examine the parameters in the models fitted
+% discuss beta for prev go
+% discuss alpha 
+% are other betas the same across models and countries.
+
 %figure 3 and 4. data and predicted incidence maps. Indonesia and Senegal only. Fig 3 ind, fig 4 rand. Data, Rand, Spatial for best model? Joint model?

### 2019-07-16 si.tex
Add loadsa si figs and first parameter table.

@@
-% Template for PLoS
-% Version 3.5 March 2018
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended 
-% to minimize problems and delays during our production 
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Once your paper is accepted for publication, 
-% PLEASE REMOVE ALL TRACKED CHANGES in this file 
-% and leave only the final text of your manuscript. 
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that 
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file. 
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig" instead of "Figure".
-% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
-%
-% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column. 
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+\documentclass[10pt,a4]{article}
+\usepackage[top=0.85in,left=.75in,footskip=0.75in]{geometry}
 
@@
 
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-
-% create \thickcline for thick horizontal lines of variable length
-\newlength\savedwidth
-\newcommand\thickcline[1]{%
-  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-  \cline{#1}%
-  \noalign{\vskip\arrayrulewidth}%
-  \noalign{\global\arrayrulewidth\savedwidth}%
-}
-
-% \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-\hline
-\noalign{\global\arrayrulewidth\savedwidth}}
-
-% Remove comment for double spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-
 % Bold the 'Figure #' in the caption and separate it from the title/caption with a period
@@
 \usepackage{epstopdf}
-%\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-%\setlength{\headheight}{27.023pt}
-%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\headrulewidth}{0pt}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\today}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
 
@@
 
+\clearpage
+\subsection{Estimated parameters}
+
+% latex table generated in R 3.4.4 by xtable 1.8-4 package
+% Mon Jul 15 21:04:30 2019
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrrrrrr}
+  \hline
+Parameters & Baseline & BaselineSD & PrevalenceGP & PrevalenceGPSD & Joint & JointSD \\ 
+  \hline
+$\beta_0$ & -5.58 & 0.29 & -4.72 & 0.57 & -5.35 & 0.51 \\ 
+  $\beta_p$ &  &  &  &  & 1.64 & 0.13 \\ 
+  LST day mean & 0.00 & 0.26 & -0.03 & 0.26 & -0.09 & 0.24 \\ 
+  EVI & 0.43 & 0.23 & 0.34 & 0.24 & 0.27 & 0.20 \\ 
+  TSI & -0.61 & 0.24 & -0.52 & 0.24 & 0.36 & 0.18 \\ 
+  accessability & -0.09 & 0.21 & -0.05 & 0.21 & 0.10 & 0.11 \\ 
+  elevation & 0.44 & 0.21 & 0.36 & 0.22 & 0.31 & 0.18 \\ 
+  LST day SD & 0.23 & 0.20 & 0.08 & 0.21 & 0.24 & 0.20 \\ 
+  Night lights & 0.10 & 0.06 & 0.09 & 0.06 & 0.05 & 0.04 \\ 
+  TCW & -0.02 & 0.28 & -0.07 & 0.28 & 0.17 & 0.24 \\ 
+  Prev GP &  &  & 0.27 & 0.17 &  &  \\ 
+  $\log(\tau)$ & 0.25 & 0.25 & 0.26 & 0.25 & -0.03 & 0.33 \\ 
+  $\log(\tau_{prev})$ &  &  &  &  & -1.06 & 0.13 \\ 
+  $\log(\sigma_u)$ & -2.48 & 0.61 & -2.26 & 0.57 & -3.41 & 0.52 \\ 
+  $\log(\rho)$ & 0.58 & 0.30 & 0.63 & 0.29 & 0.68 & 0.31 \\ 
+  $\log(\alpha)$ &  &  &  &  & -0.00 & 0.00 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+% latex table generated in R 3.4.4 by xtable 1.8-4 package
+% Mon Jul 15 21:04:30 2019
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrrrrrr}
+  \hline
+Parameters & Baseline & BaselineSD & PrevalenceGP & PrevalenceGPSD & Joint & JointSD \\ 
+  \hline
+$\beta_0$ & -3.81 & 0.32 & -2.70 & 0.31 & -3.51 & 0.54 \\ 
+  $\beta_p$ &  &  &  &  & -0.02 & 0.10 \\ 
+  LST day mean & 0.17 & 0.29 & 0.16 & 0.27 & 0.19 & 0.24 \\ 
+  EVI & 0.34 & 0.21 & 0.24 & 0.19 & 0.48 & 0.13 \\ 
+  TSI & 0.45 & 0.22 & 0.43 & 0.21 & 0.66 & 0.18 \\ 
+  accessability & 0.36 & 0.11 & 0.16 & 0.10 & 0.29 & 0.07 \\ 
+  elevation & -0.11 & 0.18 & -0.04 & 0.16 & 0.30 & 0.12 \\ 
+  LST day SD & -0.22 & 0.21 & -0.16 & 0.18 & -0.19 & 0.16 \\ 
+  Night lights & -0.01 & 0.03 & -0.02 & 0.02 & -0.02 & 0.02 \\ 
+  TCW & -0.26 & 0.26 & -0.22 & 0.25 & -0.08 & 0.15 \\ 
+  Prev GP &  &  & 0.35 & 0.07 &  &  \\ 
+  $\log(\tau)$ & 1.19 & 0.23 & 1.18 & 0.22 & 1.15 & 0.22 \\ 
+  $\log(\tau_{prev})$ &  &  &  &  & -0.85 & 0.11 \\ 
+  $\log(\sigma_u)$ & -2.57 & 0.60 & -2.48 & 0.63 & -2.02 & 0.59 \\ 
+  $\log(\rho)$ & 0.99 & 0.32 & 0.84 & 0.32 & 1.37 & 0.37 \\ 
+  $\log(\alpha)$ &  &  &  &  & 0.00 & 0.00 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\begin{figure}[h!]
+% to be removed before submission
+\makebox{\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_random_preds.png}}
+\caption{\label{predobsmapsen}
+Incidence data and predicted incidence maps.
+The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for random cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
+}
+\end{figure}
+
+\begin{figure}[h!]
+% to be removed before submission
+\makebox{\includegraphics[width = 0.8\textwidth]{figures/mdg_both_cv12_random_preds.png}}
+\caption{\label{predobsmapsen}
+Incidence data and predicted incidence maps.
+The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for random cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
+}
+\end{figure}
+
+\begin{figure}[h!]
+% to be removed before submission
+\makebox{\includegraphics[width = 0.8\textwidth]{figures/sen_both_cv12_random_preds.png}}
+\caption{\label{predobsmapsen}
+Incidence data and predicted incidence maps.
+The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for ranomd cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
+}
+\end{figure}
+
+\clearpage
+\subsection{Spatial CV predictions}
+
+\begin{figure}[h!]
+% to be removed before submission
+\makebox{\includegraphics[width = 0.8\textwidth]{figures/idn_both_cv12_preds.png}}
+\caption{\label{predobsmapsen}
+Incidence data and predicted incidence maps.
+The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
+}
+\end{figure}
+
+\clearpage
+\subsection{Full model predictions}
+\subsubsection{Madagascar}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.3\textheight]{figures/mdg_baseline_api.png}
+
+\caption{Predictions from the baseline model fitted to all data in Madagascar.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.3\textheight]{figures/mdg_prgp_api.png}
+
+\caption{Predictions from the prevalence GP model fitted to all data in Madagascar.}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.3\textheight]{figures/mdg_joint_api.png}
+
+\caption{Predictions from the joint model fitted to all data in Madagascar.}
+\end{figure}
+
+\subsubsection{Senegal}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.3\textheight]{figures/sen_baseline_api.png}
+
+\caption{Predictions from the baseline model fitted to all data in Senegal.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.3\textheight]{figures/sen_prgp_api.png}
+
+\caption{Predictions from the prevalence GP model fitted to all data in Senegal.}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.3\textheight]{figures/sen_joint_api.png}
+
+\caption{Predictions from the joint model fitted to all data in Senegal.}
+\end{figure}
+
+\clearpage
+\subsection{Full model fields}
+
+\subsubsection{Senegal}
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.3\textheight]{figures/sen_prevgp.png}
+
+\caption{The prevalence GP model that is used as a covariate.}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.3\textheight]{figures/sen_baseline_field.png}
+
+\caption{The random field as fitted to all the data in the baseline model.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.3\textheight]{figures/sen_prgp_field.png}
+
+\caption{The random field as fitted to all the data in the prevalence GP model.}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.3\textheight]{figures/sen_joint_field.png}
+
+\caption{The random field as fitted to all the data in the joint model.}
+\end{figure}
+
+\clearpage
+\subsubsection{Indonesia}
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.3\textheight]{figures/idn_prevgp.png}
+
+\caption{The prevalence GP model that is used as a covariate.}
+\end{figure}
+
+\clearpage
+\subsubsection{Madagascar}
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.3\textheight]{figures/mdg_prevgp.png}
+
+\caption{The prevalence GP model that is used as a covariate.}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.3\textheight]{figures/mdg_baseline_field.png}
+
+\caption{The random field as fitted to all the data in the baseline model.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.3\textheight]{figures/mdg_prgp_field.png}
+
+\caption{The random field as fitted to all the data in the prevalence GP model.}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.3\textheight]{figures/mdg_joint_field.png}
+
+\caption{The random field as fitted to all the data in the joint model.}
+\end{figure}
+
 \end{document}

### 2019-07-19 ms.tex
Anita edits to intro.

@@
 \usepackage[authoryear]{natbib}
+
+\usepackage{xr}
+\externaldocument{si}
+
+\usepackage[hidelinks]{hyperref}
 
@@
 This polygon incidence data can be more sensitive than prevalence point-surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \citep{cibulskis2011worldwide}.
+Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level, routine surveillance records of incidence \citep{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
 
@@
 
-Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level, routine surveillance records of incidence \citep{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
-However using polygon-level incidence data to estimate malaria risk for high resolution maps presents at least three noteworthy modelling difficulties. 
+However using only polygon-level incidence data to estimate malaria risk, and ignoring preevalence survey data, presents at least three noteworthy areas where improvements are possible. 
 (1) There are often some areas with better coverage of prevalence surveys than polygon incidence data.
@@
 %Disaggregation models aim to estimate high-resolution maps from aggregated data and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
-(2) The aggregation of cases over space means that it may be difficult to learn relationships between malaria risk and the environment from aggregated incidence data, especially if the case counts are aggregated over a large or heterogenous area.
-(3) Finally, estimates of both prevalence and incidence metrics are useful for policy makers \citep{cohen2017mapping} but typically models are fitted to observations of one metric and then a secondary model is used to convert to the other \emph{post hoc} \citep{battle2019mapping, bhatt2015effect}.
+(2) The aggregation of cases over space means that it may be difficult to learn relationships between malaria risk and the environment from aggregated incidence data, especially if the case counts are aggregated over large or heterogenous areas.
+(3) Finally, estimates of both prevalence and incidence metrics are useful for policy makers \citep{cohen2017mapping}.
+Typically models are fitted to observations of one metric and then a secondary model is used to convert to the other \emph{post hoc} \citep{battle2019mapping, bhatt2015effect}.
+However, this misses an opportunity to learn the relationship between prevalence and incidence at the same time as fitting the geographic model.
 
@@
 Firstly, the spatial information from prevalence surveys could be summarised using a seperate model and then included as a covariate in the disaggregation model.
-If the model used to summarise the prevalence surveys is expliciteply spatial, this approach would make the spatial information in the prevalence data available to be used by the disaggregation model, therefore solving issue (1) above.
+If the model used to summarise the prevalence surveys is explicitely spatial, this approach would make the spatial information in the prevalence data available to be used by the disaggregation model, therefore solving issue (1) above.
 However, this approach does not provide additional degrees of freedom in order to more accurately learn relationships between malaria risk and the environment and therefore does not solve issue (2).
@@
 
-Fully combining observations of incidence and prevalence in a joint model has the potential to alleviate all three of the above issues.
+Fully combining observations of incidence and prevalence in a joint model, with multiple likelihoods, has the potential to alleviate all three of the above issues.
 As the prevalence surveys are directly used as response data, issue (1) is solved.
 Similar, as the additional data are being used as response data, they are providing additional degrees of freedom with which to learn relationships between malaria risk and the environment, therefore solving issue (2).
-Finally, a joint model that includes prevalence as a latent variable allows predictions of prevalence and incidence to be made jointly to provide better estimates than a \emph{post hoc} conversion.
-Such a model could also learn the relationship between different metrics at the same time as making spatial estimates.
+Finally, such a model could also learn the relationship between different metrics at the same time as making spatial estimates.
 Therefore, a full joint model has the potential to solve issue (3) as well.
-
-One major barrier to a joint modelling approach, however, is that these two data types measure metrics disease transmission on different scales.
+While a joint model provides the opportunity to learn the relationship between prevalence and incidence, this is technically challenging as these two data types measure disease intensity on different scales.
 Point surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ that quantify parasite rate during a short period of time.
@@
 We then compare results from the two models with those made using a polygon-only, disaggregation model similar to previous models \citep{sturrock2014fine, wilson2017pointless}.
-Both models are fitted to data from Indonesia, Senegal and Madagascar to provide a set of case studies with disparate geographic settings and levels of malaria endemicity.
+All models are fitted to data from Indonesia, Senegal and Madagascar to provide a set of case studies with disparate geographic settings and levels of malaria endemicity.
 
@@
 
-$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) + w_b\sigma_w).$$
+$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) + w_b(\sigma_w).$$
 As well as the global intercept, $\beta_0$, this model has a prevalence survey only intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point survey is being considered.
@@
 To compare the three models we used two cross-validation schemes. 
-In the first (random), the incidence data was split into ten cross-validation folds while all the prevalence data was used in each case.
+In the first (random), the incidence data was split into ten cross-validation folds while all the prevalence data was used in each case (Figure~\ref{fig:cv_random}). 
 %This cross-validation scheme directly addresses the question of whethe
-In the second validation scheme , the incidence data was split into spatial cross-validation folds, using k means clustering on polygon centroids, while again all prevalence points were used in all folds.
+In the second validation scheme , the incidence data was split into spatial cross-validation folds, using k means clustering on polygon centroids, while again all prevalence points were used in all folds (Figure~\ref{fig:cv_spatial}).
 The number of folds was seven for Indonesia, five for Senegal and three for Madagascar due to their differing sizes and epidemiological settings.
@@
 
-\begin{table}
-\caption{\label{table2}Summary of coverage of 80\% credible intervals. The proportion of held out data points that fall within their 80\% credible intervals. 
-Cases where this is below 0.7 are highlighted in bold.}
-\centering
-\fbox{%
-\begin{tabular}{lllll}
-\hline
-{\bf Cross-validation} & {\bf Country}  & {\bf Baseline} & {\bf Prev GP} & {\bf Joint} \\
-\hline 
-Random & Indonesia  & 0.73 &  0.72 &  0.72\\
-& Senegal  & 0.76 &  0.78 &  0.80\\
-& Madagascar  & 0.78 &  0.79 &  0.78\vspace{1mm}\\
- Spatial  & Indonesia & 0.71 &  0.72 &  {\bf 0.51}\\
-& Senegal  & 0.78 &  0.88 &  0.71\\
-& Madagascar  & {\bf 0.67} &  0.70 &  0.72\\
-\end{tabular}}
-\end{table}
-
 % Coverage results
@@
 However, in most cases coverage was between 0.7 and 0.8 implying the models were a little overconfident in their predictions.
+There was no clear difference in calibration between the different models.
+
+% Look at parameters
+
+We can further examine why the models performed as they did by examining the parameters estimated in the models fitted to all data (Tables~\ref{parssen}--\ref{parsidn}).
+Firstly we can compare the regression parameter for the prevalence GP covariate in the three countries noting that in Indonesia the prevalence GP model performed worse than baseline under random cross-validation and had equal performance to baseline under spatial cross-validation.
+We see that the regression parameter for this covariate was small in Indonesia (mean = 0.06, sd = 0.12) but relatively large and positive in both Senegal (mean = 0.30, sd = 0.17) and Madagascar  (mean = 0.36, sd = 0.07).
+
+In Madagascar the joint model performed the best in the spatial cross-validation scheme and better than the baseline in the random cross-validation scheme. 
+Comparing the parameter estimates for the joint model specific parameters between Madagascar and the other two countries therefore seems useful.
+The prevalence only intercept, $\beta_p$, is large in the Senegal fit (mean = 1.36, sd = 0.13) but small in Indonesia (mean = 0.03, sd = 0.20) and Madagascar (mean = 0.07, sd = 0.10).
+This implies there is a strong bias (given the prevalence to incidence model) between the prevalence and incidence data in Senegal.
+Furthermore, the standard deviation of the prevalence point iid effect, $w_b(\sigma_w)$, is much larger in Indonesia (mean $\sigma_w$ = 13.46, mean $\log(\tau_w) = -2.6$, sd $\log(\tau_w) = 0.09$) than in Senegal (mean $\sigma_w$ = 2.80, mean $\log(\tau_w) = -1.03$, sd $\log(\tau_w) = 0.13$) or Madagascar (mean $\sigma_w$ = 2.16, mean $\log(\tau_w) = -0.77$, sd $\log(\tau_w) = 0.11$).
+This implies there is a lot of noise in the prevalence data in Indonesia.
+
+We set a strong prior on $\alpha$ being close to one, encoding our belief that the incidence prevalence relationship should be close to the previously fitted model.
+The estimated value for $\alpha$ in all three countries is very close to one (Tables~\ref{parssen}--\ref{parsidn}).
+While this might be driven by the prior, we can conclude that there is no strong evidence from the data that this relationship should be scaled differently in the different countries.
 
@@
 %\end{figure}
+
+\begin{table}
+\caption{\label{table3}Summary of coverage of 80\% credible intervals. The proportion of held out data points that fall within their 80\% credible intervals. 
+Cases where this is below 0.7 are highlighted in bold.}
+\centering
+\fbox{%
+\begin{tabular}{lllll}
+\hline
+{\bf Cross-validation} & {\bf Country}  & {\bf Baseline} & {\bf Prev GP} & {\bf Joint} \\
+\hline 
+Random & Indonesia  & 0.73 &  0.72 &  0.72\\
+& Senegal  & 0.76 &  0.78 &  0.80\\
+& Madagascar  & 0.78 &  0.79 &  0.78\vspace{1mm}\\
+ Spatial  & Indonesia & 0.71 &  0.72 &  {\bf 0.51}\\
+& Senegal  & 0.78 &  0.88 &  0.71\\
+& Madagascar  & {\bf 0.67} &  0.70 &  0.72\\
+\end{tabular}}
+\end{table}
 

### 2019-07-19 ms.tex
Add sample sizes.

@@
 To minimise temporal effects we selected one year of polygon incidence data and the surrounding five years of prevalence point-survey data for each country.
-For Indonesia we selected polygon incidence data from 2012 that covers 380 regions, and prevalence data from 2010 to 2014 that consists of todo surveys, representing todo individuals.
-For Senegal we selected 2015 for polygon incidence data (46 regions) and 2013 to 2017 for prevalence data (todo surveys, todo individuals).
-Finally, for Madagascar we selected 2013 for polygon incidence (110 regions) and 2011 to 2015 for prevalence (todo surveys, todo individuals) data.
-
-\begin{figure}
-% to be removed before submission
-\makebox{\includegraphics[width = 1.1\textwidth]{figures/sen_both_cv12_preds.png}}
-\caption{\label{predobsmapsen}
-Incidence data and predicted incidence maps.
-The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
-}
-
-\end{figure}
-
-\begin{figure}
-% to be removed before submission
-\makebox{\includegraphics[width = 1.1\textwidth]{figures/mdg_both_cv12_preds.png}}
-\caption{\label{predobsmapmdg}Input incidence data and predicted incidence maps.
-The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (right) for Senegal.
-}
-
-\end{figure}
+For Indonesia we selected polygon incidence data from 2012 that covers 379 regions, and prevalence data from 2010 to 2014 that consists of 1,233 surveys, representing 230,747 individuals.
+For Senegal we selected 2015 for polygon incidence data (41 regions) and 2013 to 2017 for prevalence data (804 surveys, 17,037 individuals).
+Finally, for Madagascar we selected 2013 for polygon incidence (110 regions) and 2011 to 2015 for prevalence (1,049 surveys, 36,411 individuals) data.
 
@@
 The covariates were standardised to have a mean of zero and a standard deviation of one.
+
+\begin{figure}
+% to be removed before submission
+\makebox{\includegraphics[width = 1.1\textwidth]{figures/sen_both_cv12_preds.png}}
+\caption{\label{predobsmapsen}
+Incidence data and predicted incidence maps.
+The incidence (log10) data (left), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (right) for Senegal.
+}
+
+\end{figure}
+
+\begin{figure}
+% to be removed before submission
+\makebox{\includegraphics[width = 1.1\textwidth]{figures/mdg_both_cv12_preds.png}}
+\caption{\label{predobsmapmdg}Input incidence data and predicted incidence maps.
+The incidence (log10) data (left), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (right) for Madagascar.
+}
+
+\end{figure}
 
@@
 
-We have compared the predictive performance of a polygon-only model and a model that jointly learns from polygon incidence data and prevalence point-surveys.
-Overal the prevalence GP model appears to peform best.
+We have compared the predictive performance of three models: a baseline polygon-only model; a disaggregation model with spatial information from prevalence surveys included as an additional covariate from a seperate Gaussian process model; and a model that jointly learns from polygon incidence data and prevalence point-surveys.
+Overall the prevalence GP model appears to peform best.
 While the joint model sometimes performs best it also performs worse than baseline half of the time.

### 2019-07-19 ms.tex
Some mre final edits.

@@
 (3) Finally, estimates of both prevalence and incidence metrics are useful for policy makers \citep{cohen2017mapping}.
-Typically models are fitted to observations of one metric and then a secondary model is used to convert to the other \emph{post hoc} \citep{battle2019mapping, bhatt2015effect}.
-However, this misses an opportunity to learn the relationship between prevalence and incidence at the same time as fitting the geographic model.
+Typically models are fitted to observations of one metric and then a secondary model is used to convert to the other metric \emph{post hoc} \citep{battle2019mapping, bhatt2015effect}.
+This misses an opportunity to learn the relationship between prevalence and incidence at the same time as fitting the geographic model.
 
@@
 For Senegal we selected 2015 for polygon incidence data (41 regions) and 2013 to 2017 for prevalence data (804 surveys, 17,037 individuals).
-Finally, for Madagascar we selected 2013 for polygon incidence (110 regions) and 2011 to 2015 for prevalence (1,049 surveys, 36,411 individuals) data.
+Finally, for Madagascar we selected 2013 for polygon incidence (110 regions) and 2011 to 2015 for prevalence data (1,049 surveys, 36,411 individuals).
 
@@
 
-The prevalence point-survey data were extracted from the Malaria Atlas Project prevalence survey database \citep{bhatt2015effect, guerra2007assembling, gething2011new, pfeffer2018ma}.
+The prevalence point-survey data were extracted from the Malaria Atlas Project prevalence survey database \citep{bhatt2015effect, guerra2007assembling, pfeffer2018ma}.
 As the prevalence point-surveys cover different age ranges they were standardised to an age-range of 2--10 using the model from \citep{smith2007standardizing}.
@@
 The iid random effect, $v_a \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $j$ being grouped together.
+Internally, this effect is parameterised as the log of the precision, $\omega_v = \log(\tau_v) = \log(\frac{1}{{\sigma_v}^2})$ to improve numeric stability.
 This random effect modelled both missing covariates and extra-Poisson sampling error.
@@
 The second iid random effect, $w_b \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
+To improve numeric stability this effect is also parameterised internally as the log of the precision, $\omega_w = \log(\tau_w) = \log(\frac{1}{{\sigma_w}^2})$.
 This effect modelled extra-binomial sampling noise.
@@
 This implies there is a strong bias (given the prevalence to incidence model) between the prevalence and incidence data in Senegal.
-Furthermore, the standard deviation of the prevalence point iid effect, $w_b(\sigma_w)$, is much larger in Indonesia (mean $\sigma_w$ = 13.46, mean $\log(\tau_w) = -2.6$, sd $\log(\tau_w) = 0.09$) than in Senegal (mean $\sigma_w$ = 2.80, mean $\log(\tau_w) = -1.03$, sd $\log(\tau_w) = 0.13$) or Madagascar (mean $\sigma_w$ = 2.16, mean $\log(\tau_w) = -0.77$, sd $\log(\tau_w) = 0.11$).
+Furthermore, the standard deviation of the prevalence point iid effect, $w_b(\sigma_w)$, is much larger in Indonesia (mean $\omega_w = -2.6$, sd $\omega_w = 0.09$ which corresponds to $\sigma_w$ = 13.46) than in Senegal (mean $\omega_w = -1.03$, sd $\omega_w = 0.13$ which corresponds to $\sigma_w$ = 2.80) or Madagascar (mean $\omega_w = -0.77$, sd $\omega_w = 0.11$ which corresponsed to $\sigma_w$ = 2.16).
 This implies there is a lot of noise in the prevalence data in Indonesia.

### 2019-07-19 si.tex
Some mre final edits.

@@
 
-\clearpage
+\section{Crossvalidation schemes}
 
@@
 
-\includegraphics[width = 0.9\textwidth]{figures/random_crossvalidation_full.png}
+\includegraphics[width = 0.8\textwidth]{figures/random_crossvalidation_full.png}
 
-\caption{{\bf Random cross-validation scheme for Indonesia, Senegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+\caption{Random cross-validation scheme for Indonesia, Senegal and Madagascar. The fold for both aggregated incidence data and prevalence point data is shown.}
 \label{fig:cv_random}
@@
 
-\includegraphics[width = 0.9\textwidth]{figures/spatial_crossvalidation_full.png}
+\includegraphics[width = 0.8\textwidth]{figures/spatial_crossvalidation_full.png}
 
-\caption{{\bf Spatial cross-validation scheme for Indonesia, Senegal and Madagascar.} The fold for both aggregated incidence data and prevalence point data is shown.}
+\caption{ Spatial cross-validation scheme for Indonesia, Senegal and Madagascar. The fold for both aggregated incidence data and prevalence point data is shown.}
 \label{fig:cv_spatial}
@@
 \clearpage
-\subsection{Estimated parameters}
+\section{Estimated parameters}
 
 % latex table generated in R 3.4.4 by xtable 1.8-4 package
-% Mon Jul 15 21:04:30 2019
+% Fri Jul 19 12:48:02 2019
 \begin{table}[ht]
@@
   \hline
-$\beta_0$ & -5.58 & 0.29 & -4.72 & 0.57 & -5.35 & 0.51 \\ 
-  $\beta_p$ &  &  &  &  & 1.64 & 0.13 \\ 
-  LST day mean & 0.00 & 0.26 & -0.03 & 0.26 & -0.09 & 0.24 \\ 
-  EVI & 0.43 & 0.23 & 0.34 & 0.24 & 0.27 & 0.20 \\ 
-  TSI & -0.61 & 0.24 & -0.52 & 0.24 & 0.36 & 0.18 \\ 
-  accessability & -0.09 & 0.21 & -0.05 & 0.21 & 0.10 & 0.11 \\ 
+$\beta_0$ & -5.58 & 0.29 & -4.66 & 0.58 & -5.35 & 0.52 \\ 
+  $\beta_p$ &  &  &  &  & 1.63 & 0.13 \\ 
+  LST day mean & 0.00 & 0.26 & -0.02 & 0.26 & -0.04 & 0.24 \\ 
+  EVI & 0.43 & 0.23 & 0.35 & 0.24 & 0.35 & 0.20 \\ 
+  TSI & -0.61 & 0.24 & -0.51 & 0.24 & 0.42 & 0.17 \\ 
+  accessability & -0.09 & 0.21 & -0.07 & 0.21 & 0.11 & 0.11 \\ 
   elevation & 0.44 & 0.21 & 0.36 & 0.22 & 0.31 & 0.18 \\ 
-  LST day SD & 0.23 & 0.20 & 0.08 & 0.21 & 0.24 & 0.20 \\ 
-  Night lights & 0.10 & 0.06 & 0.09 & 0.06 & 0.05 & 0.04 \\ 
-  TCW & -0.02 & 0.28 & -0.07 & 0.28 & 0.17 & 0.24 \\ 
-  Prev GP &  &  & 0.27 & 0.17 &  &  \\ 
-  $\log(\tau)$ & 0.25 & 0.25 & 0.26 & 0.25 & -0.03 & 0.33 \\ 
-  $\log(\tau_{prev})$ &  &  &  &  & -1.06 & 0.13 \\ 
-  $\log(\sigma_u)$ & -2.48 & 0.61 & -2.26 & 0.57 & -3.41 & 0.52 \\ 
-  $\log(\rho)$ & 0.58 & 0.30 & 0.63 & 0.29 & 0.68 & 0.31 \\ 
+  LST day SD & 0.23 & 0.20 & 0.07 & 0.21 & 0.24 & 0.20 \\ 
+  Night lights & 0.10 & 0.06 & 0.08 & 0.06 & 0.07 & 0.04 \\ 
+  TCW & -0.02 & 0.28 & -0.05 & 0.28 & 0.17 & 0.23 \\ 
+  Prev GP &  &  & 0.30 & 0.17 &  &  \\ 
+  $\omega_v$ & 0.25 & 0.25 & 0.27 & 0.25 & -0.03 & 0.32 \\ 
+  $\omega_w$ &  &  &  &  & -1.03 & 0.13 \\ 
+  $\log(\sigma_u)$ & -2.48 & 0.61 & -2.53 & 0.63 & -3.35 & 0.52 \\ 
+  $\log(\rho)$ & 0.58 & 0.30 & 0.58 & 0.30 & 0.71 & 0.31 \\ 
   $\log(\alpha)$ &  &  &  &  & -0.00 & 0.00 \\ 
@@
 \end{tabular}
+\caption{Parameter estimates for Senegal. $\omega_v = \log\left(\frac{1}{{\sigma_v}^2}\right)$ and $\omega_w = \log\left(\frac{1}{{\sigma_w}^2}\right)$} 
 \end{table}
@@
 % latex table generated in R 3.4.4 by xtable 1.8-4 package
-% Mon Jul 15 21:04:30 2019
+% Fri Jul 19 12:48:37 2019
 \begin{table}[ht]
@@
   \hline
-$\beta_0$ & -3.81 & 0.32 & -2.70 & 0.31 & -3.51 & 0.54 \\ 
-  $\beta_p$ &  &  &  &  & -0.02 & 0.10 \\ 
-  LST day mean & 0.17 & 0.29 & 0.16 & 0.27 & 0.19 & 0.24 \\ 
-  EVI & 0.34 & 0.21 & 0.24 & 0.19 & 0.48 & 0.13 \\ 
-  TSI & 0.45 & 0.22 & 0.43 & 0.21 & 0.66 & 0.18 \\ 
-  accessability & 0.36 & 0.11 & 0.16 & 0.10 & 0.29 & 0.07 \\ 
-  elevation & -0.11 & 0.18 & -0.04 & 0.16 & 0.30 & 0.12 \\ 
-  LST day SD & -0.22 & 0.21 & -0.16 & 0.18 & -0.19 & 0.16 \\ 
+$\beta_0$ & -3.81 & 0.32 & -2.66 & 0.29 & -3.77 & 0.30 \\ 
+  $\beta_p$ &  &  &  &  & 0.07 & 0.10 \\ 
+  LST day mean & 0.16 & 0.29 & 0.14 & 0.27 & 0.14 & 0.24 \\ 
+  EVI & 0.34 & 0.21 & 0.23 & 0.19 & 0.46 & 0.13 \\ 
+  TSI & 0.45 & 0.22 & 0.42 & 0.21 & 0.63 & 0.19 \\ 
+  accessability & 0.36 & 0.11 & 0.15 & 0.10 & 0.24 & 0.07 \\ 
+  elevation & -0.11 & 0.18 & -0.05 & 0.16 & 0.31 & 0.12 \\ 
+  LST day SD & -0.22 & 0.21 & -0.15 & 0.17 & -0.20 & 0.15 \\ 
   Night lights & -0.01 & 0.03 & -0.02 & 0.02 & -0.02 & 0.02 \\ 
-  TCW & -0.26 & 0.26 & -0.22 & 0.25 & -0.08 & 0.15 \\ 
-  Prev GP &  &  & 0.35 & 0.07 &  &  \\ 
-  $\log(\tau)$ & 1.19 & 0.23 & 1.18 & 0.22 & 1.15 & 0.22 \\ 
-  $\log(\tau_{prev})$ &  &  &  &  & -0.85 & 0.11 \\ 
-  $\log(\sigma_u)$ & -2.57 & 0.60 & -2.48 & 0.63 & -2.02 & 0.59 \\ 
-  $\log(\rho)$ & 0.99 & 0.32 & 0.84 & 0.32 & 1.37 & 0.37 \\ 
+  TCW & -0.26 & 0.26 & -0.22 & 0.25 & -0.15 & 0.15 \\ 
+  Prev GP &  &  & 0.36 & 0.07 &  &  \\ 
+  $\omega_v$ & 1.19 & 0.23 & 1.26 & 0.23 & 1.38 & 0.26 \\ 
+  $\omega_w$ &  &  &  &  & -0.77 & 0.11 \\ 
+  $\log(\sigma_u)$ & -2.57 & 0.60 & -2.83 & 0.63 & -3.21 & 0.49 \\ 
+  $\log(\rho)$ & 0.99 & 0.32 & 0.69 & 0.31 & 0.73 & 0.27 \\ 
   $\log(\alpha)$ &  &  &  &  & 0.00 & 0.00 \\ 
@@
 \end{tabular}
+\caption{Parameter estimates for Madagascar $\omega_v = \log\left(\frac{1}{{\sigma_v}^2}\right)$ and $\omega_w = \log\left(\frac{1}{{\sigma_w}^2}\right)$} 
 \end{table}
+
+% latex table generated in R 3.4.4 by xtable 1.8-4 package
+% Fri Jul 19 12:48:41 2019
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrrrrrr}
+  \hline
+Parameters & Baseline & BaselineSD & PrevalenceGP & PrevalenceGPSD & Joint & JointSD \\ 
+  \hline
+$\beta_0$ & -5.83 & 0.65 & -5.59 & 0.80 & -6.31 & 0.56 \\ 
+  $\beta_p$ &  &  &  &  & 0.03 & 0.20 \\ 
+  LST day mean & -0.03 & 0.20 & -0.03 & 0.20 & 0.28 & 0.27 \\ 
+  EVI & 0.11 & 0.08 & 0.11 & 0.08 & 0.55 & 0.18 \\ 
+  TSI & 0.24 & 0.19 & 0.24 & 0.19 & -0.02 & 0.24 \\ 
+  accessability & 0.73 & 0.24 & 0.73 & 0.24 & 0.36 & 0.19 \\ 
+  elevation & -0.12 & 0.12 & -0.12 & 0.12 & -0.23 & 0.22 \\ 
+  LST day SD & 0.04 & 0.11 & 0.04 & 0.11 & -0.04 & 0.18 \\ 
+  Night lights & -0.34 & 0.12 & -0.34 & 0.12 & 0.01 & 0.10 \\ 
+  TCW & 0.05 & 0.10 & 0.05 & 0.10 & 0.06 & 0.19 \\ 
+  Prev GP &  &  & 0.06 & 0.12 &  &  \\ 
+  $\omega_v$ & -1.54 & 0.11 & -1.54 & 0.11 & -1.33 & 0.11 \\ 
+  $\omega_w$ &  &  &  &  & -2.65 & 0.09 \\ 
+  $\log(\sigma_u)$ & -2.23 & 0.43 & -2.25 & 0.43 & -2.79 & 0.48 \\ 
+  $\log(\rho)$ & 1.63 & 0.23 & 1.62 & 0.23 & 1.38 & 0.24 \\ 
+  $\log(\alpha)$ &  &  &  &  & -0.00 & 0.00 \\ 
+   \hline
+\end{tabular}
+\caption{Parameter estimates for Indonesia $\omega_v = \log\left(\frac{1}{{\sigma_v}^2}\right)$ and $\omega_w = \log\left(\frac{1}{{\sigma_w}^2}\right)$} 
+\end{table}
+
+\clearpage
+\section{Cross-validation predictions}
 
@@
 % to be removed before submission
-\makebox{\includegraphics[width = 0.8\textwidth]{figures/mdg_both_cv12_random_preds.png}}
+\makebox{\includegraphics[width = 0.9\textwidth]{figures/mdg_both_cv12_random_preds.png}}
 \caption{\label{predobsmapsen}
@@
 % to be removed before submission
-\makebox{\includegraphics[width = 0.8\textwidth]{figures/sen_both_cv12_random_preds.png}}
+\makebox{\includegraphics[width = 1\textwidth]{figures/sen_both_cv12_random_preds.png}}
 \caption{\label{predobsmapsen}
 Incidence data and predicted incidence maps.
-The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for ranomd cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
+The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for random cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
 }
@@
 
+\subsubsection{Indonesia}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.5\textheight]{figures/idn_baseline_api.png}
+
+\caption{Predictions from the baseline model fitted to all data in Indonesia.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.5\textheight]{figures/idn_prgp_api.png}
+
+\caption{Predictions from the prevalence GP model fitted to all data in Indonesia.}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.5\textheight]{figures/idn_joint_api.png}
+
+\caption{Predictions from the joint model fitted to all data in Indonesia.}
+\end{figure}
+
 \clearpage
@@
 
-\includegraphics[width = 0.3\textheight]{figures/idn_prevgp.png}
+\includegraphics[width = 0.6\textheight]{figures/idn_prevgp.png}
 
 \caption{The prevalence GP model that is used as a covariate.}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.6\textheight]{figures/idn_baseline_field.png}
+
+\caption{The random field as fitted to all the data in the joint model.}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.6\textheight]{figures/idn_prgp_field.png}
+
+\caption{The random field as fitted to all the data in the joint model.}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.6\textheight]{figures/idn_joint_field.png}
+
+\caption{The random field as fitted to all the data in the joint model.}
 \end{figure}

### 2019-07-19 ms.tex
Fix capitals in plasmodium.

@@
 However, traditional mapping using prevalence point-surveys are often ineffective in low prevalence areas due to low statistical power and a lack of data.
-More recently, dissagregation regression models have been developed that can estimate risk at high spatial resolution from surveillance data that reports incidence aggregated to a geographic polygon.
+More recently, disaggregation regression models have been developed that can estimate risk at high spatial resolution from surveillance data that reports incidence aggregated to a geographic polygon.
 However, there is generally low spatial overlap between prevalence point-surveys and polygon incidence data and therefore models that make use of the spatial information from prevalence point surveys have great potential.
@@
 
-However using only polygon-level incidence data to estimate malaria risk, and ignoring preevalence survey data, presents at least three noteworthy areas where improvements are possible. 
+However using only polygon-level incidence data to estimate malaria risk, and ignoring prevalence survey data, presents at least three noteworthy areas where improvements are possible. 
 (1) There are often some areas with better coverage of prevalence surveys than polygon incidence data.
@@
 %Disaggregation models aim to estimate high-resolution maps from aggregated data and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
-(2) The aggregation of cases over space means that it may be difficult to learn relationships between malaria risk and the environment from aggregated incidence data, especially if the case counts are aggregated over large or heterogenous areas.
+(2) The aggregation of cases over space means that it may be difficult to learn relationships between malaria risk and the environment from aggregated incidence data, especially if the case counts are aggregated over large or heterogeneous areas.
 (3) Finally, estimates of both prevalence and incidence metrics are useful for policy makers \citep{cohen2017mapping}.
@@
 There are two broad ways that spatial information from prevalence surveys could be included in a dissaggregation regression model of incidence.
-Firstly, the spatial information from prevalence surveys could be summarised using a seperate model and then included as a covariate in the disaggregation model.
-If the model used to summarise the prevalence surveys is explicitely spatial, this approach would make the spatial information in the prevalence data available to be used by the disaggregation model, therefore solving issue (1) above.
+Firstly, the spatial information from prevalence surveys could be summarised using a separate model and then included as a covariate in the disaggregation model.
+If the model used to summarise the prevalence surveys is explicitly spatial, this approach would make the spatial information in the prevalence data available to be used by the disaggregation model, therefore solving issue (1) above.
 However, this approach does not provide additional degrees of freedom in order to more accurately learn relationships between malaria risk and the environment and therefore does not solve issue (2).
@@
 In contrast, routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$ over a period of time (e.g., a year) during which individuals can have multiple malaria infections.
-%One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \citep{cameron2015defining}.
+%One approach to combining these datasets is to use a separately estimated model that maps one scale to another such as \citep{cameron2015defining}.
 
@@
 The first model fits a Gaussian process to prevalence point surveys then uses predictions from this model as a covariate in the disaggregation model.
-Secondly, we formulate a joint model that combines polygon incidence data and prevalence point-surveys using seperate likelihoods for both data types.
+Secondly, we formulate a joint model that combines polygon incidence data and prevalence point-surveys using separate likelihoods for both data types.
 We relate the differing malariometric measures by using a previously estimated relationship within the model \citep{cameron2015defining} which is then adjusted as part of the model fitting process.
@@
 \begin{table}
-\caption{\label{table1}Summary of out-of-sample accuracy for all three cross-validation experiments.
+\caption{\label{table1}
+Summary of out-of-sample accuracy for all three cross-validation experiments. 
 Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.}
@@
 This implies there is a strong bias (given the prevalence to incidence model) between the prevalence and incidence data in Senegal.
-Furthermore, the standard deviation of the prevalence point iid effect, $w_b(\sigma_w)$, is much larger in Indonesia (mean $\omega_w = -2.6$, sd $\omega_w = 0.09$ which corresponds to $\sigma_w$ = 13.46) than in Senegal (mean $\omega_w = -1.03$, sd $\omega_w = 0.13$ which corresponds to $\sigma_w$ = 2.80) or Madagascar (mean $\omega_w = -0.77$, sd $\omega_w = 0.11$ which corresponsed to $\sigma_w$ = 2.16).
+Furthermore, the standard deviation of the prevalence point iid effect, $w_b(\sigma_w)$, is much larger in Indonesia (mean $\omega_w = -2.6$, sd $\omega_w = 0.09$ which corresponds to a mean of $\sigma_w$ of 13.46) than in Senegal (mean $\omega_w = -1.03$, sd $\omega_w = 0.13$ which corresponds to a mean of $\sigma_w$ of 2.80) or Madagascar (mean $\omega_w = -0.77$, sd $\omega_w = 0.11$ which corresponds to a mean of $\sigma_w$ of 2.16).
 This implies there is a lot of noise in the prevalence data in Indonesia.

### 2019-08-04 ms.tex
Continue adding dan edits

@@
 
-\usepackage[authoryear]{natbib}
+%\usepackage[authoryear]{natbib}
 
@@
 However, traditional mapping using prevalence point-surveys are often ineffective in low prevalence areas due to low statistical power and a lack of data.
-More recently, disaggregation regression models have been developed that can estimate risk at high spatial resolution from surveillance data that reports incidence aggregated to a geographic polygon.
+More recently, disaggregation regression models have been developed that can estimate risk at high spatial resolution from routine surveillance reports incidence aggregated to administrative unit polygon.
 However, there is generally low spatial overlap between prevalence point-surveys and polygon incidence data and therefore models that make use of the spatial information from prevalence point surveys have great potential.
-Here, using case studies in Indonesia, Senegal and Madagascar, we compare two methods for incorporating this spatial information into a disaggregation regression model.
+U sing case studies in Indonesia, Senegal and Madagascar, we compare two methods for incorporating point-level, spatial information into a disaggregation regression model.
 The first is a simple model that fits a Gaussian random field to prevalence point-surveys and then uses predictions from the random field as a covariate in the disaggregation regression model.
 The second is a more complex, multi-likelihood model that jointly fits a model using prevalence point-surveys and  polygon incidence data.
-We find that the simple model generally performs better than a baseline disaggregation model while the joint model sometimes performs better than baseline but often worse.
+We find that the simple model generally performs better than a baseline disaggregation model while the joint model performance was mixed.
 Our results demonstrate that a simple method can be used to combine spatial information from prevalence point-surveys and polygon incidence data and that more generally, combining these types of data improves estimates of malaria incidence.
@@
 
+% Glossary
 % Use "Eq" instead of "Equation" for equation citations.
@@
 
-% Glossary
 % Models:
@@
 
-Global malaria incidence has decreased dramatically over the last 20 years \citep{abajobir2017global, bhatt2015effect}.
-This decrease has been accompanied by a strategic shift towards aiming for elimination in low incidence countries \citep{world2016world, newby2016path}.
-Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases \citep{sturrock2016mapping, cohen2017mapping}.
-However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \citep{gething2011new, bhatt2017improved, gething2012long, bhatt2015effect} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \citep{sturrock2016mapping, sturrock2014fine}.
+Global malaria incidence has decreased dramatically over the last 20 years \citep{bhatt2015effect, weiss2019mapping, battle2019mapping}.
+This decrease has been accompanied by a strategic shift aiming for elimination in low incidence countries \citep{world2016world, newby2016path}.
+Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases as they highlight areas with ongoing \emph{Plasmodium} transmission most in need of interventions \citep{sturrock2016mapping, cohen2017mapping}.
+Mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \citep{gething2011new, bhatt2017improved, gething2012long, bhatt2015effect} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \citep{sturrock2016mapping, sturrock2014fine}.
 In low burden areas, very large sample sizes are needed before a prevalence survey is informative because so few individuals have parasitaemia that most sample points will have no cases.
-Routine surveillance data, of malaria case counts, is becoming more widely available and of better quality \citep{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
-This polygon incidence data can be more sensitive than prevalence point-surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \citep{cibulskis2011worldwide}.
+However, the availability and quality of routine surveillance data of malaria case counts, typically aggregated administrative unit polygons, is improving, thus providing an alternative data source for mapping malaria burden \citep{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
+Advantageously, the routine surveillance data can be more sensitive than prevalence point-surveys in low transmission areas because the entire public health system is being used to passively monitor disease risk \citep{cibulskis2011worldwide}.
+
 Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level, routine surveillance records of incidence \citep{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
-
-%Despite major reductions in incidence over the last fifteen years, malaria still causes millions of deaths and loads of DALYs annually \citep{abajobir2017global}.
-%Elimination of malaria, country-by-county has become a central goal in the global malaria strategy \citep{world2016world}.
-%Elimination of malaria requires high resolution maps of malaria risk, in low prevalence areas in order to optimise interventions and minimise costs \citep{sturrock2016mapping}.
-
-%cohen2017mapping Different metrics are useful for different things. Most maps use prevalence. Govts do use maps.
-
-%however surveillance data is sometimes high quality in these areas
-%pixel level maps from aggregates data is difficult (sturrock2014fine, wilson2017pointless, law2018variational, others)
-%not much information for covariates 
-%sturrock used two.
-%undeveloped area of statistics but see Leon.
-
-However using only polygon-level incidence data to estimate malaria risk, and ignoring prevalence survey data, presents at least three noteworthy areas where improvements are possible. 
-(1) There are often some areas with better coverage of prevalence surveys than polygon incidence data.
-This is particularly true when modelling at continental scales \citep{weiss2019mapping, battle2019mapping}.
-%Disaggregation models aim to estimate high-resolution maps from aggregated data and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
-(2) The aggregation of cases over space means that it may be difficult to learn relationships between malaria risk and the environment from aggregated incidence data, especially if the case counts are aggregated over large or heterogeneous areas.
-(3) Finally, estimates of both prevalence and incidence metrics are useful for policy makers \citep{cohen2017mapping}.
-Typically models are fitted to observations of one metric and then a secondary model is used to convert to the other metric \emph{post hoc} \citep{battle2019mapping, bhatt2015effect}.
-This misses an opportunity to learn the relationship between prevalence and incidence at the same time as fitting the geographic model.
+The intent of this research is to assess the utility of extending disaggregation regression approaches to model mapping malaria incidence using both point- and polygon-level response data. 
+In particular focuses on two noteworthy aspects where improvements in  the disaggregation regression may be possible:
+(1) for modelling in low-burden areas with better coverage of prevalence surveys than polygon incidence data; and
+(2) for building the statistical relationships between the response and geospatial predictor data in heterogeneous landscapes.
+An ancillary benefit of a hybridized approach is that it will simultaneously produce estimates of both prevalence and incidence metrics, which may both be useful for policy makers \emph{cohen2017mapping}.
+Typically models are fitted to observations of one metric and then a secondary model is used to convert between prevalence and incidence \emph{post hoc} \citep{battle2019mapping, bhatt2015effect}, thus missing an opportunity to learn the relationship between prevalence and incidence at the same time as fitting the geographic model.
 
@@
 
+\end{figure}
+
+\begin{figure}[h!]
+% to be removed before submission
+\makebox{\includegraphics[width = 0.8\textwidth]{figures/idn_both_cv12_preds.png}}
+\caption{\label{predobsmapidn}
+Incidence data and predicted incidence maps.
+The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
+}
 \end{figure}
@@
 However, the joint model clearly performs better in Madagascar with the polygon only model unable to predict high incidence observations accurately.
-Out-of-sample predictions, under spatial cross validation, from the prevalence GP model and full joint model can be seen in Figures~\ref{predobsmapsen} and \ref{predobsmapmdg}.
+Out-of-sample predictions, under spatial cross validation, from the prevalence GP model and full joint model can be seen in Figures~\ref{predobsmapsen} -- \ref{predobsmapidn}.
 

### 2019-08-04 ms.tex
Almost finish dan edits.

@@
 However, there is generally low spatial overlap between prevalence point-surveys and polygon incidence data and therefore models that make use of the spatial information from prevalence point surveys have great potential.
-U sing case studies in Indonesia, Senegal and Madagascar, we compare two methods for incorporating point-level, spatial information into a disaggregation regression model.
+Using case studies in Indonesia, Senegal and Madagascar, we compare two methods for incorporating point-level, spatial information into a disaggregation regression model.
 The first is a simple model that fits a Gaussian random field to prevalence point-surveys and then uses predictions from the random field as a covariate in the disaggregation regression model.
@@
 There are two broad ways that spatial information from prevalence surveys could be included in a dissaggregation regression model of incidence.
-Firstly, the spatial information from prevalence surveys could be summarised using a separate model and then included as a covariate in the disaggregation model.
-If the model used to summarise the prevalence surveys is explicitly spatial, this approach would make the spatial information in the prevalence data available to be used by the disaggregation model, therefore solving issue (1) above.
-However, this approach does not provide additional degrees of freedom in order to more accurately learn relationships between malaria risk and the environment and therefore does not solve issue (2).
-Furthermore, it does not allow joint predictions of incidence and prevalence from a single model and so does not solve issue (3).
-This broad approach of summarising the information in a different data set using a separate model has previously been used in a number of contexts such as including information on animal hosts \citep{shearer2016estimating} or summarising temperature suitability of malaria parasites \citep{weiss2014air} and using this in models of malaria prevalence \citep{bhatt2015effect, weiss2019mapping}.
-However, previous uses have not typically summarised the spatial component of the secondary response data.
+Firstly, the information from prevalence surveys could be summarised using a separate model and then included as a covariate in the disaggregation model.
+If the model used to summarise the prevalence surveys is explicitly spatial, this approach would make the spatial information in the prevalence data available to be used by the disaggregation model, thereby enhancing the model’s ability to spatially disaggregate polygon-level cases within administrative units.
+However, this approach does not provide additional degrees of freedom in order to more accurately learn relationships between malaria risk and the environment, nor does it allow joint predictions of incidence and prevalence from a single model.
+This broad approach of summarising the information in a different data set using a separate model has previously been used in a number of contexts, including information on animal hosts \citep{shearer2016estimating} or summarising temperature suitability of malaria parasites \citep{weiss2014air}, which subsequently were used as inputs for modeling malaria prevalence \citep{bhatt2015effect, weiss2019mapping}.
 
-Fully combining observations of incidence and prevalence in a joint model, with multiple likelihoods, has the potential to alleviate all three of the above issues.
-As the prevalence surveys are directly used as response data, issue (1) is solved.
-Similar, as the additional data are being used as response data, they are providing additional degrees of freedom with which to learn relationships between malaria risk and the environment, therefore solving issue (2).
-Finally, such a model could also learn the relationship between different metrics at the same time as making spatial estimates.
-Therefore, a full joint model has the potential to solve issue (3) as well.
+Fully combining observations of incidence and prevalence in a joint model, with multiple likelihoods, addresses the limitations of a simple model wherein we use a prevelance map as a covariate.
+Advantageously, as the additional response data are being used as response data, they provide more degrees of freedom with which to learn relationships between malaria risk and the environment.
+Such a model can also learn the relationship between different types of malaria response metrics at the same time as making spatial estimates, thereby producing statistically consistent outputs for both incidence and prevalence.
 While a joint model provides the opportunity to learn the relationship between prevalence and incidence, this is technically challenging as these two data types measure disease intensity on different scales.
 Point surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ that quantify parasite rate during a short period of time.
-In contrast, routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$ over a period of time (e.g., a year) during which individuals can have multiple malaria infections.
+In contrast, routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$ over a longer period of time (e.g., a year) during which individuals can have multiple malaria infections.
 %One approach to combining these datasets is to use a separately estimated model that maps one scale to another such as \citep{cameron2015defining}.
@@
 
+%Firstly, the spatial information from prevalence surveys could be summarised using a separate model and then included as a covariate in the disaggregation model.
+% If the model used to summarise the prevalence surveys is explicitly spatial, this approach would make the spatial information in the prevalence data available to be used by the
+
 Here we compare two methods for using spatial information from prevalence surveys to inform a disaggregation model fitted to polygon incidence data of \emph{Plasmodium falciparum}  malaria.
-The first model fits a Gaussian process to prevalence point surveys then uses predictions from this model as a covariate in the disaggregation model.
+The first, simpler, model summarises the spatial information in the prevalence point surveys by fitting a spatial Gaussian process model to the surveys.
+Predictions from this model are then used as an additional covariate in the disaggregation model.
 Secondly, we formulate a joint model that combines polygon incidence data and prevalence point-surveys using separate likelihoods for both data types.
@@
 We used two data sources that reflect malaria burden; prevalence point-surveys and polygon incidence data.
-We selected Indonesia, Senegal and Madagascar as case examples as they all have abundant subnational surveillance data and country wide surveys from approximately the same period.
-To minimise temporal effects we selected one year of polygon incidence data and the surrounding five years of prevalence point-survey data for each country.
-For Indonesia we selected polygon incidence data from 2012 that covers 379 regions, and prevalence data from 2010 to 2014 that consists of 1,233 surveys, representing 230,747 individuals.
-For Senegal we selected 2015 for polygon incidence data (41 regions) and 2013 to 2017 for prevalence data (804 surveys, 17,037 individuals).
-Finally, for Madagascar we selected 2013 for polygon incidence (110 regions) and 2011 to 2015 for prevalence data (1,049 surveys, 36,411 individuals).
-
-\subsection*{Prevalence survey data}
-
+Prevalence point surveys consist of geo-located household survey clusters wherein all sampled children are tested for malaria and the positive cases as well as the total number of children tested is recorded.
+Polygon incidence data is aggregated by administrative-level, typically by governmental organizations tasked with collating and summarizing data reported from hospitals. 
+Unlike the point data, polygon-level incidence only includes the number of cases and not the number of people relying on that unit’s healthcare facilities.  
+As such, to determine an incidence rate we rely on gridded population surfaces, summarized for using the administrative unit’s boundaries, to provide the denominator. 
 The prevalence point-survey data were extracted from the Malaria Atlas Project prevalence survey database  \citep{bhatt2015effect, guerra2007assembling, pfeffer2018ma}. 
@@
 The age standardisation model gives the surveys with zero positive cases a small positive prevalence. 
-
-\subsection*{Polygon incidence data}
-
-% (Figures~\ref{predobsmapidn}A and \ref{predobsmapsen}A)
-
 The polygon incidence data were collated from various government reports and adjusted to a standard metric using methods defined in \citep{cibulskis2011worldwide, weiss2019mapping}. 
@@
 These adjustments are uniform across each country. 
-The polygon incidence data for Senegal and Madagascar can be seen in Figures~\ref{predobsmapsen}A and \ref{predobsmapmdg}A).
+The polygon incidence data can be seen in Figures~\ref{predobsmapsen}--\ref{predobsmapidn}.
+
+We selected Indonesia, Senegal and Madagascar as case examples as they all have abundant subnational surveillance data and country wide surveys from approximately the same period.
+To minimise temporal effects we selected one year of polygon incidence data and the surrounding five years of prevalence point-survey data for each country.
+For Indonesia we selected polygon incidence data from 2012 that covers 379 regions, and prevalence data from 2010 to 2014 that consists of 1,233 surveys, representing 230,747 individuals.
+For Senegal we selected 2015 for polygon incidence data (41 regions) and 2013 to 2017 for prevalence data (804 surveys, 17,037 individuals).
+Finally, for Madagascar we selected 2013 for polygon incidence (110 regions) and 2011 to 2015 for prevalence data (1,049 surveys, 36,411 individuals).
 
@@
 
-We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres at the equator that included land surface temperature annual mean and standard deviation \citep{LST}, enhanced vegetation index \citep{TCB}, mosquito temperature suitability index \citep{weiss2014air}, elevation \citep{SRTMElev}, tassel cap brightness \citep{TCB}, tassel cap wetness \citep{TCB}, accessibility to cities \citep{weiss2018global}, night lights \citep{elvidge2017viirs} and proportion of urban land cover \citep{GUF}.
+We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres at the equator that included land surface temperature annual mean and standard deviation, enhanced vegetation index (EVI), \emph{P.
+falciparum} temperature suitability index \citep{weiss2014air}, elevation \citep{SRTMElev}, tassel cap brightness, tassel cap wetness, accessibility to cities \citep{weiss2018global}, night lights \citep{elvidge2017viirs} and proportion of urban land cover \citep{GUF}.
 % change to table
+The land surface temperature, EVI, and tasseled cap indices were derived from satellite imagery and gap-filled to remove missing data caused by factors like cloud-cover \citep{weiss2014effective} and rescaled to a spatial resolution of approximately 5x5km \citep{weiss2015re} that defined the output of the final prevalence and incidence maps.
 Some covariates were log-transformed to remove skewness or removed due to multicollinearity with other predictor variables using the threshold of 0.8.
@@
 We used different $\zeta$  and $\xi$ values for each country: Indonesia $\zeta = 3, \xi = 1$, Senegal $\zeta = 1, \xi = 0.5$ and Madagascar $\zeta = 1, \xi = 1$.
-We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \citep{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.
+We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected at the scale of individual countries \citep{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.
 As Senegal has a lower range of incidences in the data we set $\xi$ to a smaller value for this country.
@@
 In contrast to the random cross-validation results, the differences between models is quite strong.
-Furthermore, notable difference can be seen in the scattor plots of observed and predicted values (Figure \ref{spatial2predobspolyfacet}).
+Furthermore, notable difference can be seen in the scatter plots of observed and predicted values (Figure \ref{spatial2predobspolyfacet}).
 In Indonesia it can be seen the the joint model is more strongly biased at low incidence values with many data points being overpredicted.
-However, the joint model clearly performs better in Madagascar with the polygon only model unable to predict high incidence observations accurately.
+However, the joint model clearly performs better in Madagascar with the polygon-only model unable to predict high incidence observations accurately.
 Out-of-sample predictions, under spatial cross validation, from the prevalence GP model and full joint model can be seen in Figures~\ref{predobsmapsen} -- \ref{predobsmapidn}.
@@
 Therefore, fitting a spatial Gaussian process to prevalence points and including these predictions seems to be a more reliable way of using spatial information from prevalence points.
+ However, given this comparison was conducted using only three countries it is challenging to draw firm conclusions.
 
@@
 Therefore it is worth considering why the performance of this model was generally less good than the simpler prevalence GP model that did not benefit from the additional degrees of freedom.
-There are two main reasons why a model fitted jointly on prevalence point-surveys and polygon incidence data may perform worse than a model that does not use prevalence surveys as additional response data.
-Firstly, the data are on different scales.
+One potential reason is that the malariometric data are on different scales.
 Here we have used a previously fitted model \citep{cameron2015defining} in order to be able to fit the joint model.
-However, this model is imperfect in that it is calibrated with a relatively small amount of matched prevalence and incidence data.
+However, this model was calibrated using relatively few matched prevalence and incidence surveys as few of these have been conducted and published.
 Although we have added the parameter $\alpha$ that scales this relationship, it is a very simple scaling.
-Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality and age-structure are not constant \citep{cameron2015defining, battle2015defining, reiner2015seasonality}.
-In using a joint model we are accepting these failings in the hope that the benefits of including additional data are stronger than the costs of using mismatched data.
-The second aspect of prevalence point-survey data that could reduce the predictive ability of a polygon-only model by adding point data is if the point data is of low quality.
-In particular, non-random sampling of individuals can produce biased estimates of prevalence and this will decrease model performance.
+Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality, and population age-structure are not constant \citep{cameron2015defining, battle2015defining, reiner2015seasonality}.
+In using a joint model we are accepting these failings in the hope that the benefits of including additional data outweigh the costs of using mismatched data.
 
-For a model to be robust to shortcomings in the prevalence-incidence relationship from \citep{cameron2015defining}, future models could be more flexible in the way they use this relationship.
+Future models could potentially be improved by using a more flexible approach for addressing the shortcomings in the prevalence-incidence relationship from \citep{cameron2015defining}.
 This could be by estimating the parameters of the polynomial jointly with the rest of the model.
 Informative priors based on the original model should be used to regularise this joint fit both to prevent unbelievable inferences but also because if the relationship is too flexible, the information from the prevalence data might not contribute to learning the regression parameters and spatial random field.
-This is particularly true for even more flexible model forms that could be used such as a spline or a Gaussian process on the relationship between prevalence and incidence.
+This is particularly true for model forms such as a spline or a Gaussian process on the relationship between prevalence and incidence.
 
+The second aspect of prevalence point-survey data that could reduce the predictive ability of a polygon-only model by adding point data is if that the point data is of low utility, particularly if they captured few cases due (i.e., if most of the response data were zeros).
+This issue is noteworthy as organizations conducting the surveys typically collect a very wide range of data and are not designed to produce inputs tailored for malaria burden mapping. 
 For the model to handle noisy or biased prevalence point-surveys, the modeller can control the iid random effect on the point-surveys, $w_b$ and the prevalence-only intercept $\beta_p$. 
@@
 
-Here we have used purely linear covariates.
-It has been clearly established that simple linear combinations of environmental covariates cannot fully explain malaria risk \citep{bhatt2017improved}.
+In this research we have used only linear covariates but previous work has demonstrated that simple linear combinations of environmental covariates cannot fully explain malaria risk \citep{bhatt2017improved}.
 A number of methods could be used to include non-linear effects of covariates and interactions into the model.
-Firstly, as in \citep{bhatt2017improved}, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model.
+Firstly, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model \citep{bhatt2017improved}.
 This approach is feasible but does not allow any information from the polygons to inform non-linear relationships.
@@
 Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \citep{law2018variational}.
-These are computational expensive without variational Bayes or other approximations \citep{law2018variational, ton2018spatial} which can be difficult to derive.
-Again these models need a lot of data and careful regularisation for good predictive performance.
+Unfortunately, each of these options is computationally expensive without variational Bayes or other approximations \citep{law2018variational, ton2018spatial}, which can be difficult to derive.
+Additionally these models require a large volume of response data and careful regularisation for good predictive performance.
 
@@
 In contrast, summarising the spatial information from the prevalence surveys by fitting a spatial Gaussian process model and using predictions from this model as a new covariate nearly always improved predictive performance.
-As disaggregation regression becomes more widely used \citep{weiss2019mapping, battle2019mapping}, methods such as these to improve their performance are particularly needed
+As disaggregation regression becomes more widely used \citep{weiss2019mapping, battle2019mapping}, methods such as these should be utilized to improve modelled results where and when the requisite data are available.
 

### 2019-08-05 ms.tex
Ewans notation comments.

@@
 
-$$y_a \sim \operatorname{Pois}(i_a\mathrm{pop_a})$$
+$$y_a \sim \operatorname{Poisson}(i_a\mathrm{pop_a})$$
 
@@
 The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
-The iid random effect, $v_a \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $j$ being grouped together.
+The iid random effect, $v_a \sim \operatorname{Normal}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $j$ being grouped together.
 Internally, this effect is parameterised as the log of the precision, $\omega_v = \log(\tau_v) = \log(\frac{1}{{\sigma_v}^2})$ to improve numeric stability.
@@
 Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho, \sigma_u$ and $\sigma_v$.
-The intercept was given a wide prior, $b_0 \sim \operatorname{Norm}(-2, 4)$ with a mean less than zero as we know \emph{a priori} that these countries have low or medium levels of malaria transmission.
-We set independant, regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
+The intercept was given a wide prior, $b_0 \sim \operatorname{Normal}(-2, 4)$ with a mean less than zero as we know \emph{a priori} that these countries have low or medium levels of malaria transmission.
+We set independant, regularising priors on the regression coefficients $\beta_i \sim \operatorname{Normal}(0, 0.04)$. 
 Given the standardised covariates, an intercept of -3 and a regression coefficient from the 95\% interquartile range of this distribution, each covariate would be able to predict prevalences between 0.004 and 0.27.
@@
 
-$$z_b \sim \operatorname{Binom}(p_b, n_b) $$
+$$z_b \sim \operatorname{Binomial}(p_b, n_b) $$
 where $p_b$ is the estimated prevalence and $n_b$ is the observed survey sample size. 
@@
 The iid random effect, $v_a \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point surveys within polygon $a$ being in the same group as polygon $a$.
-The second iid random effect, $w_b \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
+The second iid random effect, $w_b \sim \operatorname{Normal}(0, \sigma_w)$, was applied to each point survey.
 To improve numeric stability this effect is also parameterised internally as the log of the precision, $\omega_w = \log(\tau_w) = \log(\frac{1}{{\sigma_w}^2})$.
@@
 Therefore, our prior belief is that $\exp(\alpha)$ is close to one (i.e.\thinspace the relationship remains unchanged) and therefore that $\alpha$ is close to zero.
-We set our prior as $\alpha \sim \operatorname{Norm}(0, 0.001)$.
+We set our prior as $\alpha \sim \operatorname{Normal}(0, 0.001)$.
 

### 2019-08-05 ms.tex
Fix authors but need to check.
Fix last dan edit. Closes #4

@@
 \email{timcdlucas@gmail.com}
-\author{Anita Nandi}
+\author{Anita K. Nandi}
 \address{Big Data Institute,
@@
 UK.}
-\author{Rosalind Howes}
+\author{Rosalind E. Howes}
 \address{Big Data Institute,
@@
 UK.}
+\author{Punam Amratia}
+\address{Big Data Institute,
+University of Oxford,
+Oxford,
+UK.}
 \author{Ewan Cameron}
@@
 UK.}
-\author{Pete Gething}
+\author{Pete W. Gething}
 \address{Big Data Institute,
@@
 More recently, disaggregation regression models have been developed that can estimate risk at high spatial resolution from routine surveillance reports incidence aggregated to administrative unit polygon.
-However, there is generally low spatial overlap between prevalence point-surveys and polygon incidence data and therefore models that make use of the spatial information from prevalence point surveys have great potential.
+However, in areas with both routine surveillance data and prevalence surveys, models that make use of the spatial information from prevalence point surveys have great potential.
 Using case studies in Indonesia, Senegal and Madagascar, we compare two methods for incorporating point-level, spatial information into a disaggregation regression model.
@@
 The intent of this research is to assess the utility of extending disaggregation regression approaches to model mapping malaria incidence using both point- and polygon-level response data. 
-In particular focuses on two noteworthy aspects where improvements in  the disaggregation regression may be possible:
+In particular it focuses on two noteworthy aspects where improvements in  the disaggregation regression may be possible:
 (1) for modelling in low-burden areas with better coverage of prevalence surveys than polygon incidence data; and
 (2) for building the statistical relationships between the response and geospatial predictor data in heterogeneous landscapes.
-An ancillary benefit of a hybridized approach is that it will simultaneously produce estimates of both prevalence and incidence metrics, which may both be useful for policy makers \emph{cohen2017mapping}.
+An ancillary benefit of a hybridized approach is that it will simultaneously produce estimates of both prevalence and incidence metrics, which may both be useful for policy makers \citep{cohen2017mapping}.
 Typically models are fitted to observations of one metric and then a secondary model is used to convert between prevalence and incidence \emph{post hoc} \citep{battle2019mapping, bhatt2015effect}, thus missing an opportunity to learn the relationship between prevalence and incidence at the same time as fitting the geographic model.

### 2019-08-06 ms.tex
Add author summary and keywords.

@@
 \end{abstract}
+
+\section{Summary}
+
+We present a comparison of two methods for combining malaria prevalence surveys and aggregated incidence count data using case studies in Indonesia, Senegal and Madagascar. 
+The first method fits a spatial Gaussian random field to the prevalence data which is then used as a covariate in a disaggregation regression model.
+The second is a full joint model that simultaneously fits a disaggregation regression model to the incidence data and prevalence surveys.
+We compare both models to a baseline disaggregation regression model and find that the simpler model works the best.
+
+\subsection{Keywords}
+Disaggregation regression, disease mapping, geostatistics, joint modelling, spatial statistics.
 

### 2019-08-06 ms.tex
Fix authors.
Shorten abstract.

--- 2019-08-05 ms.tex
@@
 \email{timcdlucas@gmail.com}
-\author{Anita K. Nandi}
-\address{Big Data Institute,
+\author{Anita K. Nandi\textsuperscript{1}}
+\author{Michele Nguyen\textsuperscript{1}}
+\author{Susan Rumisha\textsuperscript{1}}
+\author{Rosalind E. Howes}
+\author{Katherine E. Battle\textsuperscript{1}}
+\author{Penelope Hancock\textsuperscript{1}}
+\author{Punam Amratia\textsuperscript{1}}
+\author{Suzanne H. Keddie\textsuperscript{1}}
+\author{Emma L. Collins\textsuperscript{1}}
+\author{Andre Python\textsuperscript{1}}
+\author{Elisabeth G. Chestnutt\textsuperscript{1}}
+\author{Katherine A. Twohig\textsuperscript{1}}
+\author{Ewan Cameron\textsuperscript{1}}
+\author{Pete W. Gething\textsuperscript{1, 2, 3}}
+\author{Daniel J. Weiss\textsuperscript{1}}
+\address{1. Big Data Institute,
 University of Oxford,
@@
 UK.}
-\author{Michele Nguyen}
-\address{Big Data Institute,
-University of Oxford,
-Oxford,
-UK.}
-\author{Susan Rumisha}
-\address{Big Data Institute,
-University of Oxford,
-Oxford,
-UK.}
-\author{Rosalind E. Howes}
-\address{Big Data Institute,
-University of Oxford,
-Oxford,
-UK.}
-\author{Katherine E. Battle}
-\address{Big Data Institute,
-University of Oxford,
-Oxford,
-UK.}
-\author{Penelope Hancock}
-\address{Big Data Institute,
-University of Oxford,
-Oxford,
-UK.}
-\author{Andre Python}
-\address{Big Data Institute,
-University of Oxford,
-Oxford,
-UK.}
-\author{Punam Amratia}
-\address{Big Data Institute,
-University of Oxford,
-Oxford,
-UK.}
-\author{Ewan Cameron}
-\address{Big Data Institute,
-University of Oxford,
-Oxford,
-UK.}
-\author{Pete W. Gething}
-\address{Big Data Institute,
-University of Oxford,
-Oxford,
-UK.}
-\author{Daniel J. Weiss}
-\address{Big Data Institute,
-University of Oxford,
-Oxford,
-UK.}
+\address{2. Telethon Kids Institute, Perth Children’s Hospital, Perth, Australia}
+\address{3. Curtin University, Perth, Australia}
 
@@
 As malaria incidence decreases and more countries move towards elimination, maps of malaria risk in low prevalence areas are becoming increasingly needed.
-However, traditional mapping using prevalence point-surveys are often ineffective in low prevalence areas due to low statistical power and a lack of data.
-More recently, disaggregation regression models have been developed that can estimate risk at high spatial resolution from routine surveillance reports incidence aggregated to administrative unit polygon.
+For low burden areas, disaggregation regression models have been developed to estimate risk at high spatial resolution from routine surveillance reports of incidence aggregated to administrative unit polygons.
 However, in areas with both routine surveillance data and prevalence surveys, models that make use of the spatial information from prevalence point surveys have great potential.
-Using case studies in Indonesia, Senegal and Madagascar, we compare two methods for incorporating point-level, spatial information into a disaggregation regression model.
-The first is a simple model that fits a Gaussian random field to prevalence point-surveys and then uses predictions from the random field as a covariate in the disaggregation regression model.
-The second is a more complex, multi-likelihood model that jointly fits a model using prevalence point-surveys and  polygon incidence data.
+Using case studies in Indonesia, Senegal and Madagascar, we compare two methods for incorporating point-level, spatial information into disaggregation regression models.
+The first simply fits a Gaussian random field to prevalence point-surveys to create a new covariate.
+The second is a multi-likelihood model that jointly fits a model using prevalence point-surveys and polygon incidence data.
 We find that the simple model generally performs better than a baseline disaggregation model while the joint model performance was mixed.
-Our results demonstrate that a simple method can be used to combine spatial information from prevalence point-surveys and polygon incidence data and that more generally, combining these types of data improves estimates of malaria incidence.
+More generally, our results demonstrate that combining these types of data improves estimates of malaria incidence.
 \end{abstract}
+
+\subsection{Keywords}
+Disaggregation regression, disease mapping, geostatistics, joint modelling, spatial statistics.
 

### 2019-08-06 si.tex
Tidy up.

@@
 \makebox{\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_random_preds.png}}
-\caption{\label{predobsmapsen}
+\caption{\label{predobsmapsen1}
 Incidence data and predicted incidence maps.
@@
 \makebox{\includegraphics[width = 0.9\textwidth]{figures/mdg_both_cv12_random_preds.png}}
-\caption{\label{predobsmapsen}
+\caption{\label{predobsmapsen2}
 Incidence data and predicted incidence maps.
@@
 \makebox{\includegraphics[width = 1\textwidth]{figures/sen_both_cv12_random_preds.png}}
-\caption{\label{predobsmapsen}
+\caption{\label{predobsmapsen3}
 Incidence data and predicted incidence maps.
 The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for random cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
-}
-\end{figure}
-
-\clearpage
-\subsection{Spatial CV predictions}
-
-\begin{figure}[h!]
-% to be removed before submission
-\makebox{\includegraphics[width = 0.8\textwidth]{figures/idn_both_cv12_preds.png}}
-\caption{\label{predobsmapsen}
-Incidence data and predicted incidence maps.
-The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
 }
@@
 \caption{Predictions from the baseline model fitted to all data in Madagascar.}
+\label{baselinemdg}
 \end{figure}
@@
 \caption{Predictions from the prevalence GP model fitted to all data in Madagascar.}
+\label{gpmdg}
 \end{figure}
@@
 \caption{Predictions from the joint model fitted to all data in Madagascar.}
+\label{jointmdg}
 \end{figure}
@@
 \caption{Predictions from the baseline model fitted to all data in Senegal.}
+\label{baselinesen}
 \end{figure}
@@
 \caption{Predictions from the prevalence GP model fitted to all data in Senegal.}
+\label{gpsen}
 \end{figure}
@@
 \caption{Predictions from the joint model fitted to all data in Senegal.}
+\label{jointsen}
 \end{figure}
@@
 \caption{Predictions from the baseline model fitted to all data in Indonesia.}
+\label{baselineidn}
 \end{figure}
@@
 \caption{Predictions from the prevalence GP model fitted to all data in Indonesia.}
+\label{gpidn}
 \end{figure}
@@
 \caption{Predictions from the joint model fitted to all data in Indonesia.}
+\label{jointidn}
 \end{figure}
@@
 \caption{The prevalence GP model that is used as a covariate.}
+\label{gpsencov}
 \end{figure}
@@
 \caption{The random field as fitted to all the data in the baseline model.}
+\label{baselinefieldsen}
 \end{figure}
@@
 \caption{The random field as fitted to all the data in the prevalence GP model.}
+\label{gpfieldsen}
 \end{figure}
@@
 \caption{The random field as fitted to all the data in the joint model.}
+\label{jointfieldsen}
 \end{figure}
@@
 \caption{The prevalence GP model that is used as a covariate.}
+\label{gpidncov}
 \end{figure}
@@
 \caption{The random field as fitted to all the data in the joint model.}
+\label{baselinefieldidn}
 \end{figure}
@@
 \caption{The random field as fitted to all the data in the joint model.}
+\label{gpfieldidn}
 \end{figure}
@@
 \caption{The random field as fitted to all the data in the joint model.}
+\label{jointfieldidn}
 \end{figure}
@@
 \caption{The prevalence GP model that is used as a covariate.}
+\label{gpmdgcov}
 \end{figure}
@@
 \caption{The random field as fitted to all the data in the baseline model.}
+\label{baselinefieldmdg}
 \end{figure}
@@
 \caption{The random field as fitted to all the data in the prevalence GP model.}
+\label{gpfieldmdg}
 \end{figure}

### 2019-08-23 ms.tex
More ref and author mess about.
Do KT edits and dont use xr cos it aint working.

@@
 
-\usepackage{xr}
-\externaldocument{si}
-
 \usepackage[hidelinks]{hyperref}
@@
 \author{Anita K. Nandi\textsuperscript{1}}
+\author{Elisabeth G. Chestnutt\textsuperscript{1}}
+\author{Katherine A. Twohig\textsuperscript{1}}
+\author{Suzanne H. Keddie\textsuperscript{1}}
+\author{Emma L. Collins\textsuperscript{1}}
+\author{Rosalind E. Howes}
 \author{Michele Nguyen\textsuperscript{1}}
 \author{Susan Rumisha\textsuperscript{1}}
-\author{Rosalind E. Howes}
-\author{Katherine E. Battle\textsuperscript{1}}
+\author{Andre Python\textsuperscript{1}}
+\author{Rohan Arambepola\textsuperscript{1}}
+\author{Amelia Bertozzi-Villa\textsuperscript{1}}
 \author{Penelope Hancock\textsuperscript{1}}
 \author{Punam Amratia\textsuperscript{1}}
-\author{Suzanne H. Keddie\textsuperscript{1}}
-\author{Emma L. Collins\textsuperscript{1}}
-\author{Andre Python\textsuperscript{1}}
-\author{Elisabeth G. Chestnutt\textsuperscript{1}}
-\author{Katherine A. Twohig\textsuperscript{1}}
+\author{Katherine E. Battle\textsuperscript{1}}
 \author{Ewan Cameron\textsuperscript{1}}
@@
 We used two data sources that reflect malaria burden; prevalence point-surveys and polygon incidence data.
-Prevalence point surveys consist of geo-located household survey clusters wherein all sampled children are tested for malaria and the positive cases as well as the total number of children tested is recorded.
-Polygon incidence data is aggregated by administrative-level, typically by governmental organizations tasked with collating and summarizing data reported from hospitals. 
+Prevalence point surveys consist of geo-located household survey clusters wherein all sampled individuals are tested for malaria and the positive cases as well as the total number of children tested is recorded.
+Polygon incidence data is aggregated by administrative-level, typically by governmental organizations tasked with collating and summarizing data reported from hospitals and health facilities. 
 Unlike the point data, polygon-level incidence only includes the number of cases and not the number of people relying on that unit’s healthcare facilities.  
-As such, to determine an incidence rate we rely on gridded population surfaces, summarized for using the administrative unit’s boundaries, to provide the denominator. 
+As such, to determine an incidence rate we rely on gridded population surfaces, summarised using the administrative unit’s boundaries, to provide the denominator. 
 The prevalence point-survey data were extracted from the Malaria Atlas Project prevalence survey database  \citep{bhatt2015effect, guerra2007assembling, pfeffer2018ma}. 
@@
 The age standardisation model gives the surveys with zero positive cases a small positive prevalence. 
-The polygon incidence data were collated from various government reports and adjusted to a standard metric using methods defined in \citep{cibulskis2011worldwide, weiss2019mapping}. 
+The polygon incidence data were collated from various government reports and adjusted to a standard metric of malaria incidence using methods defined in \citep{cibulskis2011worldwide, weiss2019mapping}.
 These adjustments account for underreporting of clinical cases due to lack of treatment seeking, missed case reports, and cases that sought medical attention outside the public health systems \citep{battle2016treatment}.
@@
 To compare the three models we used two cross-validation schemes. 
-In the first (random), the incidence data was split into ten cross-validation folds while all the prevalence data was used in each case (Figure~\ref{fig:cv_random}). 
+In the first (random), the incidence data was split into ten cross-validation folds while all the prevalence data was used in each case (Figure~S1. 
 %This cross-validation scheme directly addresses the question of whethe
-In the second validation scheme , the incidence data was split into spatial cross-validation folds, using k means clustering on polygon centroids, while again all prevalence points were used in all folds (Figure~\ref{fig:cv_spatial}).
+In the second validation scheme , the incidence data was split into spatial cross-validation folds, using k means clustering on polygon centroids, while again all prevalence points were used in all folds (Figure~S2).
 The number of folds was seven for Indonesia, five for Senegal and three for Madagascar due to their differing sizes and epidemiological settings.
@@
 
-Under the spatial cross-validation scheme, the baseline model and prevalence GP models performed equal best in Indonesia, the prevalence GP performaced best in Senegal while the joint model performed best in Madagascar (Table \ref{table1}).
+Under the spatial cross-validation scheme, the baseline model and prevalence GP models performed best in Indonesia, the prevalence GP performaced best in Senegal while the joint model performed best in Madagascar (Table \ref{table1}).
 In contrast to the random cross-validation results, the differences between models is quite strong.
@@
 A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (cases per 1,000).
-Results from the standard downscaling model are shown in red, the prevalence GP model is shown in green while the joint model is shown in blue.
+Results from the baseline disaggregation model are shown in red, the prevalence GP model is shown in green while the joint model is shown in blue.
 The one-one line is shown with a black line and a simple linear regression through the points is shown by a coloured line.
@@
 
-We can further examine why the models performed as they did by examining the parameters estimated in the models fitted to all data (Tables~\ref{parssen}--\ref{parsidn}).
+We can further examine why the models performed as they did by examining the parameters estimated in the models fitted to all data (Tables~S1--S3).
 Firstly we can compare the regression parameter for the prevalence GP covariate in the three countries noting that in Indonesia the prevalence GP model performed worse than baseline under random cross-validation and had equal performance to baseline under spatial cross-validation.
@@
 We set a strong prior on $\alpha$ being close to one, encoding our belief that the incidence prevalence relationship should be close to the previously fitted model.
-The estimated value for $\alpha$ in all three countries is very close to one (Tables~\ref{parssen}--\ref{parsidn}).
+The estimated value for $\alpha$ in all three countries is very close to one (Tables~S1--S3).
 While this might be driven by the prior, we can conclude that there is no strong evidence from the data that this relationship should be scaled differently in the different countries.
@@
 
-We have compared the predictive performance of three models: a baseline polygon-only model; a disaggregation model with spatial information from prevalence surveys included as an additional covariate from a seperate Gaussian process model; and a model that jointly learns from polygon incidence data and prevalence point-surveys.
-Overall the prevalence GP model appears to peform best.
+We have compared the predictive performance of three models: a baseline polygon-only model; a disaggregation model with spatial information from prevalence surveys included as an additional covariate from a separate Gaussian process model; and a model that jointly learns from polygon incidence data and prevalence point-surveys.
+Overall the prevalence GP model appears to perform best.
 While the joint model sometimes performs best it also performs worse than baseline half of the time.
@@
 However, given this comparison was conducted using only three countries it is challenging to draw firm conclusions.
-
-% simple model best
-% less fiddly, but none of these models are in packages
-%
 
@@
 This is particularly true for model forms such as a spline or a Gaussian process on the relationship between prevalence and incidence.
-
-The second aspect of prevalence point-survey data that could reduce the predictive ability of a polygon-only model by adding point data is if that the point data is of low utility, particularly if they captured few cases due (i.e., if most of the response data were zeros).
-This issue is noteworthy as organizations conducting the surveys typically collect a very wide range of data and are not designed to produce inputs tailored for malaria burden mapping. 
 For the model to handle noisy or biased prevalence point-surveys, the modeller can control the iid random effect on the point-surveys, $w_b$ and the prevalence-only intercept $\beta_p$. 
@@
 
+We used three case studies, limited by the number of coutnries with good aggregated incidence data as well as good prevalence survey data.
+Given the small number of case studies it is hard to determine when these methods are likely to be most effective.
+However, the greatest benefits here were seen in Madagascar, a country with more intermediate transmission intensities.
+In the future, two groups of countries might particularly benefit from the methods presented here.
+Firstly countries who have had large prevalence surveys in the past and whose reporting systems are improving, such as Ethiopia, might benefit from these methods.
+Secondly, countries who have lots of prevalence surveys and are adjacent to countries with good reporting systems, such as Papua New Guinea, might also benefit from sharing models that share information between countries.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In contrast, summarising the spatial information from the prevalence surveys by fitting a spatial Gaussian process model and using predictions from this model as a new covariate nearly always improved predictive performance.
-As disaggregation regression becomes more widely used \citep{weiss2019mapping, battle2019mapping}, methods such as these should be utilized to improve modelled results where and when the requisite data are available.
+As more countries produce reliable routine surveillance data, and as more countries reduce their malaria prevalences to the point where prevalence surveys are no longer sensitive, disaggregation regression will become more commonly used.
+Methods such as those presented here should be utilized to improve disaggregation regression results where and when the requisite data are available.
 

### 2019-08-23 ms.tex
More kt edits.

@@
 Firstly, the information from prevalence surveys could be summarised using a separate model and then included as a covariate in the disaggregation model.
-If the model used to summarise the prevalence surveys is explicitly spatial, this approach would make the spatial information in the prevalence data available to be used by the disaggregation model, thereby enhancing the model’s ability to spatially disaggregate polygon-level cases within administrative units.
+If the model used to summarise the prevalence surveys is explicitly spatial, this approach would make the spatial information in the prevalence data available to be used by the disaggregation model, thereby enhancing the ability to spatially disaggregate polygon-level cases within administrative units.
 However, this approach does not provide additional degrees of freedom in order to more accurately learn relationships between malaria risk and the environment, nor does it allow joint predictions of incidence and prevalence from a single model.
@@
 
-Fully combining observations of incidence and prevalence in a joint model, with multiple likelihoods, addresses the limitations of a simple model wherein we use a prevelance map as a covariate.
+Fully combining observations of incidence and prevalence in a joint model, with multiple likelihoods, addresses the limitations of a simple model using a prevelance map as a covariate.
 Advantageously, as the additional response data are being used as response data, they provide more degrees of freedom with which to learn relationships between malaria risk and the environment.

### 2019-08-23 ms.tex
Susan edits.
Amelia edits.

@@
 \author{Michele Nguyen\textsuperscript{1}}
-\author{Susan Rumisha\textsuperscript{1}}
+\author{Susan F. Rumisha\textsuperscript{1}}
 \author{Andre Python\textsuperscript{1}}
@@
 \author{Ewan Cameron\textsuperscript{1}}
-\author{Pete W. Gething\textsuperscript{1, 2, 3}}
+\author{Peter W. Gething\textsuperscript{1, 2, 3}}
 \author{Daniel J. Weiss\textsuperscript{1}}
@@
 The first simply fits a Gaussian random field to prevalence point-surveys to create a new covariate.
-The second is a multi-likelihood model that jointly fits a model using prevalence point-surveys and polygon incidence data.
+The second is a multi-likelihood model that is fitted jointly to prevalence point-surveys and polygon incidence data.
 We find that the simple model generally performs better than a baseline disaggregation model while the joint model performance was mixed.
@@
 In low burden areas, very large sample sizes are needed before a prevalence survey is informative because so few individuals have parasitaemia that most sample points will have no cases.
+In most cases, these large sample sizes are neither logistically nor financially feasible.
 However, the availability and quality of routine surveillance data of malaria case counts, typically aggregated administrative unit polygons, is improving, thus providing an alternative data source for mapping malaria burden \citep{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
@@
 
-We used two data sources that reflect malaria burden; prevalence point-surveys and polygon incidence data.
+We used two data sources that reflect malaria burden: prevalence point-surveys and polygon incidence data.
 Prevalence point surveys consist of geo-located household survey clusters wherein all sampled individuals are tested for malaria and the positive cases as well as the total number of children tested is recorded.
@@
 To minimise temporal effects we selected one year of polygon incidence data and the surrounding five years of prevalence point-survey data for each country.
-For Indonesia we selected polygon incidence data from 2012 that covers 379 regions, and prevalence data from 2010 to 2014 that consists of 1,233 surveys, representing 230,747 individuals.
+For Indonesia we selected polygon incidence data from 2012 that covers 379 regions, and prevalence data from 2010 to 2014 that consists of 1,233 survey clusters (i.e.
+unique locations), representing 230,747 individuals.
 For Senegal we selected 2015 for polygon incidence data (41 regions) and 2013 to 2017 for prevalence data (804 surveys, 17,037 individuals).
@@
 
-where $i_a$ is the estimated polygon incidence rate and $\mathrm{pop_a}$ is the (assumed to be) known polygon population-at-risk.
+where $i_a$ is the estimated polygon incidence rate and $\mathrm{pop_a}$ is the population-at-risk within that admin unit polygon (as apposed to the true health centre catchment area).
 
@@
 \end{figure}
+% todo add country names to plots.
 

### 2019-09-02 ms.tex
Bold vectors.

@@
 \usepackage{amsmath}
+\usepackage{bm}
 
@@
 % change to table
-The land surface temperature, EVI, and tasseled cap indices were derived from satellite imagery and gap-filled to remove missing data caused by factors like cloud-cover \citep{weiss2014effective} and rescaled to a spatial resolution of approximately 5x5km \citep{weiss2015re} that defined the output of the final prevalence and incidence maps.
+The land surface temperature, EVI, and tasseled cap indices were derived from satellite imagery and gap-filled to remove missing data caused by factors like cloud-cover \citep{weiss2014effective} and rescaled to a spatial resolution of approximately $5\times 5$km \citep{weiss2015re} that defined the output of the final prevalence and incidence maps.
 Some covariates were log-transformed to remove skewness or removed due to multicollinearity with other predictor variables using the threshold of 0.8.
@@
 
-The linear predictor is composed of an intercept, $b_0$, covariates, $X$, and a vector of regression coefficients $\beta$.
+The linear predictor is composed of an intercept, $b_0$, covariates, $X$, and a vector of regression coefficients $\boldsymbol\beta$.
 We also include a spatial, Gaussian random field, $u(s, \rho, \sigma_u)$ and a polygon-level iid random effect, $ v_a(\sigma_v)$.
-$$\eta_b = \beta_0 + \beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) $$
+$$\eta_b = \beta_0 + \boldsymbol\beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) $$
 The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
@@
 
-Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho, \sigma_u$ and $\sigma_v$.
+Finally, we complete the model by setting priors on the parameters $\beta_0, \boldsymbol\beta, \rho, \sigma_u$ and $\sigma_v$.
 The intercept was given a wide prior, $b_0 \sim \operatorname{Normal}(-2, 4)$ with a mean less than zero as we know \emph{a priori} that these countries have low or medium levels of malaria transmission.
@@
 
-$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) + w_b(\sigma_w).$$
+$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \boldsymbol\beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) + w_b(\sigma_w).$$
 As well as the global intercept, $\beta_0$, this model has a prevalence survey only intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point survey is being considered.

### 2019-09-03 ms.tex
Most of Ros comments.

@@
 
-\title[Mapping malaria by sharing spatial information]{Mapping malaria in pre-elimination settings by sharing spatial information between incidence and prevalence datasets}
+\title[Mapping malaria by sharing spatial information]{Mapping malaria by sharing spatial information between incidence and prevalence datasets}
 \author[Tim C.D. Lucas {\it et al.}]{Tim C.D. Lucas}
@@
 \begin{abstract}
-As malaria incidence decreases and more countries move towards elimination, maps of malaria risk in low prevalence areas are becoming increasingly needed.
-For low burden areas, disaggregation regression models have been developed to estimate risk at high spatial resolution from routine surveillance reports of incidence aggregated to administrative unit polygons.
-However, in areas with both routine surveillance data and prevalence surveys, models that make use of the spatial information from prevalence point surveys have great potential.
+As malaria incidence decreases and more countries move towards elimination, maps of malaria risk in low prevalence areas are increasingly needed.
+For low burden areas, disaggregation regression models have been developed to estimate risk at high spatial resolution from routine surveillance reports aggregated by administrative unit polygons.
+However, in areas with both routine surveillance data and prevalence surveys, models that make use of the spatial information from prevalence point-surveys have great potential.
 Using case studies in Indonesia, Senegal and Madagascar, we compare two methods for incorporating point-level, spatial information into disaggregation regression models.
@@
 This decrease has been accompanied by a strategic shift aiming for elimination in low incidence countries \citep{world2016world, newby2016path}.
-Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases as they highlight areas with ongoing \emph{Plasmodium} transmission most in need of interventions \citep{sturrock2016mapping, cohen2017mapping}.
+Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases as they highlight the areas with ongoing \emph{Plasmodium} transmission most in need of interventions \citep{sturrock2016mapping, cohen2017mapping}.
 Mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \citep{gething2011new, bhatt2017improved, gething2012long, bhatt2015effect} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \citep{sturrock2016mapping, sturrock2014fine}.
-In low burden areas, very large sample sizes are needed before a prevalence survey is informative because so few individuals have parasitaemia that most sample points will have no cases.
+In low burden areas, very large sample sizes are needed before a prevalence survey is informative because so few individuals have detectable parasitaemia that most sample points will have no cases.
 In most cases, these large sample sizes are neither logistically nor financially feasible.
-However, the availability and quality of routine surveillance data of malaria case counts, typically aggregated administrative unit polygons, is improving, thus providing an alternative data source for mapping malaria burden \citep{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
-Advantageously, the routine surveillance data can be more sensitive than prevalence point-surveys in low transmission areas because the entire public health system is being used to passively monitor disease risk \citep{cibulskis2011worldwide}.
+However, the availability and quality of routine surveillance data of malaria case counts, typically aggregated by administrative unit polygons, is improving, thus providing an alternative data source for mapping malaria burden \citep{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
+Advantageously, the routine surveillance data can be more sensitive than prevalence point-surveys in low transmission areas because the entire public health system is being used to passively monitor disease occurrence \citep{cibulskis2011worldwide}.
 
 Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level, routine surveillance records of incidence \citep{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
-The intent of this research is to assess the utility of extending disaggregation regression approaches to model mapping malaria incidence using both point- and polygon-level response data. 
-In particular it focuses on two noteworthy aspects where improvements in  the disaggregation regression may be possible:
-(1) for modelling in low-burden areas with better coverage of prevalence surveys than polygon incidence data; and
-(2) for building the statistical relationships between the response and geospatial predictor data in heterogeneous landscapes.
+The intent of this research is to assess the utility of extending disaggregation regression modelling approaches to map malaria incidence using both point- and polygon-level response data. 
+In particular it focuses on two aspects where improvements in the disaggregation regression may be possible:
+(1) for modelling low-burden areas which have better coverage of prevalence surveys than polygon incidence data; and
+(2) for building the statistical relationships between the response (i.e. malaria incidence) and geospatial predictor data in heterogeneous landscapes. 
 An ancillary benefit of a hybridized approach is that it will simultaneously produce estimates of both prevalence and incidence metrics, which may both be useful for policy makers \citep{cohen2017mapping}.
-Typically models are fitted to observations of one metric and then a secondary model is used to convert between prevalence and incidence \emph{post hoc} \citep{battle2019mapping, bhatt2015effect}, thus missing an opportunity to learn the relationship between prevalence and incidence at the same time as fitting the geographic model.
+Mdels are typically fitted to observations of one metric and then a secondary model is used to convert between prevalence and incidence \emph{post hoc} \citep{battle2019mapping, bhatt2015effect}, thus missing an opportunity to learn the relationship between prevalence and incidence at the same time as fitting the geographic model.
 
@@
 Firstly, the information from prevalence surveys could be summarised using a separate model and then included as a covariate in the disaggregation model.
-If the model used to summarise the prevalence surveys is explicitly spatial, this approach would make the spatial information in the prevalence data available to be used by the disaggregation model, thereby enhancing the ability to spatially disaggregate polygon-level cases within administrative units.
+If the model used to summarise the prevalence surveys was explicitly spatial, this approach would make the spatial information in the prevalence data available to the disaggregation model, thereby enhancing the ability to spatially disaggregate polygon-level cases within administrative units.
 However, this approach does not provide additional degrees of freedom in order to more accurately learn relationships between malaria risk and the environment, nor does it allow joint predictions of incidence and prevalence from a single model.
-This broad approach of summarising the information in a different data set using a separate model has previously been used in a number of contexts, including information on animal hosts \citep{shearer2016estimating} or summarising temperature suitability of malaria parasites \citep{weiss2014air}, which subsequently were used as inputs for modeling malaria prevalence \citep{bhatt2015effect, weiss2019mapping}.
+This broad approach of summarising the information in a different data set using a separate model has previously been used in a number of contexts, including information on animal hosts \citep{shearer2016estimating} or summarising temperature suitability for malaria parasites \citep{weiss2014air}, which were subsequently used as inputs for modeling malaria prevalence \citep{bhatt2015effect, weiss2019mapping}.
 
 Fully combining observations of incidence and prevalence in a joint model, with multiple likelihoods, addresses the limitations of a simple model using a prevelance map as a covariate.
-Advantageously, as the additional response data are being used as response data, they provide more degrees of freedom with which to learn relationships between malaria risk and the environment.
-Such a model can also learn the relationship between different types of malaria response metrics at the same time as making spatial estimates, thereby producing statistically consistent outputs for both incidence and prevalence.
+Advantageously, as the additional malariometric data are being used as response data, they provide more degrees of freedom with which to learn relationships between malaria risk and the environment.
+Such a model can also learn the relationship between different types of malaria response metrics at the same time as making spatial estimates, thereby producing statistically and epidemiologically consistent outputs for both incidence and prevalence.
 While a joint model provides the opportunity to learn the relationship between prevalence and incidence, this is technically challenging as these two data types measure disease intensity on different scales.
-Point surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ that quantify parasite rate during a short period of time.
+Point-surveys are a measurement of prevalence in the range $\lbrack 0, 1\rbrack$ that quantify parasite rate at a specific point in time.
 In contrast, routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$ over a longer period of time (e.g., a year) during which individuals can have multiple malaria infections.
@@
 Here we compare two methods for using spatial information from prevalence surveys to inform a disaggregation model fitted to polygon incidence data of \emph{Plasmodium falciparum}  malaria.
-The first, simpler, model summarises the spatial information in the prevalence point surveys by fitting a spatial Gaussian process model to the surveys.
-Predictions from this model are then used as an additional covariate in the disaggregation model.
+The first, simpler, model summarises the spatial information in the prevalence point-surveys by fitting a spatial Gaussian process model to the surveys.
+Predictions from this model are then used as a covariate in the disaggregation model.
 Secondly, we formulate a joint model that combines polygon incidence data and prevalence point-surveys using separate likelihoods for both data types.
@@
 We then compare results from the two models with those made using a polygon-only, disaggregation model similar to previous models \citep{sturrock2014fine, wilson2017pointless}.
-All models are fitted to data from Indonesia, Senegal and Madagascar to provide a set of case studies with disparate geographic settings and levels of malaria endemicity.
+All models are fitted to data from Indonesia, Senegal and Madagascar to provide a set of case studies from disparate geographic settings and with differing levels of malaria endemicity.
 
@@
 
-We used two data sources that reflect malaria burden: prevalence point-surveys and polygon incidence data.
-Prevalence point surveys consist of geo-located household survey clusters wherein all sampled individuals are tested for malaria and the positive cases as well as the total number of children tested is recorded.
-Polygon incidence data is aggregated by administrative-level, typically by governmental organizations tasked with collating and summarizing data reported from hospitals and health facilities. 
-Unlike the point data, polygon-level incidence only includes the number of cases and not the number of people relying on that unit’s healthcare facilities.  
-As such, to determine an incidence rate we rely on gridded population surfaces, summarised using the administrative unit’s boundaries, to provide the denominator. 
-The prevalence point-survey data were extracted from the Malaria Atlas Project prevalence survey database  \citep{bhatt2015effect, guerra2007assembling, pfeffer2018ma}. 
-As the prevalence point-surveys cover different age ranges they were standardised to an age-range of 2--10 using the model from \citep{smith2007standardizing}. 
-The age standardisation model gives the surveys with zero positive cases a small positive prevalence. 
-The polygon incidence data were collated from various government reports and adjusted to a standard metric of malaria incidence using methods defined in \citep{cibulskis2011worldwide, weiss2019mapping}.
-These adjustments account for underreporting of clinical cases due to lack of treatment seeking, missed case reports, and cases that sought medical attention outside the public health systems \citep{battle2016treatment}.
+We used two data sources that quantify malaria burden: prevalence point-surveys and polygon incidence data.
+Prevalence point-surveys consist of geo-located survey clusters wherein all sampled individuals are tested for malaria and the positive cases as well as the total number of children tested is recorded.
+Polygon incidence data is aggregated to administrative units (e.g. districts or provinces) summarizing data reported from hospitals and health facilities. 
+Unlike the point data, polygon-level reports only include numbers of cases and not the numbers of individuals in each administrative unit.  
+As such, to determine an incidence rate we rely on gridded population surfaces, summarised to administrative unit boundaries, to provide the denominator. 
+The prevalence point-survey data were extracted from the Malaria Atlas Project database \citep{bhatt2015effect, guerra2007assembling, pfeffer2018ma}. 
+As the prevalence point-surveys cover different age ranges they were standardised to the 2--10 year-range using a previously published model \citep{smith2007standardizing}. 
+As described, the age standardisation model gives the surveys with zero positive cases a small positive prevalence. 
+The polygon incidence data were collated from various government reports and adjusted for incompleteness using methods defined by Cibulskis and colleagues \citep{cibulskis2011worldwide, weiss2019mapping}.
+These adjustments account for underreporting of clinical cases due to lack of treatment seeking, missing case reports (from a health facility that reported for 11 months in a year for example), and cases that sought medical attention outside the public health systems \citep{battle2016treatment}.
 Where species specific reports were given, these were used, and in reports that did not distinguish between species of \emph{Plasmodium} the national estimate of the ratio between \emph{P.
 falciparum} and \emph{P.
-vivax} cases were used to estimate \emph{P.
-falciparum} only cases.
-These adjustments are uniform across each country. 
-The polygon incidence data can be seen in Figures~\ref{predobsmapsen}--\ref{predobsmapidn}.
+vivax} cases was used to estimate numbers of \emph{P.
+falciparum} cases specifically.
+These adjustments were uniform across each country. 
+The polygon incidence data can be seen in Panel A of Figures~\ref{predobsmapsen}--\ref{predobsmapidn}.
 
-We selected Indonesia, Senegal and Madagascar as case examples as they all have abundant subnational surveillance data and country wide surveys from approximately the same period.
+We selected Indonesia, Senegal and Madagascar as case examples as they all have abundant subnational surveillance data and country-wide surveys from approximately the same periods.
 To minimise temporal effects we selected one year of polygon incidence data and the surrounding five years of prevalence point-survey data for each country.
-For Indonesia we selected polygon incidence data from 2012 that covers 379 regions, and prevalence data from 2010 to 2014 that consists of 1,233 survey clusters (i.e.
+Within this five year period, we considered malaria unchanging and did not model time explicitely.
+For Indonesia we selected polygon incidence data from 2012 that covers 379 administrative units, and prevalence data from 2010 to 2014 that consists of 1,233 survey clusters (i.e.
 unique locations), representing 230,747 individuals.
-For Senegal we selected 2015 for polygon incidence data (41 regions) and 2013 to 2017 for prevalence data (804 surveys, 17,037 individuals).
-Finally, for Madagascar we selected 2013 for polygon incidence (110 regions) and 2011 to 2015 for prevalence data (1,049 surveys, 36,411 individuals).
+For Senegal we selected 2015 for polygon incidence data (41 administrative units) and 2013 to 2017 for prevalence data (804 surveys, 17,037 individuals).
+Finally, for Madagascar we selected 2013 for polygon incidence (110 administrative units) and 2011 to 2015 for prevalence data (1,049 surveys, 36,411 individuals).
 
@@
 
-Raster surfaces of population for the years 2005, 2010 and 2015, were created using a hybrid of data from GPWv4 \citep{gpw4} and WorldPop \citep{tatem2017worldpop}, with the latter taking priority for those pixels where both had population data.
-Yearly population rasters were created by linear interpolation of the surrounding five-yearly rasters.
-For each year, national population estimates from the UN were raked over the interpolated population surfaces.
+Raster surfaces of population for the years 2005, 2010 and 2015, were created using a hybrid mosaic of data from the Gridded Population of the World v4 \citep{gpw4} and WorldPop \citep{tatem2017worldpop}, with the latter taking priority for those pixels where both sources had population data.
+For each year, the interpolated population surfaces were adjusted to match national population estimates from the UN. 
+Finally, the population surfaces were masked by environmental suitability so that only populations at risk were included \citep{weiss2019mapping}.
 
@@
 
-We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres at the equator that included land surface temperature annual mean and standard deviation, enhanced vegetation index (EVI), \emph{P.
+We considered a suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres at the equator that included land surface temperature annual mean and standard deviation, enhanced vegetation index (EVI), \emph{P.
 falciparum} temperature suitability index \citep{weiss2014air}, elevation \citep{SRTMElev}, tassel cap brightness, tassel cap wetness, accessibility to cities \citep{weiss2018global}, night lights \citep{elvidge2017viirs} and proportion of urban land cover \citep{GUF}.
@@
 Incidence data and predicted incidence maps.
-The incidence (log10) data (left), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (right) for Senegal.
+The incidence data (left), predicted incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted incidence from the joint model for spatially cross-validated out-of-sample polygons (right) for Senegal.
 }
@@
 \caption{\label{predobsmapmdg}Input incidence data and predicted incidence maps.
-The incidence (log10) data (left), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (right) for Madagascar.
+The incidence data (left), predicted incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted incidence from the joint model for spatially cross-validated out-of-sample polygons (right) for Madagascar.
 }
@@
 Incidence data and predicted incidence maps.
-The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
+The incidence data (top), predicted incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Indonesia.
 }
@@
 
-where $i_a$ is the estimated polygon incidence rate and $\mathrm{pop_a}$ is the population-at-risk within that admin unit polygon (as apposed to the true health centre catchment area).
+where $i_a$ is the estimated polygon incidence rate and $\mathrm{pop_a}$ is the population at risk within that admin unit polygon (as apposed to the true health centre catchment area).
 
@@
 $$p_b = \operatorname{logit}^{-1}(\eta_b)$$
-The form of this set of link functions means we get predictions of prevalence and incidence simultaneously whether we used both data types or just one.
+The form of this set of link functions means we calculated predictions of prevalence and incidence simultaneously whether both data types or just one were used.
 
@@
 $$\eta_b = \beta_0 + \boldsymbol\beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) $$
-The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
+The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range on the longitude-latitude scale (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
 The iid random effect, $v_a \sim \operatorname{Normal}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $j$ being grouped together.
@@
 Finally, we complete the model by setting priors on the parameters $\beta_0, \boldsymbol\beta, \rho, \sigma_u$ and $\sigma_v$.
-The intercept was given a wide prior, $b_0 \sim \operatorname{Normal}(-2, 4)$ with a mean less than zero as we know \emph{a priori} that these countries have low or medium levels of malaria transmission.
-We set independant, regularising priors on the regression coefficients $\beta_i \sim \operatorname{Normal}(0, 0.04)$. 
+The intercept was given a wide prior, $b_0 \sim \operatorname{Normal}(-2, 4)$, with a mean relating to a prevalence of 0.12 as we know \emph{a priori} that these countries have low or medium levels of malaria transmission.
+We set independent, regularising priors on the regression coefficients $\beta_i \sim \operatorname{Normal}(0, 0.04)$. 
 Given the standardised covariates, an intercept of -3 and a regression coefficient from the 95\% interquartile range of this distribution, each covariate would be able to predict prevalences between 0.004 and 0.27.
 This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularise the model.
-This regularisation is particularly important given the small number of observations in Senegal (n = 46) and Madagascar (n = 110).
+This regularisation is particularly important given the small number of administrative units in Senegal (n = 46) and Madagascar (n = 110).
 
@@
 We assigned $\sigma_v$ a penalised complexity prior \citep{simpson2017penalising} such that $P(\sigma_v > 0.05) = 0.0000001$
-This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for the case counts using the approach defined in \citep{cibulskis2011worldwide}.
-We found that an iid effect with a standard deviation of 0.05 is able to account for the discrepancy between the assumed Poisson error and the independently derived error.
+This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for the case counts using the approach defined by Cibulskis and colleagues \citep{cibulskis2011worldwide}.
+We found that an iid effect with a standard deviation of 0.05 was able to account for the discrepancy between the assumed Poisson error and the independently derived error.
 
@@
 
-This model (henceforth the prevalence GP model) is the same as the baseline disaggregation model except that it has one extra covariate.
+The prevalence Gaussian Process model (henceforth the prevalence GP model) is the same as the baseline disaggregation model except that it has one extra covariate.
 This covariate is created by fitting a Gaussian random field to the prevalence survey data.
@@
 
-The final model is a joint-likelihood model with separate likelihoods for prevalence point surveys and polygon incidence data.
+The final model is a joint-likelihood model with separate likelihoods for prevalence point-surveys and polygon incidence data.
 The polygon data are assigned a Poisson likelihood as before.
@@
 $$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \boldsymbol\beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) + w_b(\sigma_w).$$
-As well as the global intercept, $\beta_0$, this model has a prevalence survey only intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point survey is being considered.
-The iid random effect, $v_a \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point surveys within polygon $a$ being in the same group as polygon $a$.
-The second iid random effect, $w_b \sim \operatorname{Normal}(0, \sigma_w)$, was applied to each point survey.
+As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point-survey is being considered.
+The iid random effect, $v_a \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point-surveys within polygon $a$ being in the same group as polygon $a$.
+The second iid random effect, $w_b \sim \operatorname{Normal}(0, \sigma_w)$, was applied to each point-survey.
 To improve numeric stability this effect is also parameterised internally as the log of the precision, $\omega_w = \log(\tau_w) = \log(\frac{1}{{\sigma_w}^2})$.
@@
 In Senegal and Madagascar this value was relatively small so we set $\phi = 0.05$. 
-In Indonesia however, there are many prevalence surveys in small areas and there is large differences in estimated prevalence within the same pixel.
+In Indonesia however, there was a high density of prevalence surveys and heterogeneity in estimated prevalence within single pixels.
 Therefore we set $\phi = 0.3$.
@@
 %This cross-validation scheme directly addresses the question of whethe
-In the second validation scheme , the incidence data was split into spatial cross-validation folds, using k means clustering on polygon centroids, while again all prevalence points were used in all folds (Figure~S2).
+In the second validation scheme, the incidence data was split into spatial cross-validation folds, using k means clustering on polygon centroids, while again all prevalence points were used in all folds (Figure~S2).
 The number of folds was seven for Indonesia, five for Senegal and three for Madagascar due to their differing sizes and epidemiological settings.
-This scheme is specifically testing whether the joint model can improve predictions by increasing geographic data coverage.
+This scheme tests specifically whether the joint model can improve predictions by increasing geographic data coverage.
 %This situation is particularly common in continental scale models where some countries will have large DHS style surveys but little incidence data.
 
-We considered the ability to predict polygon incidence correctly our main objective and our performance metric was mean absolute error (MAE).
-As the models are being fitted on data on different scales we found that observations and predictions were sometimes correlated but shifted from the one-one line (i.e.
-biased) and therefore correlation metrics were misleading.
+We considered the ability of the model to predict polygon incidence to be our main objective and our performance metric for this was mean absolute error (MAE).
+As the models were fitted on data on different scales we found that observations and predictions were sometimes correlated but shifted from the one-one line (i.e.
+were biased) and therefore correlation metrics were misleading.
 % Why not correlation
@@
 \caption{\label{table1}
-Summary of out-of-sample accuracy for all three cross-validation experiments. 
+Summary of out-of-sample accuracy for all cross-validation experiments. 
 Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.}
@@
 The differences were relatively small in all three countries.
-This lack of strong differences is highlighted by the fact that there are no clear differences in scatter plots of observed and predicted data (Figure \ref{randompredobspolyfacet}).
+This lack of strong differences is highlighted by there being no clear differences in scatter plots of observed and predicted data across the three methods (Figure \ref{randompredobspolyfacet}).
 
@@
 
-Under the spatial cross-validation scheme, the baseline model and prevalence GP models performed best in Indonesia, the prevalence GP performaced best in Senegal while the joint model performed best in Madagascar (Table \ref{table1}).
-In contrast to the random cross-validation results, the differences between models is quite strong.
-Furthermore, notable difference can be seen in the scatter plots of observed and predicted values (Figure \ref{spatial2predobspolyfacet}).
-In Indonesia it can be seen the the joint model is more strongly biased at low incidence values with many data points being overpredicted.
+Under the spatial cross-validation scheme, the baseline model and prevalence GP models performed best in Indonesia, the prevalence GP performed best in Senegal while the joint model performed best in Madagascar (Table \ref{table1}).
+In contrast to the random cross-validation results, the differences between models was quite strong.
+Furthermore, notable differences can be seen in the scatter plots of observed and predicted values (Figure \ref{spatial2predobspolyfacet}).
+In Indonesia it can be seen that the joint model is more strongly biased at low incidence values with many data points being overpredicted.
 However, the joint model clearly performs better in Madagascar with the polygon-only model unable to predict high incidence observations accurately.
@@
 \caption{\label{randompredobspolyfacet} 
-Observed-predicted plots for random cross-validation experiments.
-A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (cases per 1,000).
+Observed-predicted plots (square root scale) of modelled annual malaria incidence (cases per 1000) by country from the random cross-validation experiments for Indonesia (Panel A), Senegal (Panel B) and Madagascar (Panel C).
 Results from the baseline disaggregation model are shown in red, the prevalence GP model is shown in green while the joint model is shown in blue.
@@
 \makebox{\includegraphics[width = 1.05\textwidth]{figures/spatialkeeppr_cv_poly_facet.pdf}}
-\caption{\label{spatial2predobspolyfacet} Observed-predicted plots for spatial a cross-validation experiments where all prevalence points are used in model fitting.
-A) Indonesia, B) Senegal, C) Madagascar. Square root aggregated incidence (cases per 1,000).
+\caption{\label{spatial2predobspolyfacet} 
+Observed-predicted plots (square root scale) of modelled annual malaria incidence (cases per 1000) by country from the spatial cross-validation experiments for Indonesia (Panel A), Senegal (Panel B) and Madagascar (Panel C).
 Results from the baseline disaggregation model are shown in red, the prevalence GP model is shown in green while the joint model is shown in blue.
@@
 The proportion of out-of-sample incidence datapoints being within their 80\% credible intervals ranged between 0.51 and 0.88.
-However, in most cases coverage was between 0.7 and 0.8 implying the models were a little overconfident in their predictions.
+However, in most cases coverage was between 0.7 and 0.8 implying that the models were a little overconfident in their predictions.
 There was no clear difference in calibration between the different models.
@@
 
-We can further examine why the models performed as they did by examining the parameters estimated in the models fitted to all data (Tables~S1--S3).
+We can further investigate why the models performed as they did by examining the parameters estimated in the models fitted to all data (Tables~S1--S3).
 Firstly we can compare the regression parameter for the prevalence GP covariate in the three countries noting that in Indonesia the prevalence GP model performed worse than baseline under random cross-validation and had equal performance to baseline under spatial cross-validation.
@@
 In Madagascar the joint model performed the best in the spatial cross-validation scheme and better than the baseline in the random cross-validation scheme. 
-Comparing the parameter estimates for the joint model specific parameters between Madagascar and the other two countries therefore seems useful.
-The prevalence only intercept, $\beta_p$, is large in the Senegal fit (mean = 1.36, sd = 0.13) but small in Indonesia (mean = 0.03, sd = 0.20) and Madagascar (mean = 0.07, sd = 0.10).
-This implies there is a strong bias (given the prevalence to incidence model) between the prevalence and incidence data in Senegal.
+Comparing the estimated parameters of the joint model between Madagascar and the other two countries therefore is useful.
+The prevalence intercept, $\beta_p$, is large in the Senegal fit (mean = 1.36, sd = 0.13) but small in Indonesia (mean = 0.03, sd = 0.20) and Madagascar (mean = 0.07, sd = 0.10).
+This implies there is a strong discrepency (given the prevalence to incidence model) between the prevalence and incidence data in Senegal.
 Furthermore, the standard deviation of the prevalence point iid effect, $w_b(\sigma_w)$, is much larger in Indonesia (mean $\omega_w = -2.6$, sd $\omega_w = 0.09$ which corresponds to a mean of $\sigma_w$ of 13.46) than in Senegal (mean $\omega_w = -1.03$, sd $\omega_w = 0.13$ which corresponds to a mean of $\sigma_w$ of 2.80) or Madagascar (mean $\omega_w = -0.77$, sd $\omega_w = 0.11$ which corresponds to a mean of $\sigma_w$ of 2.16).
@@
 The estimated value for $\alpha$ in all three countries is very close to one (Tables~S1--S3).
-While this might be driven by the prior, we can conclude that there is no strong evidence from the data that this relationship should be scaled differently in the different countries.
+While this might be driven by the prior, we can conclude that there is no strong evidence from the data that this relationship should be scaled differently by country.
 
@@
 
-Overall, including the spatial information from prevalence surveys yields predictions that are as good or better than the baseline model in all six experiments (three countries and two cross-validation schemes).
+Overall, inclusion of the spatial information from prevalence surveys yielded predictions that were as good or better than the baseline model in all six experiments (three countries and two cross-validation schemes).
 The prevalence GP model was as good or better than baseline in five out of six experiments.
@@
 
-We have compared the predictive performance of three models: a baseline polygon-only model; a disaggregation model with spatial information from prevalence surveys included as an additional covariate from a separate Gaussian process model; and a model that jointly learns from polygon incidence data and prevalence point-surveys.
-Overall the prevalence GP model appears to perform best.
-While the joint model sometimes performs best it also performs worse than baseline half of the time.
+We have compared the predictive performance of three models: a baseline polygon-only model; a disaggregation model with spatial information from prevalence surveys included as an additional covariate from a separate Gaussian process (GP) model; and a model that jointly learns from polygon incidence data and prevalence point-surveys.
+Overall the prevalence GP model appeared to perform best.
+While the joint model sometimes performed best it also performed worse than baseline in half of the experiments.
 Therefore, fitting a spatial Gaussian process to prevalence points and including these predictions seems to be a more reliable way of using spatial information from prevalence points.
-However, given this comparison was conducted using only three countries it is challenging to draw firm conclusions.
+However, given that this comparison was conducted on datasets from only three countries, it is challenging to draw firm conclusions.
 
@@
 
-A full joint model using both prevalence surveys and incidence data gains quite a large number of additional degrees of freedom compared to the baseline model and compared to the model that creates a new covariate from prevalence surveys.
-Therefore it is worth considering why the performance of this model was generally less good than the simpler prevalence GP model that did not benefit from the additional degrees of freedom.
+A full joint model using both prevalence surveys and incidence data gains a large number of additional degrees of freedom compared to the baseline or prevalence GP models.
+Therefore, it is worth considering why the performance of this model was generally less good than the simpler prevalence GP model that did not benefit from the additional degrees of freedom.
 One potential reason is that the malariometric data are on different scales.
-Here we have used a previously fitted model \citep{cameron2015defining} in order to be able to fit the joint model.
+Here we have used a previously fitted model \citep{cameron2015defining} to inform the joint model.
 However, this model was calibrated using relatively few matched prevalence and incidence surveys as few of these have been conducted and published.
-Although we have added the parameter $\alpha$ that scales this relationship, it is a very simple scaling.
+Although we added the parameter $\alpha$ that scales this relationship, it is a very simple scaling.
 Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality, and population age-structure are not constant \citep{cameron2015defining, battle2015defining, reiner2015seasonality}.
-In using a joint model we are accepting these failings in the hope that the benefits of including additional data outweigh the costs of using mismatched data.
+In using a joint model we are accepting these limitations in the hope that the benefits of including additional data outweigh the costs of using mismatched data.
 
-Future models could potentially be improved by using a more flexible approach for addressing the shortcomings in the prevalence-incidence relationship from \citep{cameron2015defining}.
+Future models could potentially be improved by using a more flexible approach for addressing the shortcomings in the prevalence-incidence relationship \citep{cameron2015defining}.
 This could be by estimating the parameters of the polynomial jointly with the rest of the model.
-Informative priors based on the original model should be used to regularise this joint fit both to prevent unbelievable inferences but also because if the relationship is too flexible, the information from the prevalence data might not contribute to learning the regression parameters and spatial random field.
+Informative priors based on the original model could be used to regularise this joint fit both to prevent improbable inferences but also because if the relationship were too flexible, the information from the prevalence data might not contribute to informing the regression parameters and spatial random field.
 This is particularly true for model forms such as a spline or a Gaussian process on the relationship between prevalence and incidence.
-For the model to handle noisy or biased prevalence point-surveys, the modeller can control the iid random effect on the point-surveys, $w_b$ and the prevalence-only intercept $\beta_p$. 
-Here we have tried to maximise the influence of the prevalence data by setting the prior based on the belief that the random effect should only explain extra-binomial variation that is impossible to explain with the covariates (i.e.
+For the model to handle noisy or biased prevalence point-surveys, the modeller can control the iid random effect on the point-surveys, $w_b$ and the prevalence intercept $\beta_p$. 
+Here we have tried to maximise the influence of the prevalence data by setting the prior based on the belief that the random effect should only explain extra-binomial variation that is impossible to derive from the covariates (e.g.
 based on the differences in prevalence surveys within the same pixel).
@@
 Firstly, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model \citep{bhatt2017improved}.
-This approach is feasible but does not allow any information from the polygons to inform non-linear relationships.
+This approach is feasible but would not allow any information from the polygons to inform non-linear relationships.
 Directly modelling non-linear effects in the full model could be achieved by including simple non-linear functions such as splines \citep{sissoko2017temporal, sewe2017using, hundessa2018projecting}, though the increased model complexity would require more data than was used in Senegal and Madagascar in this study.
@@
 Firstly countries who have had large prevalence surveys in the past and whose reporting systems are improving, such as Ethiopia, might benefit from these methods.
-Secondly, countries who have lots of prevalence surveys and are adjacent to countries with good reporting systems, such as Papua New Guinea, might also benefit from sharing models that share information between countries.
+Secondly, countries that have lots of prevalence surveys and are adjacent to countries with good reporting systems, (e.g.
+Papua New Guinea and neighbouring Indonesia), might also benefit from models that share information between countries.
 
@@
 As more countries produce reliable routine surveillance data, and as more countries reduce their malaria prevalences to the point where prevalence surveys are no longer sensitive, disaggregation regression will become more commonly used.
-Methods such as those presented here should be utilized to improve disaggregation regression results where and when the requisite data are available.
+Methods such as those presented here should be utilized and further refined to improve disaggregation regression results where and when the requisite data are available.
 
@@
 \section*{Acknowledgments}
-Thanks everyone.
+The authors acknowledge the National Malaria Control Programme of Madagascar for sharing their routine case data for this analysis.
 

### 2019-09-04 ms.tex
Final ros edits.

@@
 \caption{\label{predobsmapsen}
-Incidence data and predicted incidence maps.
-The incidence data (left), predicted incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted incidence from the joint model for spatially cross-validated out-of-sample polygons (right) for Senegal.
+Reported incidence data and modelled incidence maps for Senegal. 
+The adjusted input aggregated data is plotted in Panel A, while Panel B maps the predictions of the prevalence Gaussian Process model for for spatially cross-validated out-of-sample polygons and Panel C maps the predicted incidence from the joint model.
 }
@@
 \makebox{\includegraphics[width = 1.1\textwidth]{figures/mdg_both_cv12_preds.png}}
-\caption{\label{predobsmapmdg}Input incidence data and predicted incidence maps.
-The incidence data (left), predicted incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted incidence from the joint model for spatially cross-validated out-of-sample polygons (right) for Madagascar.
+\caption{\label{predobsmapmdg}
+Reported incidence data and modelled incidence maps for Madagascar. 
+The adjusted input aggregated data is plotted in Panel A, while Panel B maps the predictions of the prevalence Gaussian Process model for for spatially cross-validated out-of-sample polygons and Panel C maps the predicted incidence from the joint model.
 }
@@
 \caption{\label{predobsmapidn}
-Incidence data and predicted incidence maps.
-The incidence data (top), predicted incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Indonesia.
+Reported incidence data and modelled incidence maps for Indonesia. 
+The adjusted input aggregated data is plotted in Panel A, while Panel B maps the predictions of the prevalence Gaussian Process model for for spatially cross-validated out-of-sample polygons and Panel C maps the predicted incidence from the joint model.
 }

### 2019-09-04 ms.tex
KB edits.

@@
 However, the availability and quality of routine surveillance data of malaria case counts, typically aggregated by administrative unit polygons, is improving, thus providing an alternative data source for mapping malaria burden \citep{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
-Advantageously, the routine surveillance data can be more sensitive than prevalence point-surveys in low transmission areas because the entire public health system is being used to passively monitor disease occurrence \citep{cibulskis2011worldwide}.
+Advantageously, the routine surveillance data can be more sensitive than prevalence point-surveys in low transmission areas because the entire public health system is being used to passively monitor disease occurrence continually over a period of time\citep{cibulskis2011worldwide}.
 
@@
 An ancillary benefit of a hybridized approach is that it will simultaneously produce estimates of both prevalence and incidence metrics, which may both be useful for policy makers \citep{cohen2017mapping}.
-Mdels are typically fitted to observations of one metric and then a secondary model is used to convert between prevalence and incidence \emph{post hoc} \citep{battle2019mapping, bhatt2015effect}, thus missing an opportunity to learn the relationship between prevalence and incidence at the same time as fitting the geographic model.
+Models are typically fitted to observations of one metric and then a secondary model is used to convert between prevalence and incidence \emph{post hoc} \citep{battle2019mapping, bhatt2015effect}, thus missing an opportunity to learn the relationship between prevalence and incidence at the same time as fitting the geographic model.
 
@@
 Where species specific reports were given, these were used, and in reports that did not distinguish between species of \emph{Plasmodium} the national estimate of the ratio between \emph{P.
-falciparum} and \emph{P.
-vivax} cases was used to estimate numbers of \emph{P.
+falciparum} and \emph{Plasmodium vivax} cases was used to estimate numbers of \emph{P.
 falciparum} cases specifically.
@@
 unique locations), representing 230,747 individuals.
-For Senegal we selected 2015 for polygon incidence data (41 administrative units) and 2013 to 2017 for prevalence data (804 surveys, 17,037 individuals).
-Finally, for Madagascar we selected 2013 for polygon incidence (110 administrative units) and 2011 to 2015 for prevalence data (1,049 surveys, 36,411 individuals).
+For Senegal we selected 2015 for polygon incidence data (41 administrative units) and 2013 to 2017 for prevalence data (804 clusters, 17,037 individuals).
+Finally, for Madagascar we selected 2013 for polygon incidence (110 administrative units) and 2011 to 2015 for prevalence data (1,049 clusters, 36,411 individuals).
 
@@
 
-We assigned $\sigma_v$ a penalised complexity prior \citep{simpson2017penalising} such that $P(\sigma_v > 0.05) = 0.0000001$
+We assigned $\sigma_v$ a penalised complexity prior \citep{simpson2017penalising} such that $P(\sigma_v > 0.05) = 0.0000001$.
 This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for the case counts using the approach defined by Cibulskis and colleagues \citep{cibulskis2011worldwide}.
@@
 
-Future models could potentially be improved by using a more flexible approach for addressing the shortcomings in the prevalence-incidence relationship \citep{cameron2015defining}.
+Future models could potentially be improved by using a more flexible approach for addressing the shortcomings of the prevalence-incidence relationship \citep{cameron2015defining} being used in this context.
 This could be by estimating the parameters of the polynomial jointly with the rest of the model.
@@
 
-We used three case studies, limited by the number of coutnries with good aggregated incidence data as well as good prevalence survey data.
+We used three case studies, limited by the number of countries with good aggregated incidence data as well as good prevalence survey data.
 Given the small number of case studies it is hard to determine when these methods are likely to be most effective.

### 2019-09-06 ms.tex
Fix table (somehow) and andre edits.

@@
 The linear predictor is composed of an intercept, $b_0$, covariates, $X$, and a vector of regression coefficients $\boldsymbol\beta$.
-We also include a spatial, Gaussian random field, $u(s, \rho, \sigma_u)$ and a polygon-level iid random effect, $ v_a(\sigma_v)$.
-$$\eta_b = \beta_0 + \boldsymbol\beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) $$
+We also include a spatial, Gaussian random field, $u_s(\rho, \sigma_u)$ and a polygon-level iid random effect, $ v_a(\sigma_v)$.
+$$\eta_b = \beta_0 + \boldsymbol\beta X  + u_s(\rho, \sigma_u) + v_a(\sigma_v) $$
 The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range on the longitude-latitude scale (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
@@
 We assigned $\sigma_v$ a penalised complexity prior \citep{simpson2017penalising} such that $P(\sigma_v > 0.05) = 0.0000001$.
-This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for the case counts using the approach defined by Cibulskis and colleagues \citep{cibulskis2011worldwide}.
-We found that an iid effect with a standard deviation of 0.05 was able to account for the discrepancy between the assumed Poisson error and the independently derived error.
+This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an separately derived upper and lower bound for the case counts using the approach defined by Cibulskis and colleagues \citep{cibulskis2011worldwide}.
+We found that an iid effect with a standard deviation of 0.05 was able to account for the discrepancy between the assumed Poisson error and the separately derived measurement error.
 
@@
 
-$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \boldsymbol\beta X  + u(s, \rho, \sigma_u) + v_a(\sigma_v) + w_b(\sigma_w).$$
+$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \boldsymbol\beta X  + u_s(\rho, \sigma_u) + v_a(\sigma_v) + w_b(\sigma_w).$$
 As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point-survey is being considered.
@@
 
-We considered the ability of the model to predict polygon incidence to be our main objective and our performance metric for this was mean absolute error (MAE).
-As the models were fitted on data on different scales we found that observations and predictions were sometimes correlated but shifted from the one-one line (i.e.
-were biased) and therefore correlation metrics were misleading.
-% Why not correlation
-To assess how well the models were calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.
-%Finally, we fitted each model to the full data set and examine the parameter estimates for these models.
-
 \begin{table}
-\caption{\label{table1}
-Summary of out-of-sample accuracy for all cross-validation experiments. 
+\caption{\label{table1}Summary of out-of-sample accuracy for all cross-validation experiments. 
 Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.}
@@
 \fbox{%
-\begin{tabular}{lllll}
-\hline
+\begin{tabular}{*{5}{l}}
 {\bf Cross-validation} & {\bf Country}  & {\bf Baseline} & {\bf Prev GP} & {\bf Joint} \\
@@
 \end{table}
+
+We considered the ability of the model to predict polygon incidence to be our main objective and our performance metric for this was mean absolute error (MAE).
+As the models were fitted on data on different scales we found that observations and predictions were sometimes correlated but shifted from the one-one line (i.e.
+were biased) and therefore correlation metrics were misleading.
+% Why not correlation
+To assess how well the models were calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.
+%Finally, we fitted each model to the full data set and examine the parameter estimates for these models.
 

### 2019-12-02 ms.tex
Tidy up.

@@
 \author{Emma L. Collins\textsuperscript{1}}
-\author{Rosalind E. Howes}
+\author{Rosalind E. Howes\textsuperscript{1}}
 \author{Michele Nguyen\textsuperscript{1}}
@@
 Reported incidence data and modelled incidence maps for Senegal. 
+The national boundary of Senegal is shown in grey and missing data is left white.
 The adjusted input aggregated data is plotted in Panel A, while Panel B maps the predictions of the prevalence Gaussian Process model for for spatially cross-validated out-of-sample polygons and Panel C maps the predicted incidence from the joint model.
@@
 Reported incidence data and modelled incidence maps for Indonesia. 
+The national boundary of Indonesia is shown in grey and missing data is left white.
 The adjusted input aggregated data is plotted in Panel A, while Panel B maps the predictions of the prevalence Gaussian Process model for for spatially cross-validated out-of-sample polygons and Panel C maps the predicted incidence from the joint model.
@@
 $$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \boldsymbol\beta X  + u_s(\rho, \sigma_u) + v_a(\sigma_v) + w_b(\sigma_w).$$
-As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $b_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point-survey is being considered.
+As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $\beta_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point-survey is being considered.
 The iid random effect, $v_a \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point-surveys within polygon $a$ being in the same group as polygon $a$.

### 2019-12-02 si.tex
Do KT edits and dont use xr cos it aint working.
Tidy up.

@@
 \usepackage{multirow}
+
+\usepackage{subfig}
 
@@
 \end{tabular}
-\caption{Parameter estimates for Senegal. $\omega_v = \log\left(\frac{1}{{\sigma_v}^2}\right)$ and $\omega_w = \log\left(\frac{1}{{\sigma_w}^2}\right)$} 
+\label{parssen}
+\caption[Parameter estimates for Senegal]{Parameter estimates for Senegal. $\omega_v = \log\left(\frac{1}{{\sigma_v}^2}\right)$ and $\omega_w = \log\left(\frac{1}{{\sigma_w}^2}\right)$} 
 \end{table}
@@
 \end{tabular}
+\label{parsmdg}
 \caption{Parameter estimates for Madagascar $\omega_v = \log\left(\frac{1}{{\sigma_v}^2}\right)$ and $\omega_w = \log\left(\frac{1}{{\sigma_w}^2}\right)$} 
@@
 \end{tabular}
+\label{parsidn}
 \caption{Parameter estimates for Indonesia $\omega_v = \log\left(\frac{1}{{\sigma_v}^2}\right)$ and $\omega_w = \log\left(\frac{1}{{\sigma_w}^2}\right)$} 
@@
 \clearpage
+
 \subsection{Full model fields}
@@
 \subsubsection{Senegal}
-\begin{figure}[h!]
-\centering
-
-\includegraphics[width = 0.3\textheight]{figures/sen_prevgp.png}
-
-\caption{The prevalence GP model that is used as a covariate.}
-\label{gpsencov}
-\end{figure}
 
@@
 \end{figure}
+
 \begin{figure}[h!]
      \centering
-
-\includegraphics[width = 0.3\textheight]{figures/sen_prgp_field.png}
-
-\caption{The random field as fitted to all the data in the prevalence GP model.}
-\label{gpfieldsen}
+     \subfloat[][The prevalence GP model that is used as a covariate.]{\includegraphics[width = 0.3\textheight]{figures/sen_prevgp.png}}
+     \subfloat[][The random field as fitted to all the data in the prevalence GP model.]{\includegraphics[width = 0.3\textheight]{figures/sen_prgp_field.png}}
+     \label{gpsencov}
 \end{figure}
+%remaining part
 
@@
 \subsubsection{Indonesia}
-\begin{figure}[h!]
-\centering
-
-\includegraphics[width = 0.6\textheight]{figures/idn_prevgp.png}
-
-\caption{The prevalence GP model that is used as a covariate.}
-\label{gpidncov}
-\end{figure}
 
@@
 
-\caption{The random field as fitted to all the data in the joint model.}
+\caption{The random field as fitted to all the data in the baseline model.}
 \label{baselinefieldidn}
@@
      \centering
-
-\includegraphics[width =  0.6\textheight]{figures/idn_prgp_field.png}
-
-\caption{The random field as fitted to all the data in the joint model.}
-\label{gpfieldidn}
+     \subfloat[][The prevalence GP model that is used as a covariate.]{\includegraphics[width =0.5\textwidth ]{figures/idn_prevgp.png}}
+     \subfloat[][The random field as fitted to all the data in the prevalence GP model.]{\includegraphics[width = 0.5\textwidth]{figures/idn_prgp_field.png}}
+     \label{gpsencov}
 \end{figure}
+%remaining part
 
@@
 \subsubsection{Madagascar}
-\begin{figure}[h!]
-\centering
-
-\includegraphics[width =  0.3\textheight]{figures/mdg_prevgp.png}
-
-\caption{The prevalence GP model that is used as a covariate.}
-\label{gpmdgcov}
-\end{figure}
 
@@
 \end{figure}
+
 \begin{figure}[h!]
      \centering
-
-\includegraphics[width = 0.3\textheight]{figures/mdg_prgp_field.png}
-
-\caption{The random field as fitted to all the data in the prevalence GP model.}
-\label{gpfieldmdg}
+     \subfloat[][The prevalence GP model that is used as a covariate.]{\includegraphics[width =0.5\textwidth ]{figures/mdg_prevgp.png}}
+     \subfloat[][The random field as fitted to all the data in the prevalence GP model.]{\includegraphics[width = 0.5\textwidth]{figures/mdg_prgp_field.png}}
+     \label{gpsencov}
 \end{figure}
+%remaining part
 

### 2019-12-02 ms.tex
Explicitely state inla cant be used.
First go at additional intro.

@@
 \author{Rohan Arambepola\textsuperscript{1}}
-\author{Amelia Bertozzi-Villa\textsuperscript{1}}
+\author{Amelia Bertozzi-Villa\textsuperscript{1,2}}
 \author{Penelope Hancock\textsuperscript{1}}
@@
 \author{Ewan Cameron\textsuperscript{1}}
-\author{Peter W. Gething\textsuperscript{1, 2, 3}}
+\author{Peter W. Gething\textsuperscript{1, 3, 4}}
 \author{Daniel J. Weiss\textsuperscript{1}}
@@
 UK.}
-\address{2. Telethon Kids Institute, Perth Children’s Hospital, Perth, Australia}
-\address{3. Curtin University, Perth, Australia}
+\address{2. Institute for Disease Modeling, Bellevue, WA, USA}
+\address{3. Telethon Kids Institute, Perth Children’s Hospital, Perth, Australia}
+\address{4. Curtin University, Perth, Australia}
 
@@
 
-Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level, routine surveillance records of incidence \citep{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
+Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level, routine surveillance records of incidence \citep{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log, johnson2019spatially}.
+Disaggregation regression requires an aggregation step in which the high-resolution estimates of disease incidence are summed to match the level of the administitive unit at which the incidence data are observed.
+An important consideration is whether the aggregation step occurs in link function space or in the response space.
+In the case of the identity link function, the two cases are the same \citep{moraga2017geostatistical, roksvaag2019knowledge, wilson2017pointless}.
+However, when using a non-linear link function, the two cases imply very different models.
+In the case of the Normal--Poisson pairing  with a log-link function, performing the aggregation step in the link space before transformation back to the response space produces  a `geometric sum' operation.
+This formulation has been used for computational convenience a number of times in the literature \citep{wang2018generalized, liu2011empirical} but lacks the natural epidemiological interpretation provided by arithmetic summation in the response space.
+
 The intent of this research is to assess the utility of extending disaggregation regression modelling approaches to map malaria incidence using both point- and polygon-level response data. 
@@
 In contrast, routine surveillance measures incidence in the range $\lbrack 0, \infty\rbrack$ over a longer period of time (e.g., a year) during which individuals can have multiple malaria infections.
+The case of using areal and point data together with different likelihoods and different link functions has been examined previously \citep{wang2018generalized} but has required that the aggregation step be performed in the link function space.
+Disaggregation regression models in which the aggregation step is performed in the natural response space have been examined \citep{wilson2017pointless, taylor2017continuous}, but without combining point data with areal data or using dual likelihoods for multi-metric data.
+
 %One approach to combining these datasets is to use a separately estimated model that maps one scale to another such as \citep{cameron2015defining}.
@@
 We relate the differing malariometric measures by using a previously estimated relationship within the model \citep{cameron2015defining} which is then adjusted as part of the model fitting process.
+Unlike previous studies, this model combines areal and point level data, with different likelihoods, without performing the aggregation step in the link function space.
 We then compare results from the two models with those made using a polygon-only, disaggregation model similar to previous models \citep{sturrock2014fine, wilson2017pointless}.
@@
 The models were implemented and fitted in R \citep{R} using Template Model Builder \citep{TMB} which allows a Laplace approximation of the posterior to be calculated.
+We note that R-INLA \citep{INLA} can be used to fit disaggregation models but only when a linear link function is being used \cite{wilson2017pointless}.
 The hyperparameters are fitted using empirical Bayes whereby the hyperparameters are learned from the data but are treated as point estimates rather than using the full posterior of the hyperparameters.

### 2019-12-06 si.tex
Update si authors.

@@
 \\
-Tim C.D.
-Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Rosalind Howes \textsuperscript{1}, Katherine E.
-Battle \textsuperscript{1}, Andre Python \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Daniel J.
-Weiss\textsuperscript{1}
+Tim C.D. Lucas*\textsuperscript{1}, 
+Anita K. Nandi\textsuperscript{1},
+Elisabeth G. Chestnutt\textsuperscript{1},
+Katherine A. Twohig\textsuperscript{1},
+Suzanne H. Keddie\textsuperscript{1},
+Emma L. Collins\textsuperscript{1},
+Rosalind E. Howes\textsuperscript{1},
+Michele Nguyen\textsuperscript{1},
+Susan F. Rumisha\textsuperscript{1},
+Andre Python\textsuperscript{1},
+Rohan Arambepola\textsuperscript{1},
+Amelia Bertozzi-Villa\textsuperscript{1,2},
+Penelope Hancock\textsuperscript{1},
+Punam Amratia\textsuperscript{1},
+Katherine E. Battle\textsuperscript{1},
+Ewan Cameron\textsuperscript{1},
+Peter W. Gething\textsuperscript{1, 3, 4}
+Daniel J. Weiss\textsuperscript{1}
 \\
 \bigskip
-\textbf{1} BDI, Oxford
+1. BDI, Oxford\\
+2. Institute for Disease Modeling, Bellevue, WA, USA\\
+3. Telethon Kids Institute, Perth Children’s Hospital, Perth, Australia\\
+4. Curtin University, Perth, Australia
 \\

### 2020-06-08 ms.tex
Some edits including changing the notation.

@@
 \usepackage[hidelinks]{hyperref}
+
+\usepackage{lineno}
+\linenumbers
 
@@
 For low burden areas, disaggregation regression models have been developed to estimate risk at high spatial resolution from routine surveillance reports aggregated by administrative unit polygons.
-However, in areas with both routine surveillance data and prevalence surveys, models that make use of the spatial information from prevalence point-surveys have great potential.
+However, in areas with both routine surveillance data and prevalence surveys, models that make use of the spatial information from prevalence point-surveys might make more accurate predictions.
 Using case studies in Indonesia, Senegal and Madagascar, we compare two methods for incorporating point-level, spatial information into disaggregation regression models.
@@
 The second is a multi-likelihood model that is fitted jointly to prevalence point-surveys and polygon incidence data.
-We find that the simple model generally performs better than a baseline disaggregation model while the joint model performance was mixed.
-More generally, our results demonstrate that combining these types of data improves estimates of malaria incidence.
+We find that in most cases there is no difference in performance between the models.
+In some cases the baseline model performed the best while in one case the new models performed the best.
+More generally, our results demonstrate that combining these types of data has the potential to improve estimates of malaria incidence but that simpler baseline models should always be fitted as a benchmark.
 \end{abstract}
@@
 Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases as they highlight the areas with ongoing \emph{Plasmodium} transmission most in need of interventions \citep{sturrock2016mapping, cohen2017mapping}.
-Mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \citep{gething2011new, bhatt2017improved, gething2012long, bhatt2015effect} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \citep{sturrock2016mapping, sturrock2014fine}.
+Two important data sources for malaria mapping are cluster-level surveys of prevalence \citep{gething2011new, bhatt2017improved, gething2012long, bhatt2015effect} and routine surveillance data, typically aggregated by administrative unit polygons \citep{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
+These data sources have different strengths and different spatial coverage.
 In low burden areas, very large sample sizes are needed before a prevalence survey is informative because so few individuals have detectable parasitaemia that most sample points will have no cases.
-In most cases, these large sample sizes are neither logistically nor financially feasible.
-However, the availability and quality of routine surveillance data of malaria case counts, typically aggregated by administrative unit polygons, is improving, thus providing an alternative data source for mapping malaria burden \citep{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
-Advantageously, the routine surveillance data can be more sensitive than prevalence point-surveys in low transmission areas because the entire public health system is being used to passively monitor disease occurrence continually over a period of time\citep{cibulskis2011worldwide}.
+Routine surveillance data can be more sensitive than prevalence point-surveys in low transmission areas because the entire public health system is being used to passively monitor disease occurrence continually over a period of time \citep{cibulskis2011worldwide}.
+The availability and quality of routine surveillance data of malaria case counts can be poor, but is improving \citep{ohrt2015information, cibulskis2011worldwide}.
+Therefore, when the study area contains both low and medium/high burden areas, or when prevalence surveys and routine surveillance provide complementary spatial coverage, models that use both of these data sources have the potential to improve estimates of malaria prevalence and incidence.
 
 Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level, routine surveillance records of incidence \citep{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log, johnson2019spatially}.
-Disaggregation regression requires an aggregation step in which the high-resolution estimates of disease incidence are summed to match the level of the administitive unit at which the incidence data are observed.
+Disaggregation regression requires an aggregation step in which the high-resolution estimates of disease incidence are summed to match the level of the administrative unit at which the incidence data are observed.
 An important consideration is whether the aggregation step occurs in link function space or in the response space.
@@
 
-The intent of this research is to assess the utility of extending disaggregation regression modelling approaches to map malaria incidence using both point- and polygon-level response data. 
-In particular it focuses on two aspects where improvements in the disaggregation regression may be possible:
-(1) for modelling low-burden areas which have better coverage of prevalence surveys than polygon incidence data; and
-(2) for building the statistical relationships between the response (i.e. malaria incidence) and geospatial predictor data in heterogeneous landscapes. 
-An ancillary benefit of a hybridized approach is that it will simultaneously produce estimates of both prevalence and incidence metrics, which may both be useful for policy makers \citep{cohen2017mapping}.
-Models are typically fitted to observations of one metric and then a secondary model is used to convert between prevalence and incidence \emph{post hoc} \citep{battle2019mapping, bhatt2015effect}, thus missing an opportunity to learn the relationship between prevalence and incidence at the same time as fitting the geographic model.
-
 There are two broad ways that spatial information from prevalence surveys could be included in a dissaggregation regression model of incidence.
@@
 If the model used to summarise the prevalence surveys was explicitly spatial, this approach would make the spatial information in the prevalence data available to the disaggregation model, thereby enhancing the ability to spatially disaggregate polygon-level cases within administrative units.
-However, this approach does not provide additional degrees of freedom in order to more accurately learn relationships between malaria risk and the environment, nor does it allow joint predictions of incidence and prevalence from a single model.
+However, this approach does not use any additional statistical power  from the prevalence data in order to more accurately learn relationships between malaria risk and the environment.
+When the study area contains medium burden areas, this is a missed opportunity.
+When the spatial coverage of data is different but the whole study area is low burden this method may be appropriate.
 This broad approach of summarising the information in a different data set using a separate model has previously been used in a number of contexts, including information on animal hosts \citep{shearer2016estimating} or summarising temperature suitability for malaria parasites \citep{weiss2014air}, which were subsequently used as inputs for modeling malaria prevalence \citep{bhatt2015effect, weiss2019mapping}.
 
-Fully combining observations of incidence and prevalence in a joint model, with multiple likelihoods, addresses the limitations of a simple model using a prevelance map as a covariate.
+Fully combining observations of incidence and prevalence in a joint model, with multiple likelihoods, addresses the limitations of a simple model using a prevalence map as a covariate.
 Advantageously, as the additional malariometric data are being used as response data, they provide more degrees of freedom with which to learn relationships between malaria risk and the environment.
@@
 
-Values at the aggregated, polygon level are given the subscript $a$ while pixel or point level variables are indexed with $b$.
-The polygon incidence case count data, $y_a$ is given a Poisson likelihood
+Values at the aggregated, polygon (or areal) level are given the subscript $A$ while pixel or point level variables are indexed with $P$.
+The polygon incidence case count data, $\mathrm{Count}_A$ is given a Poisson likelihood
 
-$$y_a \sim \operatorname{Poisson}(i_a\mathrm{pop_a})$$
+$$\mathrm{Count}_A \sim \operatorname{Poisson}(\mathrm{Inc}_A\mathrm{pop}_A)$$
 
-where $i_a$ is the estimated polygon incidence rate and $\mathrm{pop_a}$ is the population at risk within that admin unit polygon (as apposed to the true health centre catchment area).
+where $\mathrm{Inc}_A$ is the estimated polygon incidence rate and $\mathrm{pop_A}$ is the population at risk within that admin unit polygon (as apposed to the true health centre catchment area).
 
-Incidence rate is linked to latent pixel-level incidence ($i_b$), prevalence ($p_b$) and predictor variables by the following system of equations.
+Incidence rate is linked to latent pixel-level incidence ($\mathrm{Inc}_P$), prevalence ($\mathrm{Prev}_P$) and predictor variables by the following system of equations.
 
-$$i_a = \frac{ \sum_{b \in a}i_b \mathrm{pop}_b}{\sum_{b \in a}\mathrm{pop}_b} $$
-Here, $b \in a$ denotes that the summation is over the pixels in polygon $a$. 
+$$\mathrm{Inc}_A = \frac{ \sum_{P \in A}\mathrm{Inc}_P \mathrm{pop}_P}{\sum_{P \in A}\mathrm{pop}_P} $$
+Here, $P \in A$ denotes that the summation is over the pixels in polygon $A$. 
 Incidence is related to prevalence by
-$$i_b = \mathrm{PrevInc}(p_b).$$
+$$\mathrm{Inc}_P = \mathrm{PrevInc}(\mathrm{Prev}_P).$$
 Here $\mathrm{PrevInc}$ is a function from a previously fitted model \citep{cameron2015defining} 
-$$\mathrm{PrevInc}: f\left(p_b\right) = 2.616p_b - 3.596{p_b}^2 + 1.594{p_b}^3.$$
-The linear predictor of the model, $\eta_b$, is related to the latent prevalence scale by a typical logit link function.
-$$p_b = \operatorname{logit}^{-1}(\eta_b)$$
+$$\mathrm{PrevInc}: f\left(\mathrm{Prev}_P\right) = 2.6\mathrm{Prev}_P - 3.6{\mathrm{Prev}_P}^2 + 1.6{\mathrm{Prev}_P}^3.$$
+The linear predictor of the model, $\eta_P$, is related to the latent prevalence scale by a typical logit link function.
+$$\mathrm{Prev}_P = \operatorname{logit}^{-1}(\eta_P)$$
 The form of this set of link functions means we calculated predictions of prevalence and incidence simultaneously whether both data types or just one were used.
 
-The linear predictor is composed of an intercept, $b_0$, covariates, $X$, and a vector of regression coefficients $\boldsymbol\beta$.
-We also include a spatial, Gaussian random field, $u_s(\rho, \sigma_u)$ and a polygon-level iid random effect, $ v_a(\sigma_v)$.
-$$\eta_b = \beta_0 + \boldsymbol\beta X  + u_s(\rho, \sigma_u) + v_a(\sigma_v) $$
-The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range on the longitude-latitude scale (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
-The iid random effect, $v_a \sim \operatorname{Normal}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $j$ being grouped together.
+The linear predictor is composed of an intercept, $b_0$, covariates, $X_P$, and a vector of regression coefficients $\boldsymbol\beta$.
+We also include a spatial, Gaussian random field, $u_P(\rho, \sigma_u)$ and a polygon-level iid random effect, $ v_A(\sigma_v)$.
+$$\eta_P = \beta_0 + \boldsymbol\beta X_P  + u_P(\rho, \sigma_u) + v_A(\sigma_v) $$
+The Gaussian spatial effect $u_P(\rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range on the longitude-latitude scale (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
+The iid random effect, $v_A \sim \operatorname{Normal}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $A$ being grouped together.
 Internally, this effect is parameterised as the log of the precision, $\omega_v = \log(\tau_v) = \log(\frac{1}{{\sigma_v}^2})$ to improve numeric stability.
@@
 The models were implemented and fitted in R \citep{R} using Template Model Builder \citep{TMB} which allows a Laplace approximation of the posterior to be calculated.
-We note that R-INLA \citep{INLA} can be used to fit disaggregation models but only when a linear link function is being used \cite{wilson2017pointless}.
+We note that R-INLA \citep{INLA} can be used to fit disaggregation models but only when a linear link function is being used \citep{wilson2017pointless}.
 The hyperparameters are fitted using empirical Bayes whereby the hyperparameters are learned from the data but are treated as point estimates rather than using the full posterior of the hyperparameters.
@@
 
-$$z_b \sim \operatorname{Binomial}(p_b, n_b) $$
-where $p_b$ is the estimated prevalence and $n_b$ is the observed survey sample size. 
+$$z_P \sim \operatorname{Binomial}(\mathrm{Prev}_P, n_P) $$
+where $mathrm{Prev}_P$ is the estimated prevalence and $n_P$ is the observed survey sample size. 
 As this model has both prevalence and incidence data we add a parameter $\alpha$ that modifies the relationship between the two.
-$$i_b = \exp(\alpha)\mathrm{PrevInc}(p_b).$$
+$$\mathrm{Inc}_P = \exp(\alpha)\mathrm{PrevInc}(\mathrm{Prev}_P).$$
 
@@
 
-$$\eta_b = \beta_0 + \mathbf{1}_p\beta_p +  \boldsymbol\beta X  + u_s(\rho, \sigma_u) + v_a(\sigma_v) + w_b(\sigma_w).$$
-As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $\beta_p$ where the indicator function, $\mathbf{1}_p$ denotes that this term is zero except when a prevalence point-survey is being considered.
-The iid random effect, $v_a \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point-surveys within polygon $a$ being in the same group as polygon $a$.
-The second iid random effect, $w_b \sim \operatorname{Normal}(0, \sigma_w)$, was applied to each point-survey.
+$$\eta_P = \beta_0 + \mathbf{1}_\mathrm{Prev}\beta_\mathrm{Prev} +  \boldsymbol\beta X_P  + u_P(\rho, \sigma_u) + v_A(\sigma_v) + w_P(\sigma_w).$$
+As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $\beta_\mathrm{Prev}$ where the indicator function, $\mathbf{1}_\mathrm{Prev}$ denotes that this term is zero except when a prevalence point-survey is being considered.
+The iid random effect, $v_A \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point-surveys within polygon $A$ being in the same group as polygon $A$.
+The second iid random effect, $w_P \sim \operatorname{Normal}(0, \sigma_w)$, was applied to each point-survey.
 To improve numeric stability this effect is also parameterised internally as the log of the precision, $\omega_w = \log(\tau_w) = \log(\frac{1}{{\sigma_w}^2})$.
@@
 This scheme tests specifically whether the joint model can improve predictions by increasing geographic data coverage.
+In each case we tested whether the differences between the new models and the baseline model was greater than expected  by chance using a paired Wilcox test.
 %This situation is particularly common in continental scale models where some countries will have large DHS style surveys but little incidence data.
@@
 \caption{\label{table1}Summary of out-of-sample accuracy for all cross-validation experiments. 
-Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.}
+Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries. 
+The best performing model in each case is shown in bold.
+Results that are significantly better or worse than the baseline (at the 95\% significance level) are indicated with a dagger.
+}
 \centering
@@
 & Madagascar  & 39.06 &  {\bf 35.82} &  36.36\vspace{3mm}\\
-Spatial & Indonesia & {\bf 14.77} &  {\bf 14.77} &  16.46\\
-& Senegal  & 13.09 &  {\bf 12.21} &  15.15\\
-& Madagascar & 67.73 &  50.38 &  {\bf 44.05}\\
+Spatial & Indonesia & {\bf 14.77} &  {\bf 14.77} &  16.46\dag\\
+& Senegal  & 13.09 &  {\bf 12.21} &  15.15\dag\\
+& Madagascar & 67.73 &  50.38\dag &  {\bf 44.05}\dag\\
 \end{tabular}}
@@
 The differences were relatively small in all three countries.
-This lack of strong differences is highlighted by there being no clear differences in scatter plots of observed and predicted data across the three methods (Figure \ref{randompredobspolyfacet}).
+This lack of strong differences is highlighted by there being no clear differences in scatter plots of observed and predicted data across the three methods (Figure S3).
 
@@
 Out-of-sample predictions, under spatial cross validation, from the prevalence GP model and full joint model can be seen in Figures~\ref{predobsmapsen} -- \ref{predobsmapidn}.
-
-\begin{figure}
-% to be removed before submission
-\makebox{\includegraphics[width = 1.05\textwidth]{figures/random_cv_poly_facet.pdf}  }
-\caption{\label{randompredobspolyfacet} 
-Observed-predicted plots (square root scale) of modelled annual malaria incidence (cases per 1000) by country from the random cross-validation experiments for Indonesia (Panel A), Senegal (Panel B) and Madagascar (Panel C).
-Results from the baseline disaggregation model are shown in red, the prevalence GP model is shown in green while the joint model is shown in blue.
-The one-one line is shown with a black line and a simple linear regression through the points is shown by a coloured line.
-}
-
-\end{figure}
-
 %figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
@@
 We have compared the predictive performance of three models: a baseline polygon-only model; a disaggregation model with spatial information from prevalence surveys included as an additional covariate from a separate Gaussian process (GP) model; and a model that jointly learns from polygon incidence data and prevalence point-surveys.
-Overall the prevalence GP model appeared to perform best.
-While the joint model sometimes performed best it also performed worse than baseline in half of the experiments.
+The prevalence GP model never performed worse than baseline and performed better than baseline in one case.
+While the joint model performed best in one case it also performed worse than baseline in two cases.
 Therefore, fitting a spatial Gaussian process to prevalence points and including these predictions seems to be a more reliable way of using spatial information from prevalence points.
@@
 
-A full joint model using both prevalence surveys and incidence data gains a large number of additional degrees of freedom compared to the baseline or prevalence GP models.
+A full joint model using both prevalence surveys and incidence data gains additional statistical power compared to the baseline or prevalence GP models.
 Therefore, it is worth considering why the performance of this model was generally less good than the simpler prevalence GP model that did not benefit from the additional degrees of freedom.
@@
 
-Overall, we have shown that including spatial information from prevalence surveys generally improves the predictive performance of disaggregation regression of aggregated incidence data.
-However, we found that the more complex joint model was unreliable in its predictive performance.
-In contrast, summarising the spatial information from the prevalence surveys by fitting a spatial Gaussian process model and using predictions from this model as a new covariate nearly always improved predictive performance.
+We have presented two methods for combining spatial information from prevalence surveys with disaggregation regression models.
+We found that while the predicted maps were quite different, the polygon-level predictive performance was usually not significantly different.
+The prevalence GP model never performs worse than baseline and performs better than baseline in one case. 
+The full joint model performs worse than baseline in two cases but is the best performing model in one case.
 As more countries produce reliable routine surveillance data, and as more countries reduce their malaria prevalences to the point where prevalence surveys are no longer sensitive, disaggregation regression will become more commonly used.
-Methods such as those presented here should be utilized and further refined to improve disaggregation regression results where and when the requisite data are available.
+Methods such as those presented here should be explored further and refined to improve disaggregation regression results where and when the requisite data are available.
 

### 2020-06-08 si.tex
Edits to SI and bib.

@@
 
+\begin{figure}
+% to be removed before submission
+\makebox{\includegraphics[width = 1.05\textwidth]{figures/random_cv_poly_facet.pdf}  }
+\caption{\label{randompredobspolyfacet} 
+Observed-predicted plots (square root scale) of modelled annual malaria incidence (cases per 1000) by country from the random cross-validation experiments for Indonesia (Panel A), Senegal (Panel B) and Madagascar (Panel C).
+Results from the baseline disaggregation model are shown in red, the prevalence GP model is shown in green while the joint model is shown in blue.
+The one-one line is shown with a black line and a simple linear regression through the points is shown by a coloured line.
+}
+
+\end{figure}
+
 \clearpage

### 2020-06-11 ms.tex
Working through comments tstill.

@@
 The polygon incidence case count data, $\mathrm{Count}_A$ is given a Poisson likelihood
-
 $$\mathrm{Count}_A \sim \operatorname{Poisson}(\mathrm{Inc}_A\mathrm{pop}_A)$$
-
-where $\mathrm{Inc}_A$ is the estimated polygon incidence rate and $\mathrm{pop_A}$ is the population at risk within that admin unit polygon (as apposed to the true health centre catchment area).
+where $\mathrm{Inc}_A$ is the estimated polygon incidence rate and $\mathrm{pop_A}$ is the population at risk within that admin unit polygon (as apposed to the true health-centre catchment area).
 
 Incidence rate is linked to latent pixel-level incidence ($\mathrm{Inc}_P$), prevalence ($\mathrm{Prev}_P$) and predictor variables by the following system of equations.
-
 $$\mathrm{Inc}_A = \frac{ \sum_{P \in A}\mathrm{Inc}_P \mathrm{pop}_P}{\sum_{P \in A}\mathrm{pop}_P} $$
@@
 $$\mathrm{Inc}_P = \mathrm{PrevInc}(\mathrm{Prev}_P).$$
-Here $\mathrm{PrevInc}$ is a function from a previously fitted model \citep{cameron2015defining} 
-$$\mathrm{PrevInc}: f\left(\mathrm{Prev}_P\right) = 2.6\mathrm{Prev}_P - 3.6{\mathrm{Prev}_P}^2 + 1.6{\mathrm{Prev}_P}^3.$$
+Here $\mathrm{PrevInc}$ is a function from a previously fitted model \citep{cameron2015defining}. 
+$$\mathrm{PrevInc}: f\left(\mathrm{Prev}_P\right) = 2.6\cdot\mathrm{Prev}_P - 3.6\cdot{\mathrm{Prev}_P}^2 + 1.6\cdot{\mathrm{Prev}_P}^3.$$
 The linear predictor of the model, $\eta_P$, is related to the latent prevalence scale by a typical logit link function.
 $$\mathrm{Prev}_P = \operatorname{logit}^{-1}(\eta_P)$$
-The form of this set of link functions means we calculated predictions of prevalence and incidence simultaneously whether both data types or just one were used.
+The baseline model is described in terms of prevalence as well as incidence, despite including no prevalence data, so that any differences in predictive ability compared to the full joint model are not simply due to the changed link function.
+Furthermore, the form of this set of link functions means we calculated predictions of prevalence and incidence simultaneously whether both data types or just one were used which can be useful in applied settings.
 
@@
 The hyperparameters are fitted using empirical Bayes whereby the hyperparameters are learned from the data but are treated as point estimates rather than using the full posterior of the hyperparameters.
+We further note that MCMC, even using efficient samplers, is prohibitively slow for these sorts of models \citep{nandi2020disaggregation}.
 
@@
 This covariate is created by fitting a Gaussian random field to the prevalence survey data.
-For each country we fitted a binomial likelihood, hierarchical Gaussian random field with the same hyperpriors for $\rho$ and $\sigma_u$ as above.
+For each country we fitted a model with a binomial likelihood.
+$$z_P \sim \operatorname{Binomial}(\mathrm{Prev}_P, n_P) $$
+Here $\mathrm{Prev}_P$ is the estimated prevalence and $n_P$ is the observed survey sample size. 
+The model only depended on a Gaussian random Field having no covariates or an intercept.
+$$\mathrm{Prev}_P = \operatorname{logit}(\eta_P)$$
+$$\eta_P= \beta_0 +  u_P(\rho, \sigma_u) + w_P(\sigma_w).$$
+We used the same hyperpriors for $\rho$ and $\sigma_u$ as above. 
 These models were fitted using R-INLA \citep{INLA}.
@@
 Additionally, the point-survey data, with positive cases $z_b$, are given a binomial likelihood
-
 $$z_P \sim \operatorname{Binomial}(\mathrm{Prev}_P, n_P) $$
-where $mathrm{Prev}_P$ is the estimated prevalence and $n_P$ is the observed survey sample size. 
+where $\mathrm{Prev}_P$ is the estimated prevalence and $n_P$ is the observed survey sample size. 
 As this model has both prevalence and incidence data we add a parameter $\alpha$ that modifies the relationship between the two.
 $$\mathrm{Inc}_P = \exp(\alpha)\mathrm{PrevInc}(\mathrm{Prev}_P).$$
-
 The only further additions to the baseline model are in the linear predictor which becomes 
-
 $$\eta_P = \beta_0 + \mathbf{1}_\mathrm{Prev}\beta_\mathrm{Prev} +  \boldsymbol\beta X_P  + u_P(\rho, \sigma_u) + v_A(\sigma_v) + w_P(\sigma_w).$$
@@
 & Senegal  & 12.41 &  {\bf 12.37} &  13.07\\
-& Madagascar  & 39.06 &  {\bf 35.82} &  36.36\vspace{3mm}\\
+& Madagascar  & 39.06 &  {\bf 35.82} &  39.01\vspace{3mm}\\
 Spatial & Indonesia & {\bf 14.77} &  {\bf 14.77} &  16.46\dag\\
@@
 
+\subsection{Sensitivity}
+
+We ran sensitivity analyses for particular aspects of the model and prior specification.
+We limited our sensitivity analysis to Madagascar and ran random cross-validation on the full joint model with a number of alterations.
+We tested a weaker prior on $\alpha$, using $\alpha \sim \operatorname{Normal}(0, 1)$ instead of $\alpha \sim \operatorname{Normal}(0, 0.001)$.
+We also examined the sensitivity of the model to the coefficient values used in the PrevInc function. 
+We reran the cross-validation using five draws from a normal distribution, centred on the original parameter values, and with a standard deviation of 0.1.
+Finally, we reran the cross-validation using weaker priors on the random effects but keeping the relative strengths of the iid and spatial random effects the same.
+We used $P(\sigma_u > 1) = 0.01$ and $P(\sigma_v > 0.05) = 0.001$.
+
 % Results and Discussion can be combined.
@@
 
-Under the random cross-validation scheme, the prevalence GP model performed best in Senegal and Madagascar while the joint model performed best in Indonesia (Table \ref{table1}).
-The differences were relatively small in all three countries.
+Under the random cross-validation scheme, there was no significant differences in model performance between models (Table \ref{table1}).
 This lack of strong differences is highlighted by there being no clear differences in scatter plots of observed and predicted data across the three methods (Figure S3).
-
-% spatial 1
-
-Under the spatial cross-validation scheme, the baseline model and prevalence GP models performed best in Indonesia, the prevalence GP performed best in Senegal while the joint model performed best in Madagascar (Table \ref{table1}).
-In contrast to the random cross-validation results, the differences between models was quite strong.
+Under the spatial cross-validation scheme, the prevalence GP model performed significantly better than baseline in Madagascar and was not significantly different from baseline in Indonesia or Senegal (Table \ref{table1}).
+The joint model performed significantly worse than baseline in Indonesia and in Senegal but was the best performing model in Madagascar.
 Furthermore, notable differences can be seen in the scatter plots of observed and predicted values (Figure \ref{spatial2predobspolyfacet}).
@@
 The estimated value for $\alpha$ in all three countries is very close to one (Tables~S1--S3).
-While this might be driven by the prior, we can conclude that there is no strong evidence from the data that this relationship should be scaled differently by country.
-
-% Overall
-
-Overall, inclusion of the spatial information from prevalence surveys yielded predictions that were as good or better than the baseline model in all six experiments (three countries and two cross-validation schemes).
-The prevalence GP model was as good or better than baseline in five out of six experiments.
-In contrast, the joint model was only better than baseline in three out of six experiments.
+While this might be driven by the prior, this indicates that there is no strong evidence from the data that this relationship should be scaled differently by country.
+The MAE for Madagascar does not change when run with a much weaker prior on this parameter.
+However, the MAE for Madagascar varies quite a lot when adding random noise to the parameter values (MAE increases by between 0 and 5.7).
+Changing the priors on the iid effect and the marginal standard deviation of the Gaussian random field did not alter predictive performance.
 
@@
 However, given that this comparison was conducted on datasets from only three countries, it is challenging to draw firm conclusions.
+The significant differences between models all occurred under spatial cross-validation.
+This makes sense given that there is little additional spatial information provided by the prevalence data under random cross-validation.
 
@@
 We used three case studies, limited by the number of countries with good aggregated incidence data as well as good prevalence survey data.
-Given the small number of case studies it is hard to determine when these methods are likely to be most effective.
+Given the small number of case studies it is hard to determine in which countries these methods are likely to be most effective.
 However, the greatest benefits here were seen in Madagascar, a country with more intermediate transmission intensities.
 In the future, two groups of countries might particularly benefit from the methods presented here.
-Firstly countries who have had large prevalence surveys in the past and whose reporting systems are improving, such as Ethiopia, might benefit from these methods.
+Firstly countries like Madagascar with intermedia transmission intensities and good surveillance data and good prevalence data.
 Secondly, countries that have lots of prevalence surveys and are adjacent to countries with good reporting systems, (e.g.

### 2020-06-11 si.tex
Working through comments tstill.

@@
 \end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.6\textheight]{figures/mdg_baseline_ci.png}
+
+\caption{Upper and lower credible intervals for the baseline model fitted to all data in Madagascar.}
+\label{basemdgci}
+\end{figure}
+
 \begin{figure}[h!]
@@
 
+\includegraphics[width = 0.6\textheight]{figures/mdg_prgp_ci.png}
+
+\caption{Upper and lower credible intervals for the prev gp model fitted to all data in Madagascar.}
+\label{prgpmdgci}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
 \includegraphics[width = 0.3\textheight]{figures/mdg_joint_api.png}
@@
 \label{jointmdg}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.6\textheight]{figures/mdg_ci.png}
+
+\caption{Upper and lower credible intervals for the joint model fitted to all data in Madagascar.}
+\label{jointmdgci}
 \end{figure}
@@
 \end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.6\textheight]{figures/sen_baseline_ci.png}
+
+\caption{Upper and lower credible intervals for the baseline model fitted to all data in Senegal.}
+\label{basesenci}
+\end{figure}
+
 \begin{figure}[h!]
@@
 
+\includegraphics[width = 0.6\textheight]{figures/sen_prgp_ci.png}
+
+\caption{Upper and lower credible intervals for the prev gp model fitted to all data in Senegal.}
+\label{prgpsenci}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
 \includegraphics[width = 0.3\textheight]{figures/sen_joint_api.png}
@@
 
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 0.6\textheight]{figures/sen_ci.png}
+
+\caption{Upper and lower credible intervals for the joint model fitted to all data in Senegal.}
+\label{jointsenci}
+\end{figure}
+
+\clearpage
 \subsubsection{Indonesia}
@@
 \end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 1.1\textwidth]{figures/idn_baseline_ci.png}
+
+\caption{Upper and lower credible intervals for the basline model fitted to all data in Indonesia.}
+\label{basemdgci}
+\end{figure}
+
 \begin{figure}[h!]
@@
 
+\includegraphics[width = 1.1\textwidth]{figures/idn_prgp_ci.png}
+
+\caption{Upper and lower credible intervals for the prev gp model fitted to all data in Indonesia.}
+\label{prgpmdgci}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
 \includegraphics[width = 0.5\textheight]{figures/idn_joint_api.png}
@@
 \label{jointidn}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width = 1.1\textwidth]{figures/idn_ci.png}
+
+\caption{Upper and lower credible intervals for the joint model fitted to all data in Indonesia.}
+\label{jointmdgci}
 \end{figure}

### 2020-06-15 ms.tex
More review edits.

@@
 However, in areas with both routine surveillance data and prevalence surveys, models that make use of the spatial information from prevalence point-surveys might make more accurate predictions.
-Using case studies in Indonesia, Senegal and Madagascar, we compare two methods for incorporating point-level, spatial information into disaggregation regression models.
-The first simply fits a Gaussian random field to prevalence point-surveys to create a new covariate.
+Using case studies in Indonesia, Senegal and Madagascar, we compare the out-of-sample mean absolute error for two methods for incorporating point-level, spatial information into disaggregation regression models.
+The first simply fits a binomial-likelihood, logit-link, Gaussian random field to prevalence point-surveys to create a new covariate.
 The second is a multi-likelihood model that is fitted jointly to prevalence point-surveys and polygon incidence data.
-We find that in most cases there is no difference in performance between the models.
+We find that in most cases there is no difference in mean absolute error between the models.
 In some cases the baseline model performed the best while in one case the new models performed the best.
-More generally, our results demonstrate that combining these types of data has the potential to improve estimates of malaria incidence but that simpler baseline models should always be fitted as a benchmark.
+More generally, our results demonstrate that combining these types of data has the potential to reduce absolute error in estimates of malaria incidence but that simpler baseline models should always be fitted as a benchmark.
 \end{abstract}
@@
 
-Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level, routine surveillance records of incidence \citep{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log, johnson2019spatially}.
+Disaggregation regression methods have been proposed as a way to model malaria burden using polygon-level, routine surveillance records of incidence \citep{sturrock2014fine, wilson2017pointless, taylor2017continuous, li2012log, johnson2019spatially, arambepola2020simulation}.
 Disaggregation regression requires an aggregation step in which the high-resolution estimates of disease incidence are summed to match the level of the administrative unit at which the incidence data are observed.
@@
 As the prevalence point-surveys cover different age ranges they were standardised to the 2--10 year-range using a previously published model \citep{smith2007standardizing}. 
+This standardisation generally makes small adjustments to the prevalence values.
+Carrying the uncertainty from this model through to the final model was deemed out of scope for this work.
 As described, the age standardisation model gives the surveys with zero positive cases a small positive prevalence. 
-The polygon incidence data were collated from various government reports and adjusted for incompleteness using methods defined by Cibulskis and colleagues \citep{cibulskis2011worldwide, weiss2019mapping}.
+The polygon incidence data were collated from various government reports and adjusted for incompleteness using methods defined by Cibulskis and colleagues \citep{cibulskis2011worldwide}
+Full details of all the preprocessing performed on this data is given in the supplementary materials of \cite{weiss2019mapping}. 
 These adjustments account for underreporting of clinical cases due to lack of treatment seeking, missing case reports (from a health facility that reported for 11 months in a year for example), and cases that sought medical attention outside the public health systems \citep{battle2016treatment}.
@@
 Here $\mathrm{PrevInc}$ is a function from a previously fitted model \citep{cameron2015defining}. 
-$$\mathrm{PrevInc}: f\left(\mathrm{Prev}_P\right) = 2.6\cdot\mathrm{Prev}_P - 3.6\cdot{\mathrm{Prev}_P}^2 + 1.6\cdot{\mathrm{Prev}_P}^3.$$
+$$\mathrm{PrevInc}: f\left(\mathrm{Prev}_P\right) = 2.6\cdot\mathrm{Prev}_P - 3.6\cdot{(\mathrm{Prev}_P)}^2 + 1.6\cdot{(\mathrm{Prev}_P)}^3.$$
 The linear predictor of the model, $\eta_P$, is related to the latent prevalence scale by a typical logit link function.
@@
 The Gaussian spatial effect $u_P(\rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range on the longitude-latitude scale (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
-The iid random effect, $v_A \sim \operatorname{Normal}(0, \sigma_v)$,  was grouped by polygon, with all pixels within polygon $A$ being grouped together.
+The iid random effect, $v_A \sim \operatorname{Normal}(\mu = 0, \sigma = \sigma_v)$,  was grouped by polygon, with all pixels within polygon $A$ being grouped together (all subsequent normal distributions are also parameterised in terms of the standard deviation).
 Internally, this effect is parameterised as the log of the precision, $\omega_v = \log(\tau_v) = \log(\frac{1}{{\sigma_v}^2})$ to improve numeric stability.
@@
 As Senegal has a lower range of incidences in the data we set $\xi$ to a smaller value for this country.
+Plots of this prior are shown in S32-33.
 
 We assigned $\sigma_v$ a penalised complexity prior \citep{simpson2017penalising} such that $P(\sigma_v > 0.05) = 0.0000001$.
+This gives a 95\% prior credible interval of $7.8\times 10^{-5}$ -- $1.1\times 10^{-2}$.
 This was based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an separately derived upper and lower bound for the case counts using the approach defined by Cibulskis and colleagues \citep{cibulskis2011worldwide}.
@@
 $$\eta_P = \beta_0 + \mathbf{1}_\mathrm{Prev}\beta_\mathrm{Prev} +  \boldsymbol\beta X_P  + u_P(\rho, \sigma_u) + v_A(\sigma_v) + w_P(\sigma_w).$$
-As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $\beta_\mathrm{Prev}$ where the indicator function, $\mathbf{1}_\mathrm{Prev}$ denotes that this term is zero except when a prevalence point-survey is being considered.
+As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $\beta_\mathrm{Prev}$ where the indicator function, $\mathbf{1}_\mathrm{Prev}$, denotes that this term is zero except when a prevalence point-survey is being considered.
 The iid random effect, $v_A \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point-surveys within polygon $A$ being in the same group as polygon $A$.
@@
 
-Given that the PrevInc relationship is fitted to the best available data, we have fairly strong \emph{a priori} confidence in it.
+The PrevInc relationship was fitted to the best available data (matched prevalence and incidence studies both at point level) and this dataset.
+Therefore we have some \emph{a priori} confidence in it and from a regularisation standpoint would not wish it to be easily overridden by the data used in these models which are mismatched in spatial scale.
 Therefore, our prior belief is that $\exp(\alpha)$ is close to one (i.e.\thinspace the relationship remains unchanged) and therefore that $\alpha$ is close to zero.
@@
 In the second validation scheme, the incidence data was split into spatial cross-validation folds, using k means clustering on polygon centroids, while again all prevalence points were used in all folds (Figure~S2).
-The number of folds was seven for Indonesia, five for Senegal and three for Madagascar due to their differing sizes and epidemiological settings.
+The number of folds was seven for Indonesia, five for Senegal and three for Madagascar.
+The number of folds was chosen based on the geographical sizes of the countries.
 This scheme tests specifically whether the joint model can improve predictions by increasing geographic data coverage.
@@
 
-\subsection{Sensitivity}
+\subsection*{Sensitivity}
 
@@
 The prevalence GP model never performed worse than baseline and performed better than baseline in one case.
-While the joint model performed best in one case it also performed worse than baseline in two cases.
+The joint model performed best in one case but also performed worse than baseline in two cases.
 Therefore, fitting a spatial Gaussian process to prevalence points and including these predictions seems to be a more reliable way of using spatial information from prevalence points.
@@
 The significant differences between models all occurred under spatial cross-validation.
-This makes sense given that there is little additional spatial information provided by the prevalence data under random cross-validation.
+This implies that the models are not using the additional data to learn more accurate relationships between the environment and malaria incidence. 
+Instead it suggests that the models are using the spatial information in the data to improve predictions.
 
@@
 
+In our sensitivity analysis we found that changing the coefficients in the relationship considerably reduced predictive ability (though weakening the prior on $\alpha$ did not). 
+We might interpret this as suggesting that the prior was too strong but that as the data did not contradict the prior relationship, this did not matter.
 Future models could potentially be improved by using a more flexible approach for addressing the shortcomings of the prevalence-incidence relationship \citep{cameron2015defining} being used in this context.
@@
 Given the small number of case studies it is hard to determine in which countries these methods are likely to be most effective.
-However, the greatest benefits here were seen in Madagascar, a country with more intermediate transmission intensities.
-In the future, two groups of countries might particularly benefit from the methods presented here.
-Firstly countries like Madagascar with intermedia transmission intensities and good surveillance data and good prevalence data.
+However, the benefits here were only seen in Madagascar, a country with more intermediate transmission intensities.
+In the future, two types of study region might particularly benefit from the methods presented here.
+Firstly countries like Madagascar with intermediate transmission intensities and good surveillance data and good prevalence data.
 Secondly, countries that have lots of prevalence surveys and are adjacent to countries with good reporting systems, (e.g.

### 2020-06-15 si.tex
Add plots of the priors.

@@
 
+\tableofcontents
+
 % Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
@@
 % Current address notes
-
+\clearpage
 \section{Crossvalidation schemes}
@@
 
+\clearpage
+\section{Out-of-sample scatter plot}
+
 \begin{figure}
@@
 \clearpage
-\subsection{Full model predictions}
-\subsubsection{Madagascar}
+\section{Full model predictions}
+\subsection{Madagascar}
 
@@
 
-\subsubsection{Senegal}
+\subsection{Senegal}
 
@@
 \clearpage
-\subsubsection{Indonesia}
+\subsection{Indonesia}
 
@@
 
-\subsection{Full model fields}
+\section{Full model fields}
 
-\subsubsection{Senegal}
+\subsection{Senegal}
 
@@
 \clearpage
-\subsubsection{Madagascar}
+\subsection{Madagascar}
 
@@
 
+\clearpage
+\section{Priors}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.8\textwidth]{figures/spatial_pc_density.png}
+
+\caption{Probability density of the penalised complexity prior for the range and marginal standard deviation for the spatial random field as used in Madagascar models..}
+\label{dens}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.8\textwidth]{figures/spatial_pc_logdensity.png}
+
+\caption{Log probability density of the penalised complexity prior for the range and marginal standard deviation for the spatial random field as used in Madagascar models..}
+\label{logdens}
+\end{figure}
+
 \end{document}

### 2020-10-15 si.tex
Add table for robustness.

@@
 \clearpage
+\section{Priors}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.8\textwidth]{figures/spatial_pc_density.png}
+
+\caption{Probability density of the penalised complexity prior for the range and marginal standard deviation for the spatial random field as used in Madagascar models..}
+\label{dens}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.8\textwidth]{figures/spatial_pc_logdensity.png}
+
+\caption{Log probability density of the penalised complexity prior for the range and marginal standard deviation for the spatial random field as used in Madagascar models..}
+\label{logdens}
+\end{figure}
+
+\clearpage
 \section{Cross-validation predictions}
@@
 \end{figure}
+
+\clearpage
 
@@
 
-\clearpage
-\section{Priors}
+\section{Robustness experiment}
 
-\begin{figure}[h!]
+\begin{table}
+\caption{\label{table1}Summary of out-of-sample accuracy for all cross-validation, robustness experiments.
+For each fold, one data point in the training set is changed to either 5 times or $\frac{1}{5}$ times its original value.
+All test data is kept the same. 
+Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries. 
+Results that are significantly better or worse than the baseline (at the 95\% significance level) are indicated with a dagger.
+}
 \centering
-
-\includegraphics[width =  0.8\textwidth]{figures/spatial_pc_density.png}
-
-\caption{Probability density of the penalised complexity prior for the range and marginal standard deviation for the spatial random field as used in Madagascar models..}
-\label{dens}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-
-\includegraphics[width =  0.8\textwidth]{figures/spatial_pc_logdensity.png}
-
-\caption{Log probability density of the penalised complexity prior for the range and marginal standard deviation for the spatial random field as used in Madagascar models..}
-\label{logdens}
-\end{figure}
+\fbox{%
+\begin{tabular}{*{5}{l}}
+{\bf Cross-validation} & {\bf Country}  & {\bf Baseline} & {\bf Prev GP} & {\bf Joint} \\
+\hline
+Random & Indonesia  &  &   &  \\
+& Senegal 13.35 & 13.28 & 14.47  &  \\
+& Madagascar  &  & &  \vspace{3mm}\\
+Spatial & Indonesia &  &  &  \\
+& Senegal 11.70 & 11.53 & 13.97   &  \\
+& Madagascar &  &   &  \\
+\end{tabular}}
+\end{table}
 

### 2021-01-09 ms.tex
Last edits from previous resubmit.

@@
 The second is a multi-likelihood model that is fitted jointly to prevalence point-surveys and polygon incidence data.
-We find that in most cases there is no difference in mean absolute error between the models.
-In some cases the baseline model performed the best while in one case the new models performed the best.
+We find that in most cases there is no difference in mean absolute error between models.
+In only one case did the new models performed the best.
 More generally, our results demonstrate that combining these types of data has the potential to reduce absolute error in estimates of malaria incidence but that simpler baseline models should always be fitted as a benchmark.
@@
 Fully combining observations of incidence and prevalence in a joint model, with multiple likelihoods, addresses the limitations of a simple model using a prevalence map as a covariate.
-Advantageously, as the additional malariometric data are being used as response data, they provide more degrees of freedom with which to learn relationships between malaria risk and the environment.
+Advantageously, as the additional malariometric data are being used as response data, they provide more statistical power with which to learn relationships between malaria risk and the environment.
 Such a model can also learn the relationship between different types of malaria response metrics at the same time as making spatial estimates, thereby producing statistically and epidemiologically consistent outputs for both incidence and prevalence.
@@
 Secondly, we formulate a joint model that combines polygon incidence data and prevalence point-surveys using separate likelihoods for both data types.
+This model therefore has the potential to learn from the prevalence data in two ways.
+First, it has the potential to learn more accurate relationships between malaria incidence and the environment from any prevalence data that is in medium transmission areas. 
+Second, it can learn from the spatial information in the prevalence data as well.
 We relate the differing malariometric measures by using a previously estimated relationship within the model \citep{cameron2015defining} which is then adjusted as part of the model fitting process.
@@
 As Senegal has a lower range of incidences in the data we set $\xi$ to a smaller value for this country.
-Plots of this prior are shown in S32-33.
+Plots of this prior are shown in Figure~S4 and S5.
 
@@
 Here $\mathrm{Prev}_P$ is the estimated prevalence and $n_P$ is the observed survey sample size. 
-The model only depended on a Gaussian random Field having no covariates or an intercept.
-$$\mathrm{Prev}_P = \operatorname{logit}(\eta_P)$$
-$$\eta_P= \beta_0 +  u_P(\rho, \sigma_u) + w_P(\sigma_w).$$
+The model only depended on a Gaussian random field having no covariates or an intercept.
+$$\mathrm{Prev}_P = \operatorname{logit}^{-1}(u_P(\rho, \sigma_u))$$
 We used the same hyperpriors for $\rho$ and $\sigma_u$ as above. 
@@
 To compare the three models we used two cross-validation schemes. 
-In the first (random), the incidence data was split into ten cross-validation folds while all the prevalence data was used in each case (Figure~S1. 
+In the first (random), the incidence data was split into ten cross-validation folds while all the prevalence data was used in each case (Figure~S1). 
 %This cross-validation scheme directly addresses the question of whethe
@@
 Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries. 
-The best performing model in each case is shown in bold.
 Results that are significantly better or worse than the baseline (at the 95\% significance level) are indicated with a dagger.
@@
 \hline
-Random & Indonesia  & 13.95 &  14.09 &  {\bf 13.79}\\
-& Senegal  & 12.41 &  {\bf 12.37} &  13.07\\
-& Madagascar  & 39.06 &  {\bf 35.82} &  39.01\vspace{3mm}\\
-Spatial & Indonesia & {\bf 14.77} &  {\bf 14.77} &  16.46\dag\\
-& Senegal  & 13.09 &  {\bf 12.21} &  15.15\dag\\
-& Madagascar & 67.73 &  50.38\dag &  {\bf 44.05}\dag\\
+Random & Indonesia  & 13.95 &  14.09 &  13.79\\
+& Senegal  & 12.41 &  12.37 &  13.07\\
+& Madagascar  & 39.06 & 35.82 &  39.01\vspace{3mm}\\
+Spatial & Indonesia & 14.77 & 14.77 &  16.46\dag\\
+& Senegal  & 13.09 &   12.21 &  15.15\dag\\
+& Madagascar & 67.73 &  50.38\dag &  44.05\dag\\
 \end{tabular}}
@@
 
-\subsection*{Sensitivity}
+\subsection*{Sensitivity analysis}
 
@@
 
-We have compared the predictive performance of three models: a baseline polygon-only model; a disaggregation model with spatial information from prevalence surveys included as an additional covariate from a separate Gaussian process (GP) model; and a model that jointly learns from polygon incidence data and prevalence point-surveys.
+We have compared the predictive performance (MAE) of three models: a baseline polygon-only model; a disaggregation model with spatial information from prevalence surveys included as an additional covariate from a separate Gaussian process (GP) model; and a model that jointly learns from polygon incidence data and prevalence point-surveys.
 The prevalence GP model never performed worse than baseline and performed better than baseline in one case.
@@
 A full joint model using both prevalence surveys and incidence data gains additional statistical power compared to the baseline or prevalence GP models.
-Therefore, it is worth considering why the performance of this model was generally less good than the simpler prevalence GP model that did not benefit from the additional degrees of freedom.
+Therefore, it is worth considering why the performance of this model was generally less good than the simpler prevalence GP model that did not benefit from the additional statistical power.
 One potential reason is that the malariometric data are on different scales.
@@
 We used three case studies, limited by the number of countries with good aggregated incidence data as well as good prevalence survey data.
+Two types of study region seemed likely to benefit from the methods presented here.
+First, countries like Madagascar with intermediate transmission intensities and good surveillance data and good prevalence data.
+Second, countries that have lots of prevalence surveys and are adjacent to countries with good reporting systems, (e.g.
+Papua New Guinea and neighbouring Indonesia), might also benefit from models that share information between countries.
 Given the small number of case studies it is hard to determine in which countries these methods are likely to be most effective.
-However, the benefits here were only seen in Madagascar, a country with more intermediate transmission intensities.
-In the future, two types of study region might particularly benefit from the methods presented here.
-Firstly countries like Madagascar with intermediate transmission intensities and good surveillance data and good prevalence data.
-Secondly, countries that have lots of prevalence surveys and are adjacent to countries with good reporting systems, (e.g.
-Papua New Guinea and neighbouring Indonesia), might also benefit from models that share information between countries.
+However, the benefits here were only seen in spatial cross-validation schemes suggesting that the models were only effectively using spatial information.
 

### 2021-01-09 ms.tex
Remove square root scaling from fig legends.

@@
 Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries. 
-Results that are significantly better or worse than the baseline (at the 95\% significance level) are indicated with a dagger.
+Results that are significantly better or worse than the baseline (at the 95\% significance level) are indicated with a dagger or asterisk respectively.
 }
@@
 & Madagascar  & 39.06 & 35.82 &  39.01\vspace{3mm}\\
-Spatial & Indonesia & 14.77 & 14.77 &  16.46\dag\\
-& Senegal  & 13.09 &   12.21 &  15.15\dag\\
+Spatial & Indonesia & 14.77 & 14.77 &  16.46$\ast$\\
+& Senegal  & 13.09 &   12.21 &  15.15$\ast$\\
 & Madagascar & 67.73 &  50.38\dag &  44.05\dag\\
@@
 \caption{\label{spatial2predobspolyfacet} 
-Observed-predicted plots (square root scale) of modelled annual malaria incidence (cases per 1000) by country from the spatial cross-validation experiments for Indonesia (Panel A), Senegal (Panel B) and Madagascar (Panel C).
+Observed-predicted plots of modelled annual malaria incidence (cases per 1000) by country from the spatial cross-validation experiments for Indonesia (Panel A), Senegal (Panel B) and Madagascar (Panel C).
 Results from the baseline disaggregation model are shown in red, the prevalence GP model is shown in green while the joint model is shown in blue.

### 2021-01-09 si.tex
Remove robustness
Remove square root scaling from fig legends.

--- 2020-06-15 si.tex
@@
 \caption{\label{randompredobspolyfacet} 
-Observed-predicted plots (square root scale) of modelled annual malaria incidence (cases per 1000) by country from the random cross-validation experiments for Indonesia (Panel A), Senegal (Panel B) and Madagascar (Panel C).
+Observed-predicted plots of modelled annual malaria incidence (cases per 1000) by country from the random cross-validation experiments for Indonesia (Panel A), Senegal (Panel B) and Madagascar (Panel C).
 Results from the baseline disaggregation model are shown in red, the prevalence GP model is shown in green while the joint model is shown in blue.
@@
 
+\end{figure}
+
+\clearpage
+\section{Priors}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.8\textwidth]{figures/spatial_pc_density.png}
+
+\caption{Probability density of the penalised complexity prior for the range and marginal standard deviation for the spatial random field as used in Madagascar models..}
+\label{dens}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.8\textwidth]{figures/spatial_pc_logdensity.png}
+
+\caption{Log probability density of the penalised complexity prior for the range and marginal standard deviation for the spatial random field as used in Madagascar models..}
+\label{logdens}
 \end{figure}
@@
 
-\clearpage
-\section{Priors}
-
-\begin{figure}[h!]
-\centering
-
-\includegraphics[width =  0.8\textwidth]{figures/spatial_pc_density.png}
-
-\caption{Probability density of the penalised complexity prior for the range and marginal standard deviation for the spatial random field as used in Madagascar models..}
-\label{dens}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-
-\includegraphics[width =  0.8\textwidth]{figures/spatial_pc_logdensity.png}
-
-\caption{Log probability density of the penalised complexity prior for the range and marginal standard deviation for the spatial random field as used in Madagascar models..}
-\label{logdens}
-\end{figure}
-
 \end{document}

### 2021-01-09 ms.tex
Describe how we examine postior widths.

@@
 To assess how well the models were calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.
+Finally we compared the widths of the posterior distributions for the regression parameters (the $\beta_i$'s) and the hyperparameters for the random field ($\rho$ and $\sigma_u$).
+For these comparisons we report the average of the standard deviations of the posteriors for each group of parameters across all the random cross-validation model fits.
+The prevalence GP model has one more $\beta_i$ than the other two models that relates to the additional covariate created by fitting a Gaussian Process to prevalence data. 
+We did not include this parameter when comparing the widths of the $\beta_i$ parameters.
 %Finally, we fitted each model to the full data set and examine the parameter estimates for these models.

### 2021-02-25 ms.tex
Final edits.

--- 2021-01-09 ms.tex
@@
 The prevalence point-survey data were extracted from the Malaria Atlas Project database \citep{bhatt2015effect, guerra2007assembling, pfeffer2018ma}. 
+This data includes DHS and MIS data as well as prevalence surveys collated from the literature.
 As the prevalence point-surveys cover different age ranges they were standardised to the 2--10 year-range using a previously published model \citep{smith2007standardizing}. 
@@
 As described, the age standardisation model gives the surveys with zero positive cases a small positive prevalence. 
-The polygon incidence data were collated from various government reports and adjusted for incompleteness using methods defined by Cibulskis and colleagues \citep{cibulskis2011worldwide}
+The polygon incidence data were collated from various government reports and adjusted for incompleteness using methods defined by Cibulskis and colleagues \citep{cibulskis2011worldwide}.
 Full details of all the preprocessing performed on this data is given in the supplementary materials of \cite{weiss2019mapping}. 
@@
 Within this five year period, we considered malaria unchanging and did not model time explicitely.
-For Indonesia we selected polygon incidence data from 2012 that covers 379 administrative units, and prevalence data from 2010 to 2014 that consists of 1,233 survey clusters (i.e.
-unique locations), representing 230,747 individuals.
+For Indonesia we selected polygon incidence data from 2012 that covers 379 administrative units, and prevalence data from 2010 to 2014 that consists of 1,233 survey clusters (i.e.\thinspace unique locations), representing 230,747 individuals.
 For Senegal we selected 2015 for polygon incidence data (41 administrative units) and 2013 to 2017 for prevalence data (804 clusters, 17,037 individuals).
+698 of these surveys were from the Senegal continuous DHS survey with 201, 114, 161 and 222 surveys areas in the years 2008 to 2011. 
 Finally, for Madagascar we selected 2013 for polygon incidence (110 administrative units) and 2011 to 2015 for prevalence data (1,049 clusters, 36,411 individuals).
+Of these, 898 surveys were from the Malaria Indicator Surveys in 2011 (266 locations), 2013 (274 locations) and 2016 (358 locations).
+In DHS surveys, but not MIS surveys, urban areas are typically oversampled.
+However, this oversampling should be accounted for by the inclusion an accessibility to cities covariate as described below.
 
@@
 
-The linear predictor is composed of an intercept, $b_0$, covariates, $X_P$, and a vector of regression coefficients $\boldsymbol\beta$.
-We also include a spatial, Gaussian random field, $u_P(\rho, \sigma_u)$ and a polygon-level iid random effect, $ v_A(\sigma_v)$.
-$$\eta_P = \beta_0 + \boldsymbol\beta X_P  + u_P(\rho, \sigma_u) + v_A(\sigma_v) $$
+The linear predictor is composed of an intercept, $\beta_0$, covariates, $X_P$, and a vector of regression coefficients $\boldsymbol\beta$.
+We also include a spatial, Gaussian random field, $u_P(\rho, \sigma_u)$ and a polygon-level iid random effect, $ v_{A_p}(\sigma_v)$.
+$$\eta_P = \beta_0 + \boldsymbol\beta X_P  + u_P(\rho, \sigma_u) + v_{A_p}(\sigma_v) $$
 The Gaussian spatial effect $u_P(\rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range on the longitude-latitude scale (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
-The iid random effect, $v_A \sim \operatorname{Normal}(\mu = 0, \sigma = \sigma_v)$,  was grouped by polygon, with all pixels within polygon $A$ being grouped together (all subsequent normal distributions are also parameterised in terms of the standard deviation).
+The iid random effect, $v_{A_p} \sim \operatorname{Normal}(\mu = 0, \sigma = \sigma_v)$,  was grouped by polygon, with all pixels within polygon $A$ being grouped together (all subsequent normal distributions are also parameterised in terms of the standard deviation).
 Internally, this effect is parameterised as the log of the precision, $\omega_v = \log(\tau_v) = \log(\frac{1}{{\sigma_v}^2})$ to improve numeric stability.
@@
 Finally, we complete the model by setting priors on the parameters $\beta_0, \boldsymbol\beta, \rho, \sigma_u$ and $\sigma_v$.
-The intercept was given a wide prior, $b_0 \sim \operatorname{Normal}(-2, 4)$, with a mean relating to a prevalence of 0.12 as we know \emph{a priori} that these countries have low or medium levels of malaria transmission.
+The intercept was given a wide prior, $\beta_0 \sim \operatorname{Normal}(-2, 4)$, with a mean relating to a prevalence of 0.12 as we know \emph{a priori} that these countries have low or medium levels of malaria transmission.
 We set independent, regularising priors on the regression coefficients $\beta_i \sim \operatorname{Normal}(0, 0.04)$. 
@@
 We used different $\zeta$  and $\xi$ values for each country: Indonesia $\zeta = 3, \xi = 1$, Senegal $\zeta = 1, \xi = 0.5$ and Madagascar $\zeta = 1, \xi = 1$.
+This gives 95\% prior credible interval for $\sigma_u$ of (0.0020, 0.18) and for $\rho$ of (2.2, 7.9) in Madagascar.
 We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected at the scale of individual countries \citep{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.
@@
 Here $\mathrm{Prev}_P$ is the estimated prevalence and $n_P$ is the observed survey sample size. 
-The model only depended on a Gaussian random field having no covariates or an intercept.
-$$\mathrm{Prev}_P = \operatorname{logit}^{-1}(u_P(\rho, \sigma_u))$$
+The model only depended on a Gaussian random field having no covariates.
+$$\mathrm{Prev}_P = \operatorname{logit}^{-1}(\beta_\mathrm{GP} + u_P(\rho, \sigma_u))$$
 We used the same hyperpriors for $\rho$ and $\sigma_u$ as above. 
 These models were fitted using R-INLA \citep{INLA}.
-To be in the correct scale for the dissagregation model, the inverse logit of the predicted Gaussian field (i.e. the linear predictor of the model) was used as the additional covariate.
+To be in the correct scale for the dissagregation model, the inverse logit of the predicted Gaussian field (i.e.\thinspace the linear predictor of the model) was used as the additional covariate.
 
@@
 $$\mathrm{Inc}_P = \exp(\alpha)\mathrm{PrevInc}(\mathrm{Prev}_P).$$
-The only further additions to the baseline model are in the linear predictor which becomes 
-$$\eta_P = \beta_0 + \mathbf{1}_\mathrm{Prev}\beta_\mathrm{Prev} +  \boldsymbol\beta X_P  + u_P(\rho, \sigma_u) + v_A(\sigma_v) + w_P(\sigma_w).$$
-As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $\beta_\mathrm{Prev}$ where the indicator function, $\mathbf{1}_\mathrm{Prev}$, denotes that this term is zero except when a prevalence point-survey is being considered.
-The iid random effect, $v_A \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point-surveys within polygon $A$ being in the same group as polygon $A$.
+The only further change to the baseline model are in the linear predictor.
+For incidence data the linear predictor remains unchanged.
+The linear predictor for the prevalence data is
+$$\eta_P = \beta_0 + \beta_\mathrm{Prev} +  \boldsymbol\beta X_P  + u_P(\rho, \sigma_u) + v_{A_p}(\sigma_v) + w_P(\sigma_w).$$
+As well as the global intercept, $\beta_0$, this model has a prevalence survey specific intercept $\beta_\mathrm{Prev}$.
+The iid random effect, $v_{A_p} \sim \operatorname{Norm}(0, \sigma_v)$, was again grouped by polygon, with all pixels and point-surveys within polygon $A$ being in the same group as polygon $A$.
 The second iid random effect, $w_P \sim \operatorname{Normal}(0, \sigma_w)$, was applied to each point-survey.
@@
 We considered the ability of the model to predict polygon incidence to be our main objective and our performance metric for this was mean absolute error (MAE).
-As the models were fitted on data on different scales we found that observations and predictions were sometimes correlated but shifted from the one-one line (i.e.
-were biased) and therefore correlation metrics were misleading.
+As the models were fitted on data on different scales we found that observations and predictions were sometimes correlated but shifted from the one-one line (i.e.\thinspace were biased) and therefore correlation metrics were misleading.
+We also calculated mean errors to assess the bias of the models.
 % Why not correlation
@@
 This lack of strong differences is highlighted by there being no clear differences in scatter plots of observed and predicted data across the three methods (Figure S3).
-Under the spatial cross-validation scheme, the prevalence GP model performed significantly better than baseline in Madagascar and was not significantly different from baseline in Indonesia or Senegal (Table \ref{table1}).
+Under the spatial cross-validation scheme, the prevalence GP model performed significantly better than baseline in Madagascar and was not significantly different from baseline in Indonesia or Senegal (Table \ref{table1}, Figure~\ref{spatial2predobspolyfacet}).
 The joint model performed significantly worse than baseline in Indonesia and in Senegal but was the best performing model in Madagascar.
@@
 However, the joint model clearly performs better in Madagascar with the polygon-only model unable to predict high incidence observations accurately.
-Out-of-sample predictions, under spatial cross validation, from the prevalence GP model and full joint model can be seen in Figures~\ref{predobsmapsen} -- \ref{predobsmapidn}.
+Maps of out-of-sample predictions, under spatial cross validation, can be seen in Figures~\ref{predobsmapsen} -- \ref{predobsmapidn}.
+In the Indonesian plots, one clear difference is that the joint model overpredicts on the island of Java. 
 %figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
@@
 There was no clear difference in calibration between the different models.
+The bias in the models was generally fairly small (less than 15) with most models having a tendency to underpredict.
+While the differences in bias were not large, the joint model had the lowest bias in four out six cases (Tables S4--S5).
+Plots of model error against observed API, under spatial cross are shown in Figures S35--37.
 
@@
 We can further investigate why the models performed as they did by examining the parameters estimated in the models fitted to all data (Tables~S1--S3).
-Firstly we can compare the regression parameter for the prevalence GP covariate in the three countries noting that in Indonesia the prevalence GP model performed worse than baseline under random cross-validation and had equal performance to baseline under spatial cross-validation.
+We can see that for all covariate regression parameters in Madagascar and Senegal (Tables~S1--S2) the standard deviation of the posterior is smaller in the joint model than in the prevalence GP model.
+For indonesia the standard deviation of the posteriors is smaller in the prevalence GP model 6 our of 8 times.
+Similarly, the standard deviation of the posteriors of the hyperparameters of the random field are smaller for the joint model in Senegal and Madagascar but larger for Indonesia.
+Given that these models are using the additional prevalence data as response data, this is to be expected.
+While noting that the coverage is similarly acceptable in all models (Table~\ref{table3}), this implies that more is being learned by the joint model and that these models might be useful for analyses that are more focused on estimating specific parameters.
+
+We can also compare the regression parameter for the prevalence GP covariate in the three countries noting that in Indonesia the prevalence GP model performed worse than baseline under random cross-validation and had equal performance to baseline under spatial cross-validation.
 We see that the regression parameter for this covariate was small in Indonesia (mean = 0.06, sd = 0.12) but relatively large and positive in both Senegal (mean = 0.30, sd = 0.17) and Madagascar  (mean = 0.36, sd = 0.07).
 
-In Madagascar the joint model performed the best in the spatial cross-validation scheme and better than the baseline in the random cross-validation scheme. 
+In Madagascar the joint model performed the best in the spatial cross-validation scheme. 
 Comparing the estimated parameters of the joint model between Madagascar and the other two countries therefore is useful.
@@
 The joint model performed best in one case but also performed worse than baseline in two cases.
-Therefore, fitting a spatial Gaussian process to prevalence points and including these predictions seems to be a more reliable way of using spatial information from prevalence points.
-However, given that this comparison was conducted on datasets from only three countries, it is challenging to draw firm conclusions.
+Therefore, fitting a spatial Gaussian process to prevalence points and including these predictions seems to be a more reliable way of using spatial information from prevalence points while the full joint model seems to have potential for being the best performing model in a given situation.
 The significant differences between models all occurred under spatial cross-validation.
@@
 A full joint model using both prevalence surveys and incidence data gains additional statistical power compared to the baseline or prevalence GP models.
-Therefore, it is worth considering why the performance of this model was generally less good than the simpler prevalence GP model that did not benefit from the additional statistical power.
-One potential reason is that the malariometric data are on different scales.
-Here we have used a previously fitted model \citep{cameron2015defining} to inform the joint model.
-However, this model was calibrated using relatively few matched prevalence and incidence surveys as few of these have been conducted and published.
-Although we added the parameter $\alpha$ that scales this relationship, it is a very simple scaling.
-Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality, and population age-structure are not constant \citep{cameron2015defining, battle2015defining, reiner2015seasonality}.
-In using a joint model we are accepting these limitations in the hope that the benefits of including additional data outweigh the costs of using mismatched data.
+When the prevalence survey random effect ($w_P(\sigma_w)$) becomes very flexible (when $\sigma_w$ goes to infinity) this joint model collapses and becomes the baseline model.
+Therefore, it is worth considering why the performance of this model was sometimes less good than the baseline model that did not benefit from the additional statistical power.
+The two comparisons in which the joint model did worse than baseline were the cross-validation scheme for Senegal and Indonesia.
+In Figure S36 we can see that in Indonesia, the joint model overpredicts a number of very low incidence areas and by looking at Figure \ref{predobsmapidn} we can see that the island of Java is overpredicted.
+In Figure S37 we can see that a number of low incidence and medium incidence areas in Senegal are overpredicted and Figure S39 shows maps of the polygon level errors.
+We can see that the baseline model clearly underpredicts many areas while the joint model overpredicts some areas in the centre of the country and in the south east.
+
+In Indonesia it seems that the prevalence-incidence relationship is the main factor driving the poor predictions.
+The relationship increases too quickly at very low incidence values due to the limited flexibility in the model structure and the lack of low incidence points used in model fitting \citep{cameron2015defining}.
+In Figure S38 we show a zoomed in plot of Java with both the incidence data and the prevalence data having been converted to incidence space using the relationship from \citep{cameron2015defining}.
+The prevalence data are sensibly distributed across the island and mostly from a systematic survey.
+However, the prevalence surveys give a considerably higher incidence than the incidence data.
+Fitting joint models to just Java, with a more flexible relationship between prevalence and incidence will be considered for future work but is beyond the scope of this paper.
+
+In contrast, in Senegal there is no clear driver of the poor performance. 
+There is very little incidence data in Senegal and it is probably the least reliable data of the three countries.
+Figure S39 demonstrates the strong bias in the baseline model compared to the less biased, but higher variance predictions of the joint model.
+Furthermore, we can see in Figure \ref{predobsmapsen} that the baseline better captures the expected increase in incidence in the south east of the country driven by the transition from desert to savannah.
+Overall, while the MAE is lower for the baseline model, we think that a subjective argument could be made that the joint model is in fact better as it is less biased and captures expected large scale trends.
+These predictions would possibly be more useful for risk stratification for example.
 
@@
 A number of methods could be used to include non-linear effects of covariates and interactions into the model.
-Firstly, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model \citep{bhatt2017improved}.
+Firstly, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model \citep{bhatt2017improved, lucas2020improving}.
 This approach is feasible but would not allow any information from the polygons to inform non-linear relationships.

### 2021-02-25 si.tex
Final edits.

@@
 % to be removed before submission
-\makebox{\includegraphics[width = 1.05\textwidth]{figures/random_cv_poly_facet.pdf}  }
+\makebox{\includegraphics[width = 1\textwidth]{figures/random_cv_poly_facet.pdf}  }
 \caption{\label{randompredobspolyfacet} 
@@
 
+\clearpage
+\section{Model Errors}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.8\textheight]{figures/random_cv_model_error.pdf}
+
+\caption{
+Density plots of the model errors on random CV hold out data.
+The x-axis on the Indonesia plot is artifically cut at -1 and 1.
+}
+\label{rnd_cv_error}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.8\textheight]{figures/spatial_cv_model_error.pdf}
+
+\caption{
+Density plots of the model errors on random CV hold out data.
+The x-axis on the Indonesia plot is artifically cut at -40.
+It can be seen that there is a bias towards overpredicting the small API values in Indonesia in the joint model. 
+Overall however this was the least biased model.
+The joint model in Senegal is not clearly biased but just has larger errors in general.
+}
+}
+\label{spat_cv_errors}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.8\textheight]{figures/mdg_model_error_vs_observed.pdf}
+
+\caption{
+Plot of prediction error against observed API for Madagascar.
+In this case the joint model was significantly better than the baseline.
+We can see that the baseline model underpredicts high incidence areas and overpredicts low incidence areas.
+The underprediction of low incidence areas is reduced in the other two models.
+}
+
+\label{mdg_error_obs}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.8\textheight]{figures/idn_model_error_vs_observed.pdf}
+
+\caption{
+Plot of prediction error against observed API for Indonesia.
+In this case the joint model was significantly worse than the baseline.
+We can see that all models underpredict high incidence areas.
+While all models overpredict the low incidence areas this is particularly pronounced in the joint model.
+}
+
+\label{idn_error_obs}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.8\textheight]{figures/sen_model_error_vs_observed.pdf}
+
+\caption{
+Plot of prediction error against observed API for Senegal.
+In this case the joint model was significantly worse than the baseline.
+Compared to the baseline and prevalence GP models, the joint model makes better predictions for high incidence areas (API over 50).
+Some of the medium incidence areas (API of 12-50) are quite strongly overpredicted while the other two models show stronger bias in the region with all medium incidence areas being underpredicted. 
+Finally, the joint model has a stronger overprediction bias in low incidence areas.
+}
+
+\label{idn_error_obs}
+\end{figure}
+
+\clearpage
+\section{Additional performance metrics}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rllrrr}
+  \hline
+ Country & Model & RMSE & MAE & Mean Error \\ 
+  \hline
+SEN & Joint & 20.53 & 13.07 & -5.84 \\ 
+  SEN & Base & 22.10 & 12.41 & -6.77 \\ 
+  SEN & PrevGP & 21.41 & 12.37 & -6.31 \\ 
+  IDN & Joint & 52.08 & 13.79 & -10.73 \\ 
+  IDN & Base & 51.73 & 13.95 & -10.65 \\ 
+  IDN & PrevGP & 51.59 & 14.09 & -9.74 \\ 
+  MDG & Joint & 60.44 & 36.36 & -10.55 \\ 
+  MDG & Base & 62.92 & 39.06 & -14.18 \\ 
+  MDG & PrevGP & 61.15 & 35.82 & -13.53 \\ 
+   \hline
+\end{tabular}
+\caption{The root mean square error, mean absolute error and mean error (i.e. bias) for the models under random crossvalidation.}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rllrrr}
+  \hline
+  Country & Model & RMSE & MAE & Mean Error \\ 
+  \hline
+SEN & Joint & 22.24 & 15.15 & -2.15 \\ 
+  SEN & Base & 22.77 & 13.09 & -10.35 \\ 
+  SEN & PrevGP & 21.68 & 12.21 & -9.32 \\ 
+  IDN & Joint & 55.39 & 16.46 & -10.92 \\ 
+  IDN & Base & 55.07 & 14.77 & -12.78 \\ 
+  IDN & PrevGP & 54.99 & 14.77 & -12.78 \\ 
+  MDG & Joint & 70.49 & 44.05 & 12.52 \\ 
+  MDG & Base & 102.80 & 67.73 & 7.73 \\ 
+  MDG & PrevGP & 76.89 & 50.38 & -14.31 \\
+
+   \hline
+\end{tabular}
+\caption{The root mean square error, mean absolute error and mean error (i.e. bias) for the models under spatial crossvalidation.}
+\end{table}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  0.8\textwidth]{figures/java_only.pdf}
+
+\caption{
+Focused map of data on the island of Java, Indonesia.
+Colour gives API (notice the log scale) for polygon incidence data and prevalence converted to estimated incidence for the point prevalence surveys.
+Areas with incidence of zero are grey.
+The area with many surveys and lots of areas with zero API, around (107, -6), is Jakarta, the current capital (as of 2021).
+The prevalence surveys mostly have sample sizes of about 100. 
+The surveys with API of close to 100 typically have prevalence of around 3\%.
+}
+\label{rnd_cv_error}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+
+\includegraphics[width =  1\textwidth, trim = ]{figures/sen_error_plot.pdf}
+
+\caption{
+Left) The observed API data.
+Middle) The error (predicted minus observed) for the spatial cross-validation scheme with the baseline model.
+Right) The error for the spatial cross-validation scheme with the joint model.
+Red is over prediction, blue is underprediction.
+}
+\label{rnd_cv_error}
+\end{figure}
+
 \end{document}
